### 2022-04-16 exploratory/20220416_descriptives.Rmd
conducted exploratory analyses on experiment 1

---
title: "20220416_descriptives"
author: "Yurun (Ellen) Ying"
date: "4/16/2022"
output: github_document

---

```{r setup, message=FALSE, include=FALSE}
# load libraries
library(tidyverse); library(ggplot2); library(magrittr); library(here); library(knitr)

# read file
casual_tib <- here("data/processed/casual_sex_sim.csv") %>% 
  read_csv()
```

## Overview

### Experiments

- Experiment 1: Experiment of heterosexual individuals `homosexual = 0`
- Experiment 2: Experiment of gay men and lesbian women `homosexual = 1`

### Conditions

|  | Likelihood - Difference<br>`diff_likelihood = 1`| No difference<br>`diff_likelihood = 0` |
| -------------------- | -------------------------------- | ------------- |
| Standard - Difference<br>`diff_standard = 1`| male-likelihood = 40%<br>female-likelihood = 25%<br>male-standard = 3<br>female-standard = 5 | male-likelihood = 25%<br>female-likelihood = 25%<br>male-standard = 3<br>female-standard = 5             |
| No difference<br>`diff_standard = 0` | male-likelihood = 40%<br>female-likelihood = 25%<br>male-standard = 5<br>female-standard = 5                                | male-likelihood = 25%<br>female-likelihood = 25%<br>male-standard = 5<br>female-standard = 5             |

### Outcome variables

- number of men and women who were in the mating pool `m_inpool` `f_inpool`
- number of men and women who were out of the mating pool `m_outpool` ` f_outpool`
- average number of short-term mating experiences of total populations of men and women `m_exp_all` `f_exp_all`
- average number of short-term mating experiences of men and women in the pool `m_exp_ip` `f_exp_ip`
- average number of short-term partners of total populations of men and women `m_partner_all` `f_partner_all`
- average number of short-term partners of men and women in the pool `m_partner_ip` `f_partner_ip`

## Experiment 1: Experiment of heterosexual individuals

### Means of the outcome variables

```{r e1_mean, echo=FALSE}
e1_mean_tib <- 
  casual_tib %>%
    filter(homosexual == 0) %>% 
    group_by(diff_likelihood, diff_standard) %>% 
    summarize(
      m_inpool = mean(m_inpool),
      f_inpool = mean(f_inpool),
      m_outpool = mean(m_outpool),
      f_outpool = mean(f_outpool),
      m_exp_all = mean(m_exp_all),
      f_exp_all = mean(f_exp_all),
      m_exp_ip = mean(m_exp_ip),
      f_exp_ip = mean(f_exp_ip),
      m_partner_all = mean(m_partner_all),
      f_partner_all = mean(f_partner_all),
      m_partner_ip = mean(m_partner_ip),
      f_partner_ip = mean(f_partner_ip),
      .groups = "keep"
    )

kable(e1_mean_tib)
```

- **Number of men and women in/out of the mating pool**
  - When there was a gender difference in short-term mating standards, there were more women than men in the mating pool, and more men than women out of the mating pool. 
  - This gender difference existed no matter whether there was a gender difference in the likelihood of short-term mating.
  - This gender difference disappeared when there was no gender difference in short-term mating standards.
- **Average number of short-term mating experiences of all/in-pool men and women**
  - No gender differences in the average number for all men and women
  - When there was a gender difference in short-term mating standards, in-pool men had a higher average number of short-term mating experiences than in-pool women. This was true no matter whether there was a gender difference in the likelihood of short-term mating.
  - This gender difference disappeared when there was no gender difference in short-term mating standards.
- **Average number of short-term partners of all/in-pool men and women**
  - No gender differences in the average number for all men and women
  - When there was a gender difference in short-term mating standards, in-pool men had a higher average number of short-term mates than in-pool women. This was true no matter whether there was a gender difference in the likelihood of short-term mating.
  - This gender difference disappeared when there was no gender difference in short-term mating standards.

### Distributions of the outcome variables
- Number of men and women in the mating pool
```{r e1_inpool_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, m_inpool, f_inpool) %>% 
  pivot_longer(m_inpool:f_inpool,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Number of Heterosexual Men and\nWomen in the Mating Pool"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term mating experiences of men and women in the mating pool
```{r e1_exp_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, m_exp_ip, f_exp_ip) %>% 
  pivot_longer(m_exp_ip:f_exp_ip,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Mating\nExperiences of In-pool Heterosexual Men and Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
    strip.background = element_rect(fill = "#FFFFFF"))
```

- Average number of short-term partners of men and women in the mating pool
```{r e1_partner_hist, fig.align='center', echo=FALSE}
casual_tib %>% 
  filter(homosexual == 0) %>% 
  select(diff_likelihood, diff_standard, 
         m_partner_ip, f_partner_ip) %>% 
  pivot_longer(m_partner_ip:f_partner_ip,
               names_to = "variable", values_to = "value") %>% 
  ggplot(aes(x = value, fill = variable)) +
  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
                 color = "#e9ecef", position = 'identity') +
  scale_fill_discrete(
    name = "Gender",
    labels = c("Women", "Men")) +
  labs(
    x = "Number of individuals", 
    y = "Frequency",
    title = "Average Number of Short-term Partners of\nIn-pool Heterosexual Men and Women"
       ) +
  facet_grid(
    diff_standard ~ diff_likelihood,
    labeller = labeller(
        diff_likelihood = c(
          `0` = "No gender difference\nin mating likelihood", 
          `1` = "Gender difference\nin mating likelihood"),
        diff_standard = c(
          `0` = "No gender difference\nin mating standards", 
          `1` = "Gender difference\nin mating standards")
    )
  ) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 12, face = "bold", hjust = 0.7),
    strip.background = element_rect(fill = "#FFFFFF"))
```

## Experiment 2: Experiment of gay men and lesbian women

### Means of the outcome variables

```{r e2_mean, echo=FALSE}
e2_mean_tib <- 
  casual_tib %>%
    filter(homosexual == 1) %>% 
    group_by(diff_likelihood, diff_standard) %>% 
    summarize(
      m_inpool = mean(m_inpool),
      f_inpool = mean(f_inpool),
      m_outpool = mean(m_outpool),
      f_outpool = mean(f_outpool),
      m_exp_all = mean(m_exp_all),
      f_exp_all = mean(f_exp_all),
      m_exp_ip = mean(m_exp_ip),
      f_exp_ip = mean(f_exp_ip),
      m_partner_all = mean(m_partner_all),
      f_partner_all = mean(f_partner_all),
      m_partner_ip = mean(m_partner_ip),
      f_partner_ip = mean(f_partner_ip),
      .groups = "keep"
    )

kable(e2_mean_tib)
```

### 2022-04-17 exploratory/20220416_descriptives.Rmd
finished the exploratory analyses, close #4

@@
 date: "4/16/2022"
-output: github_document
+output: 
+  github_document:
+    html_preview: false
 
@@
 casual_tib <- here("data/processed/casual_sex_sim.csv") %>% 
-  read_csv()
+  read_csv() %>% 
+  mutate(
+    diff_likelihood = as_factor(diff_likelihood),
+    diff_standard = as_factor(diff_standard),
+    homosexual = as_factor(homosexual)
+  )
+
+# add variables for gender differences
+casual_tib <- casual_tib %>% 
+  mutate(
+    diff_inpool = m_inpool - f_inpool,
+    diff_outpool = m_outpool - f_outpool,
+    diff_exp_all = m_exp_all - f_exp_all,
+    diff_exp_ip = m_exp_ip - f_exp_ip,
+    diff_partner_all = m_partner_all - f_partner_all,
+    diff_partner_ip = m_partner_ip - f_partner_ip
+  )
 ```
@@
 
-- number of men and women who were in the mating pool `m_inpool` `f_inpool`
-- number of men and women who were out of the mating pool `m_outpool` ` f_outpool`
-- average number of short-term mating experiences of total populations of men and women `m_exp_all` `f_exp_all`
-- average number of short-term mating experiences of men and women in the pool `m_exp_ip` `f_exp_ip`
-- average number of short-term partners of total populations of men and women `m_partner_all` `f_partner_all`
-- average number of short-term partners of men and women in the pool `m_partner_ip` `f_partner_ip`
+- number of men and women who were in the mating pool `m_inpool` `f_inpool`; gender difference `diff_inpool`
+- number of men and women who were out of the mating pool `m_outpool` ` f_outpool`; gender difference `diff_outpool`
+- average number of short-term mating experiences of total populations of men and women `m_exp_all` `f_exp_all`; gender difference `diff_exp_all`
+- average number of short-term mating experiences of men and women in the pool `m_exp_ip` `f_exp_ip`; gender difference `diff_exp_ip`
+- average number of short-term partners of total populations of men and women `m_partner_all` `f_partner_all`; gender difference `diff_partner_all`
+- average number of short-term partners of men and women in the pool `m_partner_ip` `f_partner_ip`; gender difference `diff_partner_ip`
 
@@
 
-### Distributions of the outcome variables
-- Number of men and women in the mating pool
+### Distributions
+- Number of heterosexual men and women in the mating pool
 ```{r e1_inpool_hist, fig.align='center', echo=FALSE}
@@
 
-- Average number of short-term mating experiences of men and women in the mating pool
-```{r e1_exp_hist, fig.align='center', echo=FALSE}
+- Number of heterosexual men and women out of the mating pool
+```{r e1_outpool_hist, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 0) %>% 
+  select(diff_likelihood, diff_standard, m_outpool, f_outpool) %>% 
+  pivot_longer(m_outpool:f_outpool,
+               names_to = "variable", values_to = "value") %>% 
+  ggplot(aes(x = value, fill = variable)) +
+  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
+                 color = "#e9ecef", position = 'identity') +
+  scale_fill_discrete(
+    name = "Gender",
+    labels = c("Women", "Men")) +
+  labs(
+    x = "Number of individuals", 
+    y = "Frequency",
+    title = "Number of Heterosexual Men and\nWomen out of the Mating Pool"
+       ) +
+  facet_grid(
+    diff_standard ~ diff_likelihood,
+    labeller = labeller(
+        diff_likelihood = c(
+          `0` = "No gender difference\nin mating likelihood", 
+          `1` = "Gender difference\nin mating likelihood"),
+        diff_standard = c(
+          `0` = "No gender difference\nin mating standards", 
+          `1` = "Gender difference\nin mating standards")
+    )
+  ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    strip.background = element_rect(fill = "#FFFFFF"))
+```
+
+- Average number of short-term mating experiences of heterosexual men and women from the whole population
+```{r e1_expall_hist, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 0) %>% 
+  select(diff_likelihood, diff_standard, m_exp_all, f_exp_all) %>% 
+  pivot_longer(m_exp_all:f_exp_all,
+               names_to = "variable", values_to = "value") %>% 
+  ggplot(aes(x = value, fill = variable)) +
+  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
+                 color = "#e9ecef", position = 'identity') +
+  scale_fill_discrete(
+    name = "Gender",
+    labels = c("Women", "Men")) +
+  labs(
+    x = "Number of individuals", 
+    y = "Frequency",
+    title = "Average Number of Short-term Mating\nExperiences of All Heterosexual Men and Women"
+       ) +
+  facet_grid(
+    diff_standard ~ diff_likelihood,
+    labeller = labeller(
+        diff_likelihood = c(
+          `0` = "No gender difference\nin mating likelihood", 
+          `1` = "Gender difference\nin mating likelihood"),
+        diff_standard = c(
+          `0` = "No gender difference\nin mating standards", 
+          `1` = "Gender difference\nin mating standards")
+    )
+  ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    strip.background = element_rect(fill = "#FFFFFF"))
+```
+
+- Average number of short-term mating experiences of heterosexual men and women in the mating pool
+```{r e1_expip_hist, fig.align='center', echo=FALSE}
 casual_tib %>% 
@@
 
-- Average number of short-term partners of men and women in the mating pool
-```{r e1_partner_hist, fig.align='center', echo=FALSE}
+- Average number of short-term partners of heterosexual men and women from the whole population
+```{r e1_partnerall_hist, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 0) %>% 
+  select(diff_likelihood, diff_standard, 
+         m_partner_all, f_partner_all) %>% 
+  pivot_longer(m_partner_all:f_partner_all,
+               names_to = "variable", values_to = "value") %>% 
+  ggplot(aes(x = value, fill = variable)) +
+  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
+                 color = "#e9ecef", position = 'identity') +
+  scale_fill_discrete(
+    name = "Gender",
+    labels = c("Women", "Men")) +
+  labs(
+    x = "Number of individuals", 
+    y = "Frequency",
+    title = "Average Number of Short-term Partners of\nAll Heterosexual Men and Women"
+       ) +
+  facet_grid(
+    diff_standard ~ diff_likelihood,
+    labeller = labeller(
+        diff_likelihood = c(
+          `0` = "No gender difference\nin mating likelihood", 
+          `1` = "Gender difference\nin mating likelihood"),
+        diff_standard = c(
+          `0` = "No gender difference\nin mating standards", 
+          `1` = "Gender difference\nin mating standards")
+    )
+  ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.7),
+    strip.background = element_rect(fill = "#FFFFFF"))
+```
+
+- Average number of short-term partners of heterosexual men and women in the mating pool
+```{r e1_partnerip_hist, fig.align='center', echo=FALSE}
 casual_tib %>% 
@@
 
+### Gender differences
+
+- Number of heterosexual men and women in the mating pool
+```{r e1_inpool_line, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 0) %>% 
+  select(diff_likelihood, diff_standard, diff_inpool) %>% 
+  ggplot(aes(
+    x = diff_likelihood, y = diff_inpool, group = diff_standard,
+    color = diff_standard, fill = diff_standard)) +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               width = 0.2, size = 0.5) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
+  stat_summary(fun = mean, geom = "line",
+               size = 0.4, linetype = "dashed") +
+  scale_x_discrete(
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_fill_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_color_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  labs(
+    x = "Short-term mating likelihood", 
+    y = "Gender difference\n(men - women)",
+    title = "Gender Difference in the Number of\nHeterosexual Men and Women in the Mating Pool"
+       ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    legend.key.height = unit(1.5, units = "lines"))
+```
+
+- Average number of short-term mating experiences of heterosexual men and women in the mating pool
+```{r e1_expip_line, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 0) %>% 
+  select(diff_likelihood, diff_standard, diff_exp_ip) %>% 
+  ggplot(aes(
+    x = diff_likelihood, y = diff_exp_ip, group = diff_standard,
+    color = diff_standard, fill = diff_standard)) +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               width = 0.2, size = 0.5) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
+  stat_summary(fun = mean, geom = "line",
+               size = 0.4, linetype = "dashed") +
+  scale_x_discrete(
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_fill_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_color_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  labs(
+    x = "Short-term mating likelihood", 
+    y = "Gender difference\n(men - women)",
+    title = "Gender Difference in the Average Number of\nShort-term Experiences Among\nIn-pool Heterosexual Men and Women"
+       ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    legend.key.height = unit(1.5, units = "lines"))
+```
+
+- Average number of short-term partners of heterosexual men and women in the mating pool
+```{r e1_partnerip_line, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 0) %>% 
+  select(diff_likelihood, diff_standard, diff_partner_ip) %>% 
+  ggplot(aes(
+    x = diff_likelihood, y = diff_partner_ip, group = diff_standard,
+    color = diff_standard, fill = diff_standard)) +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               width = 0.2, size = 0.5) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
+  stat_summary(fun = mean, geom = "line",
+               size = 0.4, linetype = "dashed") +
+  scale_x_discrete(
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_fill_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_color_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  labs(
+    x = "Short-term mating likelihood", 
+    y = "Gender difference\n(men - women)",
+    title = "Gender Difference in the Average Number of\nShort-term Partners Among\nIn-pool Heterosexual Men and Women"
+       ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    legend.key.height = unit(1.5, units = "lines"))
+```
+
 ## Experiment 2: Experiment of gay men and lesbian women
@@
 ```
+
+- **Number of men and women in/out of the mating pool**
+  - When there were no gender differences in short-term mating likelihood or standards, there was no gender difference in the number of men and women in/out of the mating pool. 
+  - There were more gay men than lesbian women in the mating pool, and less men than women out of the mating pool when there was a gender difference in at least one of the two parameters.
+- **Average number of short-term mating experiences of all/in-pool men and women**
+  - When there were no gender differences in short-term mating likelihood or standards, there was no gender difference in the average number of short-term mating experiences, regardless of whether the average was taken from the whole population or the in-pool men and women only.
+  - Gay men had a higher number of short-term mating experiences than lesbian women on average when there was a gender difference in at least one of the two parameters.
+This was true regardless of whether the average was taken from the whole population or the in-pool men and women only.
+- **Average number of short-term partners of all/in-pool men and women**
+  - When there were no gender differences in short-term mating likelihood or standards, there was no gender difference in the average number of short-term partners, regardless of whether the average was taken from the whole population or the in-pool men and women only.
+  - Gay men had a higher number of short-term partners than lesbian women on average when there was a gender difference in at least one of the two parameters.
+This was true regardless of whether the average was taken from the whole population or the in-pool men and women only.
+
+### Distributions 
+- Number of gay men and lesbian women in the mating pool
+```{r e2_inpool_hist, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, m_inpool, f_inpool) %>% 
+  pivot_longer(m_inpool:f_inpool,
+               names_to = "variable", values_to = "value") %>% 
+  ggplot(aes(x = value, fill = variable)) +
+  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
+                 color = "#e9ecef", position = 'identity') +
+  scale_fill_discrete(
+    name = "Gender",
+    labels = c("Women", "Men")) +
+  labs(
+    x = "Number of individuals", 
+    y = "Frequency",
+    title = "Number of Gay Men and\nLesbian Women in the Mating Pool"
+       ) +
+  facet_grid(
+    diff_standard ~ diff_likelihood,
+    labeller = labeller(
+        diff_likelihood = c(
+          `0` = "No gender difference\nin mating likelihood", 
+          `1` = "Gender difference\nin mating likelihood"),
+        diff_standard = c(
+          `0` = "No gender difference\nin mating standards", 
+          `1` = "Gender difference\nin mating standards")
+    )
+  ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    strip.background = element_rect(fill = "#FFFFFF"))
+```
+
+- Number of gay men and lesbian women out of the mating pool
+```{r e2_outpool_hist, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, m_outpool, f_outpool) %>% 
+  pivot_longer(m_outpool:f_outpool,
+               names_to = "variable", values_to = "value") %>% 
+  ggplot(aes(x = value, fill = variable)) +
+  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
+                 color = "#e9ecef", position = 'identity') +
+  scale_fill_discrete(
+    name = "Gender",
+    labels = c("Women", "Men")) +
+  labs(
+    x = "Number of individuals", 
+    y = "Frequency",
+    title = "Number of Gay Men and\nLesbian Women out of the Mating Pool"
+       ) +
+  facet_grid(
+    diff_standard ~ diff_likelihood,
+    labeller = labeller(
+        diff_likelihood = c(
+          `0` = "No gender difference\nin mating likelihood", 
+          `1` = "Gender difference\nin mating likelihood"),
+        diff_standard = c(
+          `0` = "No gender difference\nin mating standards", 
+          `1` = "Gender difference\nin mating standards")
+    )
+  ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    strip.background = element_rect(fill = "#FFFFFF"))
+```
+
+- Average number of short-term mating experiences of gay men and lesbian women from the whole population
+```{r e2_expall_hist, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, m_exp_all, f_exp_all) %>% 
+  pivot_longer(m_exp_all:f_exp_all,
+               names_to = "variable", values_to = "value") %>% 
+  ggplot(aes(x = value, fill = variable)) +
+  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
+                 color = "#e9ecef", position = 'identity') +
+  scale_fill_discrete(
+    name = "Gender",
+    labels = c("Women", "Men")) +
+  labs(
+    x = "Number of individuals", 
+    y = "Frequency",
+    title = "Average Number of Short-term Mating\nExperiences of All Gay Men and Lesbian Women"
+       ) +
+  facet_grid(
+    diff_standard ~ diff_likelihood,
+    labeller = labeller(
+        diff_likelihood = c(
+          `0` = "No gender difference\nin mating likelihood", 
+          `1` = "Gender difference\nin mating likelihood"),
+        diff_standard = c(
+          `0` = "No gender difference\nin mating standards", 
+          `1` = "Gender difference\nin mating standards")
+    )
+  ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    strip.background = element_rect(fill = "#FFFFFF"))
+```
+
+- Average number of short-term mating experiences of gay men and lesbian women in the mating pool
+```{r e2_expip_hist, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, m_exp_ip, f_exp_ip) %>% 
+  pivot_longer(m_exp_ip:f_exp_ip,
+               names_to = "variable", values_to = "value") %>% 
+  ggplot(aes(x = value, fill = variable)) +
+  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
+                 color = "#e9ecef", position = 'identity') +
+  scale_fill_discrete(
+    name = "Gender",
+    labels = c("Women", "Men")) +
+  labs(
+    x = "Number of individuals", 
+    y = "Frequency",
+    title = "Average Number of Short-term Mating\nExperiences of In-pool Gay Men and Lesbian Women"
+       ) +
+  facet_grid(
+    diff_standard ~ diff_likelihood,
+    labeller = labeller(
+        diff_likelihood = c(
+          `0` = "No gender difference\nin mating likelihood", 
+          `1` = "Gender difference\nin mating likelihood"),
+        diff_standard = c(
+          `0` = "No gender difference\nin mating standards", 
+          `1` = "Gender difference\nin mating standards")
+    )
+  ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    strip.background = element_rect(fill = "#FFFFFF"))
+```
+
+- Average number of short-term partners of gay men and lesbian women from the whole population
+```{r e2_partnerall_hist, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, 
+         m_partner_all, f_partner_all) %>% 
+  pivot_longer(m_partner_all:f_partner_all,
+               names_to = "variable", values_to = "value") %>% 
+  ggplot(aes(x = value, fill = variable)) +
+  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
+                 color = "#e9ecef", position = 'identity') +
+  scale_fill_discrete(
+    name = "Gender",
+    labels = c("Women", "Men")) +
+  labs(
+    x = "Number of individuals", 
+    y = "Frequency",
+    title = "Average Number of Short-term Partners of\nAll Gay Men and Lesbian Women"
+       ) +
+  facet_grid(
+    diff_standard ~ diff_likelihood,
+    labeller = labeller(
+        diff_likelihood = c(
+          `0` = "No gender difference\nin mating likelihood", 
+          `1` = "Gender difference\nin mating likelihood"),
+        diff_standard = c(
+          `0` = "No gender difference\nin mating standards", 
+          `1` = "Gender difference\nin mating standards")
+    )
+  ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.7),
+    strip.background = element_rect(fill = "#FFFFFF"))
+```
+
+- Average number of short-term partners of gay men and lesbian women in the mating pool
+```{r e2_partnerip_hist, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, 
+         m_partner_ip, f_partner_ip) %>% 
+  pivot_longer(m_partner_ip:f_partner_ip,
+               names_to = "variable", values_to = "value") %>% 
+  ggplot(aes(x = value, fill = variable)) +
+  geom_histogram(bins = 30, alpha = 0.3, size = 0.2,
+                 color = "#e9ecef", position = 'identity') +
+  scale_fill_discrete(
+    name = "Gender",
+    labels = c("Women", "Men")) +
+  labs(
+    x = "Number of individuals", 
+    y = "Frequency",
+    title = "Average Number of Short-term Partners of\nIn-pool Gay Men and Lesbian Women"
+       ) +
+  facet_grid(
+    diff_standard ~ diff_likelihood,
+    labeller = labeller(
+        diff_likelihood = c(
+          `0` = "No gender difference\nin mating likelihood", 
+          `1` = "Gender difference\nin mating likelihood"),
+        diff_standard = c(
+          `0` = "No gender difference\nin mating standards", 
+          `1` = "Gender difference\nin mating standards")
+    )
+  ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.7),
+    strip.background = element_rect(fill = "#FFFFFF"))
+```
+
+### Gender differences
+
+- Number of gay men and lesbian women in the mating pool
+```{r e2_inpool_line, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, diff_inpool) %>% 
+  ggplot(aes(
+    x = diff_likelihood, y = diff_inpool, group = diff_standard,
+    color = diff_standard, fill = diff_standard)) +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               width = 0.2, size = 0.5) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
+  stat_summary(fun = mean, geom = "line",
+               size = 0.4, linetype = "dashed") +
+  scale_x_discrete(
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_fill_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_color_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  labs(
+    x = "Short-term mating likelihood", 
+    y = "Gender difference\n(men - women)",
+    title = "Gender Difference in the Number of\nGay Men and Lesbian Women in the Mating Pool"
+       ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    legend.key.height = unit(1.5, units = "lines"))
+```
+
+- Average number of short-term mating experiences of gay men and lesbian women from the whole population
+```{r e2_expall_line, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, diff_exp_all) %>% 
+  ggplot(aes(
+    x = diff_likelihood, y = diff_exp_all, group = diff_standard,
+    color = diff_standard, fill = diff_standard)) +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               width = 0.2, size = 0.5) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
+  stat_summary(fun = mean, geom = "line",
+               size = 0.4, linetype = "dashed") +
+  scale_x_discrete(
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_fill_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_color_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  labs(
+    x = "Short-term mating likelihood", 
+    y = "Gender difference\n(men - women)",
+    title = "Gender Difference in the Average Number of\nShort-term Experiences Among\nAll Gay Men and Lesbian Women"
+       ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    legend.key.height = unit(1.5, units = "lines"))
+```
+
+- Average number of short-term mating experiences of gay men and lesbian women in the mating pool
+```{r e2_expip_line, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, diff_exp_ip) %>% 
+  ggplot(aes(
+    x = diff_likelihood, y = diff_exp_ip, group = diff_standard,
+    color = diff_standard, fill = diff_standard)) +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               width = 0.2, size = 0.5) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
+  stat_summary(fun = mean, geom = "line",
+               size = 0.4, linetype = "dashed") +
+  scale_x_discrete(
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_fill_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_color_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  labs(
+    x = "Short-term mating likelihood", 
+    y = "Gender difference\n(men - women)",
+    title = "Gender Difference in the Average Number of\nShort-term Experiences Among\nIn-pool Gay Men and Lesbian Women"
+       ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    legend.key.height = unit(1.5, units = "lines"))
+```
+
+- Average number of short-term partners of gay men and lesbian women from the whole population
+```{r e2_partnerall_line, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, diff_partner_all) %>% 
+  ggplot(aes(
+    x = diff_likelihood, y = diff_partner_all, group = diff_standard,
+    color = diff_standard, fill = diff_standard)) +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               width = 0.2, size = 0.5) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
+  stat_summary(fun = mean, geom = "line",
+               size = 0.4, linetype = "dashed") +
+  scale_x_discrete(
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_fill_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_color_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  labs(
+    x = "Short-term mating likelihood", 
+    y = "Gender difference\n(men - women)",
+    title = "Gender Difference in the Average Number of\nShort-term Parters Among\nAll Gay Men and Lesbian Women"
+       ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    legend.key.height = unit(1.5, units = "lines"))
+```
+
+- Average number of short-term partners of gay men and lesbian women in the mating pool
+```{r e2_partnerip_line, fig.align='center', echo=FALSE}
+casual_tib %>% 
+  filter(homosexual == 1) %>% 
+  select(diff_likelihood, diff_standard, diff_partner_ip) %>% 
+  ggplot(aes(
+    x = diff_likelihood, y = diff_partner_ip, group = diff_standard,
+    color = diff_standard, fill = diff_standard)) +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
+               width = 0.2, size = 0.5) +
+  stat_summary(fun = mean, geom = "point", size = 2) +
+  stat_summary(fun = mean, geom = "line",
+               size = 0.4, linetype = "dashed") +
+  scale_x_discrete(
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_fill_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  scale_color_discrete(
+    name = "Short-term mating\nstandards",
+    labels = c("No gender\ndifference", "Gender\ndifference")) +
+  labs(
+    x = "Short-term mating likelihood", 
+    y = "Gender difference\n(men - women)",
+    title = "Gender Difference in the Average Number of\nShort-term Partners Among\nIn-pool Gay Men and Lesbian Women"
+       ) +
+  theme_bw() +
+  theme(
+    plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
+    legend.key.height = unit(1.5, units = "lines"))
+```

### 2022-04-26 exploratory/20220426_main_plot_t_test.Rmd
generated the violin plots, conducted t-test for one var

---
title: "20220426_main_plot_t_test"
author: "Yurun (Ellen) Ying"
date: "4/26/2022"
output: 
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
# load libraries
library(tidyverse); library(ggplot2); library(wesanderson); library(magrittr); library(here); library(knitr); library(broom)

# read file
casual_tib <- here("data/processed/casual_sex_sim.csv") %>% 
  read_csv() %>% 
  mutate(
    diff_likelihood = as_factor(diff_likelihood),
    diff_standard = as_factor(diff_standard),
    homosexual = as_factor(homosexual)
  )
```

## Main plots
- Violin plots of the diff x diff condition
	- grouped by gender
	- paneled by experiments
	- separate for two dependent variables: avg num of experiences (all), avg num of partners (all)

```{r violin_exp}
casual_tib %>% 
  filter(diff_likelihood == 1, diff_standard == 1) %>% 
  select(homosexual, m_exp_all, f_exp_all) %>% 
  pivot_longer(c(m_exp_all, f_exp_all), values_to = "exp_all",
               names_to = "gender", names_pattern = "(.)_exp_all") %>% 
  ggplot(aes(x = gender, y = exp_all)) +
  geom_violin(aes(fill = gender)) +
  stat_summary(fun = "mean", geom = "point") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
  scale_fill_discrete(
    type = wes_palette("Darjeeling2", 2, type = "discrete"),
    name = "", labels = c("Women", "Men")
  ) +
  labs(x = "", y = "Average number of\nshort-term mating experiences",
       title = " Main plot 1: violin plot of average number of\nshort-term mating experiences") +
  facet_wrap(
    ~ homosexual,
    labeller = labeller(
      homosexual = c(
        `0` = "Experiment 1\nHeterosexual individuals",
        `1` = "Experiment 2\nGay men and lesbian women")
      )) +
  theme_minimal() +
  theme(
    axis.line = element_line(size = 0.3),
    axis.ticks.y = element_line(size = 0.3),
    axis.text.x = element_blank(),
    panel.grid = element_blank(),
    panel.spacing = unit(0, "npc"),
    strip.text = element_text(size = 10)
    )

```

```{r violin_partner}
casual_tib %>% 
  filter(diff_likelihood == 1, diff_standard == 1) %>% 
  select(homosexual, m_partner_all, f_partner_all) %>% 
  pivot_longer(c(m_partner_all, f_partner_all), values_to = "partner_all",
               names_to = "gender", names_pattern = "(.)_partner_all") %>% 
  ggplot(aes(x = gender, y = partner_all)) +
  geom_violin(aes(fill = gender)) +
  stat_summary(fun = "mean", geom = "point") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
  coord_cartesian(ylim = c(0, 3)) +
  scale_fill_discrete(
    type = wes_palette("Darjeeling2", 2, type = "discrete"),
    name = "", labels = c("Women", "Men")
  ) +
  labs(x = "", y = "Average number of\nshort-term patners",
       title = " Main plot 2: violin plot of average\nnumber of short-term partners") +
  facet_wrap(
    ~ homosexual,
    labeller = labeller(
      homosexual = c(
        `0` = "Experiment 1\nHeterosexual individuals",
        `1` = "Experiment 2\nGay men and lesbian women")
      )) +
  theme_minimal() +
  theme(
    axis.line = element_line(size = 0.3),
    axis.ticks.y = element_line(size = 0.3),
    axis.text.x = element_blank(),
    panel.grid = element_blank(),
    panel.spacing = unit(0, "npc"),
    strip.text = element_text(size = 10)
    )
```

## T-tests
- Independent samples *t*-test between men and women, separate for conditions and experiments
- Output into a large table

```{r t_exp_all}
# t test by groups for exp_all variable
casual_tib %>% 
  unite(homosexual, diff_likelihood, diff_standard,
              col = "condition_hs_lh_sd", sep = "_") %>% 
  pivot_longer(c(m_exp_all, f_exp_all), values_to = "exp_all",
               names_to = "gender", names_pattern = "(.)_exp_all") %>% 
  select(condition_hs_lh_sd, gender, exp_all) %>% 
  nest_by(condition_hs_lh_sd) %>% 
  mutate(t.test(exp_all ~ gender, data = data) %>% tidy()) %>% 
  select(condition_hs_lh_sd, statistic, p.value, parameter) %>% 
  kable()
```

### 2022-04-27 exploratory/20220426_main_plot_t_test.Rmd
made a table for t-tests

@@
 # load libraries
-library(tidyverse); library(ggplot2); library(wesanderson); library(magrittr); library(here); library(knitr); library(broom)
+library(tidyverse); library(ggplot2); library(wesanderson); library(magrittr); library(here); library(knitr); library(broom); library(effectsize)
 
@@
 - Independent samples *t*-test between men and women, separate for conditions and experiments
-- Output into a large table
+- Output into tables with descriptives and test results, separate by variables
 
-```{r t_exp_all}
-# t test by groups for exp_all variable
+```{r t_all_var}
+# create a long tibble
+casual_long <- 
   casual_tib %>%
   unite(homosexual, diff_likelihood, diff_standard,
-              col = "condition_hs_lh_sd", sep = "_") %>% 
-  pivot_longer(c(m_exp_all, f_exp_all), values_to = "exp_all",
-               names_to = "gender", names_pattern = "(.)_exp_all") %>% 
-  select(condition_hs_lh_sd, gender, exp_all) %>% 
-  nest_by(condition_hs_lh_sd) %>% 
-  mutate(t.test(exp_all ~ gender, data = data) %>% tidy()) %>% 
-  select(condition_hs_lh_sd, statistic, p.value, parameter) %>% 
+        col = "homosexual_dlikelihood_dstandard", sep = "_") %>% 
+  pivot_longer(-c(seed, homosexual_dlikelihood_dstandard), 
+               names_to = c("gender", ".value"), 
+               names_pattern = "(.)_(.*)"
+  )
+
+# descriptives
+casual_des <- 
+  casual_long %>% 
+  group_by(homosexual_dlikelihood_dstandard, gender) %>% 
+  summarise(across(inpool:partner_ip, 
+                   list(mean = mean, sd = sd),
+                   .names = "{.col}.{.fn}")) %>% 
+  pivot_wider(names_from = gender, 
+              values_from = -c(homosexual_dlikelihood_dstandard, gender),
+              names_glue = "{gender}_{.value}")
+
+# t test by groups for exp_all variable
+casual_t_test <- 
+  casual_long %>% 
+  nest_by(homosexual_dlikelihood_dstandard) %>% 
+  mutate(
+    inpool = t.test(inpool ~ gender, data = data) %>% tidy() %>% 
+      select(statistic, p.value, parameter),
+    outpool = t.test(outpool ~ gender, data = data) %>% tidy() %>% 
+      select(statistic, p.value, parameter),
+    exp_all = t.test(exp_all ~ gender, data = data) %>% tidy() %>% 
+      # somehow the map function doesn't work here and I wonder why...
+      select(statistic, p.value, parameter),
+    exp_ip = t.test(exp_ip ~ gender, data = data) %>% tidy() %>% 
+      select(statistic, p.value, parameter),
+    partner_all = t.test(partner_all ~ gender, data = data) %>% tidy() %>% 
+      select(statistic, p.value, parameter),
+    partner_ip = t.test(partner_ip ~ gender, data = data) %>% tidy() %>% 
+      select(statistic, p.value, parameter)
+    ) %>% 
+  select(-data) %>% 
+  unnest(cols = -homosexual_dlikelihood_dstandard, names_sep = ".")
+
+# effect size
+casual_d <- 
+  casual_long %>% 
+  nest_by(homosexual_dlikelihood_dstandard) %>% 
+  mutate(
+    inpool.d = cohens_d(inpool ~ gender, data = data) %>% pull(Cohens_d),
+    outpool.d = cohens_d(outpool ~ gender, data = data) %>% pull(Cohens_d),
+    exp_all.d = cohens_d(exp_all ~ gender, data = data) %>% pull(Cohens_d),
+    exp_ip.d = cohens_d(exp_ip ~ gender, data = data) %>% pull(Cohens_d),
+    partner_all.d = cohens_d(partner_all ~ gender, data = data) %>% pull(Cohens_d),
+    partner_ip.d = cohens_d(partner_ip ~ gender, data = data) %>% pull(Cohens_d)
+    )
+
+# combine the descriptives, test results, and effect size
+full_join(casual_des, casual_t_test, casual_d, by = "homosexual_dlikelihood_dstandard") %>% 
   kable()

### 2022-04-27 exploratory/20220426_main_plot_t_test.Rmd
fine-tuned the t-test output table, close #5

@@
     partner_ip.d = cohens_d(partner_ip ~ gender, data = data) %>% pull(Cohens_d)
-    )
+    ) %>% 
+  select(-data)
 
 # combine the descriptives, test results, and effect size
-full_join(casual_des, casual_t_test, casual_d, by = "homosexual_dlikelihood_dstandard") %>% 
+full_join(casual_des, casual_t_test, by = "homosexual_dlikelihood_dstandard") %>% 
+  full_join(., casual_d, by = "homosexual_dlikelihood_dstandard") %>% 
   kable()

### 2022-04-30 exploratory/20220426_main_plot_t_test.Rmd
embedded r codes in the manuscript and completed the results section, close #8

@@
 # combine the descriptives, test results, and effect size
+des_t_d <- 
   full_join(casual_des, casual_t_test, by = "homosexual_dlikelihood_dstandard") %>% 
-  full_join(., casual_d, by = "homosexual_dlikelihood_dstandard") %>% 
-  kable()
+  full_join(., casual_d, by = "homosexual_dlikelihood_dstandard")
+
+# display the results 
+des_t_d %>% kable()
 ```

### 2022-05-01 code/des_and_test_result.R
wrote an R script to generate the result table, close #9

@@ -1,0 +1,84 @@
+#!/usr/bin/env Rscript --vanilla
+
+# name: des_and_test_result.R
+# input: data/processed/casual_sex_sim.csv
+# output: data/processed/des_and_test_result.csv
+# notes: take in the data file, do the statistical analyses 
+#   and output into a table containing descriptive stats, t-test results, and effect size
+
+
+library(tidyverse); library(magrittr); library(here); library(broom); library(effectsize)
+
+input_file <- commandArgs(trailingOnly = TRUE)
+output_file <- "data/processed/des_and_test_result.csv"
+
+casual_tib <- here(input_file) %>% 
+  read_csv() %>% 
+  mutate(
+    diff_likelihood = as_factor(diff_likelihood),
+    diff_standard = as_factor(diff_standard),
+    homosexual = as_factor(homosexual)
+  )
+
+# create a long tibble
+casual_long <- 
+  casual_tib %>%
+  unite(homosexual, diff_likelihood, diff_standard,
+        col = "homosexual_dlikelihood_dstandard", sep = "_") %>% 
+  pivot_longer(-c(seed, homosexual_dlikelihood_dstandard), 
+               names_to = c("gender", ".value"), 
+               names_pattern = "(.)_(.*)"
+  )
+
+# descriptives
+casual_des <- 
+  casual_long %>% 
+  group_by(homosexual_dlikelihood_dstandard, gender) %>% 
+  summarise(across(inpool:partner_ip, 
+                   list(mean = mean, sd = sd),
+                   .names = "{.col}.{.fn}")) %>% 
+  pivot_wider(names_from = gender, 
+              values_from = -c(homosexual_dlikelihood_dstandard, gender),
+              names_glue = "{gender}_{.value}")
+
+# t test by groups for exp_all variable
+casual_t_test <- 
+  casual_long %>% 
+  nest_by(homosexual_dlikelihood_dstandard) %>% 
+  mutate(
+    inpool = t.test(inpool ~ gender, data = data) %>% tidy() %>% 
+      select(statistic, p.value, parameter),
+    outpool = t.test(outpool ~ gender, data = data) %>% tidy() %>% 
+      select(statistic, p.value, parameter),
+    exp_all = t.test(exp_all ~ gender, data = data) %>% tidy() %>% 
+      # somehow the map function doesn't work here and I wonder why...
[…]

### 2022-05-02 exploratory/20220430_hetero_vs_gay.Rmd
added analyses to compare heterosexual and gay men, close #10

---
title: "20220430_hetero_vs_gay"
author: "Yurun (Ellen) Ying"
date: "4/30/2022"
output: 
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
# load libraries
library(tidyverse); library(ggplot2); library(wesanderson); library(magrittr); library(here); library(knitr); library(broom); library(effectsize)

# read file
casual_tib <- here("data/processed/casual_sex_sim.csv") %>% 
  read_csv() %>% 
  mutate(
    diff_likelihood = as_factor(diff_likelihood),
    diff_standard = as_factor(diff_standard),
    homosexual = as_factor(homosexual)
  )
```

## Plots
- Violin plots of the diff x diff condition
	- grouped by sexual orientation
	- paneled by dependent variables: avg num of experiences (all), avg num of partners (all)

```{r violin_plot, fig.height=8, fig.width=5}
y_lab <- labeller(
      variable = c(
        `exp_all` = "Average number of\nshort-term mating experiences",
        `partner_all` = "Average number of\nshort-term patners"))

casual_tib %>% 
  filter(diff_likelihood == 1, diff_standard == 1) %>% 
  select(homosexual, m_exp_all, m_partner_all) %>% 
  pivot_longer(c(m_exp_all, m_partner_all), values_to = "value",
               names_to = "variable", names_pattern = "m_(.*)") %>% 
  ggplot(aes(x = homosexual, y = value)) +
  geom_violin(aes(fill = homosexual)) +
  stat_summary(fun = "mean", geom = "point") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
  scale_fill_discrete(
    type = wes_palette("Darjeeling2", 2, type = "discrete"),
    name = "", labels = c("Heterosexual men", "Gay men")
  ) +
  labs(x = "", y = NULL,
       title = " Violin plot of average number of short-term mating\nexperiences and  short-term mates, comparing\nheterosexualand gay men") +
  facet_wrap(
    ~ variable, ncol = 1, scales = "free",
    strip.position = "left",
    labeller = y_lab
    ) +
  theme_minimal() +
  theme(
    axis.line = element_line(size = 0.3),
    axis.ticks.y = element_line(size = 0.3),
    axis.text.x = element_blank(),
    panel.grid = element_blank(),
    panel.spacing = unit(0.5, "line"),
    strip.text = element_text(size = 11),
    strip.placement = "outside",
    legend.position = "bottom",
    legend.box.spacing = unit(0.1, "line")
    )

```

## T-tests
- Independent samples *t*-test between heterosexual and gay men on all outcome variables, separate for conditions
- Output into tables with descriptives and test results, separate by variables

```{r t_all_var}
# create a long tibble
casual_long <- 
  casual_tib %>%
  unite(diff_likelihood, diff_standard,
        col = "dlikelihood_dstandard", sep = "_") %>% 
  select(-c(seed, starts_with("f_")))

# descriptives
casual_des <- 
  casual_long %>% 
  group_by(dlikelihood_dstandard, homosexual) %>% 
  summarise(across(m_inpool:m_partner_ip, 
                   list(mean = mean, sd = sd),
                   .names = "{.fn}.{.col}"),
            .groups = "keep") %>% 
  pivot_wider(names_from = homosexual, 
              values_from = -c(dlikelihood_dstandard, homosexual),
              names_glue = "{.value}_{homosexual}")

# t test by groups for exp_all variable
casual_t_test <- 
  casual_long %>% 
  nest_by(dlikelihood_dstandard) %>% 
  mutate(
    m_inpool = t.test(m_inpool ~ homosexual, data = data) %>% tidy() %>% 
      select(statistic, p.value, parameter),
    m_outpool = t.test(m_outpool ~ homosexual, data = data) %>% tidy() %>% 
      select(statistic, p.value, parameter),
    m_exp_all = t.test(m_exp_all ~ homosexual, data = data) %>% tidy() %>% 
      # somehow the map function doesn't work here and I wonder why...
      select(statistic, p.value, parameter),
    m_exp_ip = t.test(m_exp_ip ~ homosexual, data = data) %>% tidy() %>% 
      select(statistic, p.value, parameter),
    m_partner_all = t.test(m_partner_all ~ homosexual, data = data) %>% tidy() %>% 
      select(statistic, p.value, parameter),
    m_partner_ip = t.test(m_partner_ip ~ homosexual, data = data) %>% tidy() %>% 
      select(statistic, p.value, parameter)
    ) %>% 
  select(-data) %>% 
  unnest(cols = -dlikelihood_dstandard, names_sep = ".")

# effect size
casual_d <- 
  casual_long %>% 
  nest_by(dlikelihood_dstandard) %>% 
  mutate(
    m_inpool.d = cohens_d(m_inpool ~ homosexual, data = data) %>% pull(Cohens_d),
    m_outpool.d = cohens_d(m_outpool ~ homosexual, data = data) %>% pull(Cohens_d),
    m_exp_all.d = cohens_d(m_exp_all ~ homosexual, data = data) %>% pull(Cohens_d),
    m_exp_ip.d = cohens_d(m_exp_ip ~ homosexual, data = data) %>% pull(Cohens_d),
    m_partner_all.d = cohens_d(m_partner_all ~ homosexual, data = data) %>% pull(Cohens_d),
    m_partner_ip.d = cohens_d(m_partner_ip ~ homosexual, data = data) %>% pull(Cohens_d)
    ) %>% 
  select(-data)

# combine the descriptives, test results, and effect size
des_t_d <- 
  full_join(casual_des, casual_t_test, by = "dlikelihood_dstandard") %>% 
  full_join(., casual_d, by = "dlikelihood_dstandard")

# display the results 
des_t_d %>% kable()
```

### 2022-05-02 code/compare_hetero_gay_men.R

@@ -1,0 +1,81 @@
+#!/usr/bin/env Rscript --vanilla
+
+# name: compare_hetero_gay_men.R
+# input: data/processed/casual_sex_sim.csv
+# output: data/processed/compare_hetero_gay_men.csv
+# notes: take in the data file, do the statistical analyses 
+#   and output into a table containing descriptive stats, t-test results, and effect size
+
+
+library(tidyverse); library(magrittr); library(here); library(broom); library(effectsize)
+
+input_file <- commandArgs(trailingOnly = TRUE)
+output_file <- "data/processed/compare_hetero_gay_men.csv"
+
+casual_tib <- here(input_file) %>% 
+  read_csv() %>% 
+  mutate(
+    diff_likelihood = as_factor(diff_likelihood),
+    diff_standard = as_factor(diff_standard),
+    homosexual = as_factor(homosexual)
+  )
+
+# create a long tibble
+casual_long <- 
+  casual_tib %>%
+  unite(diff_likelihood, diff_standard,
+        col = "dlikelihood_dstandard", sep = "_") %>% 
+  select(-c(seed, starts_with("f_")))
+
+# descriptives
+casual_des <- 
+  casual_long %>% 
+  group_by(dlikelihood_dstandard, homosexual) %>% 
+  summarise(across(m_inpool:m_partner_ip, 
+                   list(mean = mean, sd = sd),
+                   .names = "{.fn}.{.col}"),
+            .groups = "keep") %>% 
+  pivot_wider(names_from = homosexual, 
+              values_from = -c(dlikelihood_dstandard, homosexual),
+              names_glue = "{.value}_{homosexual}")
+
+# t test by groups for exp_all variable
+casual_t_test <- 
+  casual_long %>% 
+  nest_by(dlikelihood_dstandard) %>% 
+  mutate(
+    m_inpool = t.test(m_inpool ~ homosexual, data = data) %>% tidy() %>% 
+      select(statistic, p.value, parameter),
+    m_outpool = t.test(m_outpool ~ homosexual, data = data) %>% tidy() %>% 
+      select(statistic, p.value, parameter),
+    m_exp_all = t.test(m_exp_all ~ homosexual, data = data) %>% tidy() %>% 
+      # somehow the map function doesn't work here and I wonder why...
+      select(statistic, p.value, parameter),
[…]

### 2022-05-02 code/compare_hetero_gay_men.R
generated plots and added them into the manuscript, close #11

@@ -33,7 +33,7 @@ casual_des <-
   group_by(dlikelihood_dstandard, homosexual) %>% 
   summarise(across(m_inpool:m_partner_ip, 
                    list(mean = mean, sd = sd),
-                   .names = "{.fn}.{.col}"),
+                   .names = "{.col}.{.fn}"),
             .groups = "keep") %>% 
   pivot_wider(names_from = homosexual, 
               values_from = -c(dlikelihood_dstandard, homosexual),

### 2022-05-02 code/plot_hetero_vs_gay_men.R

@@ -1,0 +1,58 @@
+#!/usr/bin/env Rscript --vanilla
+
+# name: plot_hetero_vs_gay_men.R
+# input: data/processed/casual_sex_sim.csv
+# output: submission/figures/fig2_hetero_vs_gay_men.pdf
+# notes: none
+
+# load libraries
+library(tidyverse); library(ggplot2); library(wesanderson); library(magrittr); library(here); library(knitr); library(broom); library(effectsize)
+
+# read file
+casual_tib <- here("data/processed/casual_sex_sim.csv") %>% 
+  read_csv() %>% 
+  mutate(
+    diff_likelihood = as_factor(diff_likelihood),
+    diff_standard = as_factor(diff_standard),
+    homosexual = as_factor(homosexual)
+  )
+
+y_lab <- labeller(
+  variable = c(
+    `exp_all` = "Average number of\nshort-term mating experiences",
+    `partner_all` = "Average number of\nshort-term mates"))
+
+casual_tib %>% 
+  filter(diff_likelihood == 1, diff_standard == 1) %>% 
+  select(homosexual, m_exp_all, m_partner_all) %>% 
+  pivot_longer(c(m_exp_all, m_partner_all), values_to = "value",
+               names_to = "variable", names_pattern = "m_(.*)") %>% 
+  ggplot(aes(x = homosexual, y = value)) +
+  geom_violin(aes(fill = homosexual)) +
+  stat_summary(fun = "mean", geom = "point") +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
+  scale_fill_discrete(
+    type = wes_palette("Darjeeling2", 2, type = "discrete"),
+    name = "", labels = c("Heterosexual men", "Gay men")
+  ) +
+  scale_y_continuous(limits = c(0, NA), breaks = seq(0, 4, by = 1)) +
+  labs(x = "", y = NULL) +
+  facet_wrap(
+    ~ variable, ncol = 1, scales = "free",
+    strip.position = "left",
+    labeller = y_lab
+  ) +
+  theme_minimal() +
+  theme(
+    axis.line = element_line(size = 0.3),
+    axis.ticks.y = element_line(size = 0.3),
+    axis.text.x = element_blank(),
+    panel.grid = element_blank(),
+    panel.spacing = unit(0.5, "line"),
+    strip.text = element_text(size = 11),
+    strip.placement = "outside",
[…]

### 2022-05-02 code/plot_men_vs_women.R

@@ -1,0 +1,62 @@
+#!/usr/bin/env Rscript --vanilla
+
+# name: plot_men_vs_women.R
+# input: data/processed/casual_sex_sim.csv
+# output: submission/figures/fig1_men_vs_women.pdf
+# notes: none
+
+# load libraries
+library(tidyverse); library(ggplot2); library(wesanderson); library(magrittr); library(here); library(knitr); library(broom); library(effectsize)
+
+# read file
+casual_tib <- here("data/processed/casual_sex_sim.csv") %>% 
+  read_csv() %>% 
+  mutate(
+    diff_likelihood = as_factor(diff_likelihood),
+    diff_standard = as_factor(diff_standard),
+    homosexual = as_factor(homosexual)
+  )
+
+y_lab <- labeller(
+  homosexual = c(
+    `0` = "Experiment 1\nHeterosexual individuals",
+    `1` = "Experiment 2\nGay men and lesbian women"),
+  variable = c(
+    `exp_all` = "Average number of\nshort-term mating experiences",
+    `partner_all` = "Average number of\nshort-term mates")
+  )
+
+casual_tib %>% 
+  filter(diff_likelihood == 1, diff_standard == 1) %>% 
+  select(homosexual, m_exp_all, f_exp_all, m_partner_all, f_partner_all) %>% 
+  pivot_longer(c(m_exp_all, f_exp_all, m_partner_all, f_partner_all), 
+               values_to = "value", names_to = c("gender", "variable"),
+               names_pattern = "(.)_(.*)") %>% 
+  ggplot(aes(x = gender, y = value)) +
+  geom_violin(aes(fill = gender)) +
+  stat_summary(fun = "mean", geom = "point") +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
+  scale_fill_discrete(
+    type = wes_palette("Darjeeling2", 2, type = "discrete"),
+    name = "", labels = c("Women", "Men")
+  ) +
+  scale_y_continuous(limits = c(0, NA), breaks = seq(0, 4, by = 1)) +
+  labs(x = "", y = NULL) +
+  facet_grid(
+    variable ~ homosexual, scales = "free_y",
+    switch = "y", labeller = y_lab) +
+  theme_minimal() +
+  theme(
+    axis.line = element_line(size = 0.3),
+    axis.ticks.y = element_line(size = 0.3),
+    axis.text.x = element_blank(),
[…]

### 2022-05-06 README.Rmd
editted README file, close #12

---
title: "ABM simulating short-term mating behaviors"
author: "Yurun (Ellen) Ying"
date: "5/6/2022"
output: 
  github_document:
    html_preview: true
---

## Description
By using a spatial agent-based model, the present study investigated we investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances.

```{r library_calls, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(broom)
library(effectsize)
library(ggplot2)
library(rmarkdown)
library(knitr)
library(kableExtra)
```

### Dependencies:
- Netlogo version 6.2.1
- `r R.version.string`
  - `tidyverse` (v. `r packageVersion("tidyverse")`)
  - `here` (v. `r packageVersion("here")`)
  - `broom` (v. `r packageVersion("broom")`)
  - `effectsize` (v. `r packageVersion("effectsize")`)
  - `ggplot2` (v. `r packageVersion("ggplot2")`)
  - `rmarkdown` (v. `r packageVersion("rmarkdown")`)
  - `knitr` (v. `r packageVersion("knitr")`)
  - `kableExtra` (v. `r packageVersion("kableExtra")`)

### My computer

```{r sessioninfo, echo=FALSE}
sessionInfo()
```

### 2022-05-11 submission/manuscript.Rmd
modified the plots and inline output, close #16

---
output:
  pdf_document:
    keep_tex: true
  word_document: true
geometry: margin=1.0in
fontsize: 11pt
numbersections: true
bibliography: reference.bib
csl: evolution-and-human-behavior.csl
header-includes:
  - \newcommand{\bcenter}{\begin{center}}
  - \newcommand{\ecenter}{\end{center}}
  - \newcommand{\btitlepage}{\begin{titlepage}}
  - \newcommand{\etitlepage}{\end{titlepage}}
  - \usepackage{setspace}\doublespacing
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{booktabs}
  - \usepackage[font=small,labelfont=bf]{caption}
---

```{r set_up, include=FALSE}
library(tidyverse); library(here); library(knitr); library(kableExtra)

results <-
  here("data/processed/des_and_test_result.csv") %>%
  read_csv() %>%
  rename(hls = homosexual_dlikelihood_dstandard) %>%
  mutate(across(contains("p.value"), ~format(.x, digits = 2, nsmall = 3))) %>%
  mutate(across(contains("p.value"), ~ ifelse(.x >= .001,
                                              str_remove(.x, "^0"),
                                              "< .001")
                                              ))

results_hg <-
  here("data/processed/compare_hetero_gay_men.csv") %>%
  read_csv() %>%
  rename(ls = dlikelihood_dstandard) %>%
  mutate(across(contains("p.value"), ~format(.x, digits = 2, nsmall = 3))) %>%
  mutate(across(contains("p.value"), ~ ifelse(.x >= .001,
                                              str_remove(.x, "^0"),
                                              "< .001")
                                              ))

opts_chunk$set(include=FALSE)

inline_hook <- function(x) {

    if (is.numeric(x)) {

      formatted <- ifelse(
        abs(x - round(x)) < .Machine$double.eps,
        # treat as integer
        format(x, digits=0, big.mark = ","),
        # treat as floating point number
        format(x, digits=1, nsmall=2, big.mark = ",")
        )

    } else {

      formatted <- x

    }

}

knit_hooks$set(inline = inline_hook)
```

\btitlepage

\bcenter

\vspace*{30mm}

# **This is an awesome title** {-}

\vspace{30mm}

Yurun Ying^1^, Pekka Santtila^1^^,^^2^^,^^$\dagger$^

^1^ Faculty of Arts and Sciences, NYU Shanghai

^2^ NYU-ECNU Institute for Social Development at NYU Shanghai

\ecenter

\vspace{40mm}

^$\dagger$^ To whom correspondence should be addressed:

\etitlepage

\newpage

# Abstract {-}

\newpage

# Introduction

Gender differences in sexual behaviors, especially short-term mating behaviors, have been a well-documented phenomenon in human sexuality research. For example, research has found that heterosexual men, as compared to heterosexual women, have a higher average number of past short-term sexual partners [@oliver_gender_1993; @petersen_meta-analytic_2010; @rissel_heterosexual_2014], have short-term mating more frequently [@petersen_meta-analytic_2010], and engage in extramarital sex more often [@petersen_meta-analytic_2010]. These gender differences have also been observed between gay men and lesbian women [@bailey_effects_1994; @bryant_relationship_1994; @peplau_national_1997; @peplau_sexuality_2004].

In the existing literature, gender differences in sexual behaviors are not usually distinguished from those in attitudes towards or preferences for short-term mating. Some researchers study gender differences on the two levels simultaneously without a conceptual distinction [e.g., @petersen_meta-analytic_2010], whereas some implicitly equate the two, assuming that behavioral differences are a direct expression of the psychological ones [e.g., @schmitt_are_2001].

Intuitive as this line of reasoning is, there are good reasons to doubt its soundness. This is because any heterosexual sexual encounter involves both a man and a woman (the frequency of encounters involving more than two persons is negligible, [e.g., @herbenick_sexual_2017]. A new short-term mating experience for a man is, therefore, also a new experience for a woman, and the same logic applies to counting a new short-term mate. As a result, the psychological differences in short-term mating preferences may not result in behavioral ones in the heterosexual case [@archer_reality_2019].

The present study took gender differences in mating preferences as an assumption, which was proposed by sexual strategy theory [@buss_sexual_1993] and repeatedly found support by empirical studies [e.g., @schmitt_universal_2003; @walter_sex_2020]. Using an agent-based model, we investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, specifically, in the number of short-term mating experiences and short-term mates, and if they did, under what circumstances.

## Gender differences in short-term mating preferences

Gender differences in mating strategies have been studied in the light of sexual strategy theory [@buss_sexual_1993]. It posits that since the minimum investment that men devote to their offspring (contribution of sperm through one sexual act) is lower than that of women (gestation, labor, and lactation), men tend to have short-term mating as a larger part of their mating strategy than women do. This is because women's high minimum investment leads to higher opportunity cost (vs. men) if they have sex with a suboptimal partner and give birth to offspring with a low survival chance. As a result, men may have a greater interest in short-term mating, desire a larger number of short-term mates in a given period, and be less selective with respect to accepting a potential mate [@buss_sexual_1993].

The hypotheses derived from sexual strategy theory have received extensive support from empirical studies. For example, men reported to be currently seeking short-term mates to a larger extent than women did [@buss_sexual_1993; @schmitt_are_2001; @schmitt_universal_2003], and a larger proportion of them were in any way seeking short-term mates (vs. not seeking) [@schmitt_universal_2003]. These have been found among U.S. college students [@buss_sexual_1993; @schmitt_are_2001] as well as in ten world regions in a cross-cultural study [@schmitt_universal_2003]. Similarly, men across the world also reported to desire more short-term sexual partners compared to women for a number of given time periods (e.g., a month, a year) [@buss_sexual_1993; @schmitt_universal_2003; @mcburney_preferred_2005]. The gender differences were significant regardless of whether they were estimated by mean [@buss_sexual_1993; @schmitt_are_2001; @schmitt_universal_2003], median [@schmitt_are_2001; @schmitt_universal_2003], or percentage [@schmitt_universal_2003] statistics.

As for mating standards, men are more likely to accept someone as a potential short-term mate. For example, studies using U.S. college samples found that the minimum percentile ranks that men found acceptable for a potential short-term sexual partner were lower than for women both overall and on individual traits (e.g., social status, attractiveness) [@kenrick_evolution_1990; @regan_minimum_1998]. A study also found that when presented with identical descriptions of potential mates, men on average rated them as more desirable than women did [@wiederman_evolution_1998].

Some evidence shows that sexual strategy theory also predicts mating preferences among gay men and lesbian women. A survey study using a community sample from the U.S. found that gay men were more interested in short-term mating than lesbian women and that this gender difference was comparable to that existing among heterosexual individuals [@bailey_effects_1994]. An indirect piece of evidence on differential standards for short-term mates comes from a recent study finding that significantly more gay men than lesbian women reported to have accepted a casual sexual offer from a same-gender person [@matsick_gender_2021]. Past studies suggest that the gender difference in the acceptance rate of casual sexual offers may originate from men and women’s differential standards for short-term mates [@conley_women_2011; @hald_receptivity_2010]. Thus, as a postulation, gay men and lesbian women may also have different standards for short-term mates.

## Constraints on men's preferences for short-term mating
Since heterosexual sex involves both a man and a woman in most cases, men's interest in short-term mating can be constrained by women's preference for long-term relationships [@archer_reality_2019; @symons_evolution_1979]. This is because men’s short-term mating preferences can only translate into behaviors when there are women willing to have sex with them. When short-term mating occurs, the number of short-term mating encounters and short-term mates is essentially the same for men and women (although this does not necessarily mean that the total number of men and women who have ever had short-term mating must be equal). Therefore, we would expect to observe no gender difference in short-term mating behaviors among heterosexual individuals even when there were gender differences in mating preferences.

As a comparison, in the cases of gay men and lesbian women, men’s preferences are not constrained by women’s, but only by those of other men, who, arguably, have more similar preferences. This would allow for a more direct behavioral expression of men’s mating preferences. The notion that gay men have less restricted preferences was borne out in the proportion of individuals who have engaged in extradyadic sex [@peplau_sexuality_2004]. A study showed that the proportions of heterosexual men and women who have engaged in extradyadic sex were 26% and 21%, respectively, while the statistics among gay men and lesbian women were 82% and 28%, respectively [@peplau_sexuality_2004]. Therefore, we would theoretically expect to observe gender differences in short-term mating behaviors among gay men and lesbians. Moreover, we would also expect to find that gay men, as compared to heterosexual men, engaged in more short-term mating behaviors due to the lessened constraint on their mating preferences.

## A simple model of short-term mating behaviors

By using a spatial agent-based model, the present study investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances. The interest in short-term mating was modeled as an individual’s likelihood of deciding to have short-term mating at each time step. The standards for short-term mates were modeled as the minimum desirability of a potential mate with whom an individual was willing to have sex. Short-term mating behaviors were operationally defined as the number of short-term mating experiences and the number of past short-term mates.

We modeled this process among both heterosexual individuals and gay men and lesbian women to examine whether constraints set by the opposite sex’s preferences would make a difference in short-term mating behaviors. Individuals’ sexual orientation was conceptualized in terms of behaviors only in our model. Heterosexual men had short-term mating or formed a long-term relationship with women, while gay men only with other men, and vice versa for women.

We raised the following hypotheses in the present study: when there were gender differences in preferences for short-term mating, 1) there would be gender differences in short-term mating behaviors among gay men and lesbian women, with gay men being engaged in more such behaviors, and 2) gay men would engage in more short-term mating behaviors as compared to heterosexual men.

# Material and methods

## Model Design

We developed an agent-based model to represent a simplified environment where men and women can move around, search for mates, and form long-term and/or short-term relationships. Space and time are modeled as discrete variables. Space was represented as discrete locations on a two-dimensional 33*33 lattice. Agents’ movement in the space was not meant to simulate physical movement but a state of encountering potential mates. Staying at one location represented being committed to a long-term relationship.

The model measured **three** outcomes: (1) the number of men and women who had ever engaged in short-term mating **put this to the end**; (2) the number of short-term mating experiences of men and women; (3) the number of short-term mates of men and women. The number of short-term mating experienced and short-term mates were calculated by taking the average among the whole men/women population and among those who had engaged in short-term mating.

See the Supplemental Materials for the overview, design concepts, and details (ODD) protocol of the model, which includes detailed scheduling and parameterization. The model can be downloaded from the Github online repository [link masked for peer review]. The model was programmed in Netlogo 6.2.1 [@wilensky_1999].

## Experiment Design

Using the agent-based model, the present study conducted two 2 (gender difference vs. no difference in short-term mating likelihood) x 2 (gender difference vs. no difference in mating standard) experiments. Experiment 1 was run among heterosexual agents who only engaged in short-term or long-term relationships with agents of the opposite gender. Experiment 2 was run among gay men and lesbian women who only engaged in short-term or long-term relationships with agents of the same gender.

Gender differences were modeled in agents’ likelihood of engaging in short-term mating and the standard for short-term mates. The values of these parameters were set based on empirical findings in human mating psychology. We compared the conditions where there were gender differences in mating preferences with counterfactual conditions where gender differences were missing. When there was a gender difference in short-term mating likelihood, men had a 40% likelihood of deciding to engage in short-term mating upon meeting a potential mate, while women had a likelihood of 25% [@buss_sexual_1993; @schmitt_are_2001; @schmitt_universal_2003]. When there was no gender difference in short-term mating likelihood, both women and men had a likelihood of 25%. When there was a gender difference in mating standards, men had a mating standard of 3 (the minimum mate value of a potential partner with whom an agent is willing to have short-term mating, highest possible value = 10), while women had a standard of 5 [@kenrick_evolution_1990; @regan_minimum_1998]. When there was no gender difference in mating standards, both men and women had a standard of 5.

## Model Schedule

### Initial setup
In total, 150 women and 150 men were created on the lattice at random locations. All agents were initialized with (1) a three-unit maximum distance by which agents can move away from their birthplace (movement range); (2) a 10% likelihood of two agents forming a long-term relationship upon meeting; (3) single status and no long-term partner; (4) a mate value, sampled from a Gaussian distribution (*M* = 5, *SD* = 1.5); (5) no short-term mate or short-term mating history.

The likelihood of engaging in short-term mating and the standard for short-term mates were initialized either the same or differently for men and women, depending on the experimental conditions.

### Procedures
#### Heterosexual procedures.
At each time step, agents first checked whether they were in a long-term relationship. If they were not in a long-term relationship, they set their heading randomly (if they were within the movement range from the birthplace) or faced the birthplace (if they were out of the movement range from the birthplace) and moved by a random distance. The random distance was less than half of the movement range. If they were in a long-term relationship, they did not move. Then, the agents decided on whether to engage in short-term mating by a chance of the chosen likelihood (either 25% or 40%).

Women checked to see if any men were at the same location. If there were, they randomly chose one of them as their potential short-term mate. If both men and women met each other’s mating standards and both of them decided to engage in short-term mating, they had sex. This would result in increasing both parties’ number of short-term mating experiences by one. They also recorded each other on their lists of past short-term mates if they were not on the lists yet.

Then, women randomly selected one man at the same location as their potential long-term partner. There was a 10% of chance that a pair would form a long-term relationship. After forming a long-term relationship, both men and women changed to coupled status and register each other as the long-term partner.

#### Gay men and lesbian women procedures.
At each time step, men and women moved and decided on short-term mating as the agents did in the heterosexual procedures. Half of the agents (an equal number of men and women) were also given the initiator status. The initiators checked to see whether there were other agents at the same location. The rest of the procedures were identical to the heterosexual procedures, except that the agents only chose those with the same gender as themselves as potential short-term mates or long-term partners.

## Simulations
The model was run for 1,000 time steps in each simulation. We ran 10,000 simulations for each experiment, and 2,500 simulations for each condition. We controlled for initializing random seeds in the model runs. All simulations were run using Netlogo 6.2.1 [@wilensky_1999].

## Statistical analysis
Statistical analyses were conducted using `r R.version.string %>% str_replace(" \\(.*\\)", "")` [@r] and the figures were generated by the ggplot2 package [@ggplot2]. Two-tailed independent samples *t*-tests were used for all statistical comparisons. The data were assumed to be normally distributed within each condition but was not formally tested.

# Results

## Gender differences in short-term mating behaviors in each experiment

```{r sec1.1}
m_exp_all.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_exp_all.mean)
m_exp_all.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_exp_all.sd)
f_exp_all.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_exp_all.mean)
f_exp_all.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_exp_all.sd)
exp_all.d_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_all.d) %>% abs()

m_partner_all.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_partner_all.mean)
m_partner_all.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_partner_all.sd)
f_partner_all.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_partner_all.mean)
f_partner_all.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_partner_all.sd)
partner_all.d_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_all.d) %>% abs()
```

The results from Experiment 1 showed that when there were gender differences in preferences for short-term mating, there was no gender difference in the average number of short-term mating experiences among heterosexual individuals (*M~m~* = `r m_exp_all.mean_011`, *SD~m~* = `r m_exp_all.sd_011`; *M~w~* = `r f_exp_all.mean_011`, *SD~w~* = `r f_exp_all.sd_011`), Cohen's *d* = `r exp_all.d_011`. Nor was there a difference in the average number of short-term mates (*M~m~* = `r m_partner_all.mean_011`, *SD~m~* = `r m_partner_all.sd_011`; *M~w~* = `r f_partner_all.mean_011`, *SD~w~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011` (Figure 1).

\begin{figure}[h]
  \centering
  \includegraphics[width=80mm]{figures/fig1_men_vs_women.pdf}
  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. Statistics were calculated using the full population of men and women in the model (\textit{N\textsubscript{m}} = \textit{N\textsubscript{w}} = 150).}
\end{figure}

```{r sec1.2}
m_exp_all.mean_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(m_exp_all.mean)
m_exp_all.sd_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(m_exp_all.sd)
f_exp_all.mean_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(f_exp_all.mean)
f_exp_all.sd_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(f_exp_all.sd)
exp.all.parameter_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(exp_all.parameter)
exp.all.statistic_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(exp_all.statistic)
exp.all.p.value_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(exp_all.p.value)
exp_all.d_111 <-
results %>% filter(hls == "1_1_1") %>% pull(exp_all.d) %>% abs()

m_partner_all.mean_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(m_partner_all.mean)
m_partner_all.sd_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(m_partner_all.sd)
f_partner_all.mean_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(f_partner_all.mean)
f_partner_all.sd_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(f_partner_all.sd)
partner.all.parameter_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(partner_all.parameter)
partner.all.statistic_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(partner_all.statistic)
partner.all.p.value_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(partner_all.p.value)  
partner_all.d_111 <-
  results %>% filter(hls == "1_1_1") %>% pull(partner_all.d) %>% abs()
```

The results from Experiment 2 showed that when there were gender differences in preferences for short-term mating, there were gender differences in short-term mating behaviors between gay men and lesbian women (Figure 1). The average number of short-term mating experiences was higher among gay men (*M* = `r m_exp_all.mean_111`, *SD* = `r m_exp_all.sd_111`) than among lesbian women (*M* = `r f_exp_all.mean_111`, *SD* = `r f_exp_all.sd_111`), *t*(`r exp.all.parameter_111`) = `r exp.all.statistic_111`, *p* `r exp.all.p.value_111`, Cohen's *d* = `r exp_all.d_111`. Similarly, the average number of short-term mates was higher among gay men (*M* = `r m_partner_all.mean_111`, *SD* = `r m_partner_all.sd_111`) than among lesbian women (*M* = `r f_partner_all.mean_111`, *SD* = `r f_partner_all.sd_111`), *t*(`r partner.all.parameter_111`) = `r partner.all.statistic_111`, *p* `r partner.all.p.value_111`, Cohen's *d* = `r partner_all.d_111`.

```{r sec1.3}
m_exp_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_exp_ip.mean)
m_exp_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_exp_ip.sd)
f_exp_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_exp_ip.mean)
f_exp_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_exp_ip.sd)
exp_ip.parameter_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.parameter)
exp_ip.statistic_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.statistic)
exp_ip.p.value_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.p.value)
exp_ip.d_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(exp_ip.d) %>% abs()

m_partner_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_partner_ip.mean)
m_partner_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(m_partner_ip.sd)
f_partner_ip.mean_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_partner_ip.mean)
f_partner_ip.sd_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(f_partner_ip.sd)
partner_ip.parameter_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.parameter)
partner_ip.statistic_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.statistic)
partner_ip.p.value_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.p.value)
partner_ip.d_011 <-
  results %>% filter(hls == "0_1_1") %>% pull(partner_ip.d) %>% abs()
```

In Experiment 1, however, when the means of the outcome variables were calculated among men and women who were in the mating pool (i.e., those with a non-zero number of short-term mating experiences) **(the number of individuals in the mating pool: M~m~, SD~m~; M~w~, SD~w~)**, there were gender differences in short-term mating behaviors when there were gender differences in mating preferences. The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`. Likewise, the average number of short-term mates was higher among heterosexual men (*M* = `r m_partner_ip.mean_011`, *SD* = `r m_partner_ip.sd_011`) than among heterosexual women (*M* = `r f_partner_ip.mean_011`, *SD* = `r f_partner_ip.sd_011`), *t*(`r partner_ip.parameter_011`) = `r partner_ip.statistic_011`, *p* `r partner_ip.p.value_011`, Cohen's *d* = `r partner_ip.d_011`.

## Comparing short-term mating behaviors of heterosexual and gay men

```{r sec2}
m_exp_all.mean_0_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.mean_0)
m_exp_all.sd_0_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.sd_0)
m_exp_all.mean_1_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.mean_1)
m_exp_all.sd_1_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.sd_1)
exp.all.parameter_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.parameter)
exp.all.statistic_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.statistic)
exp.all.p.value_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.p.value)
exp_all.d_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.d) %>% abs()

m_partner_all.mean_0_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_partner_all.mean_0)
m_partner_all.sd_0_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_partner_all.sd_0)
m_partner_all.mean_1_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_partner_all.mean_1)
m_partner_all.sd_1_11 <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_partner_all.sd_1)
partner.all.parameter_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_partner_all.parameter)
partner.all.statistic_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_partner_all.statistic)
partner.all.p.value_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_partner_all.p.value)
partner_all.d_hg <-
  results_hg %>% filter(ls == "1_1") %>% pull(m_partner_all.d) %>% abs()
```

The results comparing across the two experiments revealed that gay men engaged in short-term mating behaviors more than heterosexual men did (Figure 2). The average number of short-term mating experiences was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`. Similarly, the average number of short-term mates was higher among gay men (*M* = `r m_partner_all.mean_1_11`, *SD* = `r m_partner_all.sd_1_11`) than among heterosexual men (*M* = `r m_partner_all.mean_0_11`, *SD* = `r m_partner_all.sd_0_11`), *t*(`r partner.all.parameter_hg`) = `r partner.all.statistic_hg`, *p* `r partner.all.p.value_hg`, Cohen's *d* = `r partner_all.d_hg`.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig2_hetero_vs_gay_men.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. Statistics were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hm}} = \textit{N\textsubscript{gm}} = 150).}
\end{figure}

## Comparing across conditions

In an exploratory manner, we also compared across conditions to see which of the two dimensions of preferences for short-term mating contributed to gender differences in sexual behaviors.

```{r sec3.1}
m_exp_ip.mean_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(m_exp_ip.mean)
m_exp_ip.sd_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(m_exp_ip.sd)
f_exp_ip.mean_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(f_exp_ip.mean)
f_exp_ip.sd_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(f_exp_ip.sd)
exp_ip.d_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(exp_ip.d) %>% abs()

m_partner_ip.mean_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(m_partner_ip.mean)
m_partner_ip.sd_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(m_partner_ip.sd)
f_partner_ip.mean_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(f_partner_ip.mean)
f_partner_ip.sd_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(f_partner_ip.sd)
partner_ip.d_001 <-
  results %>% filter(hls == "0_0_1") %>% pull(partner_ip.d) %>% abs()
```

Among heterosexual individuals, gender differences in short-term mating behaviors, as calculated among individuals in the mating pool, emerged when men and women had different standards for short-term mates. Heterosexual men in the mating pool had a higher average number of short-term mating experiences and short-term mates than women in the mating pool, even when no gender difference existed in short-term mating likelihood (experiences: *M~m~* = `r m_exp_ip.mean_001`, *SD~m~* = `r m_exp_ip.sd_001`, *M~w~* = `r f_exp_ip.mean_001`, *SD~w~* = `r f_exp_ip.sd_001`, Cohen's *d* = `r exp_ip.d_001`; partners: *M~m~* = `r m_partner_ip.mean_001`, *SD~m~* = `r m_partner_ip.sd_001`; *M~w~* = `r f_partner_ip.mean_001`, *SD~w~* = `r f_partner_ip.sd_001`, Cohen's *d* = `r partner_ip.d_001`). In comparison, virtually no gender differences in short-term mating behaviors existed when men and women had the same mating standards (Table 1).

```{r table_1, include=TRUE, echo=FALSE}
results %>%
  filter(hls %in% c("0_0_0", "0_0_1", "0_1_0", "0_1_1")) %>%
  select(m_exp_ip.mean, m_exp_ip.sd,
         f_exp_ip.mean, f_exp_ip.sd, exp_ip.d,
         m_partner_ip.mean, m_partner_ip.sd,
         f_partner_ip.mean, f_partner_ip.sd, partner_ip.d) %>%
  mutate(
    exp_ip.d = abs(exp_ip.d),
    partner_ip.d = abs(partner_ip.d)
  ) %>%
  mutate(across(where(is.numeric), inline_hook)) %>%
  mutate(
    condition =
      c("Same likelihood*Same standard",
        "Same likelihood*Different standard",
        "Different likelihood*Same standard",
        "Different likelihood*Different standard")
  ) %>%
  column_to_rownames("condition") %>%
  kable(
    digits = 2, format = "latex", booktabs = TRUE,
    caption = "\\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model}",
    row.names = TRUE, col.names = c(rep(c(rep(c("M", "SD"), 2), "d"), 2))
    ) %>%
  row_spec(0, italic = TRUE, align = "c") %>%
  add_header_above(
    c(" " = 1,
      "Men" = 2, "Women" = 2, " " = 1,
      "Men" = 2, "Women" = 2, " " = 1)
    ) %>%
  add_header_above(
    c(" " = 1,
      "Average short-term mating\nexperiences (in-pool)" = 5,
      "Average short-term\nmates (in-pool)" = 5)
    ) %>%
  column_spec(1, width = "2in") %>%
  footnote(
    general = "\\\\textit{Note.} The statistics were calculated with subsamples of men and women who had had enagged in short-term mating behaviors. See Supplementary Materials for the mean and standard deviation of sample sizes.",
    general_title = "", escape = FALSE,
    threeparttable = TRUE, fixed_small_size = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```

```{r sec3.2}
m_exp_all.mean_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(m_exp_all.mean)
m_exp_all.sd_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(m_exp_all.sd)
f_exp_all.mean_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(f_exp_all.mean)
f_exp_all.sd_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(f_exp_all.sd)
exp_all.d_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(exp_all.d) %>% abs()

m_partner_all.mean_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(m_partner_all.mean)
m_partner_all.sd_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(m_partner_all.sd)
f_partner_all.mean_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(f_partner_all.mean)
f_partner_all.sd_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(f_partner_all.sd)
partner_all.d_110 <-
  results %>% filter(hls == "1_1_0") %>% pull(partner_all.d) %>% abs()

m_exp_all.mean_101 <-
  results %>% filter(hls == "1_0_1") %>% pull(m_exp_all.mean)
m_exp_all.sd_101 <-
  results %>% filter(hls == "1_0_1") %>% pull(m_exp_all.sd)
f_exp_all.mean_101 <-
  results %>% filter(hls == "1_0_1") %>% pull(f_exp_all.mean)
f_exp_all.sd_101 <-
  results %>% filter(hls == "1_0_1") %>% pull(f_exp_all.sd)
exp_all.d_101 <-
results %>% filter(hls == "1_0_1") %>% pull(exp_all.d) %>% abs()

m_partner_all.mean_101 <-
  results %>% filter(hls == "1_0_1") %>% pull(m_partner_all.mean)
m_partner_all.sd_101 <-
  results %>% filter(hls == "1_0_1") %>% pull(m_partner_all.sd)
f_partner_all.mean_101 <-
  results %>% filter(hls == "1_0_1") %>% pull(f_partner_all.mean)
f_partner_all.sd_101 <-
  results %>% filter(hls == "1_0_1") %>% pull(f_partner_all.sd)
partner_all.d_101 <-
  results %>% filter(hls == "1_0_1") %>% pull(partner_all.d) %>% abs()
```

Among gay men and lesbian women, gender differences in short-term mating behaviors emerged either when they had different short-term mating likelihood or when their mating standards were different. Gay men had a higher average number of short-term mating experiences and short-term mates when they had a higher short-term mating likelihood than lesbian women (experiences: *M~m~* = `r m_exp_all.mean_110`, *SD~m~* = `r m_exp_all.sd_110`, *M~w~* = `r f_exp_all.mean_110`, *SD~w~* = `r f_exp_all.sd_110`, Cohen's *d* = `r exp_all.d_110`; partners: *M~m~* = `r m_partner_all.mean_110`, *SD~m~* = `r m_partner_all.sd_110`, *M~w~* = `r f_partner_all.mean_110`, *SD~w~* = `r f_partner_all.sd_110`, Cohen's *d* = `r partner_all.d_110`), or when they had a lower mating standards (experiences: *M~m~* = `r m_exp_all.mean_101`, *SD~m~* = `r m_exp_all.sd_101`, *M~w~* = `r f_exp_all.mean_101`, *SD~w~* = `r f_exp_all.sd_101`, Cohen's *d* = `r exp_all.d_101`; partners: *M~m~* = `r m_partner_all.mean_101`, *SD~m~* = `r m_partner_all.sd_101`, *M~w~* = `r f_partner_all.mean_101`, *SD~w~* = `r f_partner_all.sd_101`, Cohen's *d* = `r partner_all.d_101`). In comparison, virtually no gender differences in short-term mating behaviors existed when gay men and lesbian women had the same short-term mating likelihood and mating standards (Table 2).

```{r table_2, include=TRUE, echo=FALSE}
results %>%
  filter(hls %in% c("1_0_0", "1_0_1", "1_1_0", "1_1_1")) %>%
  select(m_exp_all.mean, m_exp_all.sd,
         f_exp_all.mean, f_exp_all.sd, exp_all.d,
         m_partner_all.mean, m_partner_all.sd,
         f_partner_all.mean, f_partner_all.sd, partner_all.d) %>%
  mutate(
    exp_all.d = abs(exp_all.d),
    partner_all.d = abs(partner_all.d)
  ) %>%
  mutate(across(where(is.numeric), inline_hook)) %>%
  mutate(
    condition =
      c("Same likelihood*Same standard",
        "Same likelihood*Different standard",
        "Different likelihood*Same standard",
        "Different likelihood*Different standard")
  ) %>%
  column_to_rownames("condition") %>%
  kable(
    digits = 2, format = "latex", booktabs = TRUE,
    caption = "\\textbf{Short-term mating behaviors of gay men and lesbian women after 1,000 time steps in the model}",
    row.names = TRUE, col.names = c(rep(c(rep(c("M", "SD"), 2), "d"), 2))
    ) %>%
  row_spec(0, italic = TRUE, align = "c") %>%
  add_header_above(
    c(" " = 1,
      "Men" = 2, "Women" = 2, " " = 1,
      "Men" = 2, "Women" = 2, " " = 1)
    ) %>%
  add_header_above(
    c(" " = 1,
      "Average short-term mating\nexperiences" = 5,
      "Average short-term mates" = 5)
    ) %>%
  column_spec(1, width = "2in") %>%
  footnote(
    general = "\\\\textit{Note.} \\\\textit{N\\\\textsubscript{m}} = \\\\textit{N\\\\textsubscript{w}} = 150 in all conditions.",
    general_title = "", escape = FALSE,
    threeparttable = TRUE, fixed_small_size = TRUE) %>%
  kable_styling(latex_options = "scale_down")
```

# Discussion

The present study aimed at using agent-based modeling to investigate whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, specifically, in the number of short-term mating experiences and short-term mates, and if they did, under what circumstances. We raised two hypotheses: 1) there would be gender differences in short-term mating behaviors among gay men and lesbian women, with gay men being engaged in more such behaviors, and 2) gay men would engage in more short-term mating behaviors as compared to heterosexual men. The results from 1,000 time steps in a model simulating men and women's mating behaviors supported our hypotheses. First of all, as compared to lesbian women, gay men had a higher average number of short-term mating experiences and short-term mates. In contrast, we found no gender differences in short-term mating behaviors between heterosexual men and women. Secondly, gay men also had a higher average number of short-term mating experiences and short-term mates as compared to heterosexual men.

As we expected, heterosexual men and women did not differ in short-term mating behaviors despite their different mating preferences. This was because the total numbers of short-term mating experiences and short-term mates of heterosexual men and women were exactly the same. Since the sex ratio was 1:1 in our model, the average number of short-term mating experiences and short-term mates must be equal between men and women as well. However, we did find that among individuals in the mating pool, men engaged in more short-term mating behaviors as compared to women. This was because there were more women than men in the mating pool (i.e., had ever engaged in short-term mating behaviors), resulting in lower averages among heterosexual women despite equal numbers of experiences and mates in total.

Moreover, gender differences in short-term mating behaviors emerged when heterosexual men and women had different standards for short-term mates, but not when they had different likelihood of engaging in short-term mating. When women had a higher standard than men did, less men than women in the population were above a potential partner's standards and thus had a chance to have sex with them. This contributed to the unequal number of men and women in the mating pool, which led to gender differences in short-term mating behaviors.

In the light of these results, the empirical observation of gender differences in short-term mating behaviors among heterosexual individuals [e.g., @petersen_meta-analytic_2010] appear to be perplexing because this is theoretically illogical [e.g., @s_j_gurman_six_1989]. Possible explanations for these empirical results have to highlight caveats in the observation process. One possibility is that there was sampling bias in the observations [e.g., @wiederman_evolution_1998] since surveys regarding short-term mating behaviors may tend to attract individuals who already engage in such behaviors. Another possibility is that heterosexual men and women tend to report short-term mating behaviors differently. This difference may be a result of social desirability bias [@alexander_truth_2003] or due to men and women's different estimation strategies (e.g., men tend to round up) [@brown_estimating_1999].

Among gay men and lesbian women, large gender differences in short-term mating behaviors existed when men and women had different mating preferences, which was in line with empirical observations [e.g., @peplau_national_1997; @peplau_sexuality_2004]. This was probably because the number of short-term mating experiences and short-term mates no longer counted towards men and women simultaneously. Any gender differences in mating preferences would result in differences in behaviors. A closer look at the results did support this postulation. Either a difference in the likelihood of short-term mating or a difference in mating standards alone could contribute to gender differences in mating behaviors. This was perhaps because the former increased the probability of both parties of a given gay couple deciding to have short-term mating, and the latter increased the probability of both of them meeting each other's standards, as compared to the case of a given lesbian couple.

Supporting the idea that gay men's preferences for short-term mating were not constrained by those of women, we found that gay men engaged in more short-term mating behaviors as compared to heterosexual men. This was consistent with the empirical literature [e.g., @peplau_national_1997]. Interestingly, gay men and heterosexual men had the same likelihood of short-term mating and the same standards for short-term mates in our model. The only difference was a change in the preferences in their potential partners. When men's partners had a stronger preferences for short-term mating (i.e., having men vs. having women as potential partners), men also appeared to engage in more short-term mating behaviors.

# Conclusion

Using agent-based modeling, the present study theoretically explored the circumstances under which men and women's different mating preferences resulted in gender differences in short-term mating behaviors. We found when men (vs. women) had a stronger preferences for short-term mating, heterosexual men and women engaged in short-term mating behaviors to the same extent, while gay men engaged in more short-term mating behaviors as compared to lesbian women. We also found that gay men engaged in more short-term mating behaviors than heterosexual men did.

Theses results highlight the distinction between psychological preferences and behaviors in human mating. Individuals' mating behaviors do not only depend on one's own preferences, but are also constrained by partners' preferences. Future research in human mating should not only focus on the psychological aspect but also pay attention to the interaction between individuals' psychology and its context. These results also cast doubt to the prevalent belief in the gender differences in short-term mating behaviors, especially among heterosexual individuals. Our findings suggest that there may be factors in the observation process that lead to such differences. Future research in human sexuality should note such possibilities and interpret any observed gender differences in short-term mating behaviors cautiously.

# Acknowledgements

# Data availability

All models, data, and analysis code can be downloaded at: [link masked for peer review]

\newpage

# References {-}

<div id="refs"></div>

### 2022-05-11 submission/manuscript.tex
modified the plots and inline output, close #16

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  11pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\newcommand{\bcenter}{\begin{center}}
\newcommand{\ecenter}{\end{center}}
\newcommand{\btitlepage}{\begin{titlepage}}
\newcommand{\etitlepage}{\end{titlepage}}
\usepackage{setspace}\doublespacing
\usepackage{helvet}
\renewcommand*\familydefault{\sfdefault}
\usepackage{booktabs}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\begin{titlepage}

\begin{center}

\vspace*{30mm}

\hypertarget{this-is-an-awesome-title}{%
\section*{\texorpdfstring{\textbf{This is an awesome
title}}{This is an awesome title}}\label{this-is-an-awesome-title}}
\addcontentsline{toc}{section}{\textbf{This is an awesome title}}

\vspace{30mm}

Yurun Ying\textsuperscript{1}, Pekka
Santtila\textsuperscript{1,2,\(\dagger\)}

\textsuperscript{1} Faculty of Arts and Sciences, NYU Shanghai

\textsuperscript{2} NYU-ECNU Institute for Social Development at NYU
Shanghai

\end{center}

\vspace{40mm}

\textsuperscript{\(\dagger\)} To whom correspondence should be
addressed:

\end{titlepage}

\newpage

\hypertarget{abstract}{%
\section*{Abstract}\label{abstract}}
\addcontentsline{toc}{section}{Abstract}

\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Gender differences in sexual behaviors, especially short-term mating
behaviors, have been a well-documented phenomenon in human sexuality
research. For example, research has found that heterosexual men, as
compared to heterosexual women, have a higher average number of past
short-term sexual partners (Oliver \& Hyde, 1993; Petersen \& Hyde,
2010; Rissel et al., 2014), have short-term mating more frequently
(Petersen \& Hyde, 2010), and engage in extramarital sex more often
(Petersen \& Hyde, 2010). These gender differences have also been
observed between gay men and lesbian women (Bailey et al., 1994; Bryant
\& Demian, 1994; Peplau et al., 1997, 2004).

In the existing literature, gender differences in sexual behaviors are
not usually distinguished from those in attitudes towards or preferences
for short-term mating. Some researchers study gender differences on the
two levels simultaneously without a conceptual distinction (e.g.,
Petersen \& Hyde, 2010), whereas some implicitly equate the two,
assuming that behavioral differences are a direct expression of the
psychological ones (e.g., Schmitt et al., 2001).

Intuitive as this line of reasoning is, there are good reasons to doubt
its soundness. This is because any heterosexual sexual encounter
involves both a man and a woman (the frequency of encounters involving
more than two persons is negligible, (e.g., Herbenick et al., 2017). A
new short-term mating experience for a man is, therefore, also a new
experience for a woman, and the same logic applies to counting a new
short-term mate. As a result, the psychological differences in
short-term mating preferences may not result in behavioral ones in the
heterosexual case (Archer, 2019).

The present study took gender differences in mating preferences as an
assumption, which was proposed by sexual strategy theory (Buss \&
Schmitt, 1993) and repeatedly found support by empirical studies (e.g.,
Schmitt, 2003; Walter et al., 2020). Using an agent-based model, we
investigated whether men and women's different mating preferences
resulted in any gender differences in short-term mating behaviors,
specifically, in the number of short-term mating experiences and
short-term mates, and if they did, under what circumstances.

\hypertarget{gender-differences-in-short-term-mating-preferences}{%
\subsection{Gender differences in short-term mating
preferences}\label{gender-differences-in-short-term-mating-preferences}}

Gender differences in mating strategies have been studied in the light
of sexual strategy theory (Buss \& Schmitt, 1993). It posits that since
the minimum investment that men devote to their offspring (contribution
of sperm through one sexual act) is lower than that of women (gestation,
labor, and lactation), men tend to have short-term mating as a larger
part of their mating strategy than women do. This is because women's
high minimum investment leads to higher opportunity cost (vs.~men) if
they have sex with a suboptimal partner and give birth to offspring with
a low survival chance. As a result, men may have a greater interest in
short-term mating, desire a larger number of short-term mates in a given
period, and be less selective with respect to accepting a potential mate
(Buss \& Schmitt, 1993).

The hypotheses derived from sexual strategy theory have received
extensive support from empirical studies. For example, men reported to
be currently seeking short-term mates to a larger extent than women did
(Buss \& Schmitt, 1993; Schmitt et al., 2001; Schmitt, 2003), and a
larger proportion of them were in any way seeking short-term mates
(vs.~not seeking) (Schmitt, 2003). These have been found among U.S.
college students (Buss \& Schmitt, 1993; Schmitt et al., 2001) as well
as in ten world regions in a cross-cultural study (Schmitt, 2003).
Similarly, men across the world also reported to desire more short-term
sexual partners compared to women for a number of given time periods
(e.g., a month, a year) (Buss \& Schmitt, 1993; McBurney et al., 2005;
Schmitt, 2003). The gender differences were significant regardless of
whether they were estimated by mean (Buss \& Schmitt, 1993; Schmitt et
al., 2001; Schmitt, 2003), median (Schmitt et al., 2001; Schmitt, 2003),
or percentage (Schmitt, 2003) statistics.

As for mating standards, men are more likely to accept someone as a
potential short-term mate. For example, studies using U.S. college
samples found that the minimum percentile ranks that men found
acceptable for a potential short-term sexual partner were lower than for
women both overall and on individual traits (e.g., social status,
attractiveness) (Kenrick et al., 1990; Regan, 1998). A study also found
that when presented with identical descriptions of potential mates, men
on average rated them as more desirable than women did (Wiederman \&
Dubois, 1998).

Some evidence shows that sexual strategy theory also predicts mating
preferences among gay men and lesbian women. A survey study using a
community sample from the U.S. found that gay men were more interested
in short-term mating than lesbian women and that this gender difference
was comparable to that existing among heterosexual individuals (Bailey
et al., 1994). An indirect piece of evidence on differential standards
for short-term mates comes from a recent study finding that
significantly more gay men than lesbian women reported to have accepted
a casual sexual offer from a same-gender person (Matsick et al., 2021).
Past studies suggest that the gender difference in the acceptance rate
of casual sexual offers may originate from men and women's differential
standards for short-term mates (Conley et al., 2011; Hald \&
Høgh-Olesen, 2010). Thus, as a postulation, gay men and lesbian women
may also have different standards for short-term mates.

\hypertarget{constraints-on-mens-preferences-for-short-term-mating}{%
\subsection{Constraints on men's preferences for short-term
mating}\label{constraints-on-mens-preferences-for-short-term-mating}}

Since heterosexual sex involves both a man and a woman in most cases,
men's interest in short-term mating can be constrained by women's
preference for long-term relationships (Archer, 2019; Symons, 1979).
This is because men's short-term mating preferences can only translate
into behaviors when there are women willing to have sex with them. When
short-term mating occurs, the number of short-term mating encounters and
short-term mates is essentially the same for men and women (although
this does not necessarily mean that the total number of men and women
who have ever had short-term mating must be equal). Therefore, we would
expect to observe no gender difference in short-term mating behaviors
among heterosexual individuals even when there were gender differences
in mating preferences.

As a comparison, in the cases of gay men and lesbian women, men's
preferences are not constrained by women's, but only by those of other
men, who, arguably, have more similar preferences. This would allow for
a more direct behavioral expression of men's mating preferences. The
notion that gay men have less restricted preferences was borne out in
the proportion of individuals who have engaged in extradyadic sex
(Peplau et al., 2004). A study showed that the proportions of
heterosexual men and women who have engaged in extradyadic sex were 26\%
and 21\%, respectively, while the statistics among gay men and lesbian
women were 82\% and 28\%, respectively (Peplau et al., 2004). Therefore,
we would theoretically expect to observe gender differences in
short-term mating behaviors among gay men and lesbians. Moreover, we
would also expect to find that gay men, as compared to heterosexual men,
engaged in more short-term mating behaviors due to the lessened
constraint on their mating preferences.

\hypertarget{a-simple-model-of-short-term-mating-behaviors}{%
\subsection{A simple model of short-term mating
behaviors}\label{a-simple-model-of-short-term-mating-behaviors}}

By using a spatial agent-based model, the present study investigated
whether men and women's different mating preferences resulted in any
gender differences in short-term mating behaviors, and if they did,
under what circumstances. The interest in short-term mating was modeled
as an individual's likelihood of deciding to have short-term mating at
each time step. The standards for short-term mates were modeled as the
minimum desirability of a potential mate with whom an individual was
willing to have sex. Short-term mating behaviors were operationally
defined as the number of short-term mating experiences and the number of
past short-term mates.

We modeled this process among both heterosexual individuals and gay men
and lesbian women to examine whether constraints set by the opposite
sex's preferences would make a difference in short-term mating
behaviors. Individuals' sexual orientation was conceptualized in terms
of behaviors only in our model. Heterosexual men had short-term mating
or formed a long-term relationship with women, while gay men only with
other men, and vice versa for women.

We raised the following hypotheses in the present study: when there were
gender differences in preferences for short-term mating, 1) there would
be gender differences in short-term mating behaviors among gay men and
lesbian women, with gay men being engaged in more such behaviors, and 2)
gay men would engage in more short-term mating behaviors as compared to
heterosexual men.

\hypertarget{material-and-methods}{%
\section{Material and methods}\label{material-and-methods}}

\hypertarget{model-design}{%
\subsection{Model Design}\label{model-design}}

We developed an agent-based model to represent a simplified environment
where men and women can move around, search for mates, and form
long-term and/or short-term relationships. Space and time are modeled as
discrete variables. Space was represented as discrete locations on a
two-dimensional 33*33 lattice. Agents' movement in the space was not
meant to simulate physical movement but a state of encountering
potential mates. Staying at one location represented being committed to
a long-term relationship.

The model measured \textbf{three} outcomes: (1) the number of men and
women who had ever engaged in short-term mating \textbf{put this to the
end}; (2) the number of short-term mating experiences of men and women;
(3) the number of short-term mates of men and women. The number of
short-term mating experienced and short-term mates were calculated by
taking the average among the whole men/women population and among those
who had engaged in short-term mating.

See the Supplemental Materials for the overview, design concepts, and
details (ODD) protocol of the model, which includes detailed scheduling
and parameterization. The model can be downloaded from the Github online
repository {[}link masked for peer review{]}. The model was programmed
in Netlogo 6.2.1 (Wilensky, 1999).

\hypertarget{experiment-design}{%
\subsection{Experiment Design}\label{experiment-design}}

Using the agent-based model, the present study conducted two 2 (gender
difference vs.~no difference in short-term mating likelihood) x 2
(gender difference vs.~no difference in mating standard) experiments.
Experiment 1 was run among heterosexual agents who only engaged in
short-term or long-term relationships with agents of the opposite
gender. Experiment 2 was run among gay men and lesbian women who only
engaged in short-term or long-term relationships with agents of the same
gender.

Gender differences were modeled in agents' likelihood of engaging in
short-term mating and the standard for short-term mates. The values of
these parameters were set based on empirical findings in human mating
psychology. We compared the conditions where there were gender
differences in mating preferences with counterfactual conditions where
gender differences were missing. When there was a gender difference in
short-term mating likelihood, men had a 40\% likelihood of deciding to
engage in short-term mating upon meeting a potential mate, while women
had a likelihood of 25\% (Buss \& Schmitt, 1993; Schmitt et al., 2001;
Schmitt, 2003). When there was no gender difference in short-term mating
likelihood, both women and men had a likelihood of 25\%. When there was
a gender difference in mating standards, men had a mating standard of 3
(the minimum mate value of a potential partner with whom an agent is
willing to have short-term mating, highest possible value = 10), while
women had a standard of 5 (Kenrick et al., 1990; Regan, 1998). When
there was no gender difference in mating standards, both men and women
had a standard of 5.

\hypertarget{model-schedule}{%
\subsection{Model Schedule}\label{model-schedule}}

\hypertarget{initial-setup}{%
\subsubsection{Initial setup}\label{initial-setup}}

In total, 150 women and 150 men were created on the lattice at random
locations. All agents were initialized with (1) a three-unit maximum
distance by which agents can move away from their birthplace (movement
range); (2) a 10\% likelihood of two agents forming a long-term
relationship upon meeting; (3) single status and no long-term partner;
(4) a mate value, sampled from a Gaussian distribution (\emph{M} = 5,
\emph{SD} = 1.5); (5) no short-term mate or short-term mating history.

The likelihood of engaging in short-term mating and the standard for
short-term mates were initialized either the same or differently for men
and women, depending on the experimental conditions.

\hypertarget{procedures}{%
\subsubsection{Procedures}\label{procedures}}

\hypertarget{heterosexual-procedures.}{%
\paragraph{Heterosexual procedures.}\label{heterosexual-procedures.}}

At each time step, agents first checked whether they were in a long-term
relationship. If they were not in a long-term relationship, they set
their heading randomly (if they were within the movement range from the
birthplace) or faced the birthplace (if they were out of the movement
range from the birthplace) and moved by a random distance. The random
distance was less than half of the movement range. If they were in a
long-term relationship, they did not move. Then, the agents decided on
whether to engage in short-term mating by a chance of the chosen
likelihood (either 25\% or 40\%).

Women checked to see if any men were at the same location. If there
were, they randomly chose one of them as their potential short-term
mate. If both men and women met each other's mating standards and both
of them decided to engage in short-term mating, they had sex. This would
result in increasing both parties' number of short-term mating
experiences by one. They also recorded each other on their lists of past
short-term mates if they were not on the lists yet.

Then, women randomly selected one man at the same location as their
potential long-term partner. There was a 10\% of chance that a pair
would form a long-term relationship. After forming a long-term
relationship, both men and women changed to coupled status and register
each other as the long-term partner.

\hypertarget{gay-men-and-lesbian-women-procedures.}{%
\paragraph{Gay men and lesbian women
procedures.}\label{gay-men-and-lesbian-women-procedures.}}

At each time step, men and women moved and decided on short-term mating
as the agents did in the heterosexual procedures. Half of the agents (an
equal number of men and women) were also given the initiator status. The
initiators checked to see whether there were other agents at the same
location. The rest of the procedures were identical to the heterosexual
procedures, except that the agents only chose those with the same gender
as themselves as potential short-term mates or long-term partners.

\hypertarget{simulations}{%
\subsection{Simulations}\label{simulations}}

The model was run for 1,000 time steps in each simulation. We ran 10,000
simulations for each experiment, and 2,500 simulations for each
condition. We controlled for initializing random seeds in the model
runs. All simulations were run using Netlogo 6.2.1 (Wilensky, 1999).

\hypertarget{statistical-analysis}{%
\subsection{Statistical analysis}\label{statistical-analysis}}

Statistical analyses were conducted using R version 4.1.3 (R Core Team,
2022) and the figures were generated by the ggplot2 package (Wickham,
2016). Two-tailed independent samples \emph{t}-tests were used for all
statistical comparisons. The data were assumed to be normally
distributed within each condition but was not formally tested.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{gender-differences-in-short-term-mating-behaviors-in-each-experiment}{%
\subsection{Gender differences in short-term mating behaviors in each
experiment}\label{gender-differences-in-short-term-mating-behaviors-in-each-experiment}}

The results from Experiment 1 showed that when there were gender
differences in preferences for short-term mating, there was no gender
difference in the average number of short-term mating experiences among
heterosexual individuals (\emph{M\textsubscript{m}} = 1.43,
\emph{SD\textsubscript{m}} = 0.24; \emph{M\textsubscript{w}} = 1.43,
\emph{SD\textsubscript{w}} = 0.24), Cohen's \emph{d} = 0. Nor was there
a difference in the average number of short-term mates
(\emph{M\textsubscript{m}} = 0.80, \emph{SD\textsubscript{m}} = 0.11;
\emph{M\textsubscript{w}} = 0.80, \emph{SD\textsubscript{w}} = 0.11),
Cohen's \emph{d} = 0 (Figure 1).

\begin{figure}[h]
  \centering
  \includegraphics[width=80mm]{figures/fig1_men_vs_women.pdf}
  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. Statistics were calculated using the full population of men and women in the model (\textit{N\textsubscript{m}} = \textit{N\textsubscript{w}} = 150).}
\end{figure}

The results from Experiment 2 showed that when there were gender
differences in preferences for short-term mating, there were gender
differences in short-term mating behaviors between gay men and lesbian
women (Figure 1). The average number of short-term mating experiences
was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37) than among
lesbian women (\emph{M} = 0.32, \emph{SD} = 0.10), \emph{t}(4,998) =
-301.78, \emph{p} \textless{} .001, Cohen's \emph{d} = 8.54. Similarly,
the average number of short-term mates was higher among gay men
(\emph{M} = 1.72, \emph{SD} = 0.19) than among lesbian women (\emph{M} =
0.25, \emph{SD} = 0.07), \emph{t}(4,998) = -357.69, \emph{p} \textless{}
.001, Cohen's \emph{d} = 10.12.

In Experiment 1, however, when the means of the outcome variables were
calculated among men and women who were in the mating pool (i.e., those
with a non-zero number of short-term mating experiences) \textbf{(the
number of individuals in the mating pool: M\textsubscript{m},
SD\textsubscript{m}; M\textsubscript{w}, SD\textsubscript{w})}, there
were gender differences in short-term mating behaviors when there were
gender differences in mating preferences. The average number of
short-term mating experiences was higher among heterosexual men
(\emph{M} = 3.78, \emph{SD} = 0.50) than among heterosexual women
(\emph{M} = 2.79, \emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p}
\textless{} .001, Cohen's \emph{d} = 2.31. Likewise, the average number
of short-term mates was higher among heterosexual men (\emph{M} = 2.12,
\emph{SD} = 0.17) than among heterosexual women (\emph{M} = 1.56,
\emph{SD} = 0.11), \emph{t}(4,998) = -135.85, \emph{p} \textless{} .001,
Cohen's \emph{d} = 3.84.

\hypertarget{comparing-short-term-mating-behaviors-of-heterosexual-and-gay-men}{%
\subsection{Comparing short-term mating behaviors of heterosexual and
gay
men}\label{comparing-short-term-mating-behaviors-of-heterosexual-and-gay-men}}

The results comparing across the two experiments revealed that gay men
engaged in short-term mating behaviors more than heterosexual men did
(Figure 2). The average number of short-term mating experiences was
higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37) than among
heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24), \emph{t}(4,998) =
-134.87, \emph{p} \textless{} .001, Cohen's \emph{d} = 3.81. Similarly,
the average number of short-term mates was higher among gay men
(\emph{M} = 1.72, \emph{SD} = 0.19) than among heterosexual men
(\emph{M} = 0.80, \emph{SD} = 0.11), \emph{t}(4,998) = -206.91, \emph{p}
\textless{} .001, Cohen's \emph{d} = 5.85.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figures/fig2_hetero_vs_gay_men.pdf}
  \caption{\textbf{Short-term mating behaviors of heterosexual and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables. Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates. Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar. Statistics were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hm}} = \textit{N\textsubscript{gm}} = 150).}
\end{figure}

\hypertarget{comparing-across-conditions}{%
\subsection{Comparing across
conditions}\label{comparing-across-conditions}}

In an exploratory manner, we also compared across conditions to see
which of the two dimensions of preferences for short-term mating
contributed to gender differences in sexual behaviors.

Among heterosexual individuals, gender differences in short-term mating
behaviors, as calculated among individuals in the mating pool, emerged
when men and women had different standards for short-term mates.
Heterosexual men in the mating pool had a higher average number of
short-term mating experiences and short-term mates than women in the
mating pool, even when no gender difference existed in short-term mating
likelihood (experiences: \emph{M\textsubscript{m}} = 2.82,
\emph{SD\textsubscript{m}} = 0.36, \emph{M\textsubscript{w}} = 2.21,
\emph{SD\textsubscript{w}} = 0.28, Cohen's \emph{d} = 1.89; partners:
\emph{M\textsubscript{m}} = 1.76, \emph{SD\textsubscript{m}} = 0.15;
\emph{M\textsubscript{w}} = 1.38, \emph{SD\textsubscript{w}} = 0.09,
Cohen's \emph{d} = 3.13). In comparison, virtually no gender differences
in short-term mating behaviors existed when men and women had the same
mating standards (Table 1).

\begin{table}

\caption{\label{tab:table_1}\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model}}
\centering
\begin{threeparttable}
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2in}llllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\makecell[c]{Average short-term mating\\experiences (in-pool)}} & \multicolumn{5}{c}{\makecell[c]{Average short-term\\mates (in-pool)}} \\
\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-11}
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){7-8} \cmidrule(l{3pt}r{3pt}){9-10}
\multicolumn{1}{c}{\em{ }} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{d}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{d}}\\
\midrule
Same likelihood*Same standard & 2.21 & 0.38 & 2.20 & 0.37 & 0.03 & 1.39 & 0.12 & 1.39 & 0.12 & 0.04\\
Same likelihood*Different standard & 2.82 & 0.36 & 2.21 & 0.28 & 1.89 & 1.76 & 0.15 & 1.38 & 0.09 & 3.13\\
Different likelihood*Same standard & 2.80 & 0.48 & 2.78 & 0.47 & 0.03 & 1.57 & 0.14 & 1.56 & 0.14 & 0.05\\
Different likelihood*Different standard & 3.78 & 0.50 & 2.79 & 0.35 & 2.31 & 2.12 & 0.17 & 1.56 & 0.11 & 3.84\\
\bottomrule
\end{tabular}}
\begin{tablenotes}
\small
\item \textit{Note.} The statistics were calculated with subsamples of men and women who had had enagged in short-term mating behaviors. See Supplementary Materials for the mean and standard deviation of sample sizes.
\end{tablenotes}
\end{threeparttable}
\end{table}

Among gay men and lesbian women, gender differences in short-term mating
behaviors emerged either when they had different short-term mating
likelihood or when their mating standards were different. Gay men had a
higher average number of short-term mating experiences and short-term
mates when they had a higher short-term mating likelihood than lesbian
women (experiences: \emph{M\textsubscript{m}} = 0.80,
\emph{SD\textsubscript{m}} = 0.23, \emph{M\textsubscript{w}} = 0.32,
\emph{SD\textsubscript{w}} = 0.10, Cohen's \emph{d} = 2.67; partners:
\emph{M\textsubscript{m}} = 0.52, \emph{SD\textsubscript{m}} = 0.13,
\emph{M\textsubscript{w}} = 0.25, \emph{SD\textsubscript{w}} = 0.07,
Cohen's \emph{d} = 2.60), or when they had a lower mating standards
(experiences: \emph{M\textsubscript{m}} = 1.05,
\emph{SD\textsubscript{m}} = 0.18, \emph{M\textsubscript{w}} = 0.32,
\emph{SD\textsubscript{w}} = 0.10, Cohen's \emph{d} = 5.10; partners:
\emph{M\textsubscript{m}} = 0.82, \emph{SD\textsubscript{m}} = 0.12,
\emph{M\textsubscript{w}} = 0.25, \emph{SD\textsubscript{w}} = 0.07,
Cohen's \emph{d} = 5.78). In comparison, virtually no gender differences
in short-term mating behaviors existed when gay men and lesbian women
had the same short-term mating likelihood and mating standards (Table
2).

\begin{table}

\caption{\label{tab:table_2}\textbf{Short-term mating behaviors of gay men and lesbian women after 1,000 time steps in the model}}
\centering
\begin{threeparttable}
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2in}llllllllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\makecell[c]{Average short-term mating\\experiences}} & \multicolumn{5}{c}{Average short-term mates} \\
\cmidrule(l{3pt}r{3pt}){2-6} \cmidrule(l{3pt}r{3pt}){7-11}
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){7-8} \cmidrule(l{3pt}r{3pt}){9-10}
\multicolumn{1}{c}{\em{ }} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{d}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{d}}\\
\midrule
Same likelihood*Same standard & 0.32 & 0.10 & 0.32 & 0.10 & 0.04 & 0.25 & 0.07 & 0.25 & 0.07 & 0.03\\
Same likelihood*Different standard & 1.05 & 0.18 & 0.32 & 0.10 & 5.10 & 0.82 & 0.12 & 0.25 & 0.07 & 5.78\\
Different likelihood*Same standard & 0.80 & 0.23 & 0.32 & 0.10 & 2.67 & 0.52 & 0.13 & 0.25 & 0.07 & 2.60\\
Different likelihood*Different standard & 2.63 & 0.37 & 0.32 & 0.10 & 8.54 & 1.72 & 0.19 & 0.25 & 0.07 & 10.12\\
\bottomrule
\end{tabular}}
\begin{tablenotes}
\small
\item \textit{Note.} \textit{N\textsubscript{m}} = \textit{N\textsubscript{w}} = 150 in all conditions.
\end{tablenotes}
\end{threeparttable}
\end{table}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The present study aimed at using agent-based modeling to investigate
whether men and women's different mating preferences resulted in any
gender differences in short-term mating behaviors, specifically, in the
number of short-term mating experiences and short-term mates, and if
they did, under what circumstances. We raised two hypotheses: 1) there
would be gender differences in short-term mating behaviors among gay men
and lesbian women, with gay men being engaged in more such behaviors,
and 2) gay men would engage in more short-term mating behaviors as
compared to heterosexual men. The results from 1,000 time steps in a
model simulating men and women's mating behaviors supported our
hypotheses. First of all, as compared to lesbian women, gay men had a
higher average number of short-term mating experiences and short-term
mates. In contrast, we found no gender differences in short-term mating
behaviors between heterosexual men and women. Secondly, gay men also had
a higher average number of short-term mating experiences and short-term
mates as compared to heterosexual men.

As we expected, heterosexual men and women did not differ in short-term
mating behaviors despite their different mating preferences. This was
because the total numbers of short-term mating experiences and
short-term mates of heterosexual men and women were exactly the same.
Since the sex ratio was 1:1 in our model, the average number of
short-term mating experiences and short-term mates must be equal between
men and women as well. However, we did find that among individuals in
the mating pool, men engaged in more short-term mating behaviors as
compared to women. This was because there were more women than men in
the mating pool (i.e., had ever engaged in short-term mating behaviors),
resulting in lower averages among heterosexual women despite equal
numbers of experiences and mates in total.

Moreover, gender differences in short-term mating behaviors emerged when
heterosexual men and women had different standards for short-term mates,
but not when they had different likelihood of engaging in short-term
mating. When women had a higher standard than men did, less men than
women in the population were above a potential partner's standards and
thus had a chance to have sex with them. This contributed to the unequal
number of men and women in the mating pool, which led to gender
differences in short-term mating behaviors.

In the light of these results, the empirical observation of gender
differences in short-term mating behaviors among heterosexual
individuals (e.g., Petersen \& Hyde, 2010) appear to be perplexing
because this is theoretically illogical (e.g., Gurman, 1989). Possible
explanations for these empirical results have to highlight caveats in
the observation process. One possibility is that there was sampling bias
in the observations (e.g., Wiederman \& Dubois, 1998) since surveys
regarding short-term mating behaviors may tend to attract individuals
who already engage in such behaviors. Another possibility is that
heterosexual men and women tend to report short-term mating behaviors
differently. This difference may be a result of social desirability bias
(Alexander \& Fisher, 2003) or due to men and women's different
estimation strategies (e.g., men tend to round up) (Brown \& Sinclair,
1999).

Among gay men and lesbian women, large gender differences in short-term
mating behaviors existed when men and women had different mating
preferences, which was in line with empirical observations (e.g., Peplau
et al., 1997, 2004). This was probably because the number of short-term
mating experiences and short-term mates no longer counted towards men
and women simultaneously. Any gender differences in mating preferences
would result in differences in behaviors. A closer look at the results
did support this postulation. Either a difference in the likelihood of
short-term mating or a difference in mating standards alone could
contribute to gender differences in mating behaviors. This was perhaps
because the former increased the probability of both parties of a given
gay couple deciding to have short-term mating, and the latter increased
the probability of both of them meeting each other's standards, as
compared to the case of a given lesbian couple.

Supporting the idea that gay men's preferences for short-term mating
were not constrained by those of women, we found that gay men engaged in
more short-term mating behaviors as compared to heterosexual men. This
was consistent with the empirical literature (e.g., Peplau et al.,
1997). Interestingly, gay men and heterosexual men had the same
likelihood of short-term mating and the same standards for short-term
mates in our model. The only difference was a change in the preferences
in their potential partners. When men's partners had a stronger
preferences for short-term mating (i.e., having men vs.~having women as
potential partners), men also appeared to engage in more short-term
mating behaviors.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

Using agent-based modeling, the present study theoretically explored the
circumstances under which men and women's different mating preferences
resulted in gender differences in short-term mating behaviors. We found
when men (vs.~women) had a stronger preferences for short-term mating,
heterosexual men and women engaged in short-term mating behaviors to the
same extent, while gay men engaged in more short-term mating behaviors
as compared to lesbian women. We also found that gay men engaged in more
short-term mating behaviors than heterosexual men did.

Theses results highlight the distinction between psychological
preferences and behaviors in human mating. Individuals' mating behaviors
do not only depend on one's own preferences, but are also constrained by
partners' preferences. Future research in human mating should not only
focus on the psychological aspect but also pay attention to the
interaction between individuals' psychology and its context. These
results also cast doubt to the prevalent belief in the gender
differences in short-term mating behaviors, especially among
heterosexual individuals. Our findings suggest that there may be factors
in the observation process that lead to such differences. Future
research in human sexuality should note such possibilities and interpret
any observed gender differences in short-term mating behaviors
cautiously.

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

\hypertarget{data-availability}{%
\section{Data availability}\label{data-availability}}

All models, data, and analysis code can be downloaded at: {[}link masked
for peer review{]}

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-alexander_truth_2003}{}}%
Alexander, M. G., \& Fisher, T. D. (2003). Truth and consequences: Using
the bogus pipeline to examine sex differences in self‐reported
sexuality. \emph{The Journal of Sex Research}, \emph{40}(1), 27--35.
\url{https://doi.org/10.1080/00224490309552164}

\leavevmode\vadjust pre{\hypertarget{ref-archer_reality_2019}{}}%
Archer, J. (2019). The reality and evolutionary significance of human
psychological sex differences. \emph{Biological Reviews}, \emph{94}(4),
1381--1415. \url{https://doi.org/10.1111/brv.12507}

\leavevmode\vadjust pre{\hypertarget{ref-bailey_effects_1994}{}}%
Bailey, J. M., Gaulin, S., Agyei, Y., \& Gladue, B. A. (1994). Effects
of gender and sexual orientation on evolutionarily relevant aspects of
human mating psychology. \emph{Journal of Personality and Social
Psychology}, \emph{66}(6), 1081--1093.
\url{https://doi.org/10.1037/0022-3514.66.6.1081}

\leavevmode\vadjust pre{\hypertarget{ref-brown_estimating_1999}{}}%
Brown, N. R., \& Sinclair, R. C. (1999). Estimating number of lifetime
sexual partners: Men and women do it differently. \emph{The Journal of
Sex Research}, \emph{36}(3), 292--297.
\url{https://doi.org/10.1080/00224499909551999}

\leavevmode\vadjust pre{\hypertarget{ref-bryant_relationship_1994}{}}%
Bryant, A. S., \& Demian. (1994). Relationship characteristics of
american gay and lesbian couples. \emph{Journal of Gay \& Lesbian Social
Services}, \emph{1}(2), 101--117.
\url{https://doi.org/10.1300/J041v01n02_06}

\leavevmode\vadjust pre{\hypertarget{ref-buss_sexual_1993}{}}%
Buss, D. M., \& Schmitt, D. P. (1993). Sexual strategies theory: An
evolutionary perspective on human mating. \emph{Psychological Review},
\emph{100}(2), 204--232.
\url{https://doi.org/doi:10.1037/0033-295X.100.2.204d}

\leavevmode\vadjust pre{\hypertarget{ref-conley_women_2011}{}}%
Conley, T. D., Moors, A. C., Matsick, J. L., Ziegler, A., \& Valentine,
B. A. (2011). Women, men, and the bedroom: Methodological and conceptual
insights that narrow, reframe, and eliminate gender differences in
sexuality. \emph{Current Directions in Psychological Science},
\emph{20}(5), 296--300. \url{https://doi.org/10.1177/0963721411418467}

\leavevmode\vadjust pre{\hypertarget{ref-s_j_gurman_six_1989}{}}%
Gurman, S. J. (1989). Six of one... \emph{Nature}, \emph{12}, 342.
\url{https://www.nature.com/articles/342012d0}

\leavevmode\vadjust pre{\hypertarget{ref-hald_receptivity_2010}{}}%
Hald, G. M., \& Høgh-Olesen, H. (2010). Receptivity to sexual
invitations from strangers of the opposite gender. \emph{Evolution and
Human Behavior}, \emph{31}(6), 453--458.
\url{https://doi.org/10.1016/j.evolhumbehav.2010.07.004}

\leavevmode\vadjust pre{\hypertarget{ref-herbenick_sexual_2017}{}}%
Herbenick, D., Bowling, J., Fu, T.-C. (Jane)., Dodge, B., Guerra-Reyes,
L., \& Sanders, S. (2017). Sexual diversity in the {United States}:
Results from a nationally representative probability sample of adult
women and men. \emph{{PLOS} {ONE}}, \emph{12}(7), e0181198.
\url{https://doi.org/10.1371/journal.pone.0181198}

\leavevmode\vadjust pre{\hypertarget{ref-kenrick_evolution_1990}{}}%
Kenrick, D. T., Sadalla, E. K., Groth, G., \& Trost, M. R. (1990).
Evolution, traits, and the stages of human courtship: Qualifying the
parental investment model. \emph{Journal of Personality}, \emph{58}(1),
97--116. \url{https://doi.org/10.1111/j.1467-6494.1990.tb00909.x}

\leavevmode\vadjust pre{\hypertarget{ref-matsick_gender_2021}{}}%
Matsick, J. L., Kruk, M., Conley, T. D., Moors, A. C., \& Ziegler, A.
(2021). Gender similarities and differences in casual sex acceptance
among lesbian women and gay men. \emph{Archives of Sexual Behavior},
\emph{50}(3), 1151--1166.
\url{https://doi.org/10.1007/s10508-020-01864-y}

\leavevmode\vadjust pre{\hypertarget{ref-mcburney_preferred_2005}{}}%
McBurney, D. H., Zapp, D. J., \& Streeter, S. A. (2005). Preferred
number of sexual partners: Tails of distributions and tales of mating
systems. \emph{Evolution and Human Behavior}, \emph{26}(3), 271--278.
\url{https://doi.org/10.1016/j.evolhumbehav.2004.09.005}

\leavevmode\vadjust pre{\hypertarget{ref-oliver_gender_1993}{}}%
Oliver, M. B., \& Hyde, J. S. (1993). Gender differences in sexuality: A
meta-analysis. \emph{Psychological Bulletin}, \emph{114}(1), 29--51.
https://doi.org/\url{http://dx.doi.org/10.1037/0033-2909.114.1.29}

\leavevmode\vadjust pre{\hypertarget{ref-peplau_national_1997}{}}%
Peplau, L. A., Cochran, S. D., \& Mays, V. (1997). A national survey of
the intimate relationships of african american lesbians and gay men: A
look at commitment, satisfaction, sexual behavior, and {HIV} disease. In
\emph{Ethnic and cultural diversity among lesbians and gay men} (pp.
11--38). Sage Publications.

\leavevmode\vadjust pre{\hypertarget{ref-peplau_sexuality_2004}{}}%
Peplau, L. A., Fingerhut, A., \& Beals, K. P. (2004). Sexuality in the
relationships of lesbians and gay men. In \emph{The handbook of
sexuality in close relationships} (pp. 349--369). Lawrence Erlbaum
Associates Publishers.

\leavevmode\vadjust pre{\hypertarget{ref-petersen_meta-analytic_2010}{}}%
Petersen, J. L., \& Hyde, J. S. (2010). A meta-analytic review of
research on gender differences in sexuality, 1993--2007.
\emph{Psychological Bulletin}, \emph{136}(1), 21--38.
\url{https://doi.org/10.1037/a0017504}

\leavevmode\vadjust pre{\hypertarget{ref-r}{}}%
R Core Team. (2022). \emph{R: A language and environment for statistical
computing}. R Foundation for Statistical Computing.
\url{https://www.R-project.org/}

\leavevmode\vadjust pre{\hypertarget{ref-regan_minimum_1998}{}}%
Regan, P. C. (1998). Minimum mate selection standards as a function of
perceived mate value, relationship context, and gender. \emph{Journal of
Psychology \& Human Sexuality}, \emph{10}(1), 53--73.
\url{https://doi.org/10.1300/J056v10n01_04}

\leavevmode\vadjust pre{\hypertarget{ref-rissel_heterosexual_2014}{}}%
Rissel, C., Badcock, P. B., Smith, A. M. A., Richters, J., Visser, R. O.
de, Grulich, A. E., Simpson, J. M., Rissel, C., Badcock, P. B., Smith,
A. M. A., Richters, J., Visser, R. O. de, Grulich, A. E., \& Simpson, J.
M. (2014). Heterosexual experience and recent heterosexual encounters
among {A}ustralian adults: The second {A}ustralian study of health and
relationships. \emph{Sexual Health}, \emph{11}(5), 416--426.
\url{https://doi.org/10.1071/SH14105}

\leavevmode\vadjust pre{\hypertarget{ref-schmitt_universal_2003}{}}%
Schmitt, D. P. (2003). Universal sex differences in the desire for
sexual variety: Tests from 52 nations, 6 continents, and 13 islands.
\emph{Journal of Personality and Social Psychology}, \emph{85}(1), 85.
\url{https://doi.org/10.1037/0022-3514.85.1.85}

\leavevmode\vadjust pre{\hypertarget{ref-schmitt_are_2001}{}}%
Schmitt, D. P., Shackelford, T. K., \& Buss, D. M. (2001). Are men
really more 'oriented' toward short-term mating than women? A critical
review of theory and research. \emph{Psychology, Evolution \& Gender},
\emph{3}(3), 211--239. \url{https://doi.org/10.1080/14616660110119331}

\leavevmode\vadjust pre{\hypertarget{ref-symons_evolution_1979}{}}%
Symons, D. (1979). \emph{The evolution of human sexuality}. Oxford
University Press.

\leavevmode\vadjust pre{\hypertarget{ref-walter_sex_2020}{}}%
Walter, K. V., Conroy-Beam, D., Buss, D. M., Asao, K., Sorokowska, A.,
Sorokowski, P., Aavik, T., Akello, G., Alhabahba, M. M., Alm, C., Amjad,
N., Anjum, A., Atama, C. S., Atamtürk Duyar, D., Ayebare, R., Batres,
C., Bendixen, M., Bensafia, A., Bizumic, B., \ldots{} Zupančič, M.
(2020). Sex differences in mate preferences across 45 countries: A
large-scale replication. \emph{Psychological Science}, \emph{31}(4),
408--423. \url{https://doi.org/10.1177/0956797620904154}

\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
Wickham, H. (2016). \emph{{ggplot2: Elegant Graphics for Data
Analysis}}. Springer-Verlag New York.
\url{https://ggplot2.tidyverse.org}

\leavevmode\vadjust pre{\hypertarget{ref-wiederman_evolution_1998}{}}%
Wiederman, M. W., \& Dubois, S. L. (1998). Evolution and sex differences
in preferences for short-term mates: Results from a policy capturing
study. \emph{Evolution and Human Behavior}, \emph{19}(3), 153--170.
\url{https://doi.org/10.1016/S1090-5138(98)00006-3}

\leavevmode\vadjust pre{\hypertarget{ref-wilensky_1999}{}}%
Wilensky, U. (1999). \emph{NetLogo}
{[}Http://ccl.northwestern.edu/netlogo/{]}. Center for Connected
Learning; Computer-Based Modeling.
\url{http://ccl.northwestern.edu/netlogo/}

\end{CSLReferences}

\end{document}

### 2022-05-11 code/compare_hetero_gay_men.R

@@ -9,8 +9,11 @@
 
 library(tidyverse); library(magrittr); library(here); library(broom); library(effectsize)
 
-input_file <- commandArgs(trailingOnly = TRUE)
-output_file <- "data/processed/compare_hetero_gay_men.csv"
+args <- commandArgs(trailingOnly = TRUE)
+#args <- c("data/processed/casual_sex_sim.csv", "data/processed/compare_hetero_gay_men.csv")
+
+input_file <- args[1]
+output_file <- args[2]
 
 casual_tib <- here(input_file) %>% 
   read_csv() %>% 
@@ -44,18 +47,18 @@ casual_t_test <-
   casual_long %>% 
   nest_by(dlikelihood_dstandard) %>% 
   mutate(
-    m_inpool = t.test(m_inpool ~ homosexual, data = data) %>% tidy() %>% 
+    m_inpool = t.test(m_inpool ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
       select(statistic, p.value, parameter),
-    m_outpool = t.test(m_outpool ~ homosexual, data = data) %>% tidy() %>% 
+    m_outpool = t.test(m_outpool ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
       select(statistic, p.value, parameter),
-    m_exp_all = t.test(m_exp_all ~ homosexual, data = data) %>% tidy() %>% 
+    m_exp_all = t.test(m_exp_all ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
       # somehow the map function doesn't work here and I wonder why...
       select(statistic, p.value, parameter),
-    m_exp_ip = t.test(m_exp_ip ~ homosexual, data = data) %>% tidy() %>% 
+    m_exp_ip = t.test(m_exp_ip ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
       select(statistic, p.value, parameter),
-    m_partner_all = t.test(m_partner_all ~ homosexual, data = data) %>% tidy() %>% 
+    m_partner_all = t.test(m_partner_all ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
       select(statistic, p.value, parameter),
-    m_partner_ip = t.test(m_partner_ip ~ homosexual, data = data) %>% tidy() %>% 
+    m_partner_ip = t.test(m_partner_ip ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
[…]

### 2022-05-11 code/des_and_test_result.R

@@ -9,8 +9,11 @@
 
 library(tidyverse); library(magrittr); library(here); library(broom); library(effectsize)
 
-input_file <- commandArgs(trailingOnly = TRUE)
-output_file <- "data/processed/des_and_test_result.csv"
+args <- commandArgs(trailingOnly = TRUE)
+#args <- c("data/processed/casual_sex_sim.csv", "data/processed/des_and_test_result.csv")
+
+input_file <- args[1]
+output_file <- args[2]
 
 casual_tib <- here(input_file) %>% 
   read_csv() %>% 
@@ -46,18 +49,18 @@ casual_t_test <-
   casual_long %>% 
   nest_by(homosexual_dlikelihood_dstandard) %>% 
   mutate(
-    inpool = t.test(inpool ~ gender, data = data) %>% tidy() %>% 
+    inpool = t.test(inpool ~ gender, data = data, var.equal = TRUE) %>% tidy() %>% 
       select(statistic, p.value, parameter),
-    outpool = t.test(outpool ~ gender, data = data) %>% tidy() %>% 
+    outpool = t.test(outpool ~ gender, data = data, var.equal = TRUE) %>% tidy() %>% 
       select(statistic, p.value, parameter),
-    exp_all = t.test(exp_all ~ gender, data = data) %>% tidy() %>% 
+    exp_all = t.test(exp_all ~ gender, data = data, var.equal = TRUE) %>% tidy() %>% 
       # somehow the map function doesn't work here and I wonder why...
       select(statistic, p.value, parameter),
-    exp_ip = t.test(exp_ip ~ gender, data = data) %>% tidy() %>% 
+    exp_ip = t.test(exp_ip ~ gender, data = data, var.equal = TRUE) %>% tidy() %>% 
       select(statistic, p.value, parameter),
-    partner_all = t.test(partner_all ~ gender, data = data) %>% tidy() %>% 
+    partner_all = t.test(partner_all ~ gender, data = data , var.equal = TRUE) %>% tidy() %>% 
       select(statistic, p.value, parameter),
-    partner_ip = t.test(partner_ip ~ gender, data = data) %>% tidy() %>% 
+    partner_ip = t.test(partner_ip ~ gender, data = data, var.equal = TRUE) %>% tidy() %>% 
       select(statistic, p.value, parameter)
   ) %>% 
   select(-data) %>% 

### 2022-05-11 code/plot_hetero_vs_gay_men.R

@@ -6,10 +6,16 @@
 # notes: none
 
 # load libraries
-library(tidyverse); library(ggplot2); library(wesanderson); library(magrittr); library(here); library(knitr); library(broom); library(effectsize)
+library(tidyverse); library(ggplot2); library(wesanderson); library(here)
+
+args <- commandArgs(trailingOnly = TRUE)
+#args <- c("data/processed/casual_sex_sim.csv", "submission/figures/fig2_hetero_vs_gay_men.pdf")
+
+input_file <- args[1]
+output_file <- args[2]
 
 # read file
-casual_tib <- here("data/processed/casual_sex_sim.csv") %>% 
+casual_tib <- here(input_file) %>% 
   read_csv() %>% 
   mutate(
     diff_likelihood = as_factor(diff_likelihood),
@@ -17,10 +23,20 @@ casual_tib <- here("data/processed/casual_sex_sim.csv") %>%
     homosexual = as_factor(homosexual)
   )
 
+# construct facet label
+facet_label <- 
+  tibble(
+    label = c("(A)", "(B)"),
+    variable = c("exp_all", "partner_all"),
+    x = 0.5
+  ) %>% 
+  mutate(y = ifelse(variable == "exp_all", 4, 2.3))
+
+# construct y-axis label
 y_lab <- labeller(
   variable = c(
     `exp_all` = "Average number of\nshort-term mating experiences",
-    `partner_all` = "Average number of\nshort-term mates"))
+    `partner_all` = "Average number of short-term mates"))
 
 casual_tib %>% 
   filter(diff_likelihood == 1, diff_standard == 1) %>% 
@@ -31,6 +47,9 @@ casual_tib %>%
   geom_violin(aes(fill = homosexual)) +
   stat_summary(fun = "mean", geom = "point") +
   stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
+  geom_text(
+    data = facet_label, aes(label = label, x = x, y = y), hjust = 0, fontface = 2
+    ) +
   scale_fill_discrete(
     type = wes_palette("Darjeeling2", 2, type = "discrete"),
     name = "", labels = c("Heterosexual men", "Gay men")
@@ -38,7 +57,7 @@ casual_tib %>%
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 4, by = 1)) +
   labs(x = "", y = NULL) +
   facet_wrap(
[…]

### 2022-05-11 code/plot_men_vs_women.R

@@ -6,10 +6,16 @@
 # notes: none
 
 # load libraries
-library(tidyverse); library(ggplot2); library(wesanderson); library(magrittr); library(here); library(knitr); library(broom); library(effectsize)
+library(tidyverse); library(ggplot2); library(wesanderson); library(here)
+
+args <- commandArgs(trailingOnly = TRUE)
+#args <- c("data/processed/casual_sex_sim.csv", "submission/figures/fig1_men_vs_women.pdf")
+
+input_file <- args[1]
+output_file <- args[2]
 
 # read file
-casual_tib <- here("data/processed/casual_sex_sim.csv") %>% 
+casual_tib <- here(input_file) %>% 
   read_csv() %>% 
   mutate(
     diff_likelihood = as_factor(diff_likelihood),
@@ -17,6 +23,17 @@ casual_tib <- here("data/processed/casual_sex_sim.csv") %>%
     homosexual = as_factor(homosexual)
   )
 
+# construct facet label
+facet_label <- 
+  tibble(
+    homosexual = rep(c(0, 1), each = 2),
+    label = c("(A)", "(B)", " ", " "),
+    variable = rep(c("exp_all", "partner_all"), 2),
+    x = 0.5
+  ) %>% 
+  mutate(y = ifelse(variable == "exp_all", 4, 2.3))
+
+# construct y-axis label
 y_lab <- labeller(
   homosexual = c(
     `0` = "Experiment 1\nHeterosexual individuals",
@@ -36,6 +53,9 @@ casual_tib %>%
   geom_violin(aes(fill = gender)) +
   stat_summary(fun = "mean", geom = "point") +
   stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
+  geom_text(
+    data = facet_label, aes(label = label, x = x, y = y), hjust = 0, fontface = 2
+  ) +
   scale_fill_discrete(
     type = wes_palette("Darjeeling2", 2, type = "discrete"),
     name = "", labels = c("Women", "Men")
@@ -43,7 +63,7 @@ casual_tib %>%
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 4, by = 1)) +
   labs(x = "", y = NULL) +
   facet_grid(
-    variable ~ homosexual, scales = "free_y",
+    variable ~ homosexual, scales = "free_y", 
     switch = "y", labeller = y_lab) +
   theme_minimal() +
   theme(
[…]

### 2022-05-12 submission/manuscript.Rmd
added abstract, minor modification of the manuscript, close #17

@@
 
+Gender differences in short-term mating behaviors have been a well-documented phenomenon in human sexuality research.
+Existing studies usually conflate gender differences in preferences for short-term mating with differences in sexual behaviors, which is theoretically dubious.
+Using an agent-based model, the present study investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances.
+The results suggested that heterosexual men and women had the same average number of short-term mating experiences and short-term mates even when gender differences in preferences fort-term mating existed.
+Gender differences in mating behaviors only emerged when heterosexual men and women in the mating pool were considered.
+Moreover, gay men had a higher average number of both outcomes than lesbian women and than heterosexual men under such a circumstance.
+These results suggest that theoretically speaking, gender differences in short-term mating behaviors only occurred among particular populations, or when men's preferences for short-term mating are not constrained by those of women.
+Suggestions for future research in human mating psychology and behaviors were provided.
+
+\
+
+*Keywords:* agent-based modeling, short-term mating, casual sex, sexual strategy theory, female choice hypothesis
+
 \newpage
@@
 
-The model measured **three** outcomes: (1) the number of men and women who had ever engaged in short-term mating **put this to the end**; (2) the number of short-term mating experiences of men and women; (3) the number of short-term mates of men and women.
-The number of short-term mating experienced and short-term mates were calculated by taking the average among the whole men/women population and among those who had engaged in short-term mating.
+The model measured two outcomes: (1) the number of short-term mating experiences of men and women; (2) the number of short-term mates of men and women.
+Additionally, we had also documented the number of men and women in the mating pool (i.e., who had ever engaged in short-term mating); The average number of short-term mating experiences and short-term mates were calculated by taking the average among the whole population of men/women (*N~m~* = *N~w~* = 150) and among those who had engaged in short-term mating.
 
@@
 In total, 150 women and 150 men were created on the lattice at random locations.
-All agents were initialized with (1) a three-unit maximum distance by which agents can move away from their birthplace (movement range); (2) a 10% likelihood of two agents forming a long-term relationship upon meeting; (3) single status and no long-term partner; (4) a mate value, sampled from a Gaussian distribution (*M* = 5, *SD* = 1.5); (5) no short-term mate or short-term mating history.
+All agents were initialized with (1) a three-unit maximum distance by which agents can move away from their birthplace (movement range); (2) a 10% likelihood of two agents forming a long-term relationship upon meeting; (3) single status and no long-term partner; (4) a mate value, sampled from a Gaussian distribution (*M* = 5.0, *SD* = 1.5); (5) no short-term mate or short-term mating history.
 

### 2022-05-12 submission/manuscript.tex
added abstract, minor modification of the manuscript, close #17

@@
 \addcontentsline{toc}{section}{Abstract}
+
+Gender differences in short-term mating behaviors have been a
+well-documented phenomenon in human sexuality research. Existing studies
+usually conflate gender differences in preferences for short-term mating
+with differences in sexual behaviors, which is theoretically dubious.
+Using an agent-based model, the present study investigated whether men
+and women's different mating preferences resulted in any gender
+differences in short-term mating behaviors, and if they did, under what
+circumstances. The results suggested that heterosexual men and women had
+the same average number of short-term mating experiences and short-term
+mates even when gender differences in preferences fort-term mating
+existed. Gender differences in mating behaviors only emerged when
+heterosexual men and women in the mating pool were considered. Moreover,
+gay men had a higher average number of both outcomes than lesbian women
+and than heterosexual men under such a circumstance. These results
+suggest that theoretically speaking, gender differences in short-term
+mating behaviors only occurred among particular populations, or when
+men's preferences for short-term mating are not constrained by those of
+women. Suggestions for future research in human mating psychology and
+behaviors were provided.
+
+~
+
+\emph{Keywords:} agent-based modeling, short-term mating, casual sex,
+sexual strategy theory, female choice hypothesis
 
@@
 
-The model measured \textbf{three} outcomes: (1) the number of men and
-women who had ever engaged in short-term mating \textbf{put this to the
-end}; (2) the number of short-term mating experiences of men and women;
-(3) the number of short-term mates of men and women. The number of
-short-term mating experienced and short-term mates were calculated by
-taking the average among the whole men/women population and among those
-who had engaged in short-term mating.
+The model measured two outcomes: (1) the number of short-term mating
+experiences of men and women; (2) the number of short-term mates of men
+and women. Additionally, we had also documented the number of men and
+women in the mating pool (i.e., who had ever engaged in short-term
+mating); The average number of short-term mating experiences and
+short-term mates were calculated by taking the average among the whole
+population of men/women (\emph{N\textsubscript{m}} =
+\emph{N\textsubscript{w}} = 150) and among those who had engaged in
+short-term mating.
 
@@
 relationship upon meeting; (3) single status and no long-term partner;
-(4) a mate value, sampled from a Gaussian distribution (\emph{M} = 5,
+(4) a mate value, sampled from a Gaussian distribution (\emph{M} = 5.0,
 \emph{SD} = 1.5); (5) no short-term mate or short-term mating history.

### 2022-05-13 submission/manuscript.Rmd
minor language edits of the manuscript, tracked the model directory, close #18

@@
     keep_tex: true
-  word_document: true
 geometry: margin=1.0in
@@
 
-# **This is an awesome title** {-}
+# An Agent-based Model of Gender Differences in Short-term Mating Behaviors as a Result of Mating Preferences {-}
 
@@
 
-Yurun Ying^1^, Pekka Santtila^1^^,^^2^^,^^$\dagger$^
+Yurun Ying^1^, Jan Antfolk^2^, Pekka Santtila^1^^,^^3^^,^^$\dagger$^
 
@@
 
-^2^ NYU-ECNU Institute for Social Development at NYU Shanghai
+^2^ xxxx
+
+^3^ NYU-ECNU Institute for Social Development at NYU Shanghai
 
@@
 
-^$\dagger$^ To whom correspondence should be addressed:
+^$\dagger$^ To whom correspondence should be addressed: [pekka.santtila@nyu.edu](pekka.santtila@nyu.edu)
 
@@
 Gender differences in short-term mating behaviors have been a well-documented phenomenon in human sexuality research.
-Existing studies usually conflate gender differences in preferences for short-term mating with differences in sexual behaviors, which is theoretically dubious.
-Using an agent-based model, the present study investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances.
-The results suggested that heterosexual men and women had the same average number of short-term mating experiences and short-term mates even when gender differences in preferences fort-term mating existed.
-Gender differences in mating behaviors only emerged when heterosexual men and women in the mating pool were considered.
-Moreover, gay men had a higher average number of both outcomes than lesbian women and than heterosexual men under such a circumstance.
-These results suggest that theoretically speaking, gender differences in short-term mating behaviors only occurred among particular populations, or when men's preferences for short-term mating are not constrained by those of women.
+Existing studies usually conflate gender differences in mating preferences with differences in sexual behaviors, which is theoretically dubious.
+Using an agent-based model, the present study investigated the circumstances under which men and women’s differential preferences for short-term mating would result in gender differences in short-term mating behaviors.
+The results from the model suggested that heterosexual men and women had the same average number of short-term mating experiences and short-term mates even when men had stronger preferences for short-term mating.
+Gender differences in mating behaviors only emerged when heterosexual men and women in the mating pool (i.e., those with a non-zero number of short-term mating experiences) were considered.
+Moreover, gay men had a higher average number of both outcomes than lesbian women as well as than heterosexual men when men had stronger preferences for short-term mating.
+These results suggest that theoretically speaking, even when gender differences in mating preferences existed, those in short-term mating behaviors only occurred among particular populations, or when men’s preferences for short-term mating are not constrained by those of women.
 Suggestions for future research in human mating psychology and behaviors were provided.
@@
 Intuitive as this line of reasoning is, there are good reasons to doubt its soundness.
-This is because any heterosexual sexual encounter involves both a man and a woman (the frequency of encounters involving more than two persons is negligible, [e.g., @herbenick_sexual_2017].
+This is because any heterosexual sexual encounter involves both a man and a woman [the frequency of encounters involving more than two persons is negligible, e.g., @herbenick_sexual_2017].
 A new short-term mating experience for a man is, therefore, also a new experience for a woman, and the same logic applies to counting a new short-term mate.
@@
 
-The present study took gender differences in mating preferences as an assumption, which was proposed by sexual strategy theory [@buss_sexual_1993] and repeatedly found support by empirical studies [e.g., @schmitt_universal_2003; @walter_sex_2020].
-Using an agent-based model, we investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, specifically, in the number of short-term mating experiences and short-term mates, and if they did, under what circumstances.
+The present study took gender differences in mating preferences as a presumption, which was conceptualized by sexual strategy theory [@buss_sexual_1993] and repeatedly found support by empirical studies [e.g., @schmitt_universal_2003; @walter_sex_2020].
+Using an agent-based model, we investigated whether men and women's differential preferences for short-term mating resulted in any gender differences in short-term mating behaviors, specifically, in the number of short-term mating experiences and short-term mates, and if they did, under what circumstances.
 
@@
 
-Gender differences in mating strategies have been studied in the light of sexual strategy theory [@buss_sexual_1993].
+Gender differences in mating preferences have been studied in the light of sexual strategy theory [@buss_sexual_1993].
 It posits that since the minimum investment that men devote to their offspring (contribution of sperm through one sexual act) is lower than that of women (gestation, labor, and lactation), men tend to have short-term mating as a larger part of their mating strategy than women do.
@@
 
-As for mating standards, men are more likely to accept someone as a potential short-term mate.
+As for mating standards, men are less selective in accepting someone as a potential short-term mate.
 For example, studies using U.S.
-college samples found that the minimum percentile ranks that men found acceptable for a potential short-term sexual partner were lower than for women both overall and on individual traits (e.g., social status, attractiveness) [@kenrick_evolution_1990; @regan_minimum_1998].
+college samples found that the minimum percentile ranks that men found acceptable for a potential short-term sexual partner were lower than those accepted by women, both in terms of overall desirability and individual traits (e.g., social status, attractiveness) [@kenrick_evolution_1990; @regan_minimum_1998].
 A study also found that when presented with identical descriptions of potential mates, men on average rated them as more desirable than women did [@wiederman_evolution_1998].
 
-Some evidence shows that sexual strategy theory also predicts mating preferences among gay men and lesbian women.
+Some evidence shows that gender differences in mating preferences also existed between gay men and lesbian women.
 A survey study using a community sample from the U.S.
-found that gay men were more interested in short-term mating than lesbian women and that this gender difference was comparable to that existing among heterosexual individuals [@bailey_effects_1994].
+found that gay men were more interested in short-term mating than lesbian women were, and that this gender difference was comparable to that existing among heterosexual individuals [@bailey_effects_1994].
 An indirect piece of evidence on differential standards for short-term mates comes from a recent study finding that significantly more gay men than lesbian women reported to have accepted a casual sexual offer from a same-gender person [@matsick_gender_2021].
 Past studies suggest that the gender difference in the acceptance rate of casual sexual offers may originate from men and women’s differential standards for short-term mates [@conley_women_2011; @hald_receptivity_2010].
-Thus, as a postulation, gay men and lesbian women may also have different standards for short-term mates.
+Thus, as a postulation, gay men may also have lower standards than lesbian women for short-term mates.
 
@@
 This is because men’s short-term mating preferences can only translate into behaviors when there are women willing to have sex with them.
-When short-term mating occurs, the number of short-term mating encounters and short-term mates is essentially the same for men and women (although this does not necessarily mean that the total number of men and women who have ever had short-term mating must be equal).
-Therefore, we would expect to observe no gender difference in short-term mating behaviors among heterosexual individuals even when there were gender differences in mating preferences.
+When a new short-term mating encounter occurs, it counts towards men’s total number of short-term mating encounters as well as towards women’s.
+Similarly, a new short-term mate counts towards both men and women’s total number of short-term mates.
+Therefore, the total number of short-term mating experiences and short-term mates must be equal between heterosexual men and women on a population level.
+However, it is important to note that although heterosexual men’s total number of short-term mating is equal to that of women, this does not necessarily mean that the total number of men and women who have ever had short-term mating must be equal.
+It is possible that there is a smaller proportion of men (vs.
+the proportion of women) who contribute to the total number of short-term mating.
+Following this line of reasoning, we would expect to observe no gender difference in short-term mating behaviors among heterosexual individuals even when there were gender differences in mating preferences.
 
@@
 A study showed that the proportions of heterosexual men and women who have engaged in extradyadic sex were 26% and 21%, respectively, while the statistics among gay men and lesbian women were 82% and 28%, respectively [@peplau_sexuality_2004].
-Therefore, we would theoretically expect to observe gender differences in short-term mating behaviors among gay men and lesbians.
+Therefore, we would theoretically expect to observe gender differences in short-term mating behaviors between gay men and lesbian women.
 Moreover, we would also expect to find that gay men, as compared to heterosexual men, engaged in more short-term mating behaviors due to the lessened constraint on their mating preferences.
@@
 
-By using a spatial agent-based model, the present study investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances.
-The interest in short-term mating was modeled as an individual’s likelihood of deciding to have short-term mating at each time step.
-The standards for short-term mates were modeled as the minimum desirability of a potential mate with whom an individual was willing to have sex.
-Short-term mating behaviors were operationally defined as the number of short-term mating experiences and the number of past short-term mates.
+By using a spatial agent-based model, the present study investigated whether men and women’s different preferences for short-term mating resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances.
+Preferences for short-term mating were operationally defined as the interest in short-term mating and standards for short-term mates [@buss_sexual_1993].
+Short-term mating behaviors were operationally defined as the number of short-term mating experiences and the number of past short-term mates [@petersen_meta-analytic_2010].
 
-We modeled this process among both heterosexual individuals and gay men and lesbian women to examine whether constraints set by the opposite sex’s preferences would make a difference in short-term mating behaviors.
+We modeled this process among both heterosexual individuals and gay men and lesbian women to examine whether constraints set by the opposite sex’s preferences would affect short-term mating behaviors.
 Individuals’ sexual orientation was conceptualized in terms of behaviors only in our model.
-Heterosexual men had short-term mating or formed a long-term relationship with women, while gay men only with other men, and vice versa for women.
+Heterosexual men had short-term mating or formed a long-term relationship only with women, while gay men only with other men, and vice versa for women.
 
@@
 The model measured two outcomes: (1) the number of short-term mating experiences of men and women; (2) the number of short-term mates of men and women.
-Additionally, we had also documented the number of men and women in the mating pool (i.e., who had ever engaged in short-term mating); The average number of short-term mating experiences and short-term mates were calculated by taking the average among the whole population of men/women (*N~m~* = *N~w~* = 150) and among those who had engaged in short-term mating.
+Additionally, we also measured the number of men and women in the mating pool (i.e., those with a non-zero number of short-term mating experiences).
+The average numbers of short-term mating experiences and short-term mates were calculated by taking the average among the whole population of men/women (*N~m~* = *N~w~* = 150) and among those who had engaged in short-term mating.
 
 See the Supplemental Materials for the overview, design concepts, and details (ODD) protocol of the model, which includes detailed scheduling and parameterization.
-The model can be downloaded from the Github online repository [link masked for peer review].
+The model can be downloaded from the Open Science Framework [link masked for peer review].
 The model was programmed in Netlogo 6.2.1 [@wilensky_1999].
@@
 Using the agent-based model, the present study conducted two 2 (gender difference vs.
-no difference in short-term mating likelihood) x 2 (gender difference vs.
-no difference in mating standard) experiments.
+no difference in the interest in short-term mating likelihood) x 2 (gender difference vs.
+no difference in mating standards) experiments.
 Experiment 1 was run among heterosexual agents who only engaged in short-term or long-term relationships with agents of the opposite gender.
@@
 
-Gender differences were modeled in agents’ likelihood of engaging in short-term mating and the standard for short-term mates.
-The values of these parameters were set based on empirical findings in human mating psychology.
-We compared the conditions where there were gender differences in mating preferences with counterfactual conditions where gender differences were missing.
-When there was a gender difference in short-term mating likelihood, men had a 40% likelihood of deciding to engage in short-term mating upon meeting a potential mate, while women had a likelihood of 25% [@buss_sexual_1993; @schmitt_are_2001; @schmitt_universal_2003].
+The interest in short-term mating was modeled as an agent’s likelihood of deciding to have short-term mating at each time step.
+The standards for short-term mates were modeled as the minimum desirability of a potential mate with whom an agent was willing to have sex.
+The values of the two parameters were set based on empirical findings in human mating psychology.
+When there was a gender difference in short-term mating likelihood, men had a 40% likelihood of deciding to engage in short-term mating, while women had a likelihood of 25% [@buss_sexual_1993; @schmitt_are_2001; @schmitt_universal_2003].
 When there was no gender difference in short-term mating likelihood, both women and men had a likelihood of 25%.
-When there was a gender difference in mating standards, men had a mating standard of 3 (the minimum mate value of a potential partner with whom an agent is willing to have short-term mating, highest possible value = 10), while women had a standard of 5 [@kenrick_evolution_1990; @regan_minimum_1998].
+When there was a gender difference in mating standards, men had a mating standard of 3 (the highest possible value = 10), while women had a standard of 5 [@kenrick_evolution_1990; @regan_minimum_1998].
 When there was no gender difference in mating standards, both men and women had a standard of 5.
@@
 
-The likelihood of engaging in short-term mating and the standard for short-term mates were initialized either the same or differently for men and women, depending on the experimental conditions.
+The likelihood of engaging in short-term mating and the standard for short-term mates were initialized either identically or differently for men and women, depending on the experimental conditions.
 
@@
 At each time step, men and women moved and decided on short-term mating as the agents did in the heterosexual procedures.
-Half of the agents (an equal number of men and women) were also given the initiator status.
+Half of the agents (75 men and 75 women) were also given the initiator status.
 The initiators checked to see whether there were other agents at the same location.
-The rest of the procedures were identical to the heterosexual procedures, except that the agents only chose those with the same gender as themselves as potential short-term mates or long-term partners.
+The rest of the procedures were identical to the heterosexual procedures, except that the agents only chose those with the same gender as potential short-term mates or long-term partners.
 
@@
 The model was run for 1,000 time steps in each simulation.
-We ran 10,000 simulations for each experiment, and 2,500 simulations for each condition.
+We ran 10,000 simulations for each experiment, including 2,500 simulations for each condition.
 We controlled for initializing random seeds in the model runs.
@@
 
-## Gender differences in short-term mating behaviors in each experiment
+## Gender differences in short-term mating behaviors
 
 ```{r sec1.1}
+# the number of experiences, difference*2, heterosexual
 m_exp_all.mean_011 <-
@@
 
+# the number of partners, difference*2, heterosexual
 m_partner_all.mean_011 <-
@@
   \centering
-  \includegraphics[width=80mm]{figures/fig1_men_vs_women.pdf}
+  \includegraphics[width=70mm]{figures/fig1_men_vs_women.pdf}
   \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women.
@@
 ```{r sec1.2}
+# the number of experiences, difference*2, gay and lesbians
 m_exp_all.mean_111 <-
@@
 
+# the number of partners, difference*2, gay and lesbians
 m_partner_all.mean_111 <-
@@
 ```{r sec1.3}
+# the number of experiences, difference*2, heterosexual in the mating pool
 m_exp_ip.mean_011 <-
@@
 
+# the number of partners, difference*2, heterosexual in the mating pool
 m_partner_ip.mean_011 <-
@@
   results %>% filter(hls == "0_1_1") %>% pull(partner_ip.d) %>% abs()
+
+# the number of in-pool, difference*2
+m_inpool.mean_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(m_inpool.mean)
+m_inpool.sd_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(m_inpool.sd)
+f_inpool.mean_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(f_inpool.mean)
+f_inpool.sd_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(f_inpool.sd)
 ```
 
-In Experiment 1, however, when the means of the outcome variables were calculated among men and women who were in the mating pool (i.e., those with a non-zero number of short-term mating experiences) **(the number of individuals in the mating pool: M~m~, SD~m~; M~w~, SD~w~)**, there were gender differences in short-term mating behaviors when there were gender differences in mating preferences.
+In Experiment 1, however, when the means of the outcome variables were calculated among men and women in the mating pool (the number of individuals in the mating pool: *M~m~* = `r m_inpool.mean_011`, *SD~m~* = `r m_inpool.sd_011`; *M~w~* = `r f_inpool.mean_011`, *SD~w~* = `r f_inpool.sd_011`), there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating.
 The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`.
@@
 
-## Comparing short-term mating behaviors of heterosexual and gay men
+## Comparing heterosexual and gay men
 
 ```{r sec2}
+# the number of experiences, difference*2, heterosexual and gay men
 m_exp_all.mean_0_11 <-
@@
 
+# the number of partners, difference*2, heterosexual and gay men
 m_partner_all.mean_0_11 <-
@@
 
-In an exploratory manner, we also compared across conditions to see which of the two dimensions of preferences for short-term mating contributed to gender differences in sexual behaviors.
+In an exploratory manner, we also compared across conditions to see which of the two dimensions of mating preferences contributed to gender differences in short-term mating behaviors.
 
 ```{r sec3.1}
+# the number of experiences, difference in standard, heterosexual
 m_exp_ip.mean_001 <-
@@
 
+# the number of partners, difference in standard, heterosexual
 m_partner_ip.mean_001 <-
@@
 Among heterosexual individuals, gender differences in short-term mating behaviors, as calculated among individuals in the mating pool, emerged when men and women had different standards for short-term mates.
-Heterosexual men in the mating pool had a higher average number of short-term mating experiences and short-term mates than women in the mating pool, even when no gender difference existed in short-term mating likelihood (experiences: *M~m~* = `r m_exp_ip.mean_001`, *SD~m~* = `r m_exp_ip.sd_001`, *M~w~* = `r f_exp_ip.mean_001`, *SD~w~* = `r f_exp_ip.sd_001`, Cohen's *d* = `r exp_ip.d_001`; partners: *M~m~* = `r m_partner_ip.mean_001`, *SD~m~* = `r m_partner_ip.sd_001`; *M~w~* = `r f_partner_ip.mean_001`, *SD~w~* = `r f_partner_ip.sd_001`, Cohen's *d* = `r partner_ip.d_001`).
+Heterosexual men (vs.
+heterosexual women) in the mating pool had a higher average number of short-term mating experiences and short-term mates as long as they had lower mating standards, even when no gender difference existed in short-term mating likelihood (experiences: *M~m~* = `r m_exp_ip.mean_001`, *SD~m~* = `r m_exp_ip.sd_001`, *M~w~* = `r f_exp_ip.mean_001`, *SD~w~* = `r f_exp_ip.sd_001`, Cohen's *d* = `r exp_ip.d_001`; partners: *M~m~* = `r m_partner_ip.mean_001`, *SD~m~* = `r m_partner_ip.sd_001`; *M~w~* = `r f_partner_ip.mean_001`, *SD~w~* = `r f_partner_ip.sd_001`, Cohen's *d* = `r partner_ip.d_001`).
 In comparison, virtually no gender differences in short-term mating behaviors existed when men and women had the same mating standards (Table 1).
@@
 ```{r sec3.2}
+# the number of experiences, difference in likelihood, gay and lesbian
 m_exp_all.mean_110 <-
@@
 
+# the number of partners, difference in likelihood, gay and lesbian
 m_partner_all.mean_110 <-
@@
 
+# the number of experiences, difference in standard, gay and lesbian
 m_exp_all.mean_101 <-
@@
 
+# the number of partners, difference in standard, gay and lesbian
 m_partner_all.mean_101 <-
@@
 Among gay men and lesbian women, gender differences in short-term mating behaviors emerged either when they had different short-term mating likelihood or when their mating standards were different.
-Gay men had a higher average number of short-term mating experiences and short-term mates when they had a higher short-term mating likelihood than lesbian women (experiences: *M~m~* = `r m_exp_all.mean_110`, *SD~m~* = `r m_exp_all.sd_110`, *M~w~* = `r f_exp_all.mean_110`, *SD~w~* = `r f_exp_all.sd_110`, Cohen's *d* = `r exp_all.d_110`; partners: *M~m~* = `r m_partner_all.mean_110`, *SD~m~* = `r m_partner_all.sd_110`, *M~w~* = `r f_partner_all.mean_110`, *SD~w~* = `r f_partner_all.sd_110`, Cohen's *d* = `r partner_all.d_110`), or when they had a lower mating standards (experiences: *M~m~* = `r m_exp_all.mean_101`, *SD~m~* = `r m_exp_all.sd_101`, *M~w~* = `r f_exp_all.mean_101`, *SD~w~* = `r f_exp_all.sd_101`, Cohen's *d* = `r exp_all.d_101`; partners: *M~m~* = `r m_partner_all.mean_101`, *SD~m~* = `r m_partner_all.sd_101`, *M~w~* = `r f_partner_all.mean_101`, *SD~w~* = `r f_partner_all.sd_101`, Cohen's *d* = `r partner_all.d_101`).
+Gay men (vs.
+lesbian women) had a higher average number of short-term mating experiences and short-term mates when they had a higher short-term mating likelihood (experiences: *M~m~* = `r m_exp_all.mean_110`, *SD~m~* = `r m_exp_all.sd_110`, *M~w~* = `r f_exp_all.mean_110`, *SD~w~* = `r f_exp_all.sd_110`, Cohen's *d* = `r exp_all.d_110`; partners: *M~m~* = `r m_partner_all.mean_110`, *SD~m~* = `r m_partner_all.sd_110`, *M~w~* = `r f_partner_all.mean_110`, *SD~w~* = `r f_partner_all.sd_110`, Cohen's *d* = `r partner_all.d_110`), or when they had lower mating standards (experiences: *M~m~* = `r m_exp_all.mean_101`, *SD~m~* = `r m_exp_all.sd_101`, *M~w~* = `r f_exp_all.mean_101`, *SD~w~* = `r f_exp_all.sd_101`, Cohen's *d* = `r exp_all.d_101`; partners: *M~m~* = `r m_partner_all.mean_101`, *SD~m~* = `r m_partner_all.sd_101`, *M~w~* = `r f_partner_all.mean_101`, *SD~w~* = `r f_partner_all.sd_101`, Cohen's *d* = `r partner_all.d_101`).
 In comparison, virtually no gender differences in short-term mating behaviors existed when gay men and lesbian women had the same short-term mating likelihood and mating standards (Table 2).
@@
 
-The present study aimed at using agent-based modeling to investigate whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, specifically, in the number of short-term mating experiences and short-term mates, and if they did, under what circumstances.
-We raised two hypotheses: 1) there would be gender differences in short-term mating behaviors among gay men and lesbian women, with gay men being engaged in more such behaviors, and 2) gay men would engage in more short-term mating behaviors as compared to heterosexual men.
-The results from 1,000 time steps in a model simulating men and women's mating behaviors supported our hypotheses.
-First of all, as compared to lesbian women, gay men had a higher average number of short-term mating experiences and short-term mates.
-In contrast, we found no gender differences in short-term mating behaviors between heterosexual men and women.
-Secondly, gay men also had a higher average number of short-term mating experiences and short-term mates as compared to heterosexual men.
+The present study aimed at using agent-based modeling to investigate whether men and women’s different preferences for short-term mating resulted in any gender differences in short-term mating behaviors, specifically, in the number of short-term mating experiences and short-term mates, and if they did, under what circumstances.
+We raised two hypotheses: 1) gay men would engage in more short-term mating behaviors as compared to lesbian women, and 2) gay men would engage in more short-term mating behaviors as compared to heterosexual men.
+The results from 1,000 time steps in a model simulating men and women’s mating behaviors supported our hypotheses.
+First of all, as compared to lesbian women, gay men had higher average numbers of short-term mating experiences and short-term mates.
+Secondly, gay men also had higher average numbers of short-term mating experiences and short-term mates as compared to heterosexual men.
+In contrast, we found no gender differences in short-term mating behaviors between heterosexual men and women, although heterosexual men in the mating pool did have higher average numbers of short-term mating experiences and short-term mates.
 
-As we expected, heterosexual men and women did not differ in short-term mating behaviors despite their different mating preferences.
-This was because the total numbers of short-term mating experiences and short-term mates of heterosexual men and women were exactly the same.
+As we expected, heterosexual men and women did not differ in short-term mating behaviors despite their differential preferences for short-term mating.
+This was because heterosexual men and women had an equal total number of short-term mating experiences , so as the total number of short-term mates.
 Since the sex ratio was 1:1 in our model, the average number of short-term mating experiences and short-term mates must be equal between men and women as well.
 However, we did find that among individuals in the mating pool, men engaged in more short-term mating behaviors as compared to women.
-This was because there were more women than men in the mating pool (i.e., had ever engaged in short-term mating behaviors), resulting in lower averages among heterosexual women despite equal numbers of experiences and mates in total.
+This was because there were more women than men in the mating pool, resulting in lower averages among heterosexual women despite the equal numbers of experiences and mates in total.
 
-Moreover, gender differences in short-term mating behaviors emerged when heterosexual men and women had different standards for short-term mates, but not when they had different likelihood of engaging in short-term mating.
-When women had a higher standard than men did, less men than women in the population were above a potential partner's standards and thus had a chance to have sex with them.
-This contributed to the unequal number of men and women in the mating pool, which led to gender differences in short-term mating behaviors.
+Moreover, gender differences in short-term mating behaviors emerged when heterosexual men and women had different mating standards, but not when they had different short-term mating likelihood.
+When women had a higher standard than men did, less men than women in the population were above a potential partner’s standard and thus had a chance to have sex with them.
+This contributed to the unequal number of men and women in the mating pool, which led to gender differences in short-term mating behaviors among this population.
 
-In the light of these results, the empirical observation of gender differences in short-term mating behaviors among heterosexual individuals [e.g., @petersen_meta-analytic_2010] appear to be perplexing because this is theoretically illogical [e.g., @s_j_gurman_six_1989].
+In the light of these results, the empirical observation of gender differences in short-term mating behaviors among heterosexual individuals [e.g., @petersen_meta-analytic_2010] appear to be perplexing because this is illogical [e.g., @s_j_gurman_six_1989].
 Possible explanations for these empirical results have to highlight caveats in the observation process.
@@
 
-Among gay men and lesbian women, large gender differences in short-term mating behaviors existed when men and women had different mating preferences, which was in line with empirical observations [e.g., @peplau_national_1997; @peplau_sexuality_2004].
+Among gay men and lesbian women, large gender differences in short-term mating behaviors existed when men and women had differential preferences for short-term mating, which was in line with empirical observations [e.g., @peplau_national_1997; @peplau_sexuality_2004].
 This was probably because the number of short-term mating experiences and short-term mates no longer counted towards men and women simultaneously.
@@
 This was consistent with the empirical literature [e.g., @peplau_national_1997].
-Interestingly, gay men and heterosexual men had the same likelihood of short-term mating and the same standards for short-term mates in our model.
-The only difference was a change in the preferences in their potential partners.
-When men's partners had a stronger preferences for short-term mating (i.e., having men vs.
+Interestingly, gay men and heterosexual men had the same mating likelihood and the same standards for short-term mates in our model.
+The only difference was a change in the preferences of potential partners.
+When men’s partners had a stronger preferences for short-term mating (i.e., having men vs.
 having women as potential partners), men also appeared to engage in more short-term mating behaviors.
@@
 
-Using agent-based modeling, the present study theoretically explored the circumstances under which men and women's different mating preferences resulted in gender differences in short-term mating behaviors.
+Using agent-based modeling, the present study theoretically explored the circumstances under which men and women’s differential preferences for short-term mating resulted in gender differences in short-term mating behaviors.
 We found when men (vs.
@@
 We also found that gay men engaged in more short-term mating behaviors than heterosexual men did.
-
-Theses results highlight the distinction between psychological preferences and behaviors in human mating.
-Individuals' mating behaviors do not only depend on one's own preferences, but are also constrained by partners' preferences.
-Future research in human mating should not only focus on the psychological aspect but also pay attention to the interaction between individuals' psychology and its context.
+Theses results highlight the distinction between preferences and behaviors in human mating.
+Individuals’ mating behaviors do not only depend on one’s own preferences, but are also constrained by partners’ preferences.
+Future research in human mating should not only focus on the psychological aspect but also pay attention to the interaction between individuals’ psychology and its context.
 These results also cast doubt to the prevalent belief in the gender differences in short-term mating behaviors, especially among heterosexual individuals.
-Our findings suggest that there may be factors in the observation process that lead to such differences.
+Our findings suggest that there may be factors in the observation process, such as sampling bias, that lead to the observed differences.
 Future research in human sexuality should note such possibilities and interpret any observed gender differences in short-term mating behaviors cautiously.

### 2022-05-13 submission/manuscript.tex
minor language edits of the manuscript, tracked the model directory, close #18

@@
 
-\hypertarget{this-is-an-awesome-title}{%
-\section*{\texorpdfstring{\textbf{This is an awesome
-title}}{This is an awesome title}}\label{this-is-an-awesome-title}}
-\addcontentsline{toc}{section}{\textbf{This is an awesome title}}
+\hypertarget{an-agent-based-model-of-gender-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}{%
+\section*{An Agent-based Model of Gender Differences in Short-term
+Mating Behaviors as a Result of Mating
+Preferences}\label{an-agent-based-model-of-gender-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}}
+\addcontentsline{toc}{section}{An Agent-based Model of Gender
+Differences in Short-term Mating Behaviors as a Result of Mating
+Preferences}
 
@@
 
-Yurun Ying\textsuperscript{1}, Pekka
-Santtila\textsuperscript{1,2,\(\dagger\)}
+Yurun Ying\textsuperscript{1}, Jan Antfolk\textsuperscript{2}, Pekka
+Santtila\textsuperscript{1,3,\(\dagger\)}
 
@@
 
-\textsuperscript{2} NYU-ECNU Institute for Social Development at NYU
+\textsuperscript{2} xxxx
+
+\textsuperscript{3} NYU-ECNU Institute for Social Development at NYU
 Shanghai
@@
 \textsuperscript{\(\dagger\)} To whom correspondence should be
-addressed:
+addressed: \url{pekka.santtila@nyu.edu}
 
@@
 well-documented phenomenon in human sexuality research. Existing studies
-usually conflate gender differences in preferences for short-term mating
-with differences in sexual behaviors, which is theoretically dubious.
-Using an agent-based model, the present study investigated whether men
-and women's different mating preferences resulted in any gender
-differences in short-term mating behaviors, and if they did, under what
-circumstances. The results suggested that heterosexual men and women had
-the same average number of short-term mating experiences and short-term
-mates even when gender differences in preferences fort-term mating
-existed. Gender differences in mating behaviors only emerged when
-heterosexual men and women in the mating pool were considered. Moreover,
-gay men had a higher average number of both outcomes than lesbian women
-and than heterosexual men under such a circumstance. These results
-suggest that theoretically speaking, gender differences in short-term
-mating behaviors only occurred among particular populations, or when
-men's preferences for short-term mating are not constrained by those of
-women. Suggestions for future research in human mating psychology and
-behaviors were provided.
+usually conflate gender differences in mating preferences with
+differences in sexual behaviors, which is theoretically dubious. Using
+an agent-based model, the present study investigated the circumstances
+under which men and women's differential preferences for short-term
+mating would result in gender differences in short-term mating
+behaviors. The results from the model suggested that heterosexual men
+and women had the same average number of short-term mating experiences
+and short-term mates even when men had stronger preferences for
+short-term mating. Gender differences in mating behaviors only emerged
+when heterosexual men and women in the mating pool (i.e., those with a
+non-zero number of short-term mating experiences) were considered.
+Moreover, gay men had a higher average number of both outcomes than
+lesbian women as well as than heterosexual men when men had stronger
+preferences for short-term mating. These results suggest that
+theoretically speaking, even when gender differences in mating
+preferences existed, those in short-term mating behaviors only occurred
+among particular populations, or when men's preferences for short-term
+mating are not constrained by those of women. Suggestions for future
+research in human mating psychology and behaviors were provided.
 
@@
 involves both a man and a woman (the frequency of encounters involving
-more than two persons is negligible, (e.g., Herbenick et al., 2017). A
+more than two persons is negligible, e.g., Herbenick et al., 2017). A
 new short-term mating experience for a man is, therefore, also a new
@@
 
-The present study took gender differences in mating preferences as an
-assumption, which was proposed by sexual strategy theory (Buss \&
+The present study took gender differences in mating preferences as a
+presumption, which was conceptualized by sexual strategy theory (Buss \&
 Schmitt, 1993) and repeatedly found support by empirical studies (e.g.,
 Schmitt, 2003; Walter et al., 2020). Using an agent-based model, we
-investigated whether men and women's different mating preferences
-resulted in any gender differences in short-term mating behaviors,
-specifically, in the number of short-term mating experiences and
-short-term mates, and if they did, under what circumstances.
+investigated whether men and women's differential preferences for
+short-term mating resulted in any gender differences in short-term
+mating behaviors, specifically, in the number of short-term mating
+experiences and short-term mates, and if they did, under what
+circumstances.
 
@@
 
-Gender differences in mating strategies have been studied in the light
+Gender differences in mating preferences have been studied in the light
 of sexual strategy theory (Buss \& Schmitt, 1993). It posits that since
@@
 
-As for mating standards, men are more likely to accept someone as a
-potential short-term mate. For example, studies using U.S. college
+As for mating standards, men are less selective in accepting someone as
+a potential short-term mate. For example, studies using U.S. college
 samples found that the minimum percentile ranks that men found
-acceptable for a potential short-term sexual partner were lower than for
-women both overall and on individual traits (e.g., social status,
-attractiveness) (Kenrick et al., 1990; Regan, 1998). A study also found
-that when presented with identical descriptions of potential mates, men
-on average rated them as more desirable than women did (Wiederman \&
-Dubois, 1998).
+acceptable for a potential short-term sexual partner were lower than
+those accepted by women, both in terms of overall desirability and
+individual traits (e.g., social status, attractiveness) (Kenrick et al.,
+1990; Regan, 1998). A study also found that when presented with
+identical descriptions of potential mates, men on average rated them as
+more desirable than women did (Wiederman \& Dubois, 1998).
 
-Some evidence shows that sexual strategy theory also predicts mating
-preferences among gay men and lesbian women. A survey study using a
+Some evidence shows that gender differences in mating preferences also
+existed between gay men and lesbian women. A survey study using a
 community sample from the U.S. found that gay men were more interested
-in short-term mating than lesbian women and that this gender difference
-was comparable to that existing among heterosexual individuals (Bailey
-et al., 1994). An indirect piece of evidence on differential standards
-for short-term mates comes from a recent study finding that
-significantly more gay men than lesbian women reported to have accepted
-a casual sexual offer from a same-gender person (Matsick et al., 2021).
-Past studies suggest that the gender difference in the acceptance rate
-of casual sexual offers may originate from men and women's differential
-standards for short-term mates (Conley et al., 2011; Hald \&
-Høgh-Olesen, 2010). Thus, as a postulation, gay men and lesbian women
-may also have different standards for short-term mates.
+in short-term mating than lesbian women were, and that this gender
+difference was comparable to that existing among heterosexual
+individuals (Bailey et al., 1994). An indirect piece of evidence on
+differential standards for short-term mates comes from a recent study
+finding that significantly more gay men than lesbian women reported to
+have accepted a casual sexual offer from a same-gender person (Matsick
+et al., 2021). Past studies suggest that the gender difference in the
+acceptance rate of casual sexual offers may originate from men and
+women's differential standards for short-term mates (Conley et al.,
+2011; Hald \& Høgh-Olesen, 2010). Thus, as a postulation, gay men may
+also have lower standards than lesbian women for short-term mates.
 
@@
 into behaviors when there are women willing to have sex with them. When
-short-term mating occurs, the number of short-term mating encounters and
-short-term mates is essentially the same for men and women (although
-this does not necessarily mean that the total number of men and women
-who have ever had short-term mating must be equal). Therefore, we would
-expect to observe no gender difference in short-term mating behaviors
-among heterosexual individuals even when there were gender differences
-in mating preferences.
+a new short-term mating encounter occurs, it counts towards men's total
+number of short-term mating encounters as well as towards women's.
+Similarly, a new short-term mate counts towards both men and women's
+total number of short-term mates. Therefore, the total number of
+short-term mating experiences and short-term mates must be equal between
+heterosexual men and women on a population level. However, it is
+important to note that although heterosexual men's total number of
+short-term mating is equal to that of women, this does not necessarily
+mean that the total number of men and women who have ever had short-term
+mating must be equal. It is possible that there is a smaller proportion
+of men (vs.~the proportion of women) who contribute to the total number
+of short-term mating. Following this line of reasoning, we would expect
+to observe no gender difference in short-term mating behaviors among
+heterosexual individuals even when there were gender differences in
+mating preferences.
 
@@
 we would theoretically expect to observe gender differences in
-short-term mating behaviors among gay men and lesbians. Moreover, we
-would also expect to find that gay men, as compared to heterosexual men,
-engaged in more short-term mating behaviors due to the lessened
+short-term mating behaviors between gay men and lesbian women. Moreover,
+we would also expect to find that gay men, as compared to heterosexual
+men, engaged in more short-term mating behaviors due to the lessened
 constraint on their mating preferences.
@@
 By using a spatial agent-based model, the present study investigated
-whether men and women's different mating preferences resulted in any
-gender differences in short-term mating behaviors, and if they did,
-under what circumstances. The interest in short-term mating was modeled
-as an individual's likelihood of deciding to have short-term mating at
-each time step. The standards for short-term mates were modeled as the
-minimum desirability of a potential mate with whom an individual was
-willing to have sex. Short-term mating behaviors were operationally
-defined as the number of short-term mating experiences and the number of
-past short-term mates.
+whether men and women's different preferences for short-term mating
+resulted in any gender differences in short-term mating behaviors, and
+if they did, under what circumstances. Preferences for short-term mating
+were operationally defined as the interest in short-term mating and
+standards for short-term mates (Buss \& Schmitt, 1993). Short-term
+mating behaviors were operationally defined as the number of short-term
+mating experiences and the number of past short-term mates (Petersen \&
+Hyde, 2010).
 
@@
 and lesbian women to examine whether constraints set by the opposite
-sex's preferences would make a difference in short-term mating
-behaviors. Individuals' sexual orientation was conceptualized in terms
-of behaviors only in our model. Heterosexual men had short-term mating
-or formed a long-term relationship with women, while gay men only with
-other men, and vice versa for women.
+sex's preferences would affect short-term mating behaviors. Individuals'
+sexual orientation was conceptualized in terms of behaviors only in our
+model. Heterosexual men had short-term mating or formed a long-term
+relationship only with women, while gay men only with other men, and
+vice versa for women.
 
@@
 experiences of men and women; (2) the number of short-term mates of men
-and women. Additionally, we had also documented the number of men and
-women in the mating pool (i.e., who had ever engaged in short-term
-mating); The average number of short-term mating experiences and
+and women. Additionally, we also measured the number of men and women in
+the mating pool (i.e., those with a non-zero number of short-term mating
+experiences). The average numbers of short-term mating experiences and
 short-term mates were calculated by taking the average among the whole
@@
 details (ODD) protocol of the model, which includes detailed scheduling
-and parameterization. The model can be downloaded from the Github online
-repository {[}link masked for peer review{]}. The model was programmed
-in Netlogo 6.2.1 (Wilensky, 1999).
+and parameterization. The model can be downloaded from the Open Science
+Framework {[}link masked for peer review{]}. The model was programmed in
+Netlogo 6.2.1 (Wilensky, 1999).
 
@@
 Using the agent-based model, the present study conducted two 2 (gender
-difference vs.~no difference in short-term mating likelihood) x 2
-(gender difference vs.~no difference in mating standard) experiments.
-Experiment 1 was run among heterosexual agents who only engaged in
-short-term or long-term relationships with agents of the opposite
-gender. Experiment 2 was run among gay men and lesbian women who only
-engaged in short-term or long-term relationships with agents of the same
-gender.
+difference vs.~no difference in the interest in short-term mating
+likelihood) x 2 (gender difference vs.~no difference in mating
+standards) experiments. Experiment 1 was run among heterosexual agents
+who only engaged in short-term or long-term relationships with agents of
+the opposite gender. Experiment 2 was run among gay men and lesbian
+women who only engaged in short-term or long-term relationships with
+agents of the same gender.
 
-Gender differences were modeled in agents' likelihood of engaging in
-short-term mating and the standard for short-term mates. The values of
-these parameters were set based on empirical findings in human mating
-psychology. We compared the conditions where there were gender
-differences in mating preferences with counterfactual conditions where
-gender differences were missing. When there was a gender difference in
-short-term mating likelihood, men had a 40\% likelihood of deciding to
-engage in short-term mating upon meeting a potential mate, while women
-had a likelihood of 25\% (Buss \& Schmitt, 1993; Schmitt et al., 2001;
-Schmitt, 2003). When there was no gender difference in short-term mating
-likelihood, both women and men had a likelihood of 25\%. When there was
-a gender difference in mating standards, men had a mating standard of 3
-(the minimum mate value of a potential partner with whom an agent is
-willing to have short-term mating, highest possible value = 10), while
-women had a standard of 5 (Kenrick et al., 1990; Regan, 1998). When
-there was no gender difference in mating standards, both men and women
-had a standard of 5.
+The interest in short-term mating was modeled as an agent's likelihood
+of deciding to have short-term mating at each time step. The standards
+for short-term mates were modeled as the minimum desirability of a
+potential mate with whom an agent was willing to have sex. The values of
+the two parameters were set based on empirical findings in human mating
+psychology. When there was a gender difference in short-term mating
+likelihood, men had a 40\% likelihood of deciding to engage in
+short-term mating, while women had a likelihood of 25\% (Buss \&
+Schmitt, 1993; Schmitt et al., 2001; Schmitt, 2003). When there was no
+gender difference in short-term mating likelihood, both women and men
+had a likelihood of 25\%. When there was a gender difference in mating
+standards, men had a mating standard of 3 (the highest possible value =
+10), while women had a standard of 5 (Kenrick et al., 1990; Regan,
+1998). When there was no gender difference in mating standards, both men
+and women had a standard of 5.
 
@@
 The likelihood of engaging in short-term mating and the standard for
-short-term mates were initialized either the same or differently for men
-and women, depending on the experimental conditions.
+short-term mates were initialized either identically or differently for
+men and women, depending on the experimental conditions.
 
@@
 At each time step, men and women moved and decided on short-term mating
-as the agents did in the heterosexual procedures. Half of the agents (an
-equal number of men and women) were also given the initiator status. The
-initiators checked to see whether there were other agents at the same
-location. The rest of the procedures were identical to the heterosexual
-procedures, except that the agents only chose those with the same gender
-as themselves as potential short-term mates or long-term partners.
+as the agents did in the heterosexual procedures. Half of the agents (75
+men and 75 women) were also given the initiator status. The initiators
+checked to see whether there were other agents at the same location. The
+rest of the procedures were identical to the heterosexual procedures,
+except that the agents only chose those with the same gender as
+potential short-term mates or long-term partners.
 
@@
 The model was run for 1,000 time steps in each simulation. We ran 10,000
-simulations for each experiment, and 2,500 simulations for each
+simulations for each experiment, including 2,500 simulations for each
 condition. We controlled for initializing random seeds in the model
@@
 
-\hypertarget{gender-differences-in-short-term-mating-behaviors-in-each-experiment}{%
-\subsection{Gender differences in short-term mating behaviors in each
-experiment}\label{gender-differences-in-short-term-mating-behaviors-in-each-experiment}}
+\hypertarget{gender-differences-in-short-term-mating-behaviors}{%
+\subsection{Gender differences in short-term mating
+behaviors}\label{gender-differences-in-short-term-mating-behaviors}}
 
@@
 In Experiment 1, however, when the means of the outcome variables were
-calculated among men and women who were in the mating pool (i.e., those
-with a non-zero number of short-term mating experiences) \textbf{(the
-number of individuals in the mating pool: M\textsubscript{m},
-SD\textsubscript{m}; M\textsubscript{w}, SD\textsubscript{w})}, there
-were gender differences in short-term mating behaviors when there were
-gender differences in mating preferences. The average number of
-short-term mating experiences was higher among heterosexual men
-(\emph{M} = 3.78, \emph{SD} = 0.50) than among heterosexual women
-(\emph{M} = 2.79, \emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p}
-\textless{} .001, Cohen's \emph{d} = 2.31. Likewise, the average number
-of short-term mates was higher among heterosexual men (\emph{M} = 2.12,
-\emph{SD} = 0.17) than among heterosexual women (\emph{M} = 1.56,
-\emph{SD} = 0.11), \emph{t}(4,998) = -135.85, \emph{p} \textless{} .001,
-Cohen's \emph{d} = 3.84.
+calculated among men and women in the mating pool (the number of
+individuals in the mating pool: \emph{M\textsubscript{m}} = 56.85,
+\emph{SD\textsubscript{m}} = 5.99; \emph{M\textsubscript{w}} = 77.04,
+\emph{SD\textsubscript{w}} = 7.53), there were gender differences in
+short-term mating behaviors when men and women had differential
+preferences for short-term mating. The average number of short-term
+mating experiences was higher among heterosexual men (\emph{M} = 3.78,
+\emph{SD} = 0.50) than among heterosexual women (\emph{M} = 2.79,
+\emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p} \textless{} .001,
+Cohen's \emph{d} = 2.31. Likewise, the average number of short-term
+mates was higher among heterosexual men (\emph{M} = 2.12, \emph{SD} =
+0.17) than among heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11),
+\emph{t}(4,998) = -135.85, \emph{p} \textless{} .001, Cohen's \emph{d} =
+3.84.
 
-\hypertarget{comparing-short-term-mating-behaviors-of-heterosexual-and-gay-men}{%
-\subsection{Comparing short-term mating behaviors of heterosexual and
-gay
-men}\label{comparing-short-term-mating-behaviors-of-heterosexual-and-gay-men}}
+\hypertarget{comparing-heterosexual-and-gay-men}{%
+\subsection{Comparing heterosexual and gay
+men}\label{comparing-heterosexual-and-gay-men}}
 
@@
 In an exploratory manner, we also compared across conditions to see
-which of the two dimensions of preferences for short-term mating
-contributed to gender differences in sexual behaviors.
+which of the two dimensions of mating preferences contributed to gender
+differences in short-term mating behaviors.
 
@@
 when men and women had different standards for short-term mates.
-Heterosexual men in the mating pool had a higher average number of
-short-term mating experiences and short-term mates than women in the
-mating pool, even when no gender difference existed in short-term mating
-likelihood (experiences: \emph{M\textsubscript{m}} = 2.82,
-\emph{SD\textsubscript{m}} = 0.36, \emph{M\textsubscript{w}} = 2.21,
-\emph{SD\textsubscript{w}} = 0.28, Cohen's \emph{d} = 1.89; partners:
-\emph{M\textsubscript{m}} = 1.76, \emph{SD\textsubscript{m}} = 0.15;
-\emph{M\textsubscript{w}} = 1.38, \emph{SD\textsubscript{w}} = 0.09,
-Cohen's \emph{d} = 3.13). In comparison, virtually no gender differences
-in short-term mating behaviors existed when men and women had the same
-mating standards (Table 1).
+Heterosexual men (vs.~heterosexual women) in the mating pool had a
+higher average number of short-term mating experiences and short-term
+mates as long as they had lower mating standards, even when no gender
+difference existed in short-term mating likelihood (experiences:
+\emph{M\textsubscript{m}} = 2.82, \emph{SD\textsubscript{m}} = 0.36,
+\emph{M\textsubscript{w}} = 2.21, \emph{SD\textsubscript{w}} = 0.28,
+Cohen's \emph{d} = 1.89; partners: \emph{M\textsubscript{m}} = 1.76,
+\emph{SD\textsubscript{m}} = 0.15; \emph{M\textsubscript{w}} = 1.38,
+\emph{SD\textsubscript{w}} = 0.09, Cohen's \emph{d} = 3.13). In
+comparison, virtually no gender differences in short-term mating
+behaviors existed when men and women had the same mating standards
+(Table 1).
 
@@
 behaviors emerged either when they had different short-term mating
-likelihood or when their mating standards were different. Gay men had a
-higher average number of short-term mating experiences and short-term
-mates when they had a higher short-term mating likelihood than lesbian
-women (experiences: \emph{M\textsubscript{m}} = 0.80,
+likelihood or when their mating standards were different. Gay men
+(vs.~lesbian women) had a higher average number of short-term mating
+experiences and short-term mates when they had a higher short-term
+mating likelihood (experiences: \emph{M\textsubscript{m}} = 0.80,
 \emph{SD\textsubscript{m}} = 0.23, \emph{M\textsubscript{w}} = 0.32,
@@
 \emph{M\textsubscript{w}} = 0.25, \emph{SD\textsubscript{w}} = 0.07,
-Cohen's \emph{d} = 2.60), or when they had a lower mating standards
+Cohen's \emph{d} = 2.60), or when they had lower mating standards
 (experiences: \emph{M\textsubscript{m}} = 1.05,
@@
 The present study aimed at using agent-based modeling to investigate
-whether men and women's different mating preferences resulted in any
-gender differences in short-term mating behaviors, specifically, in the
-number of short-term mating experiences and short-term mates, and if
-they did, under what circumstances. We raised two hypotheses: 1) there
-would be gender differences in short-term mating behaviors among gay men
-and lesbian women, with gay men being engaged in more such behaviors,
-and 2) gay men would engage in more short-term mating behaviors as
-compared to heterosexual men. The results from 1,000 time steps in a
-model simulating men and women's mating behaviors supported our
-hypotheses. First of all, as compared to lesbian women, gay men had a
-higher average number of short-term mating experiences and short-term
-mates. In contrast, we found no gender differences in short-term mating
-behaviors between heterosexual men and women. Secondly, gay men also had
-a higher average number of short-term mating experiences and short-term
-mates as compared to heterosexual men.
+whether men and women's different preferences for short-term mating
+resulted in any gender differences in short-term mating behaviors,
+specifically, in the number of short-term mating experiences and
+short-term mates, and if they did, under what circumstances. We raised
+two hypotheses: 1) gay men would engage in more short-term mating
+behaviors as compared to lesbian women, and 2) gay men would engage in
+more short-term mating behaviors as compared to heterosexual men. The
+results from 1,000 time steps in a model simulating men and women's
+mating behaviors supported our hypotheses. First of all, as compared to
+lesbian women, gay men had higher average numbers of short-term mating
+experiences and short-term mates. Secondly, gay men also had higher
+average numbers of short-term mating experiences and short-term mates as
+compared to heterosexual men. In contrast, we found no gender
+differences in short-term mating behaviors between heterosexual men and
+women, although heterosexual men in the mating pool did have higher
+average numbers of short-term mating experiences and short-term mates.
 
 As we expected, heterosexual men and women did not differ in short-term
-mating behaviors despite their different mating preferences. This was
-because the total numbers of short-term mating experiences and
-short-term mates of heterosexual men and women were exactly the same.
-Since the sex ratio was 1:1 in our model, the average number of
-short-term mating experiences and short-term mates must be equal between
-men and women as well. However, we did find that among individuals in
-the mating pool, men engaged in more short-term mating behaviors as
-compared to women. This was because there were more women than men in
-the mating pool (i.e., had ever engaged in short-term mating behaviors),
-resulting in lower averages among heterosexual women despite equal
-numbers of experiences and mates in total.
+mating behaviors despite their differential preferences for short-term
+mating. This was because heterosexual men and women had an equal total
+number of short-term mating experiences , so as the total number of
+short-term mates. Since the sex ratio was 1:1 in our model, the average
+number of short-term mating experiences and short-term mates must be
+equal between men and women as well. However, we did find that among
+individuals in the mating pool, men engaged in more short-term mating
+behaviors as compared to women. This was because there were more women
+than men in the mating pool, resulting in lower averages among
+heterosexual women despite the equal numbers of experiences and mates in
+total.
 
 Moreover, gender differences in short-term mating behaviors emerged when
-heterosexual men and women had different standards for short-term mates,
-but not when they had different likelihood of engaging in short-term
-mating. When women had a higher standard than men did, less men than
-women in the population were above a potential partner's standards and
-thus had a chance to have sex with them. This contributed to the unequal
-number of men and women in the mating pool, which led to gender
-differences in short-term mating behaviors.
+heterosexual men and women had different mating standards, but not when
+they had different short-term mating likelihood. When women had a higher
+standard than men did, less men than women in the population were above
+a potential partner's standard and thus had a chance to have sex with
+them. This contributed to the unequal number of men and women in the
+mating pool, which led to gender differences in short-term mating
+behaviors among this population.
 
@@
 individuals (e.g., Petersen \& Hyde, 2010) appear to be perplexing
-because this is theoretically illogical (e.g., Gurman, 1989). Possible
-explanations for these empirical results have to highlight caveats in
-the observation process. One possibility is that there was sampling bias
-in the observations (e.g., Wiederman \& Dubois, 1998) since surveys
-regarding short-term mating behaviors may tend to attract individuals
-who already engage in such behaviors. Another possibility is that
-heterosexual men and women tend to report short-term mating behaviors
-differently. This difference may be a result of social desirability bias
-(Alexander \& Fisher, 2003) or due to men and women's different
-estimation strategies (e.g., men tend to round up) (Brown \& Sinclair,
-1999).
+because this is illogical (e.g., Gurman, 1989). Possible explanations
+for these empirical results have to highlight caveats in the observation
+process. One possibility is that there was sampling bias in the
+observations (e.g., Wiederman \& Dubois, 1998) since surveys regarding
+short-term mating behaviors may tend to attract individuals who already
+engage in such behaviors. Another possibility is that heterosexual men
+and women tend to report short-term mating behaviors differently. This
+difference may be a result of social desirability bias (Alexander \&
+Fisher, 2003) or due to men and women's different estimation strategies
+(e.g., men tend to round up) (Brown \& Sinclair, 1999).
 
 Among gay men and lesbian women, large gender differences in short-term
-mating behaviors existed when men and women had different mating
-preferences, which was in line with empirical observations (e.g., Peplau
-et al., 1997, 2004). This was probably because the number of short-term
-mating experiences and short-term mates no longer counted towards men
-and women simultaneously. Any gender differences in mating preferences
-would result in differences in behaviors. A closer look at the results
-did support this postulation. Either a difference in the likelihood of
-short-term mating or a difference in mating standards alone could
-contribute to gender differences in mating behaviors. This was perhaps
-because the former increased the probability of both parties of a given
-gay couple deciding to have short-term mating, and the latter increased
-the probability of both of them meeting each other's standards, as
-compared to the case of a given lesbian couple.
+mating behaviors existed when men and women had differential preferences
+for short-term mating, which was in line with empirical observations
+(e.g., Peplau et al., 1997, 2004). This was probably because the number
+of short-term mating experiences and short-term mates no longer counted
+towards men and women simultaneously. Any gender differences in mating
+preferences would result in differences in behaviors. A closer look at
+the results did support this postulation. Either a difference in the
+likelihood of short-term mating or a difference in mating standards
+alone could contribute to gender differences in mating behaviors. This
+was perhaps because the former increased the probability of both parties
+of a given gay couple deciding to have short-term mating, and the latter
+increased the probability of both of them meeting each other's
+standards, as compared to the case of a given lesbian couple.
 
@@
 was consistent with the empirical literature (e.g., Peplau et al.,
-1997). Interestingly, gay men and heterosexual men had the same
-likelihood of short-term mating and the same standards for short-term
-mates in our model. The only difference was a change in the preferences
-in their potential partners. When men's partners had a stronger
-preferences for short-term mating (i.e., having men vs.~having women as
-potential partners), men also appeared to engage in more short-term
-mating behaviors.
+1997). Interestingly, gay men and heterosexual men had the same mating
+likelihood and the same standards for short-term mates in our model. The
+only difference was a change in the preferences of potential partners.
+When men's partners had a stronger preferences for short-term mating
+(i.e., having men vs.~having women as potential partners), men also
+appeared to engage in more short-term mating behaviors.
 
@@
 Using agent-based modeling, the present study theoretically explored the
-circumstances under which men and women's different mating preferences
-resulted in gender differences in short-term mating behaviors. We found
-when men (vs.~women) had a stronger preferences for short-term mating,
-heterosexual men and women engaged in short-term mating behaviors to the
-same extent, while gay men engaged in more short-term mating behaviors
-as compared to lesbian women. We also found that gay men engaged in more
-short-term mating behaviors than heterosexual men did.
-
-Theses results highlight the distinction between psychological
+circumstances under which men and women's differential preferences for
+short-term mating resulted in gender differences in short-term mating
+behaviors. We found when men (vs.~women) had a stronger preferences for
+short-term mating, heterosexual men and women engaged in short-term
+mating behaviors to the same extent, while gay men engaged in more
+short-term mating behaviors as compared to lesbian women. We also found
+that gay men engaged in more short-term mating behaviors than
+heterosexual men did. Theses results highlight the distinction between
 preferences and behaviors in human mating. Individuals' mating behaviors
@@
 heterosexual individuals. Our findings suggest that there may be factors
-in the observation process that lead to such differences. Future
-research in human sexuality should note such possibilities and interpret
-any observed gender differences in short-term mating behaviors
-cautiously.
+in the observation process, such as sampling bias, that lead to the
+observed differences. Future research in human sexuality should note
+such possibilities and interpret any observed gender differences in
+short-term mating behaviors cautiously.
 

### 2022-05-16 submission/manuscript.Rmd
minor edits to the figures

@@
     keep_tex: true
+  word_document: true
 geometry: margin=1.0in
@@
 
-# An Agent-based Model of Gender Differences in Short-term Mating Behaviors as a Result of Mating Preferences {-}
+# An Agent-Based Model of Gender Differences in Short-Term Mating Behaviors as a Result of Mating Preferences {-}
 
@@
   \centering
-  \includegraphics[width=70mm]{figures/fig1_men_vs_women.pdf}
+  \includegraphics[width=100mm]{figures/fig1_men_vs_women.pdf}
   \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women.

### 2022-05-16 submission/manuscript.tex
minor edits to the figures

@@
 \hypertarget{an-agent-based-model-of-gender-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}{%
-\section*{An Agent-based Model of Gender Differences in Short-term
+\section*{An Agent-Based Model of Gender Differences in Short-Term
 Mating Behaviors as a Result of Mating
 Preferences}\label{an-agent-based-model-of-gender-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}}
-\addcontentsline{toc}{section}{An Agent-based Model of Gender
-Differences in Short-term Mating Behaviors as a Result of Mating
+\addcontentsline{toc}{section}{An Agent-Based Model of Gender
+Differences in Short-Term Mating Behaviors as a Result of Mating
 Preferences}

### 2022-05-16 code/plot_hetero_vs_gay_men.R

@@ -68,10 +68,11 @@ casual_tib %>%
     axis.text.x = element_blank(),
     panel.grid = element_blank(),
     panel.spacing = unit(0.5, "line"),
-    strip.text = element_text(size = 11),
+    strip.text = element_text(size = 12),
     strip.placement = "outside",
     legend.position = "bottom",
-    legend.box.spacing = unit(0.1, "line")
+    legend.box.spacing = unit(0.1, "line"),
+    legend.text = element_text(size = 12)
   )
 
 ggsave(output_file, width = 9, height = 5)

### 2022-05-16 code/plot_men_vs_women.R

@@ -6,7 +6,7 @@
 # notes: none
 
 # load libraries
-library(tidyverse); library(ggplot2); library(wesanderson); library(here)
+library(tidyverse); library(wesanderson); library(here)
 
 args <- commandArgs(trailingOnly = TRUE)
 #args <- c("data/processed/casual_sex_sim.csv", "submission/figures/fig1_men_vs_women.pdf")
@@ -79,4 +79,4 @@ casual_tib %>%
     legend.box.spacing = unit(0, "npc")
   )
 
-ggsave(output_file, width = 5, height = 8)
+ggsave(output_file, width = 5, height = 6)

### 2022-05-27 submission/manuscript.Rmd
minor language edits to the manuscript

@@
 
-^2^ xxxx
+^2^ Faculty of Arts, Psychology and Theology, Åbo Akademi University
 
@@
 
-Gender differences in short-term mating behaviors have been a well-documented phenomenon in human sexuality research.
-Existing studies usually conflate gender differences in mating preferences with differences in sexual behaviors, which is theoretically dubious.
-Using an agent-based model, the present study investigated the circumstances under which men and women’s differential preferences for short-term mating would result in gender differences in short-term mating behaviors.
-The results from the model suggested that heterosexual men and women had the same average number of short-term mating experiences and short-term mates even when men had stronger preferences for short-term mating.
-Gender differences in mating behaviors only emerged when heterosexual men and women in the mating pool (i.e., those with a non-zero number of short-term mating experiences) were considered.
-Moreover, gay men had a higher average number of both outcomes than lesbian women as well as than heterosexual men when men had stronger preferences for short-term mating.
+Gender differences in short-term mating behaviors are well-documented in human sexuality research.
+Existing studies usually conflate gender differences in mating preferences with differences in sexual behaviors, which is theoretically problematic.
+Using an agent-based model, we investigated the circumstances under which heterosexual and homosexual men and women’s differential preferences for short-term mating would result in gender differences in short-term mating behaviors.
+The model showed that when all individuals in a closed heterosexual population were considered,  men and women had the same average number of short-term mating experiences and short-term mates even when men had stronger preferences for short-term mating.
+Men (vs.
+women) had a higher average number of both experiences and mates only when heterosexual men and women in the mating pool (i.e., those with a non-zero number of short-term mating experiences) were considered.
+Moreover, when men had stronger preferences for short-term mating than women, gay men had a higher average number of both experiences and mates compared to both lesbian women and heterosexual men.
 These results suggest that theoretically speaking, even when gender differences in mating preferences existed, those in short-term mating behaviors only occurred among particular populations, or when men’s preferences for short-term mating are not constrained by those of women.
@@
 
-Gender differences in sexual behaviors, especially short-term mating behaviors, have been a well-documented phenomenon in human sexuality research.
-For example, research has found that heterosexual men, as compared to heterosexual women, have a higher average number of past short-term sexual partners [@oliver_gender_1993; @petersen_meta-analytic_2010; @rissel_heterosexual_2014], have short-term mating more frequently [@petersen_meta-analytic_2010], and engage in extramarital sex more often [@petersen_meta-analytic_2010].
+Gender differences in sexual behaviors, especially short-term mating behaviors, are well-documented in human sexuality research.
+For example, research has found that heterosexual men, as compared to heterosexual women, have a higher average number of past short-term sexual partners [@oliver_gender_1993; @petersen_meta-analytic_2010; @rissel_heterosexual_2014], and engage in both short-term mating and extramarital sex more often [@petersen_meta-analytic_2010].
 These gender differences have also been observed between gay men and lesbian women [@bailey_effects_1994; @bryant_relationship_1994; @peplau_national_1997; @peplau_sexuality_2004].
 
-In the existing literature, gender differences in sexual behaviors are not usually distinguished from those in attitudes towards or preferences for short-term mating.
-Some researchers study gender differences on the two levels simultaneously without a conceptual distinction [e.g., @petersen_meta-analytic_2010], whereas some implicitly equate the two, assuming that behavioral differences are a direct expression of the psychological ones [e.g., @schmitt_are_2001].
+In the existing literature, gender differences in actual sexual behaviors are not usually distinguished from those in attitudes towards or preferences for short-term mating.
+Some researchers study gender differences at the two levels simultaneously without a conceptual distinction [e.g., @petersen_meta-analytic_2010], whereas some implicitly equate the two, assuming that behavioral differences are a direct expression of psychological ones [e.g., @schmitt_are_2001].
 
@@
 
-The present study took gender differences in mating preferences as a presumption, which was conceptualized by sexual strategy theory [@buss_sexual_1993] and repeatedly found support by empirical studies [e.g., @schmitt_universal_2003; @walter_sex_2020].
-Using an agent-based model, we investigated whether men and women's differential preferences for short-term mating resulted in any gender differences in short-term mating behaviors, specifically, in the number of short-term mating experiences and short-term mates, and if they did, under what circumstances.
+As a starting point, we took gender differences in mating preferences as conceptualized by the sexual strategy theory [@buss_sexual_1993] and repeatedly supported by empirical investigations [e.g., @schmitt_universal_2003; @walter_sex_2020].
+Using an agent-based model, we investigated whether men and women's differential preferences for short-term mating would result in gender differences in short-term mating behaviors, and if so, then under what conditions they would result in differences in the number of short-term mating experiences and short-term mates.
 
@@
 Gender differences in mating preferences have been studied in the light of sexual strategy theory [@buss_sexual_1993].
-It posits that since the minimum investment that men devote to their offspring (contribution of sperm through one sexual act) is lower than that of women (gestation, labor, and lactation), men tend to have short-term mating as a larger part of their mating strategy than women do.
-This is because women's high minimum investment leads to higher opportunity cost (vs.
-men) if they have sex with a suboptimal partner and give birth to offspring with a low survival chance.
-As a result, men may have a greater interest in short-term mating, desire a larger number of short-term mates in a given period, and be less selective with respect to accepting a potential mate [@buss_sexual_1993].
+It posits that since the minimum obligatory investment that men must devote to their offspring (contribution of sperm through one sexual act) is lower than that of women (gestation, labor, and lactation), men tend to be relatively more interested in short-term mating compared to women.
+This is because the number of offspring women can produce is limited and cannot be increased by mating with a large number of men, whereas the reverse is the case for men.
+As a result, men are predicted to not only have a greater interest in short-term mating, but also desire a larger number of short-term mates in a given period and be less selective with respect to accepting a potential mate [@buss_sexual_1993].
 
-The hypotheses derived from sexual strategy theory have received extensive support from empirical studies.
-For example, men reported to be currently seeking short-term mates to a larger extent than women did [@buss_sexual_1993; @schmitt_are_2001; @schmitt_universal_2003], and a larger proportion of them were in any way seeking short-term mates (vs.
+The hypotheses derived from sexual strategy theory have received extensive support in empirical studies.
+For example, men have reported to be currently seeking short-term mates to a larger extent than women [@buss_sexual_1993; @schmitt_are_2001; @schmitt_universal_2003], and a larger proportion of men were in any way seeking short-term mates (vs.
 not seeking) [@schmitt_universal_2003].
-These have been found among U.S.
+Similar results have been found among both U.S.
 college students [@buss_sexual_1993; @schmitt_are_2001] as well as in ten world regions in a cross-cultural study [@schmitt_universal_2003].
-Similarly, men across the world also reported to desire more short-term sexual partners compared to women for a number of given time periods (e.g., a month, a year) [@buss_sexual_1993; @schmitt_universal_2003; @mcburney_preferred_2005].
-The gender differences were significant regardless of whether they were estimated by mean [@buss_sexual_1993; @schmitt_are_2001; @schmitt_universal_2003], median [@schmitt_are_2001; @schmitt_universal_2003], or percentage [@schmitt_universal_2003] statistics.
+Similarly, men across the world have also reported to desire more short-term sexual partners compared to women over different future time periods (e.g., a month, a year) [@buss_sexual_1993; @schmitt_universal_2003; @mcburney_preferred_2005].
+The gender differences have been found regardless of whether they were estimated using mean [@buss_sexual_1993; @schmitt_are_2001; @schmitt_universal_2003], median [@schmitt_are_2001; @schmitt_universal_2003], or percentage [@schmitt_universal_2003] statistics.
 
@@
 For example, studies using U.S.
-college samples found that the minimum percentile ranks that men found acceptable for a potential short-term sexual partner were lower than those accepted by women, both in terms of overall desirability and individual traits (e.g., social status, attractiveness) [@kenrick_evolution_1990; @regan_minimum_1998].
-A study also found that when presented with identical descriptions of potential mates, men on average rated them as more desirable than women did [@wiederman_evolution_1998].
+college samples have found that the minimum percentile ranks that men found acceptable for a potential short-term sexual partner were lower than those accepted by women, both in terms of overall desirability and individual traits (e.g., social status, attractiveness) [@kenrick_evolution_1990; @regan_minimum_1998].
+Another study also found that when presented with identical descriptions of potential mates, men on average rated them as more desirable than women did [@wiederman_evolution_1998].
 
@@
 found that gay men were more interested in short-term mating than lesbian women were, and that this gender difference was comparable to that existing among heterosexual individuals [@bailey_effects_1994].
-An indirect piece of evidence on differential standards for short-term mates comes from a recent study finding that significantly more gay men than lesbian women reported to have accepted a casual sexual offer from a same-gender person [@matsick_gender_2021].
+An additional indirect piece of evidence on differential standards for short-term mates comes from a recent study finding that significantly more gay men than lesbian women reported to have accepted a casual sexual offer from a same-gender person [@matsick_gender_2021].
 Past studies suggest that the gender difference in the acceptance rate of casual sexual offers may originate from men and women’s differential standards for short-term mates [@conley_women_2011; @hald_receptivity_2010].
@@
 ## Constraints on men's preferences for short-term mating
-Since heterosexual sex involves both a man and a woman in most cases, men's interest in short-term mating can be constrained by women's preference for long-term relationships [@archer_reality_2019; @symons_evolution_1979].
-This is because men’s short-term mating preferences can only translate into behaviors when there are women willing to have sex with them.
-When a new short-term mating encounter occurs, it counts towards men’s total number of short-term mating encounters as well as towards women’s.
+Since heterosexual sex in most cases involves one man and one woman, men's relatively high interest in short-term mating can be constrained by women's preference for long-term relationships [@archer_reality_2019; @symons_evolution_1979].
+This is because men’s short-term mating preferences – with the relatively rare exception of sexual violence – can only translate into behaviors when there are women willing to have sex with them.
+When a new short-term mating encounter occurs, it counts both towards men’s total number of short-term mating encounters as well as towards women’s.
 Similarly, a new short-term mate counts towards both men and women’s total number of short-term mates.
-Therefore, the total number of short-term mating experiences and short-term mates must be equal between heterosexual men and women on a population level.
+Therefore, the total number of short-term mating experiences and short-term mates must be equal between heterosexual men and women at the population level.
 However, it is important to note that although heterosexual men’s total number of short-term mating is equal to that of women, this does not necessarily mean that the total number of men and women who have ever had short-term mating must be equal.
@@
 the proportion of women) who contribute to the total number of short-term mating.
-Following this line of reasoning, we would expect to observe no gender difference in short-term mating behaviors among heterosexual individuals even when there were gender differences in mating preferences.
+Following this line of reasoning, we would expect to observe no gender difference in short-term mating behaviors among heterosexual individuals even when there are gender differences in mating preferences.
 
-As a comparison, in the cases of gay men and lesbian women, men’s preferences are not constrained by women’s, but only by those of other men, who, arguably, have more similar preferences.
+As a comparison, in the cases of gay men and lesbian women, men’s preferences are not constrained by women’s, but only by those of other men, who, arguably, have a similar high interest in short-term mating.
 This would allow for a more direct behavioral expression of men’s mating preferences.
-The notion that gay men have less restricted preferences was borne out in the proportion of individuals who have engaged in extradyadic sex [@peplau_sexuality_2004].
-A study showed that the proportions of heterosexual men and women who have engaged in extradyadic sex were 26% and 21%, respectively, while the statistics among gay men and lesbian women were 82% and 28%, respectively [@peplau_sexuality_2004].
-Therefore, we would theoretically expect to observe gender differences in short-term mating behaviors between gay men and lesbian women.
-Moreover, we would also expect to find that gay men, as compared to heterosexual men, engaged in more short-term mating behaviors due to the lessened constraint on their mating preferences.
+The notion that gay men have less restricted preferences is borne out in the proportion of individuals who have engaged in extradyadic sex [@peplau_sexuality_2004].
+A study showed that the proportions of heterosexual men and women who had engaged in extradyadic sex were 26% and 21%, respectively, while the statistics among gay men and lesbian women were 82% and 28%, respectively [@peplau_sexuality_2004].
+Therefore, we would expect to observe gender differences in short-term mating behaviors between gay men and lesbian women.
+Moreover, we would also expect to find that gay men, compared to heterosexual men, engaged in more short-term mating behaviors due to less constraints on their mating preferences.
 
@@
 
-By using a spatial agent-based model, the present study investigated whether men and women’s different preferences for short-term mating resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances.
-Preferences for short-term mating were operationally defined as the interest in short-term mating and standards for short-term mates [@buss_sexual_1993].
+By using a spatial agent-based model, the present study investigated whether men and women’s differential preferences for short-term mating would result in gender differences in short-term mating behaviors, and if they did, under what circumstances.
+Preferences for short-term mating were operationally defined as the likelihood of engaging in short-term mating when encountering a mate as well as the standards for short-term mates [@buss_sexual_1993].
 Short-term mating behaviors were operationally defined as the number of short-term mating experiences and the number of past short-term mates [@petersen_meta-analytic_2010].
@@
 Individuals’ sexual orientation was conceptualized in terms of behaviors only in our model.
-Heterosexual men had short-term mating or formed a long-term relationship only with women, while gay men only with other men, and vice versa for women.
+Heterosexual men had short-term mating or formed a long-term relationship only with women, while gay men only with other men, and mutatis mutandis for women.
 
-We raised the following hypotheses in the present study: when there were gender differences in preferences for short-term mating, 1) there would be gender differences in short-term mating behaviors among gay men and lesbian women, with gay men being engaged in more such behaviors, and 2) gay men would engage in more short-term mating behaviors as compared to heterosexual men.
+We formulated the following hypotheses in the present study: assuming gender differences in preferences for short-term mating, 1) there would be gender differences in short-term mating behaviors among gay men and lesbian women, with gay men being engaged in more such behaviors, and 2) gay men would engage in more short-term mating behaviors as compared to heterosexual men.
 
@@
 We developed an agent-based model to represent a simplified environment where men and women can move around, search for mates, and form long-term and/or short-term relationships.
-Space and time are modeled as discrete variables.
+Space and time were modeled as discrete variables.
 Space was represented as discrete locations on a two-dimensional 33*33 lattice.
@@
 Additionally, we also measured the number of men and women in the mating pool (i.e., those with a non-zero number of short-term mating experiences).
-The average numbers of short-term mating experiences and short-term mates were calculated by taking the average among the whole population of men/women (*N~m~* = *N~w~* = 150) and among those who had engaged in short-term mating.
+The average numbers of short-term mating experiences and short-term mates were calculated by taking the average among the whole population of men and women (*N~men~* = *N~women~* = 150) and among those who had engaged in any short-term mating.
 
@@
 When there was no gender difference in short-term mating likelihood, both women and men had a likelihood of 25%.
-When there was a gender difference in mating standards, men had a mating standard of 3 (the highest possible value = 10), while women had a standard of 5 [@kenrick_evolution_1990; @regan_minimum_1998].
+When there was a gender difference in mating standards, men had a mating standard of 3 (the highest possible value = 10), while women had a standard of 5 [@kenrick_evolution_1990; @regan_minimum_1998], that is, they would not mate with a person with a lower mate value.
 When there was no gender difference in mating standards, both men and women had a standard of 5.
@@
 ### Procedures
-#### Heterosexual procedures.
+#### Procedures for heterosexual agents.
 At each time step, agents first checked whether they were in a long-term relationship.
@@
 If they were in a long-term relationship, they did not move.
-Then, the agents decided on whether to engage in short-term mating by a chance of the chosen likelihood (either 25% or 40%).
+Then, the agents decided on whether to engage in short-term mating using the predetermined likelihood (either 25% or 40%).
 
 Women checked to see if any men were at the same location.
-If there were, they randomly chose one of them as their potential short-term mate.
+If there were, they randomly chose one of them as a potential short-term mate.
 If both men and women met each other’s mating standards and both of them decided to engage in short-term mating, they had sex.
 This would result in increasing both parties’ number of short-term mating experiences by one.
-They also recorded each other on their lists of past short-term mates if they were not on the lists yet.
+They also recorded each other on their respective lists of past short-term mates if they were not on the lists yet.
 
@@
 There was a 10% of chance that a pair would form a long-term relationship.
-After forming a long-term relationship, both men and women changed to coupled status and register each other as the long-term partner.
+After forming a long-term relationship, both men and women changed to coupled status and registered each other as their long-term partner.
 
-#### Gay men and lesbian women procedures.
-At each time step, men and women moved and decided on short-term mating as the agents did in the heterosexual procedures.
-Half of the agents (75 men and 75 women) were also given the initiator status.
+#### Procedures for gay men and lesbian women agents.
+At each time step, men and women moved and decided on short-term mating as the agents did in the heterosexual case.
+Half of the agents (75 men and 75 women) were also given an initiator status.
 The initiators checked to see whether there were other agents at the same location.
@@
 
-## Statistical analysis
+## Statistical analyses
 Statistical analyses were conducted using `r R.version.string %>% str_replace(" \\(.*\\)", "")` [@r] and the figures were generated by the ggplot2 package [@ggplot2].
 Two-tailed independent samples *t*-tests were used for all statistical comparisons.
-The data were assumed to be normally distributed within each condition but was not formally tested.
+The data were assumed to be normally distributed within each condition.
 
@@
 
-The results from Experiment 1 showed that when there were gender differences in preferences for short-term mating, there was no gender difference in the average number of short-term mating experiences among heterosexual individuals (*M~m~* = `r m_exp_all.mean_011`, *SD~m~* = `r m_exp_all.sd_011`; *M~w~* = `r f_exp_all.mean_011`, *SD~w~* = `r f_exp_all.sd_011`), Cohen's *d* = `r exp_all.d_011`.
-Nor was there a difference in the average number of short-term mates (*M~m~* = `r m_partner_all.mean_011`, *SD~m~* = `r m_partner_all.sd_011`; *M~w~* = `r f_partner_all.mean_011`, *SD~w~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011` (Figure 1).
+The results from Experiment 1 showed that when there were gender differences in preferences for short-term mating, there was no gender difference in the average number of short-term mating experiences among heterosexual individuals (*M~men~* = `r m_exp_all.mean_011`, *SD~men~* = `r m_exp_all.sd_011`; *M~women~* = `r f_exp_all.mean_011`, *SD~women~* = `r f_exp_all.sd_011`), Cohen's *d* = `r exp_all.d_011`.
+Nor was there a difference in the average number of short-term mates (*M~men~* = `r m_partner_all.mean_011`, *SD~men~* = `r m_partner_all.sd_011`; *M~w~* = `r f_partner_all.mean_011`, *SD~women~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011` (Figure 1).
 
@@
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-Statistics were calculated using the full population of men and women in the model (\textit{N\textsubscript{m}} = \textit{N\textsubscript{w}} = 150).}
+Statistics were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
 \end{figure}
@@
 
-In Experiment 1, however, when the means of the outcome variables were calculated among men and women in the mating pool (the number of individuals in the mating pool: *M~m~* = `r m_inpool.mean_011`, *SD~m~* = `r m_inpool.sd_011`; *M~w~* = `r f_inpool.mean_011`, *SD~w~* = `r f_inpool.sd_011`), there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating.
+In Experiment 1, however, when the means of the outcome variables were calculated only among men and women in the mating pool (the number of individuals in the mating pool: *M~men~* = `r m_inpool.mean_011`, *SD~men~* = `r m_inpool.sd_011`; *M~women~* = `r f_inpool.mean_011`, *SD~women~* = `r f_inpool.sd_011`), there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating.
 The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`.
@@
 
-The results comparing across the two experiments revealed that gay men engaged in short-term mating behaviors more than heterosexual men did (Figure 2).
+Gay men engaged in short-term mating behaviors more than heterosexual men did (Figure 2).
 The average number of short-term mating experiences was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`.
@@
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-Statistics were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hm}} = \textit{N\textsubscript{gm}} = 150).}
+Statistics were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
 \end{figure}
@@
 
-In an exploratory manner, we also compared across conditions to see which of the two dimensions of mating preferences contributed to gender differences in short-term mating behaviors.
+We also ran analyses across conditions to see which of the two dimensions of mating preferences contributed to gender differences in short-term mating behaviors.
 
@@
 
-Among heterosexual individuals, gender differences in short-term mating behaviors, as calculated among individuals in the mating pool, emerged when men and women had different standards for short-term mates.
+Among heterosexual individuals, gender differences in short-term mating behaviors, when calculated among individuals in the mating pool, emerged when men and women had different standards for short-term mates.
 Heterosexual men (vs.
-heterosexual women) in the mating pool had a higher average number of short-term mating experiences and short-term mates as long as they had lower mating standards, even when no gender difference existed in short-term mating likelihood (experiences: *M~m~* = `r m_exp_ip.mean_001`, *SD~m~* = `r m_exp_ip.sd_001`, *M~w~* = `r f_exp_ip.mean_001`, *SD~w~* = `r f_exp_ip.sd_001`, Cohen's *d* = `r exp_ip.d_001`; partners: *M~m~* = `r m_partner_ip.mean_001`, *SD~m~* = `r m_partner_ip.sd_001`; *M~w~* = `r f_partner_ip.mean_001`, *SD~w~* = `r f_partner_ip.sd_001`, Cohen's *d* = `r partner_ip.d_001`).
+heterosexual women) in the mating pool had a higher average number of short-term mating experiences and short-term mates as long as they had lower mating standards, even when no gender difference existed in short-term mating likelihood (experiences: *M~men~* = `r m_exp_ip.mean_001`, *SD~men~* = `r m_exp_ip.sd_001`, *M~women~* = `r f_exp_ip.mean_001`, *SD~women~* = `r f_exp_ip.sd_001`, Cohen's *d* = `r exp_ip.d_001`; partners: *M~men~* = `r m_partner_ip.mean_001`, *SD~men~* = `r m_partner_ip.sd_001`; *M~women~* = `r f_partner_ip.mean_001`, *SD~women~* = `r f_partner_ip.sd_001`, Cohen's *d* = `r partner_ip.d_001`).
 In comparison, virtually no gender differences in short-term mating behaviors existed when men and women had the same mating standards (Table 1).
@@
   footnote(
-    general = "\\\\textit{Note.} The statistics were calculated with subsamples of men and women who had had enagged in short-term mating behaviors.
+    general = "\\\\textit{Note.} The statistics were calculated with subsamples of men and women who had had engaged in short-term mating behaviors.
 See Supplementary Materials for the mean and standard deviation of sample sizes.",
@@
 
-Among gay men and lesbian women, gender differences in short-term mating behaviors emerged either when they had different short-term mating likelihood or when their mating standards were different.
+Among gay men and lesbian women, gender differences in short-term mating behaviors emerged both when they had different short-term mating likelihood and when their mating standards were different.
 Gay men (vs.
-lesbian women) had a higher average number of short-term mating experiences and short-term mates when they had a higher short-term mating likelihood (experiences: *M~m~* = `r m_exp_all.mean_110`, *SD~m~* = `r m_exp_all.sd_110`, *M~w~* = `r f_exp_all.mean_110`, *SD~w~* = `r f_exp_all.sd_110`, Cohen's *d* = `r exp_all.d_110`; partners: *M~m~* = `r m_partner_all.mean_110`, *SD~m~* = `r m_partner_all.sd_110`, *M~w~* = `r f_partner_all.mean_110`, *SD~w~* = `r f_partner_all.sd_110`, Cohen's *d* = `r partner_all.d_110`), or when they had lower mating standards (experiences: *M~m~* = `r m_exp_all.mean_101`, *SD~m~* = `r m_exp_all.sd_101`, *M~w~* = `r f_exp_all.mean_101`, *SD~w~* = `r f_exp_all.sd_101`, Cohen's *d* = `r exp_all.d_101`; partners: *M~m~* = `r m_partner_all.mean_101`, *SD~m~* = `r m_partner_all.sd_101`, *M~w~* = `r f_partner_all.mean_101`, *SD~w~* = `r f_partner_all.sd_101`, Cohen's *d* = `r partner_all.d_101`).
+lesbian women) had a higher average number of short-term mating experiences and short-term mates when they had a higher short-term mating likelihood (experiences: *M~men~* = `r m_exp_all.mean_110`, *SD~men~* = `r m_exp_all.sd_110`, *M~women~* = `r f_exp_all.mean_110`, *SD~women~* = `r f_exp_all.sd_110`, Cohen's *d* = `r exp_all.d_110`; partners: *M~men~* = `r m_partner_all.mean_110`, *SD~men~* = `r m_partner_all.sd_110`, *M~women~* = `r f_partner_all.mean_110`, *SD~women~* = `r f_partner_all.sd_110`, Cohen's *d* = `r partner_all.d_110`), or when they had lower mating standards (experiences: *M~men~* = `r m_exp_all.mean_101`, *SD~men~* = `r m_exp_all.sd_101`, *M~women~* = `r f_exp_all.mean_101`, *SD~women~* = `r f_exp_all.sd_101`, Cohen's *d* = `r exp_all.d_101`; partners: *M~men~* = `r m_partner_all.mean_101`, *SD~men~* = `r m_partner_all.sd_101`, *M~women~* = `r f_partner_all.mean_101`, *SD~women~* = `r f_partner_all.sd_101`, Cohen's *d* = `r partner_all.d_101`).
 In comparison, virtually no gender differences in short-term mating behaviors existed when gay men and lesbian women had the same short-term mating likelihood and mating standards (Table 2).
@@
   footnote(
-    general = "\\\\textit{Note.} \\\\textit{N\\\\textsubscript{m}} = \\\\textit{N\\\\textsubscript{w}} = 150 in all conditions.",
+    general = "\\\\textit{Note.} \\\\textit{N\\\\textsubscript{men}} = \\\\textit{N\\\\textsubscript{women}} = 150 in all conditions.",
     general_title = "", escape = FALSE,
@@
 
-The present study aimed at using agent-based modeling to investigate whether men and women’s different preferences for short-term mating resulted in any gender differences in short-term mating behaviors, specifically, in the number of short-term mating experiences and short-term mates, and if they did, under what circumstances.
-We raised two hypotheses: 1) gay men would engage in more short-term mating behaviors as compared to lesbian women, and 2) gay men would engage in more short-term mating behaviors as compared to heterosexual men.
-The results from 1,000 time steps in a model simulating men and women’s mating behaviors supported our hypotheses.
+The present study used agent-based modeling to investigate whether men and women’s differential preferences for short-term mating would result in gender differences in short-term mating behaviors, and if so, then under what conditions they would result in differences in the number of short-term mating experiences and short-term mates.
+We formulated two hypotheses: 1) gay men would engage in more short-term mating behaviors as compared to lesbian women, and 2) gay men would engage in more short-term mating behaviors as compared to heterosexual men.
+The results from 1,000 time steps in a model simulating men and women’s mating behaviors provided strong evidence in favor of our hypotheses.
 First of all, as compared to lesbian women, gay men had higher average numbers of short-term mating experiences and short-term mates.
 Secondly, gay men also had higher average numbers of short-term mating experiences and short-term mates as compared to heterosexual men.
-In contrast, we found no gender differences in short-term mating behaviors between heterosexual men and women, although heterosexual men in the mating pool did have higher average numbers of short-term mating experiences and short-term mates.
+In contrast, we found no gender differences in short-term mating behaviors between heterosexual men and women, although heterosexual men in the mating pool had higher average numbers of short-term mating experiences and short-term mates.
 
-As we expected, heterosexual men and women did not differ in short-term mating behaviors despite their differential preferences for short-term mating.
-This was because heterosexual men and women had an equal total number of short-term mating experiences , so as the total number of short-term mates.
-Since the sex ratio was 1:1 in our model, the average number of short-term mating experiences and short-term mates must be equal between men and women as well.
-However, we did find that among individuals in the mating pool, men engaged in more short-term mating behaviors as compared to women.
+As expected, heterosexual men and women did not differ in short-term mating behaviors despite their differential preferences for short-term mating.
+This was because heterosexual men and women had an equal total number of both short-term mating experiences and short-term mates.
+This is not surprising since the sex ratio was 1:1 in our model.
+It therefore follows that the average number of short-term mating experiences and short-term mates must be equal between men and women as well.
+However, we did find that when we only looked at individuals in the mating pool (from which more men than women were excluded), men engaged in more short-term mating behaviors as compared to women.
 This was because there were more women than men in the mating pool, resulting in lower averages among heterosexual women despite the equal numbers of experiences and mates in total.
@@
 
-In the light of these results, the empirical observation of gender differences in short-term mating behaviors among heterosexual individuals [e.g., @petersen_meta-analytic_2010] appear to be perplexing because this is illogical [e.g., @s_j_gurman_six_1989].
-Possible explanations for these empirical results have to highlight caveats in the observation process.
-One possibility is that there was sampling bias in the observations [e.g., @wiederman_evolution_1998] since surveys regarding short-term mating behaviors may tend to attract individuals who already engage in such behaviors.
+In the light of these results, previous empirical observations of gender differences in short-term mating behaviors among heterosexual individuals [e.g., @petersen_meta-analytic_2010] appear perplexing [e.g., @s_j_gurman_six_1989].
+Possible explanations for these empirical results that seem illogical considering the simulation findings may have to do with features of the observation process.
+One possibility is sampling bias in the observations [e.g., @wiederman_evolution_1998] since surveys regarding short-term mating behaviors may tend to attract individuals who already engage in such behaviors.
 Another possibility is that heterosexual men and women tend to report short-term mating behaviors differently.
@@
 Among gay men and lesbian women, large gender differences in short-term mating behaviors existed when men and women had differential preferences for short-term mating, which was in line with empirical observations [e.g., @peplau_national_1997; @peplau_sexuality_2004].
-This was probably because the number of short-term mating experiences and short-term mates no longer counted towards men and women simultaneously.
+This was likely because the number of short-term mating experiences and short-term mates no longer counted towards men and women simultaneously.
 Any gender differences in mating preferences would result in differences in behaviors.
 A closer look at the results did support this postulation.
-Either a difference in the likelihood of short-term mating or a difference in mating standards alone could contribute to gender differences in mating behaviors.
-This was perhaps because the former increased the probability of both parties of a given gay couple deciding to have short-term mating, and the latter increased the probability of both of them meeting each other's standards, as compared to the case of a given lesbian couple.
+Both a difference in the likelihood of short-term mating and in mating standards alone resulted in gender differences in mating behaviors.
+This was likely because the former increased the probability of both parties of a given gay couple deciding to have short-term mating, and the latter increased the probability of both meeting each other's standards, as compared to the case of a given lesbian couple.
 
-Supporting the idea that gay men's preferences for short-term mating were not constrained by those of women, we found that gay men engaged in more short-term mating behaviors as compared to heterosexual men.
+Also, as gay men's preferences for short-term mating were not constrained by those of women, we found that gay men engaged in more short-term mating behaviors compared to heterosexual men.
 This was consistent with the empirical literature [e.g., @peplau_national_1997].
-Interestingly, gay men and heterosexual men had the same mating likelihood and the same standards for short-term mates in our model.
+Interestingly, gay men and heterosexual men had the same short-term mating likelihood and the same standards for short-term mates in our model.
 The only difference was a change in the preferences of potential partners.
@@
 
-Using agent-based modeling, the present study theoretically explored the circumstances under which men and women’s differential preferences for short-term mating resulted in gender differences in short-term mating behaviors.
+Using agent-based modeling, the present study simulated the circumstances under which men and women’s differential preferences for short-term mating resulted in gender differences in short-term mating behaviors.
 We found when men (vs.
 women) had a stronger preferences for short-term mating, heterosexual men and women engaged in short-term mating behaviors to the same extent, while gay men engaged in more short-term mating behaviors as compared to lesbian women.
-We also found that gay men engaged in more short-term mating behaviors than heterosexual men did.
-Theses results highlight the distinction between preferences and behaviors in human mating.
+Gay men engaged in more short-term mating behaviors than heterosexual men did.
+
+These results highlight the distinction between preferences and behaviors in human mating.
 Individuals’ mating behaviors do not only depend on one’s own preferences, but are also constrained by partners’ preferences.
@@
 These results also cast doubt to the prevalent belief in the gender differences in short-term mating behaviors, especially among heterosexual individuals.
-Our findings suggest that there may be factors in the observation process, such as sampling bias, that lead to the observed differences.
+Our findings suggest that there may be factors in the observation process, such as sampling bias, that contribute to the observed differences.
 Future research in human sexuality should note such possibilities and interpret any observed gender differences in short-term mating behaviors cautiously.

### 2022-05-27 submission/manuscript.tex
minor language edits to the manuscript

@@
 
-\textsuperscript{2} xxxx
+\textsuperscript{2} Faculty of Arts, Psychology and Theology, Åbo
+Akademi University
 
@@
 
-Gender differences in short-term mating behaviors have been a
-well-documented phenomenon in human sexuality research. Existing studies
-usually conflate gender differences in mating preferences with
-differences in sexual behaviors, which is theoretically dubious. Using
-an agent-based model, the present study investigated the circumstances
-under which men and women's differential preferences for short-term
-mating would result in gender differences in short-term mating
-behaviors. The results from the model suggested that heterosexual men
-and women had the same average number of short-term mating experiences
-and short-term mates even when men had stronger preferences for
-short-term mating. Gender differences in mating behaviors only emerged
-when heterosexual men and women in the mating pool (i.e., those with a
-non-zero number of short-term mating experiences) were considered.
-Moreover, gay men had a higher average number of both outcomes than
-lesbian women as well as than heterosexual men when men had stronger
-preferences for short-term mating. These results suggest that
+Gender differences in short-term mating behaviors are well-documented in
+human sexuality research. Existing studies usually conflate gender
+differences in mating preferences with differences in sexual behaviors,
+which is theoretically problematic. Using an agent-based model, we
+investigated the circumstances under which heterosexual and homosexual
+men and women's differential preferences for short-term mating would
+result in gender differences in short-term mating behaviors. The model
+showed that when all individuals in a closed heterosexual population
+were considered, men and women had the same average number of short-term
+mating experiences and short-term mates even when men had stronger
+preferences for short-term mating. Men (vs.~women) had a higher average
+number of both experiences and mates only when heterosexual men and
+women in the mating pool (i.e., those with a non-zero number of
+short-term mating experiences) were considered. Moreover, when men had
+stronger preferences for short-term mating than women, gay men had a
+higher average number of both experiences and mates compared to both
+lesbian women and heterosexual men. These results suggest that
 theoretically speaking, even when gender differences in mating
@@
 
-~
+\hfill\break
 
@@
 Gender differences in sexual behaviors, especially short-term mating
-behaviors, have been a well-documented phenomenon in human sexuality
-research. For example, research has found that heterosexual men, as
-compared to heterosexual women, have a higher average number of past
-short-term sexual partners (Oliver \& Hyde, 1993; Petersen \& Hyde,
-2010; Rissel et al., 2014), have short-term mating more frequently
-(Petersen \& Hyde, 2010), and engage in extramarital sex more often
+behaviors, are well-documented in human sexuality research. For example,
+research has found that heterosexual men, as compared to heterosexual
+women, have a higher average number of past short-term sexual partners
+(Oliver \& Hyde, 1993; Petersen \& Hyde, 2010; Rissel et al., 2014), and
+engage in both short-term mating and extramarital sex more often
 (Petersen \& Hyde, 2010). These gender differences have also been
@@
 
-In the existing literature, gender differences in sexual behaviors are
-not usually distinguished from those in attitudes towards or preferences
-for short-term mating. Some researchers study gender differences on the
-two levels simultaneously without a conceptual distinction (e.g.,
-Petersen \& Hyde, 2010), whereas some implicitly equate the two,
-assuming that behavioral differences are a direct expression of the
-psychological ones (e.g., Schmitt et al., 2001).
+In the existing literature, gender differences in actual sexual
+behaviors are not usually distinguished from those in attitudes towards
+or preferences for short-term mating. Some researchers study gender
+differences at the two levels simultaneously without a conceptual
+distinction (e.g., Petersen \& Hyde, 2010), whereas some implicitly
+equate the two, assuming that behavioral differences are a direct
+expression of psychological ones (e.g., Schmitt et al., 2001).
 
@@
 
-The present study took gender differences in mating preferences as a
-presumption, which was conceptualized by sexual strategy theory (Buss \&
-Schmitt, 1993) and repeatedly found support by empirical studies (e.g.,
-Schmitt, 2003; Walter et al., 2020). Using an agent-based model, we
-investigated whether men and women's differential preferences for
-short-term mating resulted in any gender differences in short-term
-mating behaviors, specifically, in the number of short-term mating
-experiences and short-term mates, and if they did, under what
-circumstances.
+As a starting point, we took gender differences in mating preferences as
+conceptualized by the sexual strategy theory (Buss \& Schmitt, 1993) and
+repeatedly supported by empirical investigations (e.g., Schmitt, 2003;
+Walter et al., 2020). Using an agent-based model, we investigated
+whether men and women's differential preferences for short-term mating
+would result in gender differences in short-term mating behaviors, and
+if so, then under what conditions they would result in differences in
+the number of short-term mating experiences and short-term mates.
 
@@
 of sexual strategy theory (Buss \& Schmitt, 1993). It posits that since
-the minimum investment that men devote to their offspring (contribution
-of sperm through one sexual act) is lower than that of women (gestation,
-labor, and lactation), men tend to have short-term mating as a larger
-part of their mating strategy than women do. This is because women's
-high minimum investment leads to higher opportunity cost (vs.~men) if
-they have sex with a suboptimal partner and give birth to offspring with
-a low survival chance. As a result, men may have a greater interest in
-short-term mating, desire a larger number of short-term mates in a given
-period, and be less selective with respect to accepting a potential mate
-(Buss \& Schmitt, 1993).
+the minimum obligatory investment that men must devote to their
+offspring (contribution of sperm through one sexual act) is lower than
+that of women (gestation, labor, and lactation), men tend to be
+relatively more interested in short-term mating compared to women. This
+is because the number of offspring women can produce is limited and
+cannot be increased by mating with a large number of men, whereas the
+reverse is the case for men. As a result, men are predicted to not only
+have a greater interest in short-term mating, but also desire a larger
+number of short-term mates in a given period and be less selective with
+respect to accepting a potential mate (Buss \& Schmitt, 1993).
 
 The hypotheses derived from sexual strategy theory have received
-extensive support from empirical studies. For example, men reported to
-be currently seeking short-term mates to a larger extent than women did
+extensive support in empirical studies. For example, men have reported
+to be currently seeking short-term mates to a larger extent than women
 (Buss \& Schmitt, 1993; Schmitt et al., 2001; Schmitt, 2003), and a
-larger proportion of them were in any way seeking short-term mates
-(vs.~not seeking) (Schmitt, 2003). These have been found among U.S.
-college students (Buss \& Schmitt, 1993; Schmitt et al., 2001) as well
-as in ten world regions in a cross-cultural study (Schmitt, 2003).
-Similarly, men across the world also reported to desire more short-term
-sexual partners compared to women for a number of given time periods
-(e.g., a month, a year) (Buss \& Schmitt, 1993; McBurney et al., 2005;
-Schmitt, 2003). The gender differences were significant regardless of
-whether they were estimated by mean (Buss \& Schmitt, 1993; Schmitt et
-al., 2001; Schmitt, 2003), median (Schmitt et al., 2001; Schmitt, 2003),
-or percentage (Schmitt, 2003) statistics.
+larger proportion of men were in any way seeking short-term mates
+(vs.~not seeking) (Schmitt, 2003). Similar results have been found among
+both U.S. college students (Buss \& Schmitt, 1993; Schmitt et al., 2001)
+as well as in ten world regions in a cross-cultural study (Schmitt,
+2003). Similarly, men across the world have also reported to desire more
+short-term sexual partners compared to women over different future time
+periods (e.g., a month, a year) (Buss \& Schmitt, 1993; McBurney et al.,
+2005; Schmitt, 2003). The gender differences have been found regardless
+of whether they were estimated using mean (Buss \& Schmitt, 1993;
+Schmitt et al., 2001; Schmitt, 2003), median (Schmitt et al., 2001;
+Schmitt, 2003), or percentage (Schmitt, 2003) statistics.
 
@@
 a potential short-term mate. For example, studies using U.S. college
-samples found that the minimum percentile ranks that men found
+samples have found that the minimum percentile ranks that men found
 acceptable for a potential short-term sexual partner were lower than
@@
 individual traits (e.g., social status, attractiveness) (Kenrick et al.,
-1990; Regan, 1998). A study also found that when presented with
+1990; Regan, 1998). Another study also found that when presented with
 identical descriptions of potential mates, men on average rated them as
@@
 difference was comparable to that existing among heterosexual
-individuals (Bailey et al., 1994). An indirect piece of evidence on
-differential standards for short-term mates comes from a recent study
-finding that significantly more gay men than lesbian women reported to
-have accepted a casual sexual offer from a same-gender person (Matsick
-et al., 2021). Past studies suggest that the gender difference in the
-acceptance rate of casual sexual offers may originate from men and
-women's differential standards for short-term mates (Conley et al.,
-2011; Hald \& Høgh-Olesen, 2010). Thus, as a postulation, gay men may
-also have lower standards than lesbian women for short-term mates.
+individuals (Bailey et al., 1994). An additional indirect piece of
+evidence on differential standards for short-term mates comes from a
+recent study finding that significantly more gay men than lesbian women
+reported to have accepted a casual sexual offer from a same-gender
+person (Matsick et al., 2021). Past studies suggest that the gender
+difference in the acceptance rate of casual sexual offers may originate
+from men and women's differential standards for short-term mates (Conley
+et al., 2011; Hald \& Høgh-Olesen, 2010). Thus, as a postulation, gay
+men may also have lower standards than lesbian women for short-term
+mates.
 
@@
 
-Since heterosexual sex involves both a man and a woman in most cases,
-men's interest in short-term mating can be constrained by women's
-preference for long-term relationships (Archer, 2019; Symons, 1979).
-This is because men's short-term mating preferences can only translate
-into behaviors when there are women willing to have sex with them. When
-a new short-term mating encounter occurs, it counts towards men's total
+Since heterosexual sex in most cases involves one man and one woman,
+men's relatively high interest in short-term mating can be constrained
+by women's preference for long-term relationships (Archer, 2019; Symons,
+1979). This is because men's short-term mating preferences -- with the
+relatively rare exception of sexual violence -- can only translate into
+behaviors when there are women willing to have sex with them. When a new
+short-term mating encounter occurs, it counts both towards men's total
 number of short-term mating encounters as well as towards women's.
@@
 short-term mating experiences and short-term mates must be equal between
-heterosexual men and women on a population level. However, it is
+heterosexual men and women at the population level. However, it is
 important to note that although heterosexual men's total number of
@@
 to observe no gender difference in short-term mating behaviors among
-heterosexual individuals even when there were gender differences in
+heterosexual individuals even when there are gender differences in
 mating preferences.
@@
 preferences are not constrained by women's, but only by those of other
-men, who, arguably, have more similar preferences. This would allow for
-a more direct behavioral expression of men's mating preferences. The
-notion that gay men have less restricted preferences was borne out in
-the proportion of individuals who have engaged in extradyadic sex
-(Peplau et al., 2004). A study showed that the proportions of
-heterosexual men and women who have engaged in extradyadic sex were 26\%
-and 21\%, respectively, while the statistics among gay men and lesbian
-women were 82\% and 28\%, respectively (Peplau et al., 2004). Therefore,
-we would theoretically expect to observe gender differences in
+men, who, arguably, have a similar high interest in short-term mating.
+This would allow for a more direct behavioral expression of men's mating
+preferences. The notion that gay men have less restricted preferences is
+borne out in the proportion of individuals who have engaged in
+extradyadic sex (Peplau et al., 2004). A study showed that the
+proportions of heterosexual men and women who had engaged in extradyadic
+sex were 26\% and 21\%, respectively, while the statistics among gay men
+and lesbian women were 82\% and 28\%, respectively (Peplau et al.,
+2004). Therefore, we would expect to observe gender differences in
 short-term mating behaviors between gay men and lesbian women. Moreover,
-we would also expect to find that gay men, as compared to heterosexual
-men, engaged in more short-term mating behaviors due to the lessened
-constraint on their mating preferences.
+we would also expect to find that gay men, compared to heterosexual men,
+engaged in more short-term mating behaviors due to less constraints on
+their mating preferences.
 
@@
 By using a spatial agent-based model, the present study investigated
-whether men and women's different preferences for short-term mating
-resulted in any gender differences in short-term mating behaviors, and
+whether men and women's differential preferences for short-term mating
+would result in gender differences in short-term mating behaviors, and
 if they did, under what circumstances. Preferences for short-term mating
-were operationally defined as the interest in short-term mating and
-standards for short-term mates (Buss \& Schmitt, 1993). Short-term
-mating behaviors were operationally defined as the number of short-term
-mating experiences and the number of past short-term mates (Petersen \&
-Hyde, 2010).
+were operationally defined as the likelihood of engaging in short-term
+mating when encountering a mate as well as the standards for short-term
+mates (Buss \& Schmitt, 1993). Short-term mating behaviors were
+operationally defined as the number of short-term mating experiences and
+the number of past short-term mates (Petersen \& Hyde, 2010).
 
@@
 relationship only with women, while gay men only with other men, and
-vice versa for women.
+mutatis mutandis for women.
 
-We raised the following hypotheses in the present study: when there were
+We formulated the following hypotheses in the present study: assuming
 gender differences in preferences for short-term mating, 1) there would
@@
 where men and women can move around, search for mates, and form
-long-term and/or short-term relationships. Space and time are modeled as
-discrete variables. Space was represented as discrete locations on a
+long-term and/or short-term relationships. Space and time were modeled
+as discrete variables. Space was represented as discrete locations on a
 two-dimensional 33*33 lattice. Agents' movement in the space was not
@@
 short-term mates were calculated by taking the average among the whole
-population of men/women (\emph{N\textsubscript{m}} =
-\emph{N\textsubscript{w}} = 150) and among those who had engaged in
-short-term mating.
+population of men and women (\emph{N\textsubscript{men}} =
+\emph{N\textsubscript{women}} = 150) and among those who had engaged in
+any short-term mating.
 
@@
 10), while women had a standard of 5 (Kenrick et al., 1990; Regan,
-1998). When there was no gender difference in mating standards, both men
+1998), that is, they would not mate with a person with a lower mate
+value. When there was no gender difference in mating standards, both men
 and women had a standard of 5.
@@
 
-\hypertarget{heterosexual-procedures.}{%
-\paragraph{Heterosexual procedures.}\label{heterosexual-procedures.}}
+\hypertarget{procedures-for-heterosexual-agents.}{%
+\paragraph{Procedures for heterosexual
+agents.}\label{procedures-for-heterosexual-agents.}}
 
@@
 long-term relationship, they did not move. Then, the agents decided on
-whether to engage in short-term mating by a chance of the chosen
+whether to engage in short-term mating using the predetermined
 likelihood (either 25\% or 40\%).
@@
 Women checked to see if any men were at the same location. If there
-were, they randomly chose one of them as their potential short-term
-mate. If both men and women met each other's mating standards and both
-of them decided to engage in short-term mating, they had sex. This would
-result in increasing both parties' number of short-term mating
-experiences by one. They also recorded each other on their lists of past
+were, they randomly chose one of them as a potential short-term mate. If
+both men and women met each other's mating standards and both of them
+decided to engage in short-term mating, they had sex. This would result
+in increasing both parties' number of short-term mating experiences by
+one. They also recorded each other on their respective lists of past
 short-term mates if they were not on the lists yet.
@@
 would form a long-term relationship. After forming a long-term
-relationship, both men and women changed to coupled status and register
-each other as the long-term partner.
+relationship, both men and women changed to coupled status and
+registered each other as their long-term partner.
 
-\hypertarget{gay-men-and-lesbian-women-procedures.}{%
-\paragraph{Gay men and lesbian women
-procedures.}\label{gay-men-and-lesbian-women-procedures.}}
+\hypertarget{procedures-for-gay-men-and-lesbian-women-agents.}{%
+\paragraph{Procedures for gay men and lesbian women
+agents.}\label{procedures-for-gay-men-and-lesbian-women-agents.}}
 
 At each time step, men and women moved and decided on short-term mating
-as the agents did in the heterosexual procedures. Half of the agents (75
-men and 75 women) were also given the initiator status. The initiators
+as the agents did in the heterosexual case. Half of the agents (75 men
+and 75 women) were also given an initiator status. The initiators
 checked to see whether there were other agents at the same location. The
@@
 
-\hypertarget{statistical-analysis}{%
-\subsection{Statistical analysis}\label{statistical-analysis}}
+\hypertarget{statistical-analyses}{%
+\subsection{Statistical analyses}\label{statistical-analyses}}
 
@@
 statistical comparisons. The data were assumed to be normally
-distributed within each condition but was not formally tested.
+distributed within each condition.
 
@@
 difference in the average number of short-term mating experiences among
-heterosexual individuals (\emph{M\textsubscript{m}} = 1.43,
-\emph{SD\textsubscript{m}} = 0.24; \emph{M\textsubscript{w}} = 1.43,
-\emph{SD\textsubscript{w}} = 0.24), Cohen's \emph{d} = 0. Nor was there
-a difference in the average number of short-term mates
-(\emph{M\textsubscript{m}} = 0.80, \emph{SD\textsubscript{m}} = 0.11;
-\emph{M\textsubscript{w}} = 0.80, \emph{SD\textsubscript{w}} = 0.11),
-Cohen's \emph{d} = 0 (Figure 1).
+heterosexual individuals (\emph{M\textsubscript{men}} = 1.43,
+\emph{SD\textsubscript{men}} = 0.24; \emph{M\textsubscript{women}} =
+1.43, \emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0. Nor
+was there a difference in the average number of short-term mates
+(\emph{M\textsubscript{men}} = 0.80, \emph{SD\textsubscript{men}} =
+0.11; \emph{M\textsubscript{w}} = 0.80, \emph{SD\textsubscript{women}} =
+0.11), Cohen's \emph{d} = 0 (Figure 1).
 
@@
 In Experiment 1, however, when the means of the outcome variables were
-calculated among men and women in the mating pool (the number of
-individuals in the mating pool: \emph{M\textsubscript{m}} = 56.85,
-\emph{SD\textsubscript{m}} = 5.99; \emph{M\textsubscript{w}} = 77.04,
-\emph{SD\textsubscript{w}} = 7.53), there were gender differences in
-short-term mating behaviors when men and women had differential
-preferences for short-term mating. The average number of short-term
-mating experiences was higher among heterosexual men (\emph{M} = 3.78,
-\emph{SD} = 0.50) than among heterosexual women (\emph{M} = 2.79,
-\emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p} \textless{} .001,
-Cohen's \emph{d} = 2.31. Likewise, the average number of short-term
-mates was higher among heterosexual men (\emph{M} = 2.12, \emph{SD} =
-0.17) than among heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11),
-\emph{t}(4,998) = -135.85, \emph{p} \textless{} .001, Cohen's \emph{d} =
-3.84.
+calculated only among men and women in the mating pool (the number of
+individuals in the mating pool: \emph{M\textsubscript{men}} = 56.85,
+\emph{SD\textsubscript{men}} = 5.99; \emph{M\textsubscript{women}} =
+77.04, \emph{SD\textsubscript{women}} = 7.53), there were gender
+differences in short-term mating behaviors when men and women had
+differential preferences for short-term mating. The average number of
+short-term mating experiences was higher among heterosexual men
+(\emph{M} = 3.78, \emph{SD} = 0.50) than among heterosexual women
+(\emph{M} = 2.79, \emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p}
+\textless{} .001, Cohen's \emph{d} = 2.31. Likewise, the average number
+of short-term mates was higher among heterosexual men (\emph{M} = 2.12,
+\emph{SD} = 0.17) than among heterosexual women (\emph{M} = 1.56,
+\emph{SD} = 0.11), \emph{t}(4,998) = -135.85, \emph{p} \textless{} .001,
+Cohen's \emph{d} = 3.84.
 
@@
 
-The results comparing across the two experiments revealed that gay men
-engaged in short-term mating behaviors more than heterosexual men did
-(Figure 2). The average number of short-term mating experiences was
-higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37) than among
+Gay men engaged in short-term mating behaviors more than heterosexual
+men did (Figure 2). The average number of short-term mating experiences
+was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37) than among
 heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24), \emph{t}(4,998) =
@@
 
-In an exploratory manner, we also compared across conditions to see
-which of the two dimensions of mating preferences contributed to gender
-differences in short-term mating behaviors.
+We also ran analyses across conditions to see which of the two
+dimensions of mating preferences contributed to gender differences in
+short-term mating behaviors.
 
 Among heterosexual individuals, gender differences in short-term mating
-behaviors, as calculated among individuals in the mating pool, emerged
+behaviors, when calculated among individuals in the mating pool, emerged
 when men and women had different standards for short-term mates.
@@
 difference existed in short-term mating likelihood (experiences:
-\emph{M\textsubscript{m}} = 2.82, \emph{SD\textsubscript{m}} = 0.36,
-\emph{M\textsubscript{w}} = 2.21, \emph{SD\textsubscript{w}} = 0.28,
-Cohen's \emph{d} = 1.89; partners: \emph{M\textsubscript{m}} = 1.76,
-\emph{SD\textsubscript{m}} = 0.15; \emph{M\textsubscript{w}} = 1.38,
-\emph{SD\textsubscript{w}} = 0.09, Cohen's \emph{d} = 3.13). In
-comparison, virtually no gender differences in short-term mating
+\emph{M\textsubscript{men}} = 2.82, \emph{SD\textsubscript{men}} = 0.36,
+\emph{M\textsubscript{women}} = 2.21, \emph{SD\textsubscript{women}} =
+0.28, Cohen's \emph{d} = 1.89; partners: \emph{M\textsubscript{men}} =
+1.76, \emph{SD\textsubscript{men}} = 0.15; \emph{M\textsubscript{women}}
+= 1.38, \emph{SD\textsubscript{women}} = 0.09, Cohen's \emph{d} = 3.13).
+In comparison, virtually no gender differences in short-term mating
 behaviors existed when men and women had the same mating standards
@@
 \small
-\item \textit{Note.} The statistics were calculated with subsamples of men and women who had had enagged in short-term mating behaviors.
+\item \textit{Note.} The statistics were calculated with subsamples of men and women who had had engaged in short-term mating behaviors.
 See Supplementary Materials for the mean and standard deviation of sample sizes.
@@
 Among gay men and lesbian women, gender differences in short-term mating
-behaviors emerged either when they had different short-term mating
-likelihood or when their mating standards were different. Gay men
+behaviors emerged both when they had different short-term mating
+likelihood and when their mating standards were different. Gay men
 (vs.~lesbian women) had a higher average number of short-term mating
 experiences and short-term mates when they had a higher short-term
-mating likelihood (experiences: \emph{M\textsubscript{m}} = 0.80,
-\emph{SD\textsubscript{m}} = 0.23, \emph{M\textsubscript{w}} = 0.32,
-\emph{SD\textsubscript{w}} = 0.10, Cohen's \emph{d} = 2.67; partners:
-\emph{M\textsubscript{m}} = 0.52, \emph{SD\textsubscript{m}} = 0.13,
-\emph{M\textsubscript{w}} = 0.25, \emph{SD\textsubscript{w}} = 0.07,
-Cohen's \emph{d} = 2.60), or when they had lower mating standards
-(experiences: \emph{M\textsubscript{m}} = 1.05,
-\emph{SD\textsubscript{m}} = 0.18, \emph{M\textsubscript{w}} = 0.32,
-\emph{SD\textsubscript{w}} = 0.10, Cohen's \emph{d} = 5.10; partners:
-\emph{M\textsubscript{m}} = 0.82, \emph{SD\textsubscript{m}} = 0.12,
-\emph{M\textsubscript{w}} = 0.25, \emph{SD\textsubscript{w}} = 0.07,
-Cohen's \emph{d} = 5.78). In comparison, virtually no gender differences
-in short-term mating behaviors existed when gay men and lesbian women
-had the same short-term mating likelihood and mating standards (Table
-2).
+mating likelihood (experiences: \emph{M\textsubscript{men}} = 0.80,
+\emph{SD\textsubscript{men}} = 0.23, \emph{M\textsubscript{women}} =
+0.32, \emph{SD\textsubscript{women}} = 0.10, Cohen's \emph{d} = 2.67;
+partners: \emph{M\textsubscript{men}} = 0.52,
+\emph{SD\textsubscript{men}} = 0.13, \emph{M\textsubscript{women}} =
+0.25, \emph{SD\textsubscript{women}} = 0.07, Cohen's \emph{d} = 2.60),
+or when they had lower mating standards (experiences:
+\emph{M\textsubscript{men}} = 1.05, \emph{SD\textsubscript{men}} = 0.18,
+\emph{M\textsubscript{women}} = 0.32, \emph{SD\textsubscript{women}} =
+0.10, Cohen's \emph{d} = 5.10; partners: \emph{M\textsubscript{men}} =
+0.82, \emph{SD\textsubscript{men}} = 0.12, \emph{M\textsubscript{women}}
+= 0.25, \emph{SD\textsubscript{women}} = 0.07, Cohen's \emph{d} = 5.78).
+In comparison, virtually no gender differences in short-term mating
+behaviors existed when gay men and lesbian women had the same short-term
+mating likelihood and mating standards (Table 2).
 
@@
 \small
-\item \textit{Note.} \textit{N\textsubscript{m}} = \textit{N\textsubscript{w}} = 150 in all conditions.
+\item \textit{Note.} \textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150 in all conditions.
 \end{tablenotes}
@@
 
-The present study aimed at using agent-based modeling to investigate
-whether men and women's different preferences for short-term mating
-resulted in any gender differences in short-term mating behaviors,
-specifically, in the number of short-term mating experiences and
-short-term mates, and if they did, under what circumstances. We raised
-two hypotheses: 1) gay men would engage in more short-term mating
-behaviors as compared to lesbian women, and 2) gay men would engage in
-more short-term mating behaviors as compared to heterosexual men. The
-results from 1,000 time steps in a model simulating men and women's
-mating behaviors supported our hypotheses. First of all, as compared to
-lesbian women, gay men had higher average numbers of short-term mating
-experiences and short-term mates. Secondly, gay men also had higher
-average numbers of short-term mating experiences and short-term mates as
-compared to heterosexual men. In contrast, we found no gender
-differences in short-term mating behaviors between heterosexual men and
-women, although heterosexual men in the mating pool did have higher
-average numbers of short-term mating experiences and short-term mates.
+The present study used agent-based modeling to investigate whether men
+and women's differential preferences for short-term mating would result
+in gender differences in short-term mating behaviors, and if so, then
+under what conditions they would result in differences in the number of
+short-term mating experiences and short-term mates. We formulated two
+hypotheses: 1) gay men would engage in more short-term mating behaviors
+as compared to lesbian women, and 2) gay men would engage in more
+short-term mating behaviors as compared to heterosexual men. The results
+from 1,000 time steps in a model simulating men and women's mating
+behaviors provided strong evidence in favor of our hypotheses. First of
+all, as compared to lesbian women, gay men had higher average numbers of
+short-term mating experiences and short-term mates. Secondly, gay men
+also had higher average numbers of short-term mating experiences and
+short-term mates as compared to heterosexual men. In contrast, we found
+no gender differences in short-term mating behaviors between
+heterosexual men and women, although heterosexual men in the mating pool
+had higher average numbers of short-term mating experiences and
+short-term mates.
 
-As we expected, heterosexual men and women did not differ in short-term
+As expected, heterosexual men and women did not differ in short-term
 mating behaviors despite their differential preferences for short-term
 mating. This was because heterosexual men and women had an equal total
-number of short-term mating experiences , so as the total number of
-short-term mates. Since the sex ratio was 1:1 in our model, the average
-number of short-term mating experiences and short-term mates must be
-equal between men and women as well. However, we did find that among
-individuals in the mating pool, men engaged in more short-term mating
-behaviors as compared to women. This was because there were more women
-than men in the mating pool, resulting in lower averages among
-heterosexual women despite the equal numbers of experiences and mates in
-total.
+number of both short-term mating experiences and short-term mates. This
+is not surprising since the sex ratio was 1:1 in our model. It therefore
+follows that the average number of short-term mating experiences and
+short-term mates must be equal between men and women as well. However,
+we did find that when we only looked at individuals in the mating pool
+(from which more men than women were excluded), men engaged in more
+short-term mating behaviors as compared to women. This was because there
+were more women than men in the mating pool, resulting in lower averages
+among heterosexual women despite the equal numbers of experiences and
+mates in total.
 
@@
 
-In the light of these results, the empirical observation of gender
+In the light of these results, previous empirical observations of gender
 differences in short-term mating behaviors among heterosexual
-individuals (e.g., Petersen \& Hyde, 2010) appear to be perplexing
-because this is illogical (e.g., Gurman, 1989). Possible explanations
-for these empirical results have to highlight caveats in the observation
-process. One possibility is that there was sampling bias in the
-observations (e.g., Wiederman \& Dubois, 1998) since surveys regarding
-short-term mating behaviors may tend to attract individuals who already
-engage in such behaviors. Another possibility is that heterosexual men
-and women tend to report short-term mating behaviors differently. This
-difference may be a result of social desirability bias (Alexander \&
-Fisher, 2003) or due to men and women's different estimation strategies
-(e.g., men tend to round up) (Brown \& Sinclair, 1999).
+individuals (e.g., Petersen \& Hyde, 2010) appear perplexing (e.g.,
+Gurman, 1989). Possible explanations for these empirical results that
+seem illogical considering the simulation findings may have to do with
+features of the observation process. One possibility is sampling bias in
+the observations (e.g., Wiederman \& Dubois, 1998) since surveys
+regarding short-term mating behaviors may tend to attract individuals
+who already engage in such behaviors. Another possibility is that
+heterosexual men and women tend to report short-term mating behaviors
+differently. This difference may be a result of social desirability bias
+(Alexander \& Fisher, 2003) or due to men and women's different
+estimation strategies (e.g., men tend to round up) (Brown \& Sinclair,
+1999).
 
@@
 for short-term mating, which was in line with empirical observations
-(e.g., Peplau et al., 1997, 2004). This was probably because the number
-of short-term mating experiences and short-term mates no longer counted
+(e.g., Peplau et al., 1997, 2004). This was likely because the number of
+short-term mating experiences and short-term mates no longer counted
 towards men and women simultaneously. Any gender differences in mating
 preferences would result in differences in behaviors. A closer look at
-the results did support this postulation. Either a difference in the
-likelihood of short-term mating or a difference in mating standards
-alone could contribute to gender differences in mating behaviors. This
-was perhaps because the former increased the probability of both parties
-of a given gay couple deciding to have short-term mating, and the latter
-increased the probability of both of them meeting each other's
-standards, as compared to the case of a given lesbian couple.
+the results did support this postulation. Both a difference in the
+likelihood of short-term mating and in mating standards alone resulted
+in gender differences in mating behaviors. This was likely because the
+former increased the probability of both parties of a given gay couple
+deciding to have short-term mating, and the latter increased the
+probability of both meeting each other's standards, as compared to the
+case of a given lesbian couple.
 
-Supporting the idea that gay men's preferences for short-term mating
-were not constrained by those of women, we found that gay men engaged in
-more short-term mating behaviors as compared to heterosexual men. This
-was consistent with the empirical literature (e.g., Peplau et al.,
-1997). Interestingly, gay men and heterosexual men had the same mating
-likelihood and the same standards for short-term mates in our model. The
-only difference was a change in the preferences of potential partners.
-When men's partners had a stronger preferences for short-term mating
-(i.e., having men vs.~having women as potential partners), men also
-appeared to engage in more short-term mating behaviors.
+Also, as gay men's preferences for short-term mating were not
+constrained by those of women, we found that gay men engaged in more
+short-term mating behaviors compared to heterosexual men. This was
+consistent with the empirical literature (e.g., Peplau et al., 1997).
+Interestingly, gay men and heterosexual men had the same short-term
+mating likelihood and the same standards for short-term mates in our
+model. The only difference was a change in the preferences of potential
+partners. When men's partners had a stronger preferences for short-term
+mating (i.e., having men vs.~having women as potential partners), men
+also appeared to engage in more short-term mating behaviors.
 
@@
 
-Using agent-based modeling, the present study theoretically explored the
+Using agent-based modeling, the present study simulated the
 circumstances under which men and women's differential preferences for
@@
 mating behaviors to the same extent, while gay men engaged in more
-short-term mating behaviors as compared to lesbian women. We also found
-that gay men engaged in more short-term mating behaviors than
-heterosexual men did. Theses results highlight the distinction between
-preferences and behaviors in human mating. Individuals' mating behaviors
-do not only depend on one's own preferences, but are also constrained by
-partners' preferences. Future research in human mating should not only
-focus on the psychological aspect but also pay attention to the
-interaction between individuals' psychology and its context. These
-results also cast doubt to the prevalent belief in the gender
-differences in short-term mating behaviors, especially among
-heterosexual individuals. Our findings suggest that there may be factors
-in the observation process, such as sampling bias, that lead to the
-observed differences. Future research in human sexuality should note
-such possibilities and interpret any observed gender differences in
-short-term mating behaviors cautiously.
+short-term mating behaviors as compared to lesbian women. Gay men
+engaged in more short-term mating behaviors than heterosexual men did.
+
+These results highlight the distinction between preferences and
+behaviors in human mating. Individuals' mating behaviors do not only
+depend on one's own preferences, but are also constrained by partners'
+preferences. Future research in human mating should not only focus on
+the psychological aspect but also pay attention to the interaction
+between individuals' psychology and its context. These results also cast
+doubt to the prevalent belief in the gender differences in short-term
+mating behaviors, especially among heterosexual individuals. Our
+findings suggest that there may be factors in the observation process,
+such as sampling bias, that contribute to the observed differences.
+Future research in human sexuality should note such possibilities and
+interpret any observed gender differences in short-term mating behaviors
+cautiously.
 

### 2022-05-30 submission/manuscript.Rmd
edits in writing

@@
 Men (vs.
-women) had a higher average number of both experiences and mates only when heterosexual men and women in the mating pool (i.e., those with a non-zero number of short-term mating experiences) were considered.
-Moreover, when men had stronger preferences for short-term mating than women, gay men had a higher average number of both experiences and mates compared to both lesbian women and heterosexual men.
-These results suggest that theoretically speaking, even when gender differences in mating preferences existed, those in short-term mating behaviors only occurred among particular populations, or when men’s preferences for short-term mating are not constrained by those of women.
+women) had a higher average number of both experiences and mates only when heterosexual men and women who successfully participated in the mating pool (i.e., those with a non-zero number of short-term mating experiences) were considered.
+Moreover, when men (vs.
+women) had stronger preferences for short-term mating, gay men had a higher average number of both experiences and mates compared to both lesbian women and heterosexual men.
+These results suggest that theoretically speaking, even when gender differences in mating preferences exist, those in short-term mating behaviors only occur among particular populations, or when men’s preferences for short-term mating are not constrained by those of women.
 Suggestions for future research in human mating psychology and behaviors were provided.
@@
 Gender differences in sexual behaviors, especially short-term mating behaviors, are well-documented in human sexuality research.
-For example, research has found that heterosexual men, as compared to heterosexual women, have a higher average number of past short-term sexual partners [@oliver_gender_1993; @petersen_meta-analytic_2010; @rissel_heterosexual_2014], and engage in both short-term mating and extramarital sex more often [@petersen_meta-analytic_2010].
+For example, research has found that heterosexual men, as compared to heterosexual women, report to have a higher average number of past short-term sexual partners [@oliver_gender_1993; @petersen_meta-analytic_2010; @rissel_heterosexual_2014], and engage in both short-term mating and extramarital sex more often [@petersen_meta-analytic_2010].
 These gender differences have also been observed between gay men and lesbian women [@bailey_effects_1994; @bryant_relationship_1994; @peplau_national_1997; @peplau_sexuality_2004].
@@
 This is because any heterosexual sexual encounter involves both a man and a woman [the frequency of encounters involving more than two persons is negligible, e.g., @herbenick_sexual_2017].
-A new short-term mating experience for a man is, therefore, also a new experience for a woman, and the same logic applies to counting a new short-term mate.
+A new short-term mating experience for a man is, therefore, also a new experience for a woman.
+Likewise, when a man has a new short-term mate, so does his partner.
 As a result, the psychological differences in short-term mating preferences may not result in behavioral ones in the heterosexual case [@archer_reality_2019].
 
-As a starting point, we took gender differences in mating preferences as conceptualized by the sexual strategy theory [@buss_sexual_1993] and repeatedly supported by empirical investigations [e.g., @schmitt_universal_2003; @walter_sex_2020].
+As a starting point, we took gender differences in mating preferences as conceptualized by the sexual strategy theory [@buss_sexual_1993], which is repeatedly supported by empirical investigations [e.g., @schmitt_universal_2003; @walter_sex_2020].
 Using an agent-based model, we investigated whether men and women's differential preferences for short-term mating would result in gender differences in short-term mating behaviors, and if so, then under what conditions they would result in differences in the number of short-term mating experiences and short-term mates.
@@
 For example, studies using U.S.
-college samples have found that the minimum percentile ranks that men found acceptable for a potential short-term sexual partner were lower than those accepted by women, both in terms of overall desirability and individual traits (e.g., social status, attractiveness) [@kenrick_evolution_1990; @regan_minimum_1998].
+college samples have found that the minimum percentile ranks of the desirability of a potential short-term sexual partner accepted by men were lower than those accepted by women, in terms of both the overall desirability and the desirability of individual traits (e.g., social status, attractiveness) [@kenrick_evolution_1990; @regan_minimum_1998].
 Another study also found that when presented with identical descriptions of potential mates, men on average rated them as more desirable than women did [@wiederman_evolution_1998].
 
-Some evidence shows that gender differences in mating preferences also existed between gay men and lesbian women.
+Some evidence shows that gender differences in mating preferences also exist between gay men and lesbian women, suggesting that these differences are based on individuals' gender rather than their sexual orientation.
 A survey study using a community sample from the U.S.
@@
 Since heterosexual sex in most cases involves one man and one woman, men's relatively high interest in short-term mating can be constrained by women's preference for long-term relationships [@archer_reality_2019; @symons_evolution_1979].
-This is because men’s short-term mating preferences – with the relatively rare exception of sexual violence – can only translate into behaviors when there are women willing to have sex with them.
-When a new short-term mating encounter occurs, it counts both towards men’s total number of short-term mating encounters as well as towards women’s.
-Similarly, a new short-term mate counts towards both men and women’s total number of short-term mates.
+This is because men’s short-term mating preferences – with the exception of sexual violence – can only translate into behaviors when there are women willing to have sex with them.
+When a new short-term mating encounter occurs, it counts towards both men’s total number of short-term mating encounters as well as women’s, and both men and women have new short-term mates.
 Therefore, the total number of short-term mating experiences and short-term mates must be equal between heterosexual men and women at the population level.
@@
 By using a spatial agent-based model, the present study investigated whether men and women’s differential preferences for short-term mating would result in gender differences in short-term mating behaviors, and if they did, under what circumstances.
-Preferences for short-term mating were operationally defined as the likelihood of engaging in short-term mating when encountering a mate as well as the standards for short-term mates [@buss_sexual_1993].
+Preferences for short-term mating were operationally defined as the likelihood of engaging in short-term mating upon encountering a mate and the standards for short-term mates [@buss_sexual_1993].
 Short-term mating behaviors were operationally defined as the number of short-term mating experiences and the number of past short-term mates [@petersen_meta-analytic_2010].
 
-We modeled this process among both heterosexual individuals and gay men and lesbian women to examine whether constraints set by the opposite sex’s preferences would affect short-term mating behaviors.
+We also modeled forming long-term relationships as a background process.
+A pair of individuals had a possibility to commit to a long-term relationship upon meeting each other.
+We modeled forming long-term relationships as a behavioral outcome and ignored the psychological processes behind it, although we recognize gender differences may also exist in long-term mating strategy [@buss_sexual_1993].
+
+We modeled these processes among both heterosexual individuals and gay men and lesbian women to examine whether constraints set by the opposite sex’s preferences would affect short-term mating behaviors.
 Individuals’ sexual orientation was conceptualized in terms of behaviors only in our model.
@@
 
-The likelihood of engaging in short-term mating and the standard for short-term mates were initialized either identically or differently for men and women, depending on the experimental conditions.
+The likelihood of engaging in short-term mating and the standard for short-term mates were initialized to the values discussed previously.
+Whether men and women had the same initial values depended on the experimental conditions.
 
@@
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-Statistics were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
+The averages were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
 \end{figure}
@@
 Gay men engaged in short-term mating behaviors more than heterosexual men did (Figure 2).
-The average number of short-term mating experiences was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`.
-Similarly, the average number of short-term mates was higher among gay men (*M* = `r m_partner_all.mean_1_11`, *SD* = `r m_partner_all.sd_1_11`) than among heterosexual men (*M* = `r m_partner_all.mean_0_11`, *SD* = `r m_partner_all.sd_0_11`), *t*(`r partner.all.parameter_hg`) = `r partner.all.statistic_hg`, *p* `r partner.all.p.value_hg`, Cohen's *d* = `r partner_all.d_hg`.
+The average number of short-term mating experiences (as calculated using the full population of men) was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`.
+Similarly, the average number of short-term mates (as calculated using the full population of men) was higher among gay men (*M* = `r m_partner_all.mean_1_11`, *SD* = `r m_partner_all.sd_1_11`) than among heterosexual men (*M* = `r m_partner_all.mean_0_11`, *SD* = `r m_partner_all.sd_0_11`), *t*(`r partner.all.parameter_hg`) = `r partner.all.statistic_hg`, *p* `r partner.all.p.value_hg`, Cohen's *d* = `r partner_all.d_hg`.
 
@@
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-Statistics were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
+The averages were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
 \end{figure}
@@
   footnote(
-    general = "\\\\textit{Note.} The statistics were calculated with subsamples of men and women who had had engaged in short-term mating behaviors.
+    general = "\\\\textit{Note.} The averages were calculated with subsamples of men and women who had had engaged in short-term mating behaviors.
 See Supplementary Materials for the mean and standard deviation of sample sizes.",
@@
 This contributed to the unequal number of men and women in the mating pool, which led to gender differences in short-term mating behaviors among this population.
+In comparison, even when men and women had different short-term mating likelihood, the probability of any pair of them ending up having sex is the product of their individual likelihood (since men and women made decisions independently).
+As this probability is the same for both parties, the gender difference in short-term mating likelihood did not translate into different behaviors.
 
@@
 One possibility is sampling bias in the observations [e.g., @wiederman_evolution_1998] since surveys regarding short-term mating behaviors may tend to attract individuals who already engage in such behaviors.
-Another possibility is that heterosexual men and women tend to report short-term mating behaviors differently.
-This difference may be a result of social desirability bias [@alexander_truth_2003] or due to men and women's different estimation strategies (e.g., men tend to round up) [@brown_estimating_1999].
+Our results suggest that when this group of individuals is considered, there can be gender differences in short-term mating behaviors that do not exist in the full population.
+A second explanation is that heterosexual men and women's self-reported sexual behaviors are affected by social desirability bias due to gender norms.
+Men may overreport since having more sexual partners can show their masculinity and yield them reputation benefits, while women may underreport because this violates the chastity norm [@fisher2013gender].
+A third explanation is that men and women have different estimation strategies of their sexual experiences.
+Men may tend to approximate and round up, while women's tendency to count instances may lead to lower estimations [@brown_estimating_1999; @mitchell_why_2019].
 
@@
 
-Using agent-based modeling, the present study simulated the circumstances under which men and women’s differential preferences for short-term mating resulted in gender differences in short-term mating behaviors.
-We found when men (vs.
+Using agent-based modeling to simulate short-term mating behaviors, we found when men (vs.
 women) had a stronger preferences for short-term mating, heterosexual men and women engaged in short-term mating behaviors to the same extent, while gay men engaged in more short-term mating behaviors as compared to lesbian women.

### 2022-05-30 submission/manuscript.tex
edits in writing

@@
 number of both experiences and mates only when heterosexual men and
-women in the mating pool (i.e., those with a non-zero number of
-short-term mating experiences) were considered. Moreover, when men had
-stronger preferences for short-term mating than women, gay men had a
-higher average number of both experiences and mates compared to both
-lesbian women and heterosexual men. These results suggest that
-theoretically speaking, even when gender differences in mating
-preferences existed, those in short-term mating behaviors only occurred
-among particular populations, or when men's preferences for short-term
-mating are not constrained by those of women. Suggestions for future
-research in human mating psychology and behaviors were provided.
+women who successfully participated in the mating pool (i.e., those with
+a non-zero number of short-term mating experiences) were considered.
+Moreover, when men (vs.~women) had stronger preferences for short-term
+mating, gay men had a higher average number of both experiences and
+mates compared to both lesbian women and heterosexual men. These results
+suggest that theoretically speaking, even when gender differences in
+mating preferences exist, those in short-term mating behaviors only
+occur among particular populations, or when men's preferences for
+short-term mating are not constrained by those of women. Suggestions for
+future research in human mating psychology and behaviors were provided.
 
@@
 research has found that heterosexual men, as compared to heterosexual
-women, have a higher average number of past short-term sexual partners
-(Oliver \& Hyde, 1993; Petersen \& Hyde, 2010; Rissel et al., 2014), and
-engage in both short-term mating and extramarital sex more often
-(Petersen \& Hyde, 2010). These gender differences have also been
+women, report to have a higher average number of past short-term sexual
+partners (Oliver \& Hyde, 1993; Petersen \& Hyde, 2010; Rissel et al.,
+2014), and engage in both short-term mating and extramarital sex more
+often (Petersen \& Hyde, 2010). These gender differences have also been
 observed between gay men and lesbian women (Bailey et al., 1994; Bryant
@@
 new short-term mating experience for a man is, therefore, also a new
-experience for a woman, and the same logic applies to counting a new
-short-term mate. As a result, the psychological differences in
+experience for a woman. Likewise, when a man has a new short-term mate,
+so does his partner. As a result, the psychological differences in
 short-term mating preferences may not result in behavioral ones in the
@@
 As a starting point, we took gender differences in mating preferences as
-conceptualized by the sexual strategy theory (Buss \& Schmitt, 1993) and
-repeatedly supported by empirical investigations (e.g., Schmitt, 2003;
-Walter et al., 2020). Using an agent-based model, we investigated
-whether men and women's differential preferences for short-term mating
-would result in gender differences in short-term mating behaviors, and
-if so, then under what conditions they would result in differences in
-the number of short-term mating experiences and short-term mates.
+conceptualized by the sexual strategy theory (Buss \& Schmitt, 1993),
+which is repeatedly supported by empirical investigations (e.g.,
+Schmitt, 2003; Walter et al., 2020). Using an agent-based model, we
+investigated whether men and women's differential preferences for
+short-term mating would result in gender differences in short-term
+mating behaviors, and if so, then under what conditions they would
+result in differences in the number of short-term mating experiences and
+short-term mates.
 
@@
 a potential short-term mate. For example, studies using U.S. college
-samples have found that the minimum percentile ranks that men found
-acceptable for a potential short-term sexual partner were lower than
-those accepted by women, both in terms of overall desirability and
-individual traits (e.g., social status, attractiveness) (Kenrick et al.,
-1990; Regan, 1998). Another study also found that when presented with
-identical descriptions of potential mates, men on average rated them as
-more desirable than women did (Wiederman \& Dubois, 1998).
+samples have found that the minimum percentile ranks of the desirability
+of a potential short-term sexual partner accepted by men were lower than
+those accepted by women, in terms of both the overall desirability and
+the desirability of individual traits (e.g., social status,
+attractiveness) (Kenrick et al., 1990; Regan, 1998). Another study also
+found that when presented with identical descriptions of potential
+mates, men on average rated them as more desirable than women did
+(Wiederman \& Dubois, 1998).
 
 Some evidence shows that gender differences in mating preferences also
-existed between gay men and lesbian women. A survey study using a
-community sample from the U.S. found that gay men were more interested
-in short-term mating than lesbian women were, and that this gender
-difference was comparable to that existing among heterosexual
-individuals (Bailey et al., 1994). An additional indirect piece of
-evidence on differential standards for short-term mates comes from a
-recent study finding that significantly more gay men than lesbian women
-reported to have accepted a casual sexual offer from a same-gender
-person (Matsick et al., 2021). Past studies suggest that the gender
-difference in the acceptance rate of casual sexual offers may originate
-from men and women's differential standards for short-term mates (Conley
-et al., 2011; Hald \& Høgh-Olesen, 2010). Thus, as a postulation, gay
-men may also have lower standards than lesbian women for short-term
-mates.
+exist between gay men and lesbian women, suggesting that these
+differences are based on individuals' gender rather than their sexual
+orientation. A survey study using a community sample from the U.S. found
+that gay men were more interested in short-term mating than lesbian
+women were, and that this gender difference was comparable to that
+existing among heterosexual individuals (Bailey et al., 1994). An
+additional indirect piece of evidence on differential standards for
+short-term mates comes from a recent study finding that significantly
+more gay men than lesbian women reported to have accepted a casual
+sexual offer from a same-gender person (Matsick et al., 2021). Past
+studies suggest that the gender difference in the acceptance rate of
+casual sexual offers may originate from men and women's differential
+standards for short-term mates (Conley et al., 2011; Hald \&
+Høgh-Olesen, 2010). Thus, as a postulation, gay men may also have lower
+standards than lesbian women for short-term mates.
 
@@
 1979). This is because men's short-term mating preferences -- with the
-relatively rare exception of sexual violence -- can only translate into
-behaviors when there are women willing to have sex with them. When a new
-short-term mating encounter occurs, it counts both towards men's total
-number of short-term mating encounters as well as towards women's.
-Similarly, a new short-term mate counts towards both men and women's
-total number of short-term mates. Therefore, the total number of
-short-term mating experiences and short-term mates must be equal between
+exception of sexual violence -- can only translate into behaviors when
+there are women willing to have sex with them. When a new short-term
+mating encounter occurs, it counts towards both men's total number of
+short-term mating encounters as well as women's, and both men and women
+have new short-term mates. Therefore, the total number of short-term
+mating experiences and short-term mates must be equal between
 heterosexual men and women at the population level. However, it is
@@
 were operationally defined as the likelihood of engaging in short-term
-mating when encountering a mate as well as the standards for short-term
-mates (Buss \& Schmitt, 1993). Short-term mating behaviors were
-operationally defined as the number of short-term mating experiences and
-the number of past short-term mates (Petersen \& Hyde, 2010).
+mating upon encountering a mate and the standards for short-term mates
+(Buss \& Schmitt, 1993). Short-term mating behaviors were operationally
+defined as the number of short-term mating experiences and the number of
+past short-term mates (Petersen \& Hyde, 2010).
 
-We modeled this process among both heterosexual individuals and gay men
-and lesbian women to examine whether constraints set by the opposite
+We also modeled forming long-term relationships as a background process.
+A pair of individuals had a possibility to commit to a long-term
+relationship upon meeting each other. We modeled forming long-term
+relationships as a behavioral outcome and ignored the psychological
+processes behind it, although we recognize gender differences may also
+exist in long-term mating strategy (Buss \& Schmitt, 1993).
+
+We modeled these processes among both heterosexual individuals and gay
+men and lesbian women to examine whether constraints set by the opposite
 sex's preferences would affect short-term mating behaviors. Individuals'
@@
 The likelihood of engaging in short-term mating and the standard for
-short-term mates were initialized either identically or differently for
-men and women, depending on the experimental conditions.
+short-term mates were initialized to the values discussed previously.
+Whether men and women had the same initial values depended on the
+experimental conditions.
 
@@
 men did (Figure 2). The average number of short-term mating experiences
-was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37) than among
-heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24), \emph{t}(4,998) =
--134.87, \emph{p} \textless{} .001, Cohen's \emph{d} = 3.81. Similarly,
-the average number of short-term mates was higher among gay men
-(\emph{M} = 1.72, \emph{SD} = 0.19) than among heterosexual men
-(\emph{M} = 0.80, \emph{SD} = 0.11), \emph{t}(4,998) = -206.91, \emph{p}
-\textless{} .001, Cohen's \emph{d} = 5.85.
+(as calculated using the full population of men) was higher among gay
+men (\emph{M} = 2.63, \emph{SD} = 0.37) than among heterosexual men
+(\emph{M} = 1.43, \emph{SD} = 0.24), \emph{t}(4,998) = -134.87, \emph{p}
+\textless{} .001, Cohen's \emph{d} = 3.81. Similarly, the average number
+of short-term mates (as calculated using the full population of men) was
+higher among gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among
+heterosexual men (\emph{M} = 0.80, \emph{SD} = 0.11), \emph{t}(4,998) =
+-206.91, \emph{p} \textless{} .001, Cohen's \emph{d} = 5.85.
 
@@
 \small
-\item \textit{Note.} The statistics were calculated with subsamples of men and women who had had engaged in short-term mating behaviors.
+\item \textit{Note.} The averages were calculated with subsamples of men and women who had had engaged in short-term mating behaviors.
 See Supplementary Materials for the mean and standard deviation of sample sizes.
@@
 mating pool, which led to gender differences in short-term mating
-behaviors among this population.
+behaviors among this population. In comparison, even when men and women
+had different short-term mating likelihood, the probability of any pair
+of them ending up having sex is the product of their individual
+likelihood (since men and women made decisions independently). As this
+probability is the same for both parties, the gender difference in
+short-term mating likelihood did not translate into different behaviors.
 
@@
 regarding short-term mating behaviors may tend to attract individuals
-who already engage in such behaviors. Another possibility is that
-heterosexual men and women tend to report short-term mating behaviors
-differently. This difference may be a result of social desirability bias
-(Alexander \& Fisher, 2003) or due to men and women's different
-estimation strategies (e.g., men tend to round up) (Brown \& Sinclair,
-1999).
+who already engage in such behaviors. Our results suggest that when this
+group of individuals is considered, there can be gender differences in
+short-term mating behaviors that do not exist in the full population. A
+second explanation is that heterosexual men and women's self-reported
+sexual behaviors are affected by social desirability bias due to gender
+norms. Men may overreport since having more sexual partners can show
+their masculinity and yield them reputation benefits, while women may
+underreport because this violates the chastity norm (Fisher, 2013). A
+third explanation is that men and women have different estimation
+strategies of their sexual experiences. Men may tend to approximate and
+round up, while women's tendency to count instances may lead to lower
+estimations (Brown \& Sinclair, 1999; Mitchell et al., 2019).
 
@@
 
-Using agent-based modeling, the present study simulated the
-circumstances under which men and women's differential preferences for
-short-term mating resulted in gender differences in short-term mating
-behaviors. We found when men (vs.~women) had a stronger preferences for
-short-term mating, heterosexual men and women engaged in short-term
-mating behaviors to the same extent, while gay men engaged in more
-short-term mating behaviors as compared to lesbian women. Gay men
-engaged in more short-term mating behaviors than heterosexual men did.
+Using agent-based modeling to simulate short-term mating behaviors, we
+found when men (vs.~women) had a stronger preferences for short-term
+mating, heterosexual men and women engaged in short-term mating
+behaviors to the same extent, while gay men engaged in more short-term
+mating behaviors as compared to lesbian women. Gay men engaged in more
+short-term mating behaviors than heterosexual men did.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-alexander_truth_2003}{}}%
-Alexander, M. G., \& Fisher, T. D. (2003). Truth and consequences: Using
-the bogus pipeline to examine sex differences in self‐reported
-sexuality. \emph{The Journal of Sex Research}, \emph{40}(1), 27--35.
-\url{https://doi.org/10.1080/00224490309552164}
-
 \leavevmode\vadjust pre{\hypertarget{ref-archer_reality_2019}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-fisher2013gender}{}}%
+Fisher, T. D. (2013). Gender roles and pressure to be truthful: The
+bogus pipeline modifies gender differences in sexual but not non-sexual
+behavior. \emph{Sex Roles}, \emph{68}(7), 401--414.
+
 \leavevmode\vadjust pre{\hypertarget{ref-s_j_gurman_six_1989}{}}%
@@
 \url{https://doi.org/10.1016/j.evolhumbehav.2004.09.005}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mitchell_why_2019}{}}%
+Mitchell, K. R., Mercer, C. H., Prah, P., Clifton, S., Tanton, C.,
+Wellings, K., \& Copas, A. (2019). Why do men report more opposite-sex
+sexual partners than women? Analysis of the gender discrepancy in a
+british national probability survey. \emph{The Journal of Sex Research},
+\emph{56}(1), 1--8. \url{https://doi.org/10.1080/00224499.2018.1481193}
 

### 2022-06-01 submission/manuscript.Rmd
added texts to explain in-poll differences and added hypos

@@
       formatted <- ifelse(
-        abs(x - round(x)) < .Machine$double.eps,
+        abs(x - round(x)) < .Machine$double.eps & x != 0,
         # treat as integer
@@
 
-As a starting point, we took gender differences in mating preferences as conceptualized by the sexual strategy theory [@buss_sexual_1993], which is repeatedly supported by empirical investigations [e.g., @schmitt_universal_2003; @walter_sex_2020].
+As a starting point, we took gender differences in mating preferences as conceptualized by the sexual strategy theory [@buss_sexual_1993; @buss2019mate], which is repeatedly supported by empirical investigations [e.g., @schmitt_universal_2003; @walter_sex_2020].
 Using an agent-based model, we investigated whether men and women's differential preferences for short-term mating would result in gender differences in short-term mating behaviors, and if so, then under what conditions they would result in differences in the number of short-term mating experiences and short-term mates.
@@
 
-Gender differences in mating preferences have been studied in the light of sexual strategy theory [@buss_sexual_1993].
+Gender differences in mating preferences have been studied in the light of sexual strategy theory [@buss_sexual_1993; @buss2019mate].
 It posits that since the minimum obligatory investment that men must devote to their offspring (contribution of sperm through one sexual act) is lower than that of women (gestation, labor, and lactation), men tend to be relatively more interested in short-term mating compared to women.
@@
 ## Constraints on men's preferences for short-term mating
+
 Since heterosexual sex in most cases involves one man and one woman, men's relatively high interest in short-term mating can be constrained by women's preference for long-term relationships [@archer_reality_2019; @symons_evolution_1979].
@@
 Therefore, the total number of short-term mating experiences and short-term mates must be equal between heterosexual men and women at the population level.
+In a closed population with equal sex ratio, it follows that the average number of experiences and mates should also be equal between men and women.
+Following this line of reasoning, we would expect to observe no gender difference in short-term mating behaviors among heterosexual individuals even when there were gender differences in mating preferences.
+
 However, it is important to note that although heterosexual men’s total number of short-term mating is equal to that of women, this does not necessarily mean that the total number of men and women who have ever had short-term mating must be equal.
-It is possible that there is a smaller proportion of men (vs.
-the proportion of women) who contribute to the total number of short-term mating.
-Following this line of reasoning, we would expect to observe no gender difference in short-term mating behaviors among heterosexual individuals even when there are gender differences in mating preferences.
+Since women have higher standards for short-term mates than men [@buss_sexual_1993], it is possible that the proportion of individuals who meet a potential partner's standards is lower among men than among women, assuming both men and women's desirability values follow the same distribution.
+Consequently, there may be a smaller proportion of men (vs.
+the proportion of women) who participate in the mating pool and contribute to the total number of short-term mating.
+For example, suppose that there is a population of 20 individuals with an equal sex ratio.
+There are 8 men and 8 women with a desirability value greater than x~1~ and 3 men and 3 women with a value greater than x~2~ (x~1~ < x~2~).
+Suppose that x~1~ and x~2~ happen to be men and women's standards for short-term mates, then in a long enough period of time, the 8 women who meet men's standards and the 3 men who meet women's standards will have had short-term mating.
+Since the total number of short-term mating behaviors is the same between men and women, we would expect that in a population of individuals who had any short-term mating, the average number of short-term mating experiences and mates was higher among men than women (e.g., in the aforementioned example, the number is n/3 for men and n/8 for women, where n can be the total number of short-term mating experiences or the number of short-term mates).
 
@@
 A pair of individuals had a possibility to commit to a long-term relationship upon meeting each other.
-We modeled forming long-term relationships as a behavioral outcome and ignored the psychological processes behind it, although we recognize gender differences may also exist in long-term mating strategy [@buss_sexual_1993].
+We modeled forming long-term relationships as a behavioral outcome and ignored the psychological processes behind it, although we recognize gender differences may also exist in long-term mating strategy [@buss_sexual_1993; @buss2019mate].
 
@@
 
-We formulated the following hypotheses in the present study: assuming gender differences in preferences for short-term mating, 1) there would be gender differences in short-term mating behaviors among gay men and lesbian women, with gay men being engaged in more such behaviors, and 2) gay men would engage in more short-term mating behaviors as compared to heterosexual men.
+We formulated the following hypotheses in the present study: assuming gender differences in preferences for short-term mating, 1) there would be no gender differences in short-term mating behaviors among all heterosexual men and women, 2) a smaller proportion of heterosexual men had ever engaged into short-term mating compared to the proportion of heterosexual women, 3) in a population of heterosexual individuals who had any short-term mating, men had higher average number of short-term mating behaviors than women, 4) there would be gender differences in short-term mating behaviors among gay men and lesbian women, with gay men being engaged in more such behaviors, and 5) gay men would engage in more short-term mating behaviors compared to heterosexual men.
 
@@
 
-## Gender differences in short-term mating behaviors
+## Gender differences in short-term mating behaviors in the full population
 
@@
 The results from Experiment 1 showed that when there were gender differences in preferences for short-term mating, there was no gender difference in the average number of short-term mating experiences among heterosexual individuals (*M~men~* = `r m_exp_all.mean_011`, *SD~men~* = `r m_exp_all.sd_011`; *M~women~* = `r f_exp_all.mean_011`, *SD~women~* = `r f_exp_all.sd_011`), Cohen's *d* = `r exp_all.d_011`.
-Nor was there a difference in the average number of short-term mates (*M~men~* = `r m_partner_all.mean_011`, *SD~men~* = `r m_partner_all.sd_011`; *M~w~* = `r f_partner_all.mean_011`, *SD~women~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011` (Figure 1).
+Nor was there a difference in the average number of short-term mates (*M~men~* = `r m_partner_all.mean_011`, *SD~men~* = `r m_partner_all.sd_011`; *M~women~* = `r f_partner_all.mean_011`, *SD~women~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011` (Figure 1).
 
@@
 
-```{r sec1.3}
+## Heterosexual individuals in the mating pool
+
+```{r sec2.2}
 # the number of experiences, difference*2, heterosexual in the mating pool

### 2022-06-01 submission/manuscript.tex
added texts to explain in-poll differences and added hypos

@@
 As a starting point, we took gender differences in mating preferences as
-conceptualized by the sexual strategy theory (Buss \& Schmitt, 1993),
-which is repeatedly supported by empirical investigations (e.g.,
-Schmitt, 2003; Walter et al., 2020). Using an agent-based model, we
-investigated whether men and women's differential preferences for
-short-term mating would result in gender differences in short-term
-mating behaviors, and if so, then under what conditions they would
-result in differences in the number of short-term mating experiences and
-short-term mates.
+conceptualized by the sexual strategy theory (Buss \& Schmitt, 1993;
+Buss \& Schmitt, 2019), which is repeatedly supported by empirical
+investigations (e.g., Schmitt, 2003; Walter et al., 2020). Using an
+agent-based model, we investigated whether men and women's differential
+preferences for short-term mating would result in gender differences in
+short-term mating behaviors, and if so, then under what conditions they
+would result in differences in the number of short-term mating
+experiences and short-term mates.
 
@@
 Gender differences in mating preferences have been studied in the light
-of sexual strategy theory (Buss \& Schmitt, 1993). It posits that since
-the minimum obligatory investment that men must devote to their
-offspring (contribution of sperm through one sexual act) is lower than
-that of women (gestation, labor, and lactation), men tend to be
-relatively more interested in short-term mating compared to women. This
-is because the number of offspring women can produce is limited and
-cannot be increased by mating with a large number of men, whereas the
-reverse is the case for men. As a result, men are predicted to not only
-have a greater interest in short-term mating, but also desire a larger
-number of short-term mates in a given period and be less selective with
-respect to accepting a potential mate (Buss \& Schmitt, 1993).
+of sexual strategy theory (Buss \& Schmitt, 1993; Buss \& Schmitt,
+2019). It posits that since the minimum obligatory investment that men
+must devote to their offspring (contribution of sperm through one sexual
+act) is lower than that of women (gestation, labor, and lactation), men
+tend to be relatively more interested in short-term mating compared to
+women. This is because the number of offspring women can produce is
+limited and cannot be increased by mating with a large number of men,
+whereas the reverse is the case for men. As a result, men are predicted
+to not only have a greater interest in short-term mating, but also
+desire a larger number of short-term mates in a given period and be less
+selective with respect to accepting a potential mate (Buss \& Schmitt,
+1993).
 
@@
 mating experiences and short-term mates must be equal between
-heterosexual men and women at the population level. However, it is
-important to note that although heterosexual men's total number of
-short-term mating is equal to that of women, this does not necessarily
-mean that the total number of men and women who have ever had short-term
-mating must be equal. It is possible that there is a smaller proportion
-of men (vs.~the proportion of women) who contribute to the total number
-of short-term mating. Following this line of reasoning, we would expect
-to observe no gender difference in short-term mating behaviors among
-heterosexual individuals even when there are gender differences in
-mating preferences.
+heterosexual men and women at the population level. In a closed
+population with equal sex ratio, it follows that the average number of
+experiences and mates should also be equal between men and women.
+Following this line of reasoning, we would expect to observe no gender
+difference in short-term mating behaviors among heterosexual individuals
+even when there were gender differences in mating preferences.
+
+However, it is important to note that although heterosexual men's total
+number of short-term mating is equal to that of women, this does not
+necessarily mean that the total number of men and women who have ever
+had short-term mating must be equal. Since women have higher standards
+for short-term mates than men (Buss \& Schmitt, 1993), it is possible
+that the proportion of individuals who meet a potential partner's
+standards is lower among men than among women, assuming both men and
+women's desirability values follow the same distribution. Consequently,
+there may be a smaller proportion of men (vs.~the proportion of women)
+who participate in the mating pool and contribute to the total number of
+short-term mating. For example, suppose that there is a population of 20
+individuals with an equal sex ratio. There are 8 men and 8 women with a
+desirability value greater than x\textsubscript{1} and 3 men and 3 women
+with a value greater than x\textsubscript{2} (x\textsubscript{1}
+\textless{} x\textsubscript{2}). Suppose that x\textsubscript{1} and
+x\textsubscript{2} happen to be men and women's standards for short-term
+mates, then in a long enough period of time, the 8 women who meet men's
+standards and the 3 men who meet women's standards will have had
+short-term mating. Since the total number of short-term mating behaviors
+is the same between men and women, we would expect that in a population
+of individuals who had any short-term mating, the average number of
+short-term mating experiences and mates was higher among men than women
+(e.g., in the aforementioned example, the number is n/3 for men and n/8
+for women, where n can be the total number of short-term mating
+experiences or the number of short-term mates).
 
@@
 processes behind it, although we recognize gender differences may also
-exist in long-term mating strategy (Buss \& Schmitt, 1993).
+exist in long-term mating strategy (Buss \& Schmitt, 1993; Buss \&
+Schmitt, 2019).
 
@@
 gender differences in preferences for short-term mating, 1) there would
-be gender differences in short-term mating behaviors among gay men and
-lesbian women, with gay men being engaged in more such behaviors, and 2)
-gay men would engage in more short-term mating behaviors as compared to
-heterosexual men.
+be no gender differences in short-term mating behaviors among all
+heterosexual men and women, 2) a smaller proportion of heterosexual men
+had ever engaged into short-term mating compared to the proportion of
+heterosexual women, 3) in a population of heterosexual individuals who
+had any short-term mating, men had higher average number of short-term
+mating behaviors than women, 4) there would be gender differences in
+short-term mating behaviors among gay men and lesbian women, with gay
+men being engaged in more such behaviors, and 5) gay men would engage in
+more short-term mating behaviors compared to heterosexual men.
 
@@
 
-\hypertarget{gender-differences-in-short-term-mating-behaviors}{%
-\subsection{Gender differences in short-term mating
-behaviors}\label{gender-differences-in-short-term-mating-behaviors}}
+\hypertarget{gender-differences-in-short-term-mating-behaviors-in-the-full-population}{%
+\subsection{Gender differences in short-term mating behaviors in the
+full
+population}\label{gender-differences-in-short-term-mating-behaviors-in-the-full-population}}
 
@@
 \emph{SD\textsubscript{men}} = 0.24; \emph{M\textsubscript{women}} =
-1.43, \emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0. Nor
-was there a difference in the average number of short-term mates
+1.43, \emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0.00.
+Nor was there a difference in the average number of short-term mates
 (\emph{M\textsubscript{men}} = 0.80, \emph{SD\textsubscript{men}} =
 0.11; \emph{M\textsubscript{w}} = 0.80, \emph{SD\textsubscript{women}} =
-0.11), Cohen's \emph{d} = 0 (Figure 1).
+0.11), Cohen's \emph{d} = 0.00 (Figure 1).
 
@@
 .001, Cohen's \emph{d} = 10.12.
+
+\hypertarget{heterosexual-individuals-in-the-mating-pool}{%
+\subsection{Heterosexual individuals in the mating
+pool}\label{heterosexual-individuals-in-the-mating-pool}}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-buss2019mate}{}}%
+Buss, D. M., \& Schmitt, D. P. (2019). Mate preferences and their
+behavioral manifestations. \emph{Annual Review of Psychology},
+\emph{70}, 77--110.
+
 \leavevmode\vadjust pre{\hypertarget{ref-conley_women_2011}{}}%

### 2022-06-01 submission/manuscript.Rmd
added texts for the in-pool number difference and stats tests

@@
 library(tidyverse); library(here); library(knitr); library(kableExtra)
+
+N <- 150
 
@@
 
-The results from Experiment 1 showed that when there were gender differences in preferences for short-term mating, there was no gender difference in the average number of short-term mating experiences among heterosexual individuals (*M~men~* = `r m_exp_all.mean_011`, *SD~men~* = `r m_exp_all.sd_011`; *M~women~* = `r f_exp_all.mean_011`, *SD~women~* = `r f_exp_all.sd_011`), Cohen's *d* = `r exp_all.d_011`.
-Nor was there a difference in the average number of short-term mates (*M~men~* = `r m_partner_all.mean_011`, *SD~men~* = `r m_partner_all.sd_011`; *M~women~* = `r f_partner_all.mean_011`, *SD~women~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011` (Figure 1).
+The results from Experiment 1 showed that when there were gender differences in preferences for short-term mating, there was no gender difference in the average number of short-term mating experiences among the full population of heterosexual individuals (*M~men~* = `r m_exp_all.mean_011`, *SD~men~* = `r m_exp_all.sd_011`; *M~women~* = `r f_exp_all.mean_011`, *SD~women~* = `r f_exp_all.sd_011`), Cohen's *d* = `r exp_all.d_011`.
+Nor was there a difference in the average number of short-term mates (*M~men~* = `r m_partner_all.mean_011`, *SD~men~* = `r m_partner_all.sd_011`; *M~women~* = `r f_partner_all.mean_011`, *SD~women~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011` (Figure \ref{fig:men_vs_women}).
 
@@
 The averages were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
+  \label{fig:men_vs_women}
 \end{figure}
@@
 
-The results from Experiment 2 showed that when there were gender differences in preferences for short-term mating, there were gender differences in short-term mating behaviors between gay men and lesbian women (Figure 1).
+The results from Experiment 2 showed that when there were gender differences in preferences for short-term mating, there were gender differences in short-term mating behaviors between gay men and lesbian women (Figure \ref{fig:men_vs_women}).
 The average number of short-term mating experiences was higher among gay men (*M* = `r m_exp_all.mean_111`, *SD* = `r m_exp_all.sd_111`) than among lesbian women (*M* = `r f_exp_all.mean_111`, *SD* = `r f_exp_all.sd_111`), *t*(`r exp.all.parameter_111`) = `r exp.all.statistic_111`, *p* `r exp.all.p.value_111`, Cohen's *d* = `r exp_all.d_111`.
@@
 
-```{r sec2.2}
+```{r sec2}
+# the number of in-pool, difference*2
+m_inpool.mean_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(m_inpool.mean)
+m_inpool.sd_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(m_inpool.sd)
+f_inpool.mean_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(f_inpool.mean)
+f_inpool.sd_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(f_inpool.sd)
+inpool.parameter_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(inpool.parameter)
+inpool.statistic_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(inpool.statistic)
+inpool.p.value_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(inpool.p.value)
+inpool.d_011 <-
+  results %>% filter(hls == "0_1_1") %>% pull(inpool.d) %>% abs()
+
 # the number of experiences, difference*2, heterosexual in the mating pool
@@
   results %>% filter(hls == "0_1_1") %>% pull(partner_ip.d) %>% abs()
-
-# the number of in-pool, difference*2
-m_inpool.mean_011 <-
-  results %>% filter(hls == "0_1_1") %>% pull(m_inpool.mean)
-m_inpool.sd_011 <-
-  results %>% filter(hls == "0_1_1") %>% pull(m_inpool.sd)
-f_inpool.mean_011 <-
-  results %>% filter(hls == "0_1_1") %>% pull(f_inpool.mean)
-f_inpool.sd_011 <-
-  results %>% filter(hls == "0_1_1") %>% pull(f_inpool.sd)
 ```
 
-In Experiment 1, however, when the means of the outcome variables were calculated only among men and women in the mating pool (the number of individuals in the mating pool: *M~men~* = `r m_inpool.mean_011`, *SD~men~* = `r m_inpool.sd_011`; *M~women~* = `r f_inpool.mean_011`, *SD~women~* = `r f_inpool.sd_011`), there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating.
+In Experiment 1, there was a smaller proportion of heterosexual men in the mating pool (*M* = `r m_inpool.mean_011/N`, *SD* = `r m_inpool.sd_011/N`) compared to women (*M* = `r f_inpool.mean_011/N`, *SD* = `r f_inpool.sd_011/N`)), *t*(`r inpool.parameter_011`) = `r inpool.statistic_011`, *p* `r inpool.p.value_011`, Cohen's *d* = `r inpool.d_011`.
+In this population, there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating (Figure **x**).
 The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`.
@@
 
-```{r sec2}
+```{r sec3}
 # the number of experiences, difference*2, heterosexual and gay men
@@
 
-Gay men engaged in short-term mating behaviors more than heterosexual men did (Figure 2).
+Gay men engaged in short-term mating behaviors more than heterosexual men did (Figure \ref{fig:hetero_vs_gay}).
 The average number of short-term mating experiences (as calculated using the full population of men) was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`.
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{figures/fig2_hetero_vs_gay_men.pdf}
+  \includegraphics[width=0.8\columnwidth]{figures/fig3_hetero_vs_gay_men.pdf}
   \caption{\textbf{Short-term mating behaviors of heterosexual and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
@@
 The averages were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
+  \label{fig:hetero_vs_gay}
 \end{figure}
@@
 
-```{r sec3.1}
+```{r sec4.1}
 # the number of experiences, difference in standard, heterosexual
@@
 
-```{r sec3.2}
+```{r sec4.2}
 # the number of experiences, difference in likelihood, gay and lesbian

### 2022-06-01 submission/manuscript.tex
added texts for the in-pool number difference and stats tests

@@
 difference in the average number of short-term mating experiences among
-heterosexual individuals (\emph{M\textsubscript{men}} = 1.43,
-\emph{SD\textsubscript{men}} = 0.24; \emph{M\textsubscript{women}} =
-1.43, \emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0.00.
-Nor was there a difference in the average number of short-term mates
+the full population of heterosexual individuals
+(\emph{M\textsubscript{men}} = 1.43, \emph{SD\textsubscript{men}} =
+0.24; \emph{M\textsubscript{women}} = 1.43,
+\emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0.00. Nor was
+there a difference in the average number of short-term mates
 (\emph{M\textsubscript{men}} = 0.80, \emph{SD\textsubscript{men}} =
-0.11; \emph{M\textsubscript{w}} = 0.80, \emph{SD\textsubscript{women}} =
-0.11), Cohen's \emph{d} = 0.00 (Figure 1).
+0.11; \emph{M\textsubscript{women}} = 0.80,
+\emph{SD\textsubscript{women}} = 0.11), Cohen's \emph{d} = 0.00 (Figure
+\ref{fig:men_vs_women}).
 
@@
 differences in short-term mating behaviors between gay men and lesbian
-women (Figure 1). The average number of short-term mating experiences
-was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37) than among
-lesbian women (\emph{M} = 0.32, \emph{SD} = 0.10), \emph{t}(4,998) =
--301.78, \emph{p} \textless{} .001, Cohen's \emph{d} = 8.54. Similarly,
-the average number of short-term mates was higher among gay men
-(\emph{M} = 1.72, \emph{SD} = 0.19) than among lesbian women (\emph{M} =
-0.25, \emph{SD} = 0.07), \emph{t}(4,998) = -357.69, \emph{p} \textless{}
-.001, Cohen's \emph{d} = 10.12.
+women (Figure \ref{fig:men_vs_women}). The average number of short-term
+mating experiences was higher among gay men (\emph{M} = 2.63, \emph{SD}
+= 0.37) than among lesbian women (\emph{M} = 0.32, \emph{SD} = 0.10),
+\emph{t}(4,998) = -301.78, \emph{p} \textless{} .001, Cohen's \emph{d} =
+8.54. Similarly, the average number of short-term mates was higher among
+gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among lesbian women
+(\emph{M} = 0.25, \emph{SD} = 0.07), \emph{t}(4,998) = -357.69, \emph{p}
+\textless{} .001, Cohen's \emph{d} = 10.12.
 
@@
 
-In Experiment 1, however, when the means of the outcome variables were
-calculated only among men and women in the mating pool (the number of
-individuals in the mating pool: \emph{M\textsubscript{men}} = 56.85,
-\emph{SD\textsubscript{men}} = 5.99; \emph{M\textsubscript{women}} =
-77.04, \emph{SD\textsubscript{women}} = 7.53), there were gender
-differences in short-term mating behaviors when men and women had
-differential preferences for short-term mating. The average number of
-short-term mating experiences was higher among heterosexual men
-(\emph{M} = 3.78, \emph{SD} = 0.50) than among heterosexual women
-(\emph{M} = 2.79, \emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p}
-\textless{} .001, Cohen's \emph{d} = 2.31. Likewise, the average number
-of short-term mates was higher among heterosexual men (\emph{M} = 2.12,
-\emph{SD} = 0.17) than among heterosexual women (\emph{M} = 1.56,
-\emph{SD} = 0.11), \emph{t}(4,998) = -135.85, \emph{p} \textless{} .001,
-Cohen's \emph{d} = 3.84.
+In Experiment 1, there was a smaller proportion of heterosexual men in
+the mating pool (\emph{M} = 0.38, \emph{SD} = 0.04) compared to women
+(\emph{M} = 0.51, \emph{SD} = 0.05)), \emph{t}(4,998) = 104.85, \emph{p}
+\textless{} .001, Cohen's \emph{d} = 2.97. In this population, there
+were gender differences in short-term mating behaviors when men and
+women had differential preferences for short-term mating (Figure
+\textbf{x}). The average number of short-term mating experiences was
+higher among heterosexual men (\emph{M} = 3.78, \emph{SD} = 0.50) than
+among heterosexual women (\emph{M} = 2.79, \emph{SD} = 0.35),
+\emph{t}(4,998) = -81.53, \emph{p} \textless{} .001, Cohen's \emph{d} =
+2.31. Likewise, the average number of short-term mates was higher among
+heterosexual men (\emph{M} = 2.12, \emph{SD} = 0.17) than among
+heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11), \emph{t}(4,998)
+= -135.85, \emph{p} \textless{} .001, Cohen's \emph{d} = 3.84.
 
@@
 Gay men engaged in short-term mating behaviors more than heterosexual
-men did (Figure 2). The average number of short-term mating experiences
-(as calculated using the full population of men) was higher among gay
-men (\emph{M} = 2.63, \emph{SD} = 0.37) than among heterosexual men
-(\emph{M} = 1.43, \emph{SD} = 0.24), \emph{t}(4,998) = -134.87, \emph{p}
-\textless{} .001, Cohen's \emph{d} = 3.81. Similarly, the average number
-of short-term mates (as calculated using the full population of men) was
-higher among gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among
-heterosexual men (\emph{M} = 0.80, \emph{SD} = 0.11), \emph{t}(4,998) =
--206.91, \emph{p} \textless{} .001, Cohen's \emph{d} = 5.85.
+men did (Figure \ref{fig:hetero_vs_gay}). The average number of
+short-term mating experiences (as calculated using the full population
+of men) was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37)
+than among heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24),
+\emph{t}(4,998) = -134.87, \emph{p} \textless{} .001, Cohen's \emph{d} =
+3.81. Similarly, the average number of short-term mates (as calculated
+using the full population of men) was higher among gay men (\emph{M} =
+1.72, \emph{SD} = 0.19) than among heterosexual men (\emph{M} = 0.80,
+\emph{SD} = 0.11), \emph{t}(4,998) = -206.91, \emph{p} \textless{} .001,
+Cohen's \emph{d} = 5.85.
 

### 2022-06-01 submission/manuscript.Rmd
added plots for in-pool difference

@@
 
-Yurun Ying^1^, Jan Antfolk^2^, Pekka Santtila^1^^,^^3^^,^^$\dagger$^
+Yurun Ying^1^^,^^$\dagger$^, Jan Antfolk^2^, Pekka Santtila^1^^,^^3^
 
@@
 
-^$\dagger$^ To whom correspondence should be addressed: [pekka.santtila@nyu.edu](pekka.santtila@nyu.edu)
+^$\dagger$^ To whom correspondence should be addressed: [yurun.ying@nyu.edu](yurun.ying@nyu.edu)
 
@@
 
-In Experiment 1, there was a smaller proportion of heterosexual men in the mating pool (*M* = `r m_inpool.mean_011/N`, *SD* = `r m_inpool.sd_011/N`) compared to women (*M* = `r f_inpool.mean_011/N`, *SD* = `r f_inpool.sd_011/N`)), *t*(`r inpool.parameter_011`) = `r inpool.statistic_011`, *p* `r inpool.p.value_011`, Cohen's *d* = `r inpool.d_011`.
-In this population, there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating (Figure **x**).
+In Experiment 1, there was a smaller proportion of heterosexual men in the mating pool (*M* = `r m_inpool.mean_011/N`, *SD* = `r m_inpool.sd_011/N`) compared to women (*M* = `r f_inpool.mean_011/N`, *SD* = `r f_inpool.sd_011/N`), *t*(`r inpool.parameter_011`) = `r inpool.statistic_011`, *p* `r inpool.p.value_011`, Cohen's *d* = `r inpool.d_011`.
+In this population, there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating (Figure \ref{fig:men_vs_women_inpool}).
 The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`.
 Likewise, the average number of short-term mates was higher among heterosexual men (*M* = `r m_partner_ip.mean_011`, *SD* = `r m_partner_ip.sd_011`) than among heterosexual women (*M* = `r f_partner_ip.mean_011`, *SD* = `r f_partner_ip.sd_011`), *t*(`r partner_ip.parameter_011`) = `r partner_ip.statistic_011`, *p* `r partner_ip.p.value_011`, Cohen's *d* = `r partner_ip.d_011`.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figures/fig2_men_vs_women_inpool.pdf}
+  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
+Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool.
+Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
+The averages were calculated using the population of heterosexual men and women in the mating pool (\textit{M\textsubscript{men}} = `r m_inpool.mean_011`, \textit{M\textsubscript{men}} = `r f_inpool.mean_011`).}
+  \label{fig:men_vs_women_inpool}
+\end{figure}
 

### 2022-06-01 submission/manuscript.tex
added plots for in-pool difference

@@
 
-Yurun Ying\textsuperscript{1}, Jan Antfolk\textsuperscript{2}, Pekka
-Santtila\textsuperscript{1,3,\(\dagger\)}
+Yurun Ying\textsuperscript{1,\(\dagger\)}, Jan
+Antfolk\textsuperscript{2}, Pekka Santtila\textsuperscript{1,3}
 
@@
 \textsuperscript{\(\dagger\)} To whom correspondence should be
-addressed: \url{pekka.santtila@nyu.edu}
+addressed: \url{yurun.ying@nyu.edu}
 
@@
 the mating pool (\emph{M} = 0.38, \emph{SD} = 0.04) compared to women
-(\emph{M} = 0.51, \emph{SD} = 0.05)), \emph{t}(4,998) = 104.85, \emph{p}
+(\emph{M} = 0.51, \emph{SD} = 0.05), \emph{t}(4,998) = 104.85, \emph{p}
 \textless{} .001, Cohen's \emph{d} = 2.97. In this population, there
@@
 women had differential preferences for short-term mating (Figure
-\textbf{x}). The average number of short-term mating experiences was
-higher among heterosexual men (\emph{M} = 3.78, \emph{SD} = 0.50) than
-among heterosexual women (\emph{M} = 2.79, \emph{SD} = 0.35),
-\emph{t}(4,998) = -81.53, \emph{p} \textless{} .001, Cohen's \emph{d} =
-2.31. Likewise, the average number of short-term mates was higher among
-heterosexual men (\emph{M} = 2.12, \emph{SD} = 0.17) than among
-heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11), \emph{t}(4,998)
-= -135.85, \emph{p} \textless{} .001, Cohen's \emph{d} = 3.84.
+\ref{fig:men_vs_women_inpool}). The average number of short-term mating
+experiences was higher among heterosexual men (\emph{M} = 3.78,
+\emph{SD} = 0.50) than among heterosexual women (\emph{M} = 2.79,
+\emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p} \textless{} .001,
+Cohen's \emph{d} = 2.31. Likewise, the average number of short-term
+mates was higher among heterosexual men (\emph{M} = 2.12, \emph{SD} =
+0.17) than among heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11),
+\emph{t}(4,998) = -135.85, \emph{p} \textless{} .001, Cohen's \emph{d} =
+3.84.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figures/fig2_men_vs_women_inpool.pdf}
+  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
+Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool.
+Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
+The averages were calculated using the population of heterosexual men and women in the mating pool (\textit{M\textsubscript{men}} = 56.85, \textit{M\textsubscript{men}} = 77.04).}
+  \label{fig:men_vs_women_inpool}
+\end{figure}
 

### 2022-06-01 code/plot_men_vs_women_inpool.R

@@ -1,0 +1,80 @@
+#!/usr/bin/env Rscript --vanilla
+
+# name: plot_men_vs_women_inpool.R
+# input: data/processed/casual_sex_sim.csv
+# output: submission/figures/fig1_men_vs_women_inpool.pdf
+# notes: none
+
+# load libraries
+library(tidyverse); library(wesanderson); library(here)
+
+args <- commandArgs(trailingOnly = TRUE)
+#args <- c("data/processed/casual_sex_sim.csv", "submission/figures/fig2_men_vs_women_inpool.pdf")
+
+input_file <- args[1]
+output_file <- args[2]
+
+# read file
+casual_tib <- here(input_file) %>% 
+  read_csv() %>% 
+  mutate(
+    diff_likelihood = as_factor(diff_likelihood),
+    diff_standard = as_factor(diff_standard),
+    homosexual = as_factor(homosexual)
+  )
+
+# construct facet label
+facet_label <- 
+  tibble(
+    label = c("(A)", "(B)"),
+    variable = c("exp_ip", "partner_ip"),
+    x = 0.5
+  ) %>% 
+  mutate(y = ifelse(variable == "exp_ip", 5.9, 2.8))
+
+# construct y-axis label
+y_lab <- labeller(
+  variable = c(
+    `exp_ip` = "Average number of short-term\nmating experiences in the mating pool",
+    `partner_ip` = "Average number of short-term\nmates in the mating pool")
+)
+
+casual_tib %>% 
+  filter(homosexual == 0, diff_likelihood == 1, diff_standard == 1) %>% 
+  select(m_exp_ip, f_exp_ip, m_partner_ip, f_partner_ip) %>% 
+  pivot_longer(c(m_exp_ip, f_exp_ip, m_partner_ip, f_partner_ip), 
+               values_to = "value", names_to = c("gender", "variable"),
+               names_pattern = "(.)_(.*)") %>% 
+  ggplot(aes(x = gender, y = value)) +
+  geom_violin(aes(fill = gender)) +
+  stat_summary(fun = "mean", geom = "point") +
+  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2) +
+  geom_text(
+    data = facet_label, aes(label = label, x = x, y = y), hjust = 0, fontface = 2
+  ) +
+  scale_fill_discrete(
+    type = wes_palette("Darjeeling2", 2, type = "discrete"),
+    name = "", labels = c("Women", "Men")
+  ) +
[…]

### 2022-06-01 code/plot_hetero_vs_gay_men.R
minor edits

@@ -2,14 +2,14 @@
 
 # name: plot_hetero_vs_gay_men.R
 # input: data/processed/casual_sex_sim.csv
-# output: submission/figures/fig2_hetero_vs_gay_men.pdf
+# output: submission/figures/fig3_hetero_vs_gay_men.pdf
 # notes: none
 
 # load libraries
 library(tidyverse); library(ggplot2); library(wesanderson); library(here)
 
 args <- commandArgs(trailingOnly = TRUE)
-#args <- c("data/processed/casual_sex_sim.csv", "submission/figures/fig2_hetero_vs_gay_men.pdf")
+#args <- c("data/processed/casual_sex_sim.csv", "submission/figures/fig3_hetero_vs_gay_men.pdf")
 
 input_file <- args[1]
 output_file <- args[2]

### 2022-06-02 README.Rmd
minor edits to the figures
minor edits to the README file

@@
   github_document:
-    html_preview: true
+    html_preview: false
 ---
@@
 ## Description
-By using a spatial agent-based model, the present study investigated we investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances.
+By using a spatial agent-based model, the present study investigated whether men and women's different mating preferences resulted in any gender differences in short-term mating behaviors, and if they did, under what circumstances.
 
@@
 library(effectsize)
-library(ggplot2)
 library(rmarkdown)
@@
   - `effectsize` (v. `r packageVersion("effectsize")`)
-  - `ggplot2` (v. `r packageVersion("ggplot2")`)
   - `rmarkdown` (v. `r packageVersion("rmarkdown")`)

### 2022-06-02 submission/manuscript.tex
added confidence interval in the results section, close #21

@@
 0.24; \emph{M\textsubscript{women}} = 1.43,
-\emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0.00. Nor was
-there a difference in the average number of short-term mates
-(\emph{M\textsubscript{men}} = 0.80, \emph{SD\textsubscript{men}} =
-0.11; \emph{M\textsubscript{women}} = 0.80,
-\emph{SD\textsubscript{women}} = 0.11), Cohen's \emph{d} = 0.00 (Figure
-\ref{fig:men_vs_women}).
+\emph{SD\textsubscript{women}} = 0.24), Cohen's \emph{d} = 0.00, 95\% CI
+= --0.01 to 0.01. Nor was there a difference in the average number of
+short-term mates (\emph{M\textsubscript{men}} = 0.80,
+\emph{SD\textsubscript{men}} = 0.11; \emph{M\textsubscript{women}} =
+0.80, \emph{SD\textsubscript{women}} = 0.11), Cohen's \emph{d} = 0.00,
+95\% CI = --0.01 to 0.01 (Figure \ref{fig:men_vs_women}).
 
@@
 = 0.37) than among lesbian women (\emph{M} = 0.32, \emph{SD} = 0.10),
-\emph{t}(4,998) = -301.78, \emph{p} \textless{} .001, Cohen's \emph{d} =
-8.54. Similarly, the average number of short-term mates was higher among
-gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among lesbian women
-(\emph{M} = 0.25, \emph{SD} = 0.07), \emph{t}(4,998) = -357.69, \emph{p}
-\textless{} .001, Cohen's \emph{d} = 10.12.
+\emph{t}(4,998) = --301.78, \emph{p} \textless{} .001, Cohen's \emph{d}
+= 8.54, 95\% CI = --2.33 to --2.30. Similarly, the average number of
+short-term mates was higher among gay men (\emph{M} = 1.72, \emph{SD} =
+0.19) than among lesbian women (\emph{M} = 0.25, \emph{SD} = 0.07),
+\emph{t}(4,998) = --357.69, \emph{p} \textless{} .001, Cohen's \emph{d}
+= 10.12, 95\% CI = --1.48 to --1.46.
 
@@
 (\emph{M} = 0.51, \emph{SD} = 0.05), \emph{t}(4,998) = 104.85, \emph{p}
-\textless{} .001, Cohen's \emph{d} = 2.97. In this population, there
-were gender differences in short-term mating behaviors when men and
-women had differential preferences for short-term mating (Figure
-\ref{fig:men_vs_women_inpool}). The average number of short-term mating
-experiences was higher among heterosexual men (\emph{M} = 3.78,
-\emph{SD} = 0.50) than among heterosexual women (\emph{M} = 2.79,
-\emph{SD} = 0.35), \emph{t}(4,998) = -81.53, \emph{p} \textless{} .001,
-Cohen's \emph{d} = 2.31. Likewise, the average number of short-term
-mates was higher among heterosexual men (\emph{M} = 2.12, \emph{SD} =
-0.17) than among heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11),
-\emph{t}(4,998) = -135.85, \emph{p} \textless{} .001, Cohen's \emph{d} =
-3.84.
+\textless{} .001, Cohen's \emph{d} = 2.97, 95\% CI = 0.13 to 0.14. In
+this population, there were gender differences in short-term mating
+behaviors when men and women had differential preferences for short-term
+mating (Figure \ref{fig:men_vs_women_inpool}). The average number of
+short-term mating experiences was higher among heterosexual men
+(\emph{M} = 3.78, \emph{SD} = 0.50) than among heterosexual women
+(\emph{M} = 2.79, \emph{SD} = 0.35), \emph{t}(4,998) = --81.53, \emph{p}
+\textless{} .001, Cohen's \emph{d} = 2.31, 95\% CI = --1.02 to --0.97.
+Likewise, the average number of short-term mates was higher among
+heterosexual men (\emph{M} = 2.12, \emph{SD} = 0.17) than among
+heterosexual women (\emph{M} = 1.56, \emph{SD} = 0.11), \emph{t}(4,998)
+= --135.85, \emph{p} \textless{} .001, Cohen's \emph{d} = 3.84, 95\% CI
+= --0.57 to --0.55.
 
@@
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The averages were calculated using the population of heterosexual men and women in the mating pool (\textit{M\textsubscript{men}} = 56.85, \textit{M\textsubscript{men}} = 77.04).}
+The averages were calculated using the population of heterosexual men and women in the mating pool (proportion: \textit{M\textsubscript{men}} = 0.38, \textit{M\textsubscript{women}} = 0.51).}
   \label{fig:men_vs_women_inpool}
@@
 than among heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24),
-\emph{t}(4,998) = -134.87, \emph{p} \textless{} .001, Cohen's \emph{d} =
-3.81. Similarly, the average number of short-term mates (as calculated
-using the full population of men) was higher among gay men (\emph{M} =
-1.72, \emph{SD} = 0.19) than among heterosexual men (\emph{M} = 0.80,
-\emph{SD} = 0.11), \emph{t}(4,998) = -206.91, \emph{p} \textless{} .001,
-Cohen's \emph{d} = 5.85.
+\emph{t}(4,998) = --134.87, \emph{p} \textless{} .001, Cohen's \emph{d}
+= 3.81, 95\% CI = --1.21 to --1.18. Similarly, the average number of
+short-term mates (as calculated using the full population of men) was
+higher among gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among
+heterosexual men (\emph{M} = 0.80, \emph{SD} = 0.11), \emph{t}(4,998) =
+--206.91, \emph{p} \textless{} .001, Cohen's \emph{d} = 5.85, 95\% CI =
+--0.92 to --0.91.
 

### 2022-06-02 code/compare_hetero_gay_men.R

@@ -48,18 +48,18 @@ casual_t_test <-
   nest_by(dlikelihood_dstandard) %>% 
   mutate(
     m_inpool = t.test(m_inpool ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
-      select(statistic, p.value, parameter),
+      select(statistic, p.value, parameter, conf.low, conf.high),
     m_outpool = t.test(m_outpool ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
-      select(statistic, p.value, parameter),
+      select(statistic, p.value, parameter, conf.low, conf.high),
     m_exp_all = t.test(m_exp_all ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
       # somehow the map function doesn't work here and I wonder why...
-      select(statistic, p.value, parameter),
+      select(statistic, p.value, parameter, conf.low, conf.high),
     m_exp_ip = t.test(m_exp_ip ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
-      select(statistic, p.value, parameter),
+      select(statistic, p.value, parameter, conf.low, conf.high),
     m_partner_all = t.test(m_partner_all ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
-      select(statistic, p.value, parameter),
+      select(statistic, p.value, parameter, conf.low, conf.high),
     m_partner_ip = t.test(m_partner_ip ~ homosexual, data = data, var.equal = TRUE) %>% tidy() %>% 
-      select(statistic, p.value, parameter)
+      select(statistic, p.value, parameter, conf.low, conf.high)
   ) %>% 
   select(-data) %>% 
   unnest(cols = -dlikelihood_dstandard, names_sep = ".")

### 2022-06-02 code/des_and_test_result.R

@@ -39,7 +39,8 @@ casual_des <-
   group_by(homosexual_dlikelihood_dstandard, gender) %>% 
   summarise(across(inpool:partner_ip, 
                    list(mean = mean, sd = sd),
-                   .names = "{.col}.{.fn}")) %>% 
+            .names = "{.col}.{.fn}"),
+            .groups = "drop") %>% 
   pivot_wider(names_from = gender, 
               values_from = -c(homosexual_dlikelihood_dstandard, gender),
               names_glue = "{gender}_{.value}")
@@ -50,18 +51,18 @@ casual_t_test <-
   nest_by(homosexual_dlikelihood_dstandard) %>% 
   mutate(
     inpool = t.test(inpool ~ gender, data = data, var.equal = TRUE) %>% tidy() %>% 
-      select(statistic, p.value, parameter),
+      select(statistic, p.value, parameter, conf.low, conf.high),
     outpool = t.test(outpool ~ gender, data = data, var.equal = TRUE) %>% tidy() %>% 
-      select(statistic, p.value, parameter),
+      select(statistic, p.value, parameter, conf.low, conf.high),
     exp_all = t.test(exp_all ~ gender, data = data, var.equal = TRUE) %>% tidy() %>% 
       # somehow the map function doesn't work here and I wonder why...
-      select(statistic, p.value, parameter),
+      select(statistic, p.value, parameter, conf.low, conf.high),
     exp_ip = t.test(exp_ip ~ gender, data = data, var.equal = TRUE) %>% tidy() %>% 
-      select(statistic, p.value, parameter),
+      select(statistic, p.value, parameter, conf.low, conf.high),
     partner_all = t.test(partner_all ~ gender, data = data , var.equal = TRUE) %>% tidy() %>% 
-      select(statistic, p.value, parameter),
+      select(statistic, p.value, parameter, conf.low, conf.high),
     partner_ip = t.test(partner_ip ~ gender, data = data, var.equal = TRUE) %>% tidy() %>% 
-      select(statistic, p.value, parameter)
+      select(statistic, p.value, parameter, conf.low, conf.high)
   ) %>% 
   select(-data) %>% 
   unnest(cols = -homosexual_dlikelihood_dstandard, names_sep = ".")

### 2022-06-02 submission/manuscript.Rmd

@@
 
-N <- 150
-
+# read data
 results <-
@@
   rename(hls = homosexual_dlikelihood_dstandard) %>%
+  mutate(across(.col = c(f_inpool.mean:m_outpool.sd, 
+                inpool.conf.low:inpool.conf.high, 
+                outpool.conf.low:outpool.conf.high), 
+                ~ .x/150)) %>% 
   mutate(across(contains("p.value"), ~format(.x, digits = 2, nsmall = 3))) %>%
@@
 
+# define inline hook
 inline_hook <- function(x) {
@@
         format(x, digits=1, nsmall=2, big.mark = ",")
-        )
+        ) %>% 
+        str_replace("-", "–")
 
@@
 knit_hooks$set(inline = inline_hook)
+
+# function to get CI
+get_CI <- function(data, condition, var) {
+
+  # data <- results
+  # condition <- "0_1_1"
+  # var <- "exp_all"
+
+  ll_name <- paste0(var, ".conf.low")
+  ul_name <- paste0(var, ".conf.high")
+  ll <- data %>% filter(hls == condition) %>% pull(!!as.name(ll_name)) %>% round(2) %>% inline_hook
+  ul <- data %>% filter(hls == condition) %>% pull(!!as.name(ul_name)) %>% round(2) %>% inline_hook
+
+  ci <- paste("95% CI =", ll, "to", ul)
+  return(ci)
+}
+
+get_CI_hg <- function(data, condition, var) {
+
+  # data <- results
+  # condition <- "0_1_1"
+  # var <- "exp_all"
+
+  ll_name <- paste0(var, ".conf.low")
+  ul_name <- paste0(var, ".conf.high")
+  ll <- data %>% filter(ls == condition) %>% pull(!!as.name(ll_name)) %>% round(2) %>% inline_hook
+  ul <- data %>% filter(ls == condition) %>% pull(!!as.name(ul_name)) %>% round(2) %>% inline_hook
+
+  ci <- paste("95% CI =", ll, "to", ul)
+  return(ci)
+}
 ```
@@
   results %>% filter(hls == "0_1_1") %>% pull(exp_all.d) %>% abs()
+exp_all.ci_011 <- get_CI(results, "0_1_1", "exp_all")
 
@@
   results %>% filter(hls == "0_1_1") %>% pull(partner_all.d) %>% abs()
+partner_all.ci_011 <- get_CI(results, "0_1_1", "partner_all")
 ```
 
-The results from Experiment 1 showed that when there were gender differences in preferences for short-term mating, there was no gender difference in the average number of short-term mating experiences among the full population of heterosexual individuals (*M~men~* = `r m_exp_all.mean_011`, *SD~men~* = `r m_exp_all.sd_011`; *M~women~* = `r f_exp_all.mean_011`, *SD~women~* = `r f_exp_all.sd_011`), Cohen's *d* = `r exp_all.d_011`.
-Nor was there a difference in the average number of short-term mates (*M~men~* = `r m_partner_all.mean_011`, *SD~men~* = `r m_partner_all.sd_011`; *M~women~* = `r f_partner_all.mean_011`, *SD~women~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011` (Figure \ref{fig:men_vs_women}).
+The results from Experiment 1 showed that when there were gender differences in preferences for short-term mating, there was no gender difference in the average number of short-term mating experiences among the full population of heterosexual individuals (*M~men~* = `r m_exp_all.mean_011`, *SD~men~* = `r m_exp_all.sd_011`; *M~women~* = `r f_exp_all.mean_011`, *SD~women~* = `r f_exp_all.sd_011`), Cohen's *d* = `r exp_all.d_011`, `r exp_all.ci_011`.
+Nor was there a difference in the average number of short-term mates (*M~men~* = `r m_partner_all.mean_011`, *SD~men~* = `r m_partner_all.sd_011`; *M~women~* = `r f_partner_all.mean_011`, *SD~women~* = `r f_partner_all.sd_011`), Cohen's *d* = `r partner_all.d_011`, `r partner_all.ci_011` (Figure \ref{fig:men_vs_women}).
 
@@
 results %>% filter(hls == "1_1_1") %>% pull(exp_all.d) %>% abs()
+exp_all.ci_111 <- get_CI(results, "1_1_1", "exp_all")
 
@@
   results %>% filter(hls == "1_1_1") %>% pull(partner_all.d) %>% abs()
+partner_all.ci_111 <- get_CI(results, "1_1_1", "partner_all")
 ```
@@
 The results from Experiment 2 showed that when there were gender differences in preferences for short-term mating, there were gender differences in short-term mating behaviors between gay men and lesbian women (Figure \ref{fig:men_vs_women}).
-The average number of short-term mating experiences was higher among gay men (*M* = `r m_exp_all.mean_111`, *SD* = `r m_exp_all.sd_111`) than among lesbian women (*M* = `r f_exp_all.mean_111`, *SD* = `r f_exp_all.sd_111`), *t*(`r exp.all.parameter_111`) = `r exp.all.statistic_111`, *p* `r exp.all.p.value_111`, Cohen's *d* = `r exp_all.d_111`.
-Similarly, the average number of short-term mates was higher among gay men (*M* = `r m_partner_all.mean_111`, *SD* = `r m_partner_all.sd_111`) than among lesbian women (*M* = `r f_partner_all.mean_111`, *SD* = `r f_partner_all.sd_111`), *t*(`r partner.all.parameter_111`) = `r partner.all.statistic_111`, *p* `r partner.all.p.value_111`, Cohen's *d* = `r partner_all.d_111`.
+The average number of short-term mating experiences was higher among gay men (*M* = `r m_exp_all.mean_111`, *SD* = `r m_exp_all.sd_111`) than among lesbian women (*M* = `r f_exp_all.mean_111`, *SD* = `r f_exp_all.sd_111`), *t*(`r exp.all.parameter_111`) = `r exp.all.statistic_111`, *p* `r exp.all.p.value_111`, Cohen's *d* = `r exp_all.d_111`, `r exp_all.ci_111`.
+Similarly, the average number of short-term mates was higher among gay men (*M* = `r m_partner_all.mean_111`, *SD* = `r m_partner_all.sd_111`) than among lesbian women (*M* = `r f_partner_all.mean_111`, *SD* = `r f_partner_all.sd_111`), *t*(`r partner.all.parameter_111`) = `r partner.all.statistic_111`, *p* `r partner.all.p.value_111`, Cohen's *d* = `r partner_all.d_111`, `r partner_all.ci_111`.
 
@@
   results %>% filter(hls == "0_1_1") %>% pull(inpool.d) %>% abs()
+inpool.ci_011 <- get_CI(results, "0_1_1", "inpool")
 
@@
   results %>% filter(hls == "0_1_1") %>% pull(exp_ip.d) %>% abs()
+exp_ip.ci_011 <- get_CI(results, "0_1_1", "exp_ip")
 
@@
   results %>% filter(hls == "0_1_1") %>% pull(partner_ip.d) %>% abs()
+partner_ip.ci_011 <- get_CI(results, "0_1_1", "partner_ip")
 ```
 
-In Experiment 1, there was a smaller proportion of heterosexual men in the mating pool (*M* = `r m_inpool.mean_011/N`, *SD* = `r m_inpool.sd_011/N`) compared to women (*M* = `r f_inpool.mean_011/N`, *SD* = `r f_inpool.sd_011/N`), *t*(`r inpool.parameter_011`) = `r inpool.statistic_011`, *p* `r inpool.p.value_011`, Cohen's *d* = `r inpool.d_011`.
+In Experiment 1, there was a smaller proportion of heterosexual men in the mating pool (*M* = `r m_inpool.mean_011`, *SD* = `r m_inpool.sd_011`) compared to women (*M* = `r f_inpool.mean_011`, *SD* = `r f_inpool.sd_011`), *t*(`r inpool.parameter_011`) = `r inpool.statistic_011`, *p* `r inpool.p.value_011`, Cohen's *d* = `r inpool.d_011`, `r inpool.ci_011`.
 In this population, there were gender differences in short-term mating behaviors when men and women had differential preferences for short-term mating (Figure \ref{fig:men_vs_women_inpool}).
-The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`.
-Likewise, the average number of short-term mates was higher among heterosexual men (*M* = `r m_partner_ip.mean_011`, *SD* = `r m_partner_ip.sd_011`) than among heterosexual women (*M* = `r f_partner_ip.mean_011`, *SD* = `r f_partner_ip.sd_011`), *t*(`r partner_ip.parameter_011`) = `r partner_ip.statistic_011`, *p* `r partner_ip.p.value_011`, Cohen's *d* = `r partner_ip.d_011`.
+The average number of short-term mating experiences was higher among heterosexual men (*M* = `r m_exp_ip.mean_011`, *SD* = `r m_exp_ip.sd_011`) than among heterosexual women (*M* = `r f_exp_ip.mean_011`, *SD* = `r f_exp_ip.sd_011`), *t*(`r exp_ip.parameter_011`) = `r exp_ip.statistic_011`, *p* `r exp_ip.p.value_011`, Cohen's *d* = `r exp_ip.d_011`, `r exp_ip.ci_011`.
+Likewise, the average number of short-term mates was higher among heterosexual men (*M* = `r m_partner_ip.mean_011`, *SD* = `r m_partner_ip.sd_011`) than among heterosexual women (*M* = `r f_partner_ip.mean_011`, *SD* = `r f_partner_ip.sd_011`), *t*(`r partner_ip.parameter_011`) = `r partner_ip.statistic_011`, *p* `r partner_ip.p.value_011`, Cohen's *d* = `r partner_ip.d_011`, `r partner_ip.ci_011`.
 
@@
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The averages were calculated using the population of heterosexual men and women in the mating pool (\textit{M\textsubscript{men}} = `r m_inpool.mean_011`, \textit{M\textsubscript{men}} = `r f_inpool.mean_011`).}
+The averages were calculated using the population of heterosexual men and women in the mating pool (proportion: \textit{M\textsubscript{men}} = `r m_inpool.mean_011`, \textit{M\textsubscript{women}} = `r f_inpool.mean_011`).}
   \label{fig:men_vs_women_inpool}
@@
   results_hg %>% filter(ls == "1_1") %>% pull(m_exp_all.d) %>% abs()
+exp_all.ci_hg <- get_CI_hg(results_hg, "1_1", "m_exp_all")
 
@@
   results_hg %>% filter(ls == "1_1") %>% pull(m_partner_all.d) %>% abs()
+partner_all.ci_hg <- get_CI_hg(results_hg, "1_1", "m_partner_all")
 ```
@@
 Gay men engaged in short-term mating behaviors more than heterosexual men did (Figure \ref{fig:hetero_vs_gay}).
-The average number of short-term mating experiences (as calculated using the full population of men) was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`.
-Similarly, the average number of short-term mates (as calculated using the full population of men) was higher among gay men (*M* = `r m_partner_all.mean_1_11`, *SD* = `r m_partner_all.sd_1_11`) than among heterosexual men (*M* = `r m_partner_all.mean_0_11`, *SD* = `r m_partner_all.sd_0_11`), *t*(`r partner.all.parameter_hg`) = `r partner.all.statistic_hg`, *p* `r partner.all.p.value_hg`, Cohen's *d* = `r partner_all.d_hg`.
+The average number of short-term mating experiences (as calculated using the full population of men) was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`, `r exp_all.ci_hg`.
+Similarly, the average number of short-term mates (as calculated using the full population of men) was higher among gay men (*M* = `r m_partner_all.mean_1_11`, *SD* = `r m_partner_all.sd_1_11`) than among heterosexual men (*M* = `r m_partner_all.mean_0_11`, *SD* = `r m_partner_all.sd_0_11`), *t*(`r partner.all.parameter_hg`) = `r partner.all.statistic_hg`, *p* `r partner.all.p.value_hg`, Cohen's *d* = `r partner_all.d_hg`, `r partner_all.ci_hg`.
 

### 2022-06-03 submission/manuscript.Rmd
edited the manuscript based on feedback, close #20

@@
 However, it is important to note that although heterosexual men’s total number of short-term mating is equal to that of women, this does not necessarily mean that the total number of men and women who have ever had short-term mating must be equal.
-Since women have higher standards for short-term mates than men [@buss_sexual_1993], it is possible that the proportion of individuals who meet a potential partner's standards is lower among men than among women, assuming both men and women's desirability values follow the same distribution.
-Consequently, there may be a smaller proportion of men (vs.
+Empirical studies have found that the proportion of individuals who are sexual inexperienced is slightly higher among men than women in most age groups above 18 years old [@haydon2014prevalence; @ghaznavi2019trends].
+As a postulation, there may be a smaller proportion of men (vs.
 the proportion of women) who participate in the mating pool and contribute to the total number of short-term mating.
 For example, suppose that there is a population of 20 individuals with an equal sex ratio.
-There are 8 men and 8 women with a desirability value greater than x~1~ and 3 men and 3 women with a value greater than x~2~ (x~1~ < x~2~).
-Suppose that x~1~ and x~2~ happen to be men and women's standards for short-term mates, then in a long enough period of time, the 8 women who meet men's standards and the 3 men who meet women's standards will have had short-term mating.
-Since the total number of short-term mating behaviors is the same between men and women, we would expect that in a population of individuals who had any short-term mating, the average number of short-term mating experiences and mates was higher among men than women (e.g., in the aforementioned example, the number is n/3 for men and n/8 for women, where n can be the total number of short-term mating experiences or the number of short-term mates).
+Heterosexual short-term mating has happened \(n\) times in this population, but only 3 men and 8 women have had any short-term mating experiences.
+Since the total number of short-term mating behaviors is the same between men and women, we would expect that in a population of individuals who had any short-term mating, the average number of short-term mating experiences and mates was higher among men than women (e.g., in the aforementioned example, the average number of short-term experiences is \(\frac{n}{3}\) for men and \(\frac{n}{8}\) for women who are in the mating pool).
 
@@
 A pair of individuals had a possibility to commit to a long-term relationship upon meeting each other.
-We modeled forming long-term relationships as a behavioral outcome and ignored the psychological processes behind it, although we recognize gender differences may also exist in long-term mating strategy [@buss_sexual_1993; @buss2019mate].
+This process was modeled at a behavioral level and the psychological processes behind it was ignored, although we recognized gender differences may also exist in long-term mating strategy [@buss_sexual_1993; @buss2019mate].
 
@@
 
-We formulated the following hypotheses in the present study: assuming gender differences in preferences for short-term mating, 1) there would be no gender differences in short-term mating behaviors among all heterosexual men and women, 2) a smaller proportion of heterosexual men had ever engaged into short-term mating compared to the proportion of heterosexual women, 3) in a population of heterosexual individuals who had any short-term mating, men had higher average number of short-term mating behaviors than women, 4) there would be gender differences in short-term mating behaviors among gay men and lesbian women, with gay men being engaged in more such behaviors, and 5) gay men would engage in more short-term mating behaviors compared to heterosexual men.
+We formulated the following hypotheses in the present study: assuming gender differences in preferences for short-term mating, 1) there would be no gender differences in short-term mating behaviors between heterosexual men and women when the full population was considered, 2) a smaller proportion of heterosexual men (vs.
+heterosexual women) had ever engaged in short-term mating, 3) in a population of heterosexual individuals who had any short-term mating, men had higher average number of short-term mating behaviors than women, 4) gay men would engage in more short-term mating behaviors compared to lesbian women, and 5) gay men would engage in more short-term mating behaviors compared to heterosexual men.
 
@@
 The present study used agent-based modeling to investigate whether men and women’s differential preferences for short-term mating would result in gender differences in short-term mating behaviors, and if so, then under what conditions they would result in differences in the number of short-term mating experiences and short-term mates.
-We formulated two hypotheses: 1) gay men would engage in more short-term mating behaviors as compared to lesbian women, and 2) gay men would engage in more short-term mating behaviors as compared to heterosexual men.
+We formulated five hypotheses: 1) there would be no gender differences in short-term mating behaviors between heterosexual men and women when the full population was considered, 2) a smaller proportion of heterosexual men (vs.
+heterosexual women) had ever engaged in short-term mating, 3) in a population of heterosexual individuals who had any short-term mating, men had higher average number of short-term mating behaviors than women, 4) gay men would engage in more short-term mating behaviors compared to lesbian women, and 5) gay men would engage in more short-term mating behaviors compared to heterosexual men.
 The results from 1,000 time steps in a model simulating men and women’s mating behaviors provided strong evidence in favor of our hypotheses.
-First of all, as compared to lesbian women, gay men had higher average numbers of short-term mating experiences and short-term mates.
-Secondly, gay men also had higher average numbers of short-term mating experiences and short-term mates as compared to heterosexual men.
-In contrast, we found no gender differences in short-term mating behaviors between heterosexual men and women, although heterosexual men in the mating pool had higher average numbers of short-term mating experiences and short-term mates.
+First of all, we found no gender differences in short-term mating behaviors between heterosexual men and women when the full population was considered.
+However, compared to heterosexual women, there was a smaller proportion of heterosexual men participating in the mating pool, but they had higher average numbers of short-term mating experiences and short-term mates.
+Secondly, as compared to lesbian women, gay men had higher average numbers of short-term mating experiences and short-term mates.
+Finally, gay men also had higher average numbers of short-term mating experiences and short-term mates as compared to heterosexual men.
 
-As expected, heterosexual men and women did not differ in short-term mating behaviors despite their differential preferences for short-term mating.
+As expected, when the full population was considered, heterosexual men and women did not differ in short-term mating behaviors despite their differential preferences for short-term mating.
 This was because heterosexual men and women had an equal total number of both short-term mating experiences and short-term mates.
@@
 Using agent-based modeling to simulate short-term mating behaviors, we found when men (vs.
-women) had a stronger preferences for short-term mating, heterosexual men and women engaged in short-term mating behaviors to the same extent, while gay men engaged in more short-term mating behaviors as compared to lesbian women.
-Gay men engaged in more short-term mating behaviors than heterosexual men did.
+women) had a stronger preferences for short-term mating, heterosexual men and women engaged in short-term mating behaviors to the same extent when the full population was considered, while men in the mating pool had more such behaviors than women in the mating pool.
+Gay men engaged in more short-term mating behaviors compared to both lesbian women and heterosexual men.
 
@@
 Individuals’ mating behaviors do not only depend on one’s own preferences, but are also constrained by partners’ preferences.
-Future research in human mating should not only focus on the psychological aspect but also pay attention to the interaction between individuals’ psychology and its context.
+Future research in human mating should not only focus on the psychological aspect but also pay attention to the interaction between individuals’ psychology and its behavioral context.
 These results also cast doubt to the prevalent belief in the gender differences in short-term mating behaviors, especially among heterosexual individuals.
 Our findings suggest that there may be factors in the observation process, such as sampling bias, that contribute to the observed differences.
-Future research in human sexuality should note such possibilities and interpret any observed gender differences in short-term mating behaviors cautiously.
+Future research in human sexuality should note such possibilities and interpret any observed gender differences in short-term mating behaviors with caution.
 
 # Acknowledgements
+
+We thank Gu Li and Jiannan Shi for providing helpful feedback in the development of this study.
 

### 2022-06-03 submission/manuscript.tex
edited the manuscript based on feedback, close #20

@@
 necessarily mean that the total number of men and women who have ever
-had short-term mating must be equal. Since women have higher standards
-for short-term mates than men (Buss \& Schmitt, 1993), it is possible
-that the proportion of individuals who meet a potential partner's
-standards is lower among men than among women, assuming both men and
-women's desirability values follow the same distribution. Consequently,
-there may be a smaller proportion of men (vs.~the proportion of women)
-who participate in the mating pool and contribute to the total number of
+had short-term mating must be equal. Empirical studies have found that
+the proportion of individuals who are sexual inexperienced is slightly
+higher among men than women in most age groups above 18 years old
+(Ghaznavi et al., 2019; Haydon et al., 2014). As a postulation, there
+may be a smaller proportion of men (vs.~the proportion of women) who
+participate in the mating pool and contribute to the total number of
 short-term mating. For example, suppose that there is a population of 20
-individuals with an equal sex ratio. There are 8 men and 8 women with a
-desirability value greater than x\textsubscript{1} and 3 men and 3 women
-with a value greater than x\textsubscript{2} (x\textsubscript{1}
-\textless{} x\textsubscript{2}). Suppose that x\textsubscript{1} and
-x\textsubscript{2} happen to be men and women's standards for short-term
-mates, then in a long enough period of time, the 8 women who meet men's
-standards and the 3 men who meet women's standards will have had
-short-term mating. Since the total number of short-term mating behaviors
-is the same between men and women, we would expect that in a population
-of individuals who had any short-term mating, the average number of
-short-term mating experiences and mates was higher among men than women
-(e.g., in the aforementioned example, the number is n/3 for men and n/8
-for women, where n can be the total number of short-term mating
-experiences or the number of short-term mates).
+individuals with an equal sex ratio. Heterosexual short-term mating has
+happened \(n\) times in this population, but only 3 men and 8 women have
+had any short-term mating experiences. Since the total number of
+short-term mating behaviors is the same between men and women, we would
+expect that in a population of individuals who had any short-term
+mating, the average number of short-term mating experiences and mates
+was higher among men than women (e.g., in the aforementioned example,
+the average number of short-term experiences is \(\frac{n}{3}\) for men
+and \(\frac{n}{8}\) for women who are in the mating pool).
 
@@
 A pair of individuals had a possibility to commit to a long-term
-relationship upon meeting each other. We modeled forming long-term
-relationships as a behavioral outcome and ignored the psychological
-processes behind it, although we recognize gender differences may also
-exist in long-term mating strategy (Buss \& Schmitt, 1993; Buss \&
-Schmitt, 2019).
+relationship upon meeting each other. This process was modeled at a
+behavioral level and the psychological processes behind it was ignored,
+although we recognized gender differences may also exist in long-term
+mating strategy (Buss \& Schmitt, 1993; Buss \& Schmitt, 2019).
 
@@
 gender differences in preferences for short-term mating, 1) there would
-be no gender differences in short-term mating behaviors among all
-heterosexual men and women, 2) a smaller proportion of heterosexual men
-had ever engaged into short-term mating compared to the proportion of
-heterosexual women, 3) in a population of heterosexual individuals who
-had any short-term mating, men had higher average number of short-term
-mating behaviors than women, 4) there would be gender differences in
-short-term mating behaviors among gay men and lesbian women, with gay
-men being engaged in more such behaviors, and 5) gay men would engage in
-more short-term mating behaviors compared to heterosexual men.
+be no gender differences in short-term mating behaviors between
+heterosexual men and women when the full population was considered, 2) a
+smaller proportion of heterosexual men (vs.~heterosexual women) had ever
+engaged in short-term mating, 3) in a population of heterosexual
+individuals who had any short-term mating, men had higher average number
+of short-term mating behaviors than women, 4) gay men would engage in
+more short-term mating behaviors compared to lesbian women, and 5) gay
+men would engage in more short-term mating behaviors compared to
+heterosexual men.
 
@@
 under what conditions they would result in differences in the number of
-short-term mating experiences and short-term mates. We formulated two
-hypotheses: 1) gay men would engage in more short-term mating behaviors
-as compared to lesbian women, and 2) gay men would engage in more
-short-term mating behaviors as compared to heterosexual men. The results
-from 1,000 time steps in a model simulating men and women's mating
-behaviors provided strong evidence in favor of our hypotheses. First of
-all, as compared to lesbian women, gay men had higher average numbers of
-short-term mating experiences and short-term mates. Secondly, gay men
+short-term mating experiences and short-term mates. We formulated five
+hypotheses: 1) there would be no gender differences in short-term mating
+behaviors between heterosexual men and women when the full population
+was considered, 2) a smaller proportion of heterosexual men
+(vs.~heterosexual women) had ever engaged in short-term mating, 3) in a
+population of heterosexual individuals who had any short-term mating,
+men had higher average number of short-term mating behaviors than women,
+4) gay men would engage in more short-term mating behaviors compared to
+lesbian women, and 5) gay men would engage in more short-term mating
+behaviors compared to heterosexual men. The results from 1,000 time
+steps in a model simulating men and women's mating behaviors provided
+strong evidence in favor of our hypotheses. First of all, we found no
+gender differences in short-term mating behaviors between heterosexual
+men and women when the full population was considered. However, compared
+to heterosexual women, there was a smaller proportion of heterosexual
+men participating in the mating pool, but they had higher average
+numbers of short-term mating experiences and short-term mates. Secondly,
+as compared to lesbian women, gay men had higher average numbers of
+short-term mating experiences and short-term mates. Finally, gay men
 also had higher average numbers of short-term mating experiences and
-short-term mates as compared to heterosexual men. In contrast, we found
-no gender differences in short-term mating behaviors between
-heterosexual men and women, although heterosexual men in the mating pool
-had higher average numbers of short-term mating experiences and
-short-term mates.
-
-As expected, heterosexual men and women did not differ in short-term
-mating behaviors despite their differential preferences for short-term
-mating. This was because heterosexual men and women had an equal total
-number of both short-term mating experiences and short-term mates. This
-is not surprising since the sex ratio was 1:1 in our model. It therefore
-follows that the average number of short-term mating experiences and
-short-term mates must be equal between men and women as well. However,
-we did find that when we only looked at individuals in the mating pool
-(from which more men than women were excluded), men engaged in more
-short-term mating behaviors as compared to women. This was because there
-were more women than men in the mating pool, resulting in lower averages
-among heterosexual women despite the equal numbers of experiences and
-mates in total.
+short-term mates as compared to heterosexual men.
+
+As expected, when the full population was considered, heterosexual men
+and women did not differ in short-term mating behaviors despite their
+differential preferences for short-term mating. This was because
+heterosexual men and women had an equal total number of both short-term
+mating experiences and short-term mates. This is not surprising since
+the sex ratio was 1:1 in our model. It therefore follows that the
+average number of short-term mating experiences and short-term mates
+must be equal between men and women as well. However, we did find that
+when we only looked at individuals in the mating pool (from which more
+men than women were excluded), men engaged in more short-term mating
+behaviors as compared to women. This was because there were more women
+than men in the mating pool, resulting in lower averages among
+heterosexual women despite the equal numbers of experiences and mates in
+total.
 
@@
 mating, heterosexual men and women engaged in short-term mating
-behaviors to the same extent, while gay men engaged in more short-term
-mating behaviors as compared to lesbian women. Gay men engaged in more
-short-term mating behaviors than heterosexual men did.
+behaviors to the same extent when the full population was considered,
+while men in the mating pool had more such behaviors than women in the
+mating pool. Gay men engaged in more short-term mating behaviors
+compared to both lesbian women and heterosexual men.
 
@@
 the psychological aspect but also pay attention to the interaction
-between individuals' psychology and its context. These results also cast
-doubt to the prevalent belief in the gender differences in short-term
-mating behaviors, especially among heterosexual individuals. Our
-findings suggest that there may be factors in the observation process,
-such as sampling bias, that contribute to the observed differences.
-Future research in human sexuality should note such possibilities and
-interpret any observed gender differences in short-term mating behaviors
-cautiously.
+between individuals' psychology and its behavioral context. These
+results also cast doubt to the prevalent belief in the gender
+differences in short-term mating behaviors, especially among
+heterosexual individuals. Our findings suggest that there may be factors
+in the observation process, such as sampling bias, that contribute to
+the observed differences. Future research in human sexuality should note
+such possibilities and interpret any observed gender differences in
+short-term mating behaviors with caution.
 
@@
 \section{Acknowledgements}\label{acknowledgements}}
+
+We thank Gu Li and Jiannan Shi for providing helpful feedback in the
+development of this study.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-ghaznavi2019trends}{}}%
+Ghaznavi, C., Sakamoto, H., Yoneoka, D., Nomura, S., Shibuya, K., \&
+Ueda, P. (2019). Trends in heterosexual inexperience among young adults
+in japan: Analysis of national surveys, 1987--2015. \emph{BMC Public
+Health}, \emph{19}(1), 1--10.
+
 \leavevmode\vadjust pre{\hypertarget{ref-s_j_gurman_six_1989}{}}%
@@
 \url{https://doi.org/10.1016/j.evolhumbehav.2010.07.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-haydon2014prevalence}{}}%
+Haydon, A. A., Cheng, M. M., Herring, A. H., McRee, A.-L., \& Halpern,
+C. T. (2014). Prevalence and predictors of sexual inexperience in
+adulthood. \emph{Archives of Sexual Behavior}, \emph{43}(2), 221--230.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-wilensky_1999}{}}%
-Wilensky, U. (1999). \emph{NetLogo}
-{[}Http://ccl.northwestern.edu/netlogo/{]}. Center for Connected
-Learning; Computer-Based Modeling.
-\url{http://ccl.northwestern.edu/netlogo/}
+Wilensky, U. (1999). \emph{NetLogo}. Center for Connected Learning;
+Computer-Based Modeling. \url{http://ccl.northwestern.edu/netlogo/}
 

### 2022-06-04 submission/manuscript.Rmd
minor edit

@@
     general = "\\\\textit{Note.} The averages were calculated with subsamples of men and women who had had engaged in short-term mating behaviors.
-See Supplementary Materials for the mean and standard deviation of sample sizes.",
+See Supplemental Materials for the mean and standard deviation of sample sizes.",
     general_title = "", escape = FALSE,

### 2022-06-05 submission/supplemental_materials.Rmd
compiled supplemental materials, close #22

---
output:
  pdf_document
geometry: margin=1.0in
fontsize: 11pt
numbersections: false
indent: true
bibliography: reference.bib
csl: evolution-and-human-behavior.csl
header-includes:
  - \newcommand{\bcenter}{\begin{center}}
  - \newcommand{\ecenter}{\end{center}}
  - \newcommand{\btitlepage}{\begin{titlepage}}
  - \newcommand{\etitlepage}{\end{titlepage}}
  - \usepackage{setspace}\doublespacing
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{booktabs}
  - \usepackage[font=small,labelfont=bf]{caption}
  - \usepackage{indentfirst}
  - \pagenumbering{gobble}
---

```{r set_up, include=FALSE}
library(tidyverse); library(here); library(knitr); library(kableExtra)

options(knitr.kable.NA = '')

results_inpool <-
  here("data/processed/des_and_test_result.csv") %>%
  read_csv() %>%
  rename(hls = homosexual_dlikelihood_dstandard) %>%
  mutate(across(.col = c(f_inpool.mean:m_outpool.sd,
                inpool.conf.low:inpool.conf.high,
                outpool.conf.low:outpool.conf.high),
                ~ .x/150)) %>%
  select(hls, m_inpool.mean, m_inpool.sd, f_inpool.mean, f_inpool.sd) %>% 
  filter(str_detect(hls, "^0"))

# define inline hook
inline_hook <- function(x) {

    if (is.numeric(x)) {

      formatted <- ifelse(
        abs(x - round(x)) < .Machine$double.eps & x != 0,
        # treat as integer
        format(x, digits=0, big.mark = ","),
        # treat as floating point number
        format(x, digits=1, nsmall=2, big.mark = ",")
        ) %>%
        str_replace("-", "–")

    } else {

      formatted <- x

    }

}

knit_hooks$set(inline = inline_hook)
```

\btitlepage

\bcenter

\vspace*{30mm}

# Supplemental Materials to "An Agent-Based Model of Gender and Sexual Orientation Differences in Short-Term Mating Behaviors as a Result of Mating Preferences"

\ecenter

\etitlepage

\newpage

\bcenter

## Overview, Design Concepts, and Details of the Model

\ecenter

This description of the model follows the standard ODD protocol of reporting individual-based and agent-based modeling [@grimm_standard_2006].

### Purpose

The model simulated sex differences in short-term mating behavior. Findings in evolutionary psychology suggest that men have a stronger desire for short-term mating than women [@regan_minimum_1998]. They are also less choosy regarding short-term mating partners [@buss2019mate; @buss_sexual_1993]. This model explores both heterosexual and gay men’s as well as heterosexual and lesbian women’s behavioral outcomes under these assumptions.

The first version of the model simulated short-term mating behaviors among heterosexual individuals, short-term mating and/or long-term relationships were formed only between individuals of the opposite sex. The second version of the model simulated the behaviors among gay men and lesbian women, where individuals only had short-term matings and/or formed long-term relationships with those of the same sex. The key parameters were individuals’ likelihood of engaging in short-term mating and their standards for a short-term partner. We varied those parameters to examine conditions under which sex differences in behavioral outcomes may emerge.

### Entities, state variables, and scales

The model included two types of entities: global and agents. In this model, time and space were modeled as discrete variables. During each time step, agents executed the commands described in the schedule. Space was represented as discrete locations on a two-dimensional 33*33 lattice. All state variables are summarized in Table S1.

### Process overview and scheduling

The model was written using Netlogo 6.2.1 **citation needed**. The model proceeded in discrete time steps, and the entities executed commands in the following order:

\begin{enumerate}

  \item Setting up (Global, only executed once)
  \begin{enumerate}
    \item 300 agents were created with all state variables set to the default
    \item A number of agents were set to either men (number-of-male) or women (300 - number-of-men) with their respective short-term mating likelihood (short-term-likelihood), and standard for a short-term mate (mating-standard) 
  \end{enumerate}

  \item Moving (The following procedures were executed by agents unless specified otherwise)

  \begin{enumerate}
    \item If not coupled
    \begin{enumerate}
      \item If staying within a distance of movement-range from the initial point on both the x and y axis, randomly set their heading and move by a random distance less than movement-range / 2
      \item If staying outside the distance of movement-range from the initial point on either the x or y axis, head toward the initial point and move by a random distance less than movement-range / 2
    \end{enumerate}
    \item If coupled, do not move
  \end{enumerate}

  \item Deciding on short-term mating behavior
  \begin{enumerate}
    \item Set short-term-mate? to true by short-term-likelihood
  \end{enumerate}

  \item Short-term and long-term mating (To avoid double count, only women execute this chunk. This does not affect the model outcomes.)
  \begin{enumerate}
    \item If any men here, women randomly select one as the target for short-term mating
    \begin{enumerate}
      \item If the target has desirability higher than her mating-standard \& she has desirability higher than the target’s mating-standard \& both of them have short-term-mate? set to true,
      \begin{enumerate}
        \item Both of them add 1 to short-term-count
        \item Both of them add each other’s ID number to their short-term-history if not in it yet
      \end{enumerate}
    \end{enumerate}
    \item If any men here and women are not coupled, women randomly select one as the potential partner for long-term mating
    \begin{enumerate}
      \item By long-term-likelihood, they form a long-term relationship, and
      \begin{enumerate}
        \item Both of them set coupled? to true
        \item Both of them set each other as their long-term partner
      \end{enumerate}
    \end{enumerate}
  \end{enumerate}

  \item Updating state variables
  \begin{enumerate}
    \item Set number-of-partner-short the length of short-term-history
    \item If short-term-likelihood equals male-/female-short-term-likelihood, set short-term-likelihood to a third of its value
  \end{enumerate}

\end{enumerate}

### Design concepts

*Sensing.* Agents were able to detect other agents’ mate value so that they could decide whether to have short-term mating with them.

*Interaction.* Women and men interacted to have short-term mating behaviors or form long-term relationships.

*Stochasticity.* Agents' movement in this model had stochastic elements, with the heading and the movement distance being randomly selected. Whether agents decided to have short-term mating or form long-term relationships was also randomly determined.

*Observation.* Simulations were run for 1,000 time steps. The dependent variables were measured at the end of each run.

\newpage

\noindent \textbf{Supplemental Table 3:} Mean proportion of heterosexual men and women in the mating pool and its standard deviation after 1,000 time steps in the model.

\begingroup
\renewcommand{\arraystretch}{1.5}

```{r inpool,echo=FALSE}
results_inpool %>%
  mutate(across(where(is.numeric), inline_hook)) %>%
  mutate(
    condition =
      c("Same likelihood*Same standard",
        "Same likelihood*Different standard",
        "Different likelihood*Same standard",
        "Different likelihood*Different standard")
  ) %>%
  select(-hls) %>% 
  column_to_rownames("condition") %>%
  kable(
    digits = 2, format = "latex", booktabs = TRUE, align = "cccc",
    row.names = TRUE, col.names = rep(c("M", "SD"), 2)
    ) %>%
  row_spec(0, italic = TRUE, align = "c") %>%
  add_header_above(
    c(" " = 1,
      "Men" = 2, "Women" = 2)
    ) %>%
  column_spec(1, width = "2.5in") %>%
  column_spec(c(2, 3, 4, 5), width = "0.8in") %>%
  footnote(
    general = "\\\\textit{Note.} \\\\textit{N} = 2,500 in each condition.",
    general_title = "", escape = FALSE,
    threeparttable = TRUE, fixed_small_size = TRUE) %>%
  kable_styling(position = "center", latex_options = "hold_position")
```

\endgroup

\newpage

## References

<div id="refs"></div>

### 2022-06-06 submission/supplemental_materials.Rmd
minor edits to supplemental materials

@@
 Space was represented as discrete locations on a two-dimensional 33*33 lattice.
-All state variables are summarized in Table S1.
+All state variables are summarized in Supplemental Table 1.
 
@@
 
-The model was written using Netlogo 6.2.1 **citation needed**. The model proceeded in discrete time steps, and the entities executed commands in the following order:
+The model was written using Netlogo 6.2.1 [@wilensky_1999]. The model proceeded in discrete time steps, and the entities executed commands in the following order:
 
@@
     \item 300 agents were created with all state variables set to the default
-    \item A number of agents were set to either men (number-of-male) or women (300 - number-of-men) with their respective short-term mating likelihood (short-term-likelihood), and standard for a short-term mate (mating-standard)
+    \item A number of agents were set to either men (number-of-male) or women (300 – number-of-men) with their respective short-term mating likelihood (short-term-likelihood), and standard for a short-term mate (mating-standard)
   \end{enumerate}

### 2022-06-06 submission/manuscript.Rmd
minor edits based on feedback

@@
 
-# An Agent-Based Model of Gender Differences in Short-Term Mating Behaviors as a Result of Mating Preferences {-}
+# An Agent-Based Model of Gender and Sexual Orientation Differences in Short-Term Mating Behaviors as a Result of Mating Preferences {-}
 
@@
 Existing studies usually conflate gender differences in mating preferences with differences in sexual behaviors, which is theoretically problematic.
-Using an agent-based model, we investigated the circumstances under which heterosexual and homosexual men and women’s differential preferences for short-term mating would result in gender differences in short-term mating behaviors.
+Using an agent-based model, we investigated the circumstances under which men and women’s differential preferences for short-term mating would result in gender differences in short-term mating behaviors.
 The model showed that when all individuals in a closed heterosexual population were considered,  men and women had the same average number of short-term mating experiences and short-term mates even when men had stronger preferences for short-term mating.
 Men (vs.
-women) had a higher average number of both experiences and mates only when heterosexual men and women who successfully participated in the mating pool (i.e., those with a non-zero number of short-term mating experiences) were considered.
+women) had a higher average number of both experiences and mates when analyses were limited to only heterosexual men and women who successfully participated in the mating pool (i.e., those with a non-zero number of short-term mating experiences).
 Moreover, when men (vs.
 women) had stronger preferences for short-term mating, gay men had a higher average number of both experiences and mates compared to both lesbian women and heterosexual men.
-These results suggest that theoretically speaking, even when gender differences in mating preferences exist, those in short-term mating behaviors only occur among particular populations, or when men’s preferences for short-term mating are not constrained by those of women.
+These results suggest that even when gender differences in mating preferences exist, those in short-term mating behaviors only occur among particular populations, or when men’s preferences for short-term mating are not constrained by those of women.
 Suggestions for future research in human mating psychology and behaviors were provided.
@@
 
-*Keywords:* agent-based modeling, short-term mating, casual sex, sexual strategy theory, female choice hypothesis
+*Keywords:* agent-based modeling, short-term mating, casual sex, sexual strategies theory, female choice hypothesis
 
@@
 
-As a starting point, we took gender differences in mating preferences as conceptualized by the sexual strategy theory [@buss_sexual_1993; @buss2019mate], which is repeatedly supported by empirical investigations [e.g., @schmitt_universal_2003; @walter_sex_2020].
+As a starting point, we took gender differences in mating preferences as conceptualized by the sexual strategies theory [@buss_sexual_1993; @buss2019mate], which is repeatedly supported by empirical investigations [e.g., @schmitt_universal_2003; @walter_sex_2020].
 Using an agent-based model, we investigated whether men and women's differential preferences for short-term mating would result in gender differences in short-term mating behaviors, and if so, then under what conditions they would result in differences in the number of short-term mating experiences and short-term mates.
@@
 
-Gender differences in mating preferences have been studied in the light of sexual strategy theory [@buss_sexual_1993; @buss2019mate].
+Gender differences in mating preferences have been studied in the light of sexual strategies theory [@buss_sexual_1993; @buss2019mate].
 It posits that since the minimum obligatory investment that men must devote to their offspring (contribution of sperm through one sexual act) is lower than that of women (gestation, labor, and lactation), men tend to be relatively more interested in short-term mating compared to women.
@@
 
-The hypotheses derived from sexual strategy theory have received extensive support in empirical studies.
+The hypotheses derived from sexual strategies theory have received extensive support in empirical studies.
 For example, men have reported to be currently seeking short-term mates to a larger extent than women [@buss_sexual_1993; @schmitt_are_2001; @schmitt_universal_2003], and a larger proportion of men were in any way seeking short-term mates (vs.
@@
 
-However, it is important to note that although heterosexual men’s total number of short-term mating is equal to that of women, this does not necessarily mean that the total number of men and women who have ever had short-term mating must be equal.
-Empirical studies have found that the proportion of individuals who are sexual inexperienced is slightly higher among men than women in most age groups above 18 years old [@haydon2014prevalence; @ghaznavi2019trends].
-As a postulation, there may be a smaller proportion of men (vs.
+However, it is important to note that although heterosexual men’s total number of short-term matings would be equal to that of women, this does not necessarily mean that the total number of men and women who have ever had short-term mating must be equal.
+Empirical studies have found that the proportion of individuals who are sexually inexperienced is slightly higher among men than women in most age groups above 18 years old [@haydon2014prevalence; @ghaznavi2019trends].
+Therefore, as a postulation, there may be a smaller proportion of men (vs.
 the proportion of women) who participate in the mating pool and contribute to the total number of short-term mating.
 For example, suppose that there is a population of 20 individuals with an equal sex ratio.
-Heterosexual short-term mating has happened \(n\) times in this population, but only 3 men and 8 women have had any short-term mating experiences.
+Heterosexual short-term matings have happened \(n\) times in this population, but only 3 men and 8 women have had any short-term mating experiences.
 Since the total number of short-term mating behaviors is the same between men and women, we would expect that in a population of individuals who had any short-term mating, the average number of short-term mating experiences and mates was higher among men than women (e.g., in the aforementioned example, the average number of short-term experiences is \(\frac{n}{3}\) for men and \(\frac{n}{8}\) for women who are in the mating pool).
 
-As a comparison, in the cases of gay men and lesbian women, men’s preferences are not constrained by women’s, but only by those of other men, who, arguably, have a similar high interest in short-term mating.
+As a comparison, in the cases of gay men and lesbian women, men’s preferences are not constrained by those of women’s, but only by those of other men, who, arguably, have a similar high interest in short-term mating.
 This would allow for a more direct behavioral expression of men’s mating preferences.
-The notion that gay men have less restricted preferences is borne out in the proportion of individuals who have engaged in extradyadic sex [@peplau_sexuality_2004].
-A study showed that the proportions of heterosexual men and women who had engaged in extradyadic sex were 26% and 21%, respectively, while the statistics among gay men and lesbian women were 82% and 28%, respectively [@peplau_sexuality_2004].
+The notion that gay men have less restricted preferences is born out in the proportion of individuals who have engaged in extradyadic sex [@peplau_sexuality_2004].
+A study showed that the proportions of heterosexual men and women who had engaged in extradyadic sex were 26% and 21%, respectively, while the numbers among gay men and lesbian women were 82% and 28%, respectively [@peplau_sexuality_2004].
 Therefore, we would expect to observe gender differences in short-term mating behaviors between gay men and lesbian women.
-Moreover, we would also expect to find that gay men, compared to heterosexual men, engaged in more short-term mating behaviors due to less constraints on their mating preferences.
+Moreover, we would also expect to find that gay men would engage in more short-term mating behaviors compared to heterosexual men due to less constraints on gay men's mating preferences.
 
@@
 A pair of individuals had a possibility to commit to a long-term relationship upon meeting each other.
-This process was modeled at a behavioral level and the psychological processes behind it was ignored, although we recognized gender differences may also exist in long-term mating strategy [@buss_sexual_1993; @buss2019mate].
+This process was modeled at a behavioral level and the psychological processes behind it was ignored, although we recognized that gender differences may also exist in long-term mating strategy [@buss_sexual_1993; @buss2019mate].
 
 We modeled these processes among both heterosexual individuals and gay men and lesbian women to examine whether constraints set by the opposite sex’s preferences would affect short-term mating behaviors.
-Individuals’ sexual orientation was conceptualized in terms of behaviors only in our model.
+Individuals’ sexual orientation was conceptualized as categorical in terms of behaviors only in our model.
 Heterosexual men had short-term mating or formed a long-term relationship only with women, while gay men only with other men, and mutatis mutandis for women.
 
-We formulated the following hypotheses in the present study: assuming gender differences in preferences for short-term mating, 1) there would be no gender differences in short-term mating behaviors between heterosexual men and women when the full population was considered, 2) a smaller proportion of heterosexual men (vs.
-heterosexual women) had ever engaged in short-term mating, 3) in a population of heterosexual individuals who had any short-term mating, men had higher average number of short-term mating behaviors than women, 4) gay men would engage in more short-term mating behaviors compared to lesbian women, and 5) gay men would engage in more short-term mating behaviors compared to heterosexual men.
+We formulated the following hypotheses: assuming gender differences in preferences for short-term mating, 1) there would be no gender differences in short-term mating behaviors between heterosexual men and women when considering the full population, 2) a smaller proportion of heterosexual men (vs.
+heterosexual women) would have ever engaged in short-term mating, 3) in a population of heterosexual individuals who had any short-term mating, men would have a higher average number of short-term mating behaviors than women, 4) gay men would engage in more short-term mating behaviors compared to lesbian women, and 5) compared to heterosexual men.
 
@@
 
-## Comparing across conditions
+## Experimental conditions giving rise to gender differences in short-term mating behaviors
 
@@
 The present study used agent-based modeling to investigate whether men and women’s differential preferences for short-term mating would result in gender differences in short-term mating behaviors, and if so, then under what conditions they would result in differences in the number of short-term mating experiences and short-term mates.
-We formulated five hypotheses: 1) there would be no gender differences in short-term mating behaviors between heterosexual men and women when the full population was considered, 2) a smaller proportion of heterosexual men (vs.
-heterosexual women) had ever engaged in short-term mating, 3) in a population of heterosexual individuals who had any short-term mating, men had higher average number of short-term mating behaviors than women, 4) gay men would engage in more short-term mating behaviors compared to lesbian women, and 5) gay men would engage in more short-term mating behaviors compared to heterosexual men.
+We formulated five hypotheses: 1) there would be no gender differences in short-term mating behaviors between heterosexual men and women when considering the full population, 2) a smaller proportion of heterosexual men (vs.
+heterosexual women) would have ever engaged in short-term mating, 3) in a population of heterosexual individuals who had any short-term mating, men would have a higher average number of short-term mating behaviors than women, 4) gay men would engage in more short-term mating behaviors compared to lesbian women, and 5) compared to heterosexual men.
 The results from 1,000 time steps in a model simulating men and women’s mating behaviors provided strong evidence in favor of our hypotheses.
@@
 The only difference was a change in the preferences of potential partners.
-When men’s partners had a stronger preferences for short-term mating (i.e., having men vs.
+When men’s partners had stronger preferences for short-term mating (i.e., having men vs.
 having women as potential partners), men also appeared to engage in more short-term mating behaviors.
@@
 Using agent-based modeling to simulate short-term mating behaviors, we found when men (vs.
-women) had a stronger preferences for short-term mating, heterosexual men and women engaged in short-term mating behaviors to the same extent when the full population was considered, while men in the mating pool had more such behaviors than women in the mating pool.
+women) had stronger preferences for short-term mating, heterosexual men and women engaged in short-term mating behaviors to the same extent when the full population was considered, while men in the mating pool had more such behaviors than women in the mating pool.
 Gay men engaged in more short-term mating behaviors compared to both lesbian women and heterosexual men.

### 2022-06-10 submission/manuscript.Rmd
final edits

@@
 
-\vspace{30mm}
-
-Yurun Ying^1^^,^^$\dagger$^, Jan Antfolk^2^, Pekka Santtila^1^^,^^3^
-
-^1^ Faculty of Arts and Sciences, NYU Shanghai
-
-^2^ Faculty of Arts, Psychology and Theology, Åbo Akademi University
-
-^3^ NYU-ECNU Institute for Social Development at NYU Shanghai
-
 \ecenter
-
-\vspace{40mm}
-
-^$\dagger$^ To whom correspondence should be addressed: [yurun.ying@nyu.edu](yurun.ying@nyu.edu)
 
@@
 Moreover, when men (vs.
-women) had stronger preferences for short-term mating, gay men had a higher average number of both experiences and mates compared to both lesbian women and heterosexual men.
+women) had stronger preferences for short-term mating, gay men had a higher average number of experiences and mates compared to both lesbian women and heterosexual men.
 These results suggest that even when gender differences in mating preferences exist, those in short-term mating behaviors only occur among particular populations, or when men’s preferences for short-term mating are not constrained by those of women.
@@
 For example, studies using U.S.
-college samples have found that the minimum percentile ranks of the desirability of a potential short-term sexual partner accepted by men were lower than those accepted by women, in terms of both the overall desirability and the desirability of individual traits (e.g., social status, attractiveness) [@kenrick_evolution_1990; @regan_minimum_1998].
+college samples have found that men' acceptable minimum percentile ranks of the desirability of a potential short-term sexual partner were lower than those accepted by women, in terms of both the overall desirability and the desirability of individual traits (e.g., social status, attractiveness) [@kenrick_evolution_1990; @regan_minimum_1998].
 Another study also found that when presented with identical descriptions of potential mates, men on average rated them as more desirable than women did [@wiederman_evolution_1998].
@@
 This is because men’s short-term mating preferences – with the exception of sexual violence – can only translate into behaviors when there are women willing to have sex with them.
-When a new short-term mating encounter occurs, it counts towards both men’s total number of short-term mating encounters as well as women’s, and both men and women have new short-term mates.
+When a new short-term mating encounter occurs, both men’s and women's total number of short-term mating experiences and the number of short-term mates increase by one.
 Therefore, the total number of short-term mating experiences and short-term mates must be equal between heterosexual men and women at the population level.
@@
 Heterosexual short-term matings have happened \(n\) times in this population, but only 3 men and 8 women have had any short-term mating experiences.
-Since the total number of short-term mating behaviors is the same between men and women, we would expect that in a population of individuals who had any short-term mating, the average number of short-term mating experiences and mates was higher among men than women (e.g., in the aforementioned example, the average number of short-term experiences is \(\frac{n}{3}\) for men and \(\frac{n}{8}\) for women who are in the mating pool).
+Since the total number of short-term mating behaviors is the same between men and women, we would expect that in a population of individuals who participate in the mating pool, the average numbers of short-term mating experiences and mates are higher among men than women (e.g., in the aforementioned example, the average number of short-term experiences is \(\frac{n}{3}\) for men and \(\frac{n}{8}\) for women who are in the mating pool).
 
@@
 Additionally, we also measured the number of men and women in the mating pool (i.e., those with a non-zero number of short-term mating experiences).
-The average numbers of short-term mating experiences and short-term mates were calculated by taking the average among the whole population of men and women (*N~men~* = *N~women~* = 150) and among those who had engaged in any short-term mating.
+The average numbers of short-term mating experiences and short-term mates were calculated by taking the average among the whole population of men and women (*N~men~* = *N~women~* = 150) and among those who had ever engaged in any short-term mating.
 
@@
 At each time step, agents first checked whether they were in a long-term relationship.
+If they were in a long-term relationship, they did not move.
 If they were not in a long-term relationship, they set their heading randomly (if they were within the movement range from the birthplace) or faced the birthplace (if they were out of the movement range from the birthplace) and moved by a random distance.
 The random distance was less than half of the movement range.
-If they were in a long-term relationship, they did not move.
 Then, the agents decided on whether to engage in short-term mating using the predetermined likelihood (either 25% or 40%).
@@
 Then, women randomly selected one man at the same location as their potential long-term partner.
-There was a 10% of chance that a pair would form a long-term relationship.
+There was a 10% of chance that a pair of individuals would form a long-term relationship.
 After forming a long-term relationship, both men and women changed to coupled status and registered each other as their long-term partner.
@@
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The averages were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
+The means were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
   \label{fig:men_vs_women}
@@
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The averages were calculated using the population of heterosexual men and women in the mating pool (proportion: \textit{M\textsubscript{men}} = `r m_inpool.mean_011`, \textit{M\textsubscript{women}} = `r f_inpool.mean_011`).}
+The means were calculated using the population of heterosexual men and women who successfully participated in the mating pool (proportion: \textit{M\textsubscript{men}} = `r m_inpool.mean_011`, \textit{M\textsubscript{women}} = `r f_inpool.mean_011`).}
   \label{fig:men_vs_women_inpool}
@@
 Gay men engaged in short-term mating behaviors more than heterosexual men did (Figure \ref{fig:hetero_vs_gay}).
-The average number of short-term mating experiences (as calculated using the full population of men) was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`, `r exp_all.ci_hg`.
-Similarly, the average number of short-term mates (as calculated using the full population of men) was higher among gay men (*M* = `r m_partner_all.mean_1_11`, *SD* = `r m_partner_all.sd_1_11`) than among heterosexual men (*M* = `r m_partner_all.mean_0_11`, *SD* = `r m_partner_all.sd_0_11`), *t*(`r partner.all.parameter_hg`) = `r partner.all.statistic_hg`, *p* `r partner.all.p.value_hg`, Cohen's *d* = `r partner_all.d_hg`, `r partner_all.ci_hg`.
+The average number of short-term mating experiences (calculated using the full population of men) was higher among gay men (*M* = `r m_exp_all.mean_1_11`, *SD* = `r m_exp_all.sd_1_11`) than among heterosexual men (*M* = `r m_exp_all.mean_0_11`, *SD* = `r m_exp_all.sd_0_11`), *t*(`r exp.all.parameter_hg`) = `r exp.all.statistic_hg`, *p* `r exp.all.p.value_hg`, Cohen's *d* = `r exp_all.d_hg`, `r exp_all.ci_hg`.
+Similarly, the average number of short-term mates (calculated using the full population of men) was higher among gay men (*M* = `r m_partner_all.mean_1_11`, *SD* = `r m_partner_all.sd_1_11`) than among heterosexual men (*M* = `r m_partner_all.mean_0_11`, *SD* = `r m_partner_all.sd_0_11`), *t*(`r partner.all.parameter_hg`) = `r partner.all.statistic_hg`, *p* `r partner.all.p.value_hg`, Cohen's *d* = `r partner_all.d_hg`, `r partner_all.ci_hg`.
 
@@
   \includegraphics[width=0.8\columnwidth]{figures/fig3_hetero_vs_gay_men.pdf}
-  \caption{\textbf{Short-term mating behaviors of heterosexual and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
+  \caption{\textbf{Short-term mating behaviors of heterosexual men and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
 Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The averages were calculated using the full population of heterosexual and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
+The means were calculated using the full population of heterosexual men and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
   \label{fig:hetero_vs_gay}
@@
   footnote(
-    general = "\\\\textit{Note.} The averages were calculated with subsamples of men and women who had had engaged in short-term mating behaviors.
+    general = "\\\\textit{Note.} The means were calculated with subsamples of men and women who had ever engaged in short-term mating behaviors.
 See Supplemental Materials for the mean and standard deviation of sample sizes.",
@@
 
-Among gay men and lesbian women, gender differences in short-term mating behaviors emerged both when they had different short-term mating likelihood and when their mating standards were different.
+Among gay men and lesbian women, gender differences in short-term mating behaviors emerged both when they had different short-term mating likelihood and when they had different mating standards.
 Gay men (vs.
@@
 However, compared to heterosexual women, there was a smaller proportion of heterosexual men participating in the mating pool, but they had higher average numbers of short-term mating experiences and short-term mates.
-Secondly, as compared to lesbian women, gay men had higher average numbers of short-term mating experiences and short-term mates.
-Finally, gay men also had higher average numbers of short-term mating experiences and short-term mates as compared to heterosexual men.
+Secondly, gay men had higher average numbers of short-term mating experiences and short-term mate compared to both lesbian women and heterosexual men.
 
-As expected, when the full population was considered, heterosexual men and women did not differ in short-term mating behaviors despite their differential preferences for short-term mating.
-This was because heterosexual men and women had an equal total number of both short-term mating experiences and short-term mates.
+As expected, when all individuals in the population were considered, heterosexual men and women did not differ in short-term mating behaviors despite their differential preferences for short-term mating.
 This is not surprising since the sex ratio was 1:1 in our model.
+Heterosexual men and women had an equal total number of both short-term mating experiences and short-term mates.
 It therefore follows that the average number of short-term mating experiences and short-term mates must be equal between men and women as well.
-However, we did find that when we only looked at individuals in the mating pool (from which more men than women were excluded), men engaged in more short-term mating behaviors as compared to women.
+However, we did find that when we only looked at individuals in the mating pool (from which more men than women were excluded), men engaged in more short-term mating behaviors compared to women.
 This was because there were more women than men in the mating pool, resulting in lower averages among heterosexual women despite the equal numbers of experiences and mates in total.
 
-Moreover, gender differences in short-term mating behaviors emerged when heterosexual men and women had different mating standards, but not when they had different short-term mating likelihood.
-When women had a higher standard than men did, less men than women in the population were above a potential partner’s standard and thus had a chance to have sex with them.
+Moreover, gender differences in short-term mating behaviors emerged among individuals in the mating pool when heterosexual men and women had different mating standards, but not when they had different short-term mating likelihood.
+When women had a higher standard than men, less men than women in the population were above a potential partner’s standard and thus had a chance to have sex with them.
 This contributed to the unequal number of men and women in the mating pool, which led to gender differences in short-term mating behaviors among this population.
-In comparison, even when men and women had different short-term mating likelihood, the probability of any pair of them ending up having sex is the product of their individual likelihood (since men and women made decisions independently).
+In comparison, when men and women had different short-term mating likelihood, the probability of any pair of them ending up having sex is always the product of their individual likelihood (since men and women made decisions independently).
 As this probability is the same for both parties, the gender difference in short-term mating likelihood did not translate into different behaviors.
@@
 Both a difference in the likelihood of short-term mating and in mating standards alone resulted in gender differences in mating behaviors.
-This was likely because the former increased the probability of both parties of a given gay couple deciding to have short-term mating, and the latter increased the probability of both meeting each other's standards, as compared to the case of a given lesbian couple.
+This was likely because the former increased the probability of both parties of a given gay couple deciding to have short-term mating, and the latter increased the probability of both meeting each other's standards, compared to the case of a given lesbian couple.
 
@@
 Using agent-based modeling to simulate short-term mating behaviors, we found when men (vs.
-women) had stronger preferences for short-term mating, heterosexual men and women engaged in short-term mating behaviors to the same extent when the full population was considered, while men in the mating pool had more such behaviors than women in the mating pool.
+women) had stronger preferences for short-term mating, heterosexual men and women engaged in short-term mating behaviors to the same extent when all individuals in the population were considered.
+However, among individuals who participated in the mating pool, men had more such behaviors than women.
 Gay men engaged in more short-term mating behaviors compared to both lesbian women and heterosexual men.
@@
 Individuals’ mating behaviors do not only depend on one’s own preferences, but are also constrained by partners’ preferences.
-Future research in human mating should not only focus on the psychological aspect but also pay attention to the interaction between individuals’ psychology and its behavioral context.
+Future research should not only focus on the psychological aspect of human mating but also pay attention to the interaction between individuals’ psychology and its behavioral context.
 These results also cast doubt to the prevalent belief in the gender differences in short-term mating behaviors, especially among heterosexual individuals.
@@
 
-We thank Gu Li and Jiannan Shi for providing helpful feedback in the development of this study.
+We thank [name masked for peer review] and [name masked for peer review] for providing helpful feedback in the development of this study.
+This research did not receive any specific grant from funding agencies in the public, commercial, or not-for-profit sectors.
 
@@
 
-All models, data, and analysis code can be downloaded at: [link masked for peer review]
+All model, data, and analysis code (including its history) are available at: [link masked for peer review].
 

### 2022-06-10 submission/manuscript.tex
final edits

@@
 
-\hypertarget{an-agent-based-model-of-gender-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}{%
-\section*{An Agent-Based Model of Gender Differences in Short-Term
-Mating Behaviors as a Result of Mating
-Preferences}\label{an-agent-based-model-of-gender-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}}
-\addcontentsline{toc}{section}{An Agent-Based Model of Gender
+\hypertarget{an-agent-based-model-of-gender-and-sexual-orientation-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}{%
+\section*{An Agent-Based Model of Gender and Sexual Orientation
 Differences in Short-Term Mating Behaviors as a Result of Mating
-Preferences}
-
-\vspace{30mm}
-
-Yurun Ying\textsuperscript{1,\(\dagger\)}, Jan
-Antfolk\textsuperscript{2}, Pekka Santtila\textsuperscript{1,3}
-
-\textsuperscript{1} Faculty of Arts and Sciences, NYU Shanghai
-
-\textsuperscript{2} Faculty of Arts, Psychology and Theology, Åbo
-Akademi University
-
-\textsuperscript{3} NYU-ECNU Institute for Social Development at NYU
-Shanghai
+Preferences}\label{an-agent-based-model-of-gender-and-sexual-orientation-differences-in-short-term-mating-behaviors-as-a-result-of-mating-preferences}}
+\addcontentsline{toc}{section}{An Agent-Based Model of Gender and Sexual
+Orientation Differences in Short-Term Mating Behaviors as a Result of
+Mating Preferences}
 
 \end{center}
-
-\vspace{40mm}
-
-\textsuperscript{\(\dagger\)} To whom correspondence should be
-addressed: \url{yurun.ying@nyu.edu}
 
@@
 which is theoretically problematic. Using an agent-based model, we
-investigated the circumstances under which heterosexual and homosexual
-men and women's differential preferences for short-term mating would
-result in gender differences in short-term mating behaviors. The model
-showed that when all individuals in a closed heterosexual population
-were considered, men and women had the same average number of short-term
-mating experiences and short-term mates even when men had stronger
-preferences for short-term mating. Men (vs.~women) had a higher average
-number of both experiences and mates only when heterosexual men and
-women who successfully participated in the mating pool (i.e., those with
-a non-zero number of short-term mating experiences) were considered.
-Moreover, when men (vs.~women) had stronger preferences for short-term
-mating, gay men had a higher average number of both experiences and
-mates compared to both lesbian women and heterosexual men. These results
-suggest that theoretically speaking, even when gender differences in
-mating preferences exist, those in short-term mating behaviors only
-occur among particular populations, or when men's preferences for
-short-term mating are not constrained by those of women. Suggestions for
-future research in human mating psychology and behaviors were provided.
+investigated the circumstances under which men and women's differential
+preferences for short-term mating would result in gender differences in
+short-term mating behaviors. The model showed that when all individuals
+in a closed heterosexual population were considered, men and women had
+the same average number of short-term mating experiences and short-term
+mates even when men had stronger preferences for short-term mating. Men
+(vs.~women) had a higher average number of both experiences and mates
+when analyses were limited to only heterosexual men and women who
+successfully participated in the mating pool (i.e., those with a
+non-zero number of short-term mating experiences). Moreover, when men
+(vs.~women) had stronger preferences for short-term mating, gay men had
+a higher average number of experiences and mates compared to both
+lesbian women and heterosexual men. These results suggest that even when
+gender differences in mating preferences exist, those in short-term
+mating behaviors only occur among particular populations, or when men's
+preferences for short-term mating are not constrained by those of women.
+Suggestions for future research in human mating psychology and behaviors
+were provided.
 
@@
 \emph{Keywords:} agent-based modeling, short-term mating, casual sex,
-sexual strategy theory, female choice hypothesis
+sexual strategies theory, female choice hypothesis
 
@@
 As a starting point, we took gender differences in mating preferences as
-conceptualized by the sexual strategy theory (Buss \& Schmitt, 1993;
+conceptualized by the sexual strategies theory (Buss \& Schmitt, 1993;
 Buss \& Schmitt, 2019), which is repeatedly supported by empirical
@@
 Gender differences in mating preferences have been studied in the light
-of sexual strategy theory (Buss \& Schmitt, 1993; Buss \& Schmitt,
+of sexual strategies theory (Buss \& Schmitt, 1993; Buss \& Schmitt,
 2019). It posits that since the minimum obligatory investment that men
@@
 
-The hypotheses derived from sexual strategy theory have received
+The hypotheses derived from sexual strategies theory have received
 extensive support in empirical studies. For example, men have reported
@@
 a potential short-term mate. For example, studies using U.S. college
-samples have found that the minimum percentile ranks of the desirability
-of a potential short-term sexual partner accepted by men were lower than
+samples have found that men' acceptable minimum percentile ranks of the
+desirability of a potential short-term sexual partner were lower than
 those accepted by women, in terms of both the overall desirability and
@@
 there are women willing to have sex with them. When a new short-term
-mating encounter occurs, it counts towards both men's total number of
-short-term mating encounters as well as women's, and both men and women
-have new short-term mates. Therefore, the total number of short-term
-mating experiences and short-term mates must be equal between
-heterosexual men and women at the population level. In a closed
-population with equal sex ratio, it follows that the average number of
-experiences and mates should also be equal between men and women.
-Following this line of reasoning, we would expect to observe no gender
-difference in short-term mating behaviors among heterosexual individuals
-even when there were gender differences in mating preferences.
+mating encounter occurs, both men's and women's total number of
+short-term mating experiences and the number of short-term mates
+increase by one. Therefore, the total number of short-term mating
+experiences and short-term mates must be equal between heterosexual men
+and women at the population level. In a closed population with equal sex
+ratio, it follows that the average number of experiences and mates
+should also be equal between men and women. Following this line of
+reasoning, we would expect to observe no gender difference in short-term
+mating behaviors among heterosexual individuals even when there were
+gender differences in mating preferences.
 
 However, it is important to note that although heterosexual men's total
-number of short-term mating is equal to that of women, this does not
-necessarily mean that the total number of men and women who have ever
-had short-term mating must be equal. Empirical studies have found that
-the proportion of individuals who are sexual inexperienced is slightly
-higher among men than women in most age groups above 18 years old
-(Ghaznavi et al., 2019; Haydon et al., 2014). As a postulation, there
-may be a smaller proportion of men (vs.~the proportion of women) who
-participate in the mating pool and contribute to the total number of
-short-term mating. For example, suppose that there is a population of 20
-individuals with an equal sex ratio. Heterosexual short-term mating has
-happened \(n\) times in this population, but only 3 men and 8 women have
-had any short-term mating experiences. Since the total number of
-short-term mating behaviors is the same between men and women, we would
-expect that in a population of individuals who had any short-term
-mating, the average number of short-term mating experiences and mates
-was higher among men than women (e.g., in the aforementioned example,
-the average number of short-term experiences is \(\frac{n}{3}\) for men
-and \(\frac{n}{8}\) for women who are in the mating pool).
+number of short-term matings would be equal to that of women, this does
+not necessarily mean that the total number of men and women who have
+ever had short-term mating must be equal. Empirical studies have found
+that the proportion of individuals who are sexually inexperienced is
+slightly higher among men than women in most age groups above 18 years
+old (Ghaznavi et al., 2019; Haydon et al., 2014). Therefore, as a
+postulation, there may be a smaller proportion of men (vs.~the
+proportion of women) who participate in the mating pool and contribute
+to the total number of short-term mating. For example, suppose that
+there is a population of 20 individuals with an equal sex ratio.
+Heterosexual short-term matings have happened \(n\) times in this
+population, but only 3 men and 8 women have had any short-term mating
+experiences. Since the total number of short-term mating behaviors is
+the same between men and women, we would expect that in a population of
+individuals who participate in the mating pool, the average numbers of
+short-term mating experiences and mates are higher among men than women
+(e.g., in the aforementioned example, the average number of short-term
+experiences is \(\frac{n}{3}\) for men and \(\frac{n}{8}\) for women who
+are in the mating pool).
 
 As a comparison, in the cases of gay men and lesbian women, men's
-preferences are not constrained by women's, but only by those of other
-men, who, arguably, have a similar high interest in short-term mating.
-This would allow for a more direct behavioral expression of men's mating
-preferences. The notion that gay men have less restricted preferences is
-borne out in the proportion of individuals who have engaged in
-extradyadic sex (Peplau et al., 2004). A study showed that the
-proportions of heterosexual men and women who had engaged in extradyadic
-sex were 26\% and 21\%, respectively, while the statistics among gay men
-and lesbian women were 82\% and 28\%, respectively (Peplau et al.,
-2004). Therefore, we would expect to observe gender differences in
-short-term mating behaviors between gay men and lesbian women. Moreover,
-we would also expect to find that gay men, compared to heterosexual men,
-engaged in more short-term mating behaviors due to less constraints on
-their mating preferences.
+preferences are not constrained by those of women's, but only by those
+of other men, who, arguably, have a similar high interest in short-term
+mating. This would allow for a more direct behavioral expression of
+men's mating preferences. The notion that gay men have less restricted
+preferences is born out in the proportion of individuals who have
+engaged in extradyadic sex (Peplau et al., 2004). A study showed that
+the proportions of heterosexual men and women who had engaged in
+extradyadic sex were 26\% and 21\%, respectively, while the numbers
+among gay men and lesbian women were 82\% and 28\%, respectively (Peplau
+et al., 2004). Therefore, we would expect to observe gender differences
+in short-term mating behaviors between gay men and lesbian women.
+Moreover, we would also expect to find that gay men would engage in more
+short-term mating behaviors compared to heterosexual men due to less
+constraints on gay men's mating preferences.
 
@@
 behavioral level and the psychological processes behind it was ignored,
-although we recognized gender differences may also exist in long-term
-mating strategy (Buss \& Schmitt, 1993; Buss \& Schmitt, 2019).
+although we recognized that gender differences may also exist in
+long-term mating strategy (Buss \& Schmitt, 1993; Buss \& Schmitt,
+2019).
 
@@
 sex's preferences would affect short-term mating behaviors. Individuals'
-sexual orientation was conceptualized in terms of behaviors only in our
-model. Heterosexual men had short-term mating or formed a long-term
-relationship only with women, while gay men only with other men, and
-mutatis mutandis for women.
-
-We formulated the following hypotheses in the present study: assuming
-gender differences in preferences for short-term mating, 1) there would
-be no gender differences in short-term mating behaviors between
-heterosexual men and women when the full population was considered, 2) a
-smaller proportion of heterosexual men (vs.~heterosexual women) had ever
-engaged in short-term mating, 3) in a population of heterosexual
-individuals who had any short-term mating, men had higher average number
-of short-term mating behaviors than women, 4) gay men would engage in
-more short-term mating behaviors compared to lesbian women, and 5) gay
-men would engage in more short-term mating behaviors compared to
-heterosexual men.
+sexual orientation was conceptualized as categorical in terms of
+behaviors only in our model. Heterosexual men had short-term mating or
+formed a long-term relationship only with women, while gay men only with
+other men, and mutatis mutandis for women.
+
+We formulated the following hypotheses: assuming gender differences in
+preferences for short-term mating, 1) there would be no gender
+differences in short-term mating behaviors between heterosexual men and
+women when considering the full population, 2) a smaller proportion of
+heterosexual men (vs.~heterosexual women) would have ever engaged in
+short-term mating, 3) in a population of heterosexual individuals who
+had any short-term mating, men would have a higher average number of
+short-term mating behaviors than women, 4) gay men would engage in more
+short-term mating behaviors compared to lesbian women, and 5) compared
+to heterosexual men.
 
@@
 population of men and women (\emph{N\textsubscript{men}} =
-\emph{N\textsubscript{women}} = 150) and among those who had engaged in
-any short-term mating.
+\emph{N\textsubscript{women}} = 150) and among those who had ever
+engaged in any short-term mating.
 
@@
 At each time step, agents first checked whether they were in a long-term
-relationship. If they were not in a long-term relationship, they set
-their heading randomly (if they were within the movement range from the
+relationship. If they were in a long-term relationship, they did not
+move. If they were not in a long-term relationship, they set their
+heading randomly (if they were within the movement range from the
 birthplace) or faced the birthplace (if they were out of the movement
 range from the birthplace) and moved by a random distance. The random
-distance was less than half of the movement range. If they were in a
-long-term relationship, they did not move. Then, the agents decided on
-whether to engage in short-term mating using the predetermined
-likelihood (either 25\% or 40\%).
+distance was less than half of the movement range. Then, the agents
+decided on whether to engage in short-term mating using the
+predetermined likelihood (either 25\% or 40\%).
 
@@
 Then, women randomly selected one man at the same location as their
-potential long-term partner. There was a 10\% of chance that a pair
-would form a long-term relationship. After forming a long-term
-relationship, both men and women changed to coupled status and
+potential long-term partner. There was a 10\% of chance that a pair of
+individuals would form a long-term relationship. After forming a
+long-term relationship, both men and women changed to coupled status and
 registered each other as their long-term partner.
@@
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The averages were calculated using the population of heterosexual men and women in the mating pool (proportion: \textit{M\textsubscript{men}} = 0.38, \textit{M\textsubscript{women}} = 0.51).}
+The means were calculated using the population of heterosexual men and women who successfully participated in the mating pool (proportion: \textit{M\textsubscript{men}} = 0.38, \textit{M\textsubscript{women}} = 0.51).}
   \label{fig:men_vs_women_inpool}
@@
 men did (Figure \ref{fig:hetero_vs_gay}). The average number of
-short-term mating experiences (as calculated using the full population
-of men) was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37)
-than among heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24),
+short-term mating experiences (calculated using the full population of
+men) was higher among gay men (\emph{M} = 2.63, \emph{SD} = 0.37) than
+among heterosexual men (\emph{M} = 1.43, \emph{SD} = 0.24),
 \emph{t}(4,998) = --134.87, \emph{p} \textless{} .001, Cohen's \emph{d}
 = 3.81, 95\% CI = --1.21 to --1.18. Similarly, the average number of
-short-term mates (as calculated using the full population of men) was
+short-term mates (calculated using the full population of men) was
 higher among gay men (\emph{M} = 1.72, \emph{SD} = 0.19) than among
@@
 
-\hypertarget{comparing-across-conditions}{%
-\subsection{Comparing across
-conditions}\label{comparing-across-conditions}}
+\hypertarget{experimental-conditions-giving-rise-to-gender-differences-in-short-term-mating-behaviors}{%
+\subsection{Experimental conditions giving rise to gender differences in
+short-term mating
+behaviors}\label{experimental-conditions-giving-rise-to-gender-differences-in-short-term-mating-behaviors}}
 
@@
 \small
-\item \textit{Note.} The averages were calculated with subsamples of men and women who had had engaged in short-term mating behaviors.
-See Supplementary Materials for the mean and standard deviation of sample sizes.
+\item \textit{Note.} The means were calculated with subsamples of men and women who had ever engaged in short-term mating behaviors.
+See Supplemental Materials for the mean and standard deviation of sample sizes.
 \end{tablenotes}
@@
 behaviors emerged both when they had different short-term mating
-likelihood and when their mating standards were different. Gay men
+likelihood and when they had different mating standards. Gay men
 (vs.~lesbian women) had a higher average number of short-term mating
@@
 hypotheses: 1) there would be no gender differences in short-term mating
-behaviors between heterosexual men and women when the full population
-was considered, 2) a smaller proportion of heterosexual men
-(vs.~heterosexual women) had ever engaged in short-term mating, 3) in a
-population of heterosexual individuals who had any short-term mating,
-men had higher average number of short-term mating behaviors than women,
-4) gay men would engage in more short-term mating behaviors compared to
-lesbian women, and 5) gay men would engage in more short-term mating
-behaviors compared to heterosexual men. The results from 1,000 time
-steps in a model simulating men and women's mating behaviors provided
-strong evidence in favor of our hypotheses. First of all, we found no
-gender differences in short-term mating behaviors between heterosexual
-men and women when the full population was considered. However, compared
-to heterosexual women, there was a smaller proportion of heterosexual
-men participating in the mating pool, but they had higher average
-numbers of short-term mating experiences and short-term mates. Secondly,
-as compared to lesbian women, gay men had higher average numbers of
-short-term mating experiences and short-term mates. Finally, gay men
-also had higher average numbers of short-term mating experiences and
-short-term mates as compared to heterosexual men.
-
-As expected, when the full population was considered, heterosexual men
-and women did not differ in short-term mating behaviors despite their
-differential preferences for short-term mating. This was because
-heterosexual men and women had an equal total number of both short-term
-mating experiences and short-term mates. This is not surprising since
-the sex ratio was 1:1 in our model. It therefore follows that the
-average number of short-term mating experiences and short-term mates
-must be equal between men and women as well. However, we did find that
-when we only looked at individuals in the mating pool (from which more
-men than women were excluded), men engaged in more short-term mating
-behaviors as compared to women. This was because there were more women
-than men in the mating pool, resulting in lower averages among
-heterosexual women despite the equal numbers of experiences and mates in
-total.
-
-Moreover, gender differences in short-term mating behaviors emerged when
-heterosexual men and women had different mating standards, but not when
-they had different short-term mating likelihood. When women had a higher
-standard than men did, less men than women in the population were above
-a potential partner's standard and thus had a chance to have sex with
-them. This contributed to the unequal number of men and women in the
-mating pool, which led to gender differences in short-term mating
-behaviors among this population. In comparison, even when men and women
-had different short-term mating likelihood, the probability of any pair
-of them ending up having sex is the product of their individual
-likelihood (since men and women made decisions independently). As this
-probability is the same for both parties, the gender difference in
-short-term mating likelihood did not translate into different behaviors.
+behaviors between heterosexual men and women when considering the full
+population, 2) a smaller proportion of heterosexual men
+(vs.~heterosexual women) would have ever engaged in short-term mating,
+3) in a population of heterosexual individuals who had any short-term
+mating, men would have a higher average number of short-term mating
+behaviors than women, 4) gay men would engage in more short-term mating
+behaviors compared to lesbian women, and 5) compared to heterosexual
+men. The results from 1,000 time steps in a model simulating men and
+women's mating behaviors provided strong evidence in favor of our
+hypotheses. First of all, we found no gender differences in short-term
+mating behaviors between heterosexual men and women when the full
+population was considered. However, compared to heterosexual women,
+there was a smaller proportion of heterosexual men participating in the
+mating pool, but they had higher average numbers of short-term mating
+experiences and short-term mates. Secondly, gay men had higher average
+numbers of short-term mating experiences and short-term mate compared to
+both lesbian women and heterosexual men.
+
+As expected, when all individuals in the population were considered,
+heterosexual men and women did not differ in short-term mating behaviors
+despite their differential preferences for short-term mating. This is
+not surprising since the sex ratio was 1:1 in our model. Heterosexual
+men and women had an equal total number of both short-term mating
+experiences and short-term mates. It therefore follows that the average
+number of short-term mating experiences and short-term mates must be
+equal between men and women as well. However, we did find that when we
+only looked at individuals in the mating pool (from which more men than
+women were excluded), men engaged in more short-term mating behaviors
+compared to women. This was because there were more women than men in
+the mating pool, resulting in lower averages among heterosexual women
+despite the equal numbers of experiences and mates in total.
+
+Moreover, gender differences in short-term mating behaviors emerged
+among individuals in the mating pool when heterosexual men and women had
+different mating standards, but not when they had different short-term
+mating likelihood. When women had a higher standard than men, less men
+than women in the population were above a potential partner's standard
+and thus had a chance to have sex with them. This contributed to the
+unequal number of men and women in the mating pool, which led to gender
+differences in short-term mating behaviors among this population. In
+comparison, when men and women had different short-term mating
+likelihood, the probability of any pair of them ending up having sex is
+always the product of their individual likelihood (since men and women
+made decisions independently). As this probability is the same for both
+parties, the gender difference in short-term mating likelihood did not
+translate into different behaviors.
 
@@
 deciding to have short-term mating, and the latter increased the
-probability of both meeting each other's standards, as compared to the
-case of a given lesbian couple.
+probability of both meeting each other's standards, compared to the case
+of a given lesbian couple.
 
@@
 model. The only difference was a change in the preferences of potential
-partners. When men's partners had a stronger preferences for short-term
+partners. When men's partners had stronger preferences for short-term
 mating (i.e., having men vs.~having women as potential partners), men
@@
 Using agent-based modeling to simulate short-term mating behaviors, we
-found when men (vs.~women) had a stronger preferences for short-term
+found when men (vs.~women) had stronger preferences for short-term
 mating, heterosexual men and women engaged in short-term mating
-behaviors to the same extent when the full population was considered,
-while men in the mating pool had more such behaviors than women in the
-mating pool. Gay men engaged in more short-term mating behaviors
-compared to both lesbian women and heterosexual men.
+behaviors to the same extent when all individuals in the population were
+considered. However, among individuals who participated in the mating
+pool, men had more such behaviors than women. Gay men engaged in more
+short-term mating behaviors compared to both lesbian women and
+heterosexual men.
 
@@
 depend on one's own preferences, but are also constrained by partners'
-preferences. Future research in human mating should not only focus on
-the psychological aspect but also pay attention to the interaction
-between individuals' psychology and its behavioral context. These
-results also cast doubt to the prevalent belief in the gender
-differences in short-term mating behaviors, especially among
-heterosexual individuals. Our findings suggest that there may be factors
-in the observation process, such as sampling bias, that contribute to
-the observed differences. Future research in human sexuality should note
-such possibilities and interpret any observed gender differences in
+preferences. Future research should not only focus on the psychological
+aspect of human mating but also pay attention to the interaction between
+individuals' psychology and its behavioral context. These results also
+cast doubt to the prevalent belief in the gender differences in
+short-term mating behaviors, especially among heterosexual individuals.
+Our findings suggest that there may be factors in the observation
+process, such as sampling bias, that contribute to the observed
+differences. Future research in human sexuality should note such
+possibilities and interpret any observed gender differences in
 short-term mating behaviors with caution.
@@
 
-We thank Gu Li and Jiannan Shi for providing helpful feedback in the
-development of this study.
+We thank {[}name masked for peer review{]} and {[}name masked for peer
+review{]} for providing helpful feedback in the development of this
+study. This research did not receive any specific grant from funding
+agencies in the public, commercial, or not-for-profit sectors.
 
@@
 
-All models, data, and analysis code can be downloaded at: {[}link masked
-for peer review{]}
+All model, data, and analysis code (including its history) are available
+at: {[}link masked for peer review{]}.
 

### 2022-06-10 submission/title_page.Rmd
added cover letter and title page, close #23

---
output:
  pdf_document
geometry: margin=1.0in
fontsize: 11pt
header-includes:
  - \newcommand{\bcenter}{\begin{center}}
  - \newcommand{\ecenter}{\end{center}}
  - \newcommand{\btitlepage}{\begin{titlepage}}
  - \newcommand{\etitlepage}{\end{titlepage}}
  - \usepackage{setspace}\doublespacing
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
---

\btitlepage

\bcenter

\vspace*{20mm}

# An Agent-Based Model of Gender and Sexual Orientation Differences in Short-Term Mating Behaviors as a Result of Mating Preferences {-}

\vspace{20mm}

Yurun Ying^a^^,^^$\dagger$^, Jan Antfolk^b^, Pekka Santtila^a^^,^^c^

^a^ Faculty of Arts and Sciences, NYU Shanghai, Shanghai, China

^b^ Faculty of Arts, Psychology and Theology, Åbo Akademi University, Turku, Finland

^c^ NYU-ECNU Institute for Social Development at NYU Shanghai, Shanghai, China

\ecenter

\vspace{30mm}

^$\dagger$^ To whom correspondence should be addressed: 1555 Century Avenue, Pudong New District, Shanghai, China, 200136. Email: [yurun.ying@nyu.edu](yurun.ying@nyu.edu).

\vspace{5mm}

**Declaration of Competing Interest:** We declare that there are no known competing interests that might have influenced the work reported in this paper.

\vspace{5mm}

Word count: 5103

\etitlepage

### 2022-07-21 submission/manuscript.Rmd
edit for resubmission to JSR, close #24

@@
     keep_tex: true
+    latex_engine: xelatex
   word_document: true
+mainfont: Times New Roman
 geometry: margin=1.0in
-fontsize: 11pt
-numbersections: true
+fontsize: 12pt
 bibliography: reference.bib
@@
   - \usepackage{setspace}\doublespacing
-  - \usepackage{helvet}
-  - \renewcommand*\familydefault{\sfdefault}
   - \usepackage{booktabs}
@@
 
-# Abstract {-}
+**Abstract**
 
@@
 
-# Introduction
+**Introduction**
 
@@
 
-## Gender differences in short-term mating preferences
+***Gender Differences in Short-term Mating Preferences***
 
@@
 
-## Constraints on men's preferences for short-term mating
+***Constraints on Men's Preferences for Short-term Mating***
 
@@
 
-## A simple model of short-term mating behaviors
+***A Simple Model of Short-term Mating Behaviors***
 
@@
 
+The present study contributed to the existing literature by explicitly investigating the causal consequences of mating preferences on mating behaviors.
+It also compared heterosexual and gay men's mating behaviors under the same set of assumptions regarding preferences.
 We formulated the following hypotheses: assuming gender differences in preferences for short-term mating, 1) there would be no gender differences in short-term mating behaviors between heterosexual men and women when considering the full population, 2) a smaller proportion of heterosexual men (vs.
@@
 
-# Material and methods
+\vspace{5mm}
 
-## Model Design
+**Materials and Methods**
+
+***Model Design***
 
@@
 
-## Experiment Design
+***Experiment Design***
 
@@
 
-## Model Schedule
+***Model Schedule***
 
-### Initial setup
+*Initial Setup*
+
 In total, 150 women and 150 men were created on the lattice at random locations.
@@
 
-### Procedures
-#### Procedures for heterosexual agents.
-At each time step, agents first checked whether they were in a long-term relationship.
+*Procedures*
+
+***Procedures for heterosexual agents.*** At each time step, agents first checked whether they were in a long-term relationship.
 If they were in a long-term relationship, they did not move.
@@
 
-#### Procedures for gay men and lesbian women agents.
-At each time step, men and women moved and decided on short-term mating as the agents did in the heterosexual case.
+***Procedures for gay men and lesbian women agents.*** At each time step, men and women moved and decided on short-term mating as the agents did in the heterosexual case.
 Half of the agents (75 men and 75 women) were also given an initiator status.
@@
 
-## Simulations
+***Simulations***
+
 The model was run for 1,000 time steps in each simulation.
@@
 
-## Statistical analyses
+***Statistical Analyses***
+
 Statistical analyses were conducted using `r R.version.string %>% str_replace(" \\(.*\\)", "")` [@r] and the figures were generated by the ggplot2 package [@ggplot2].
@@
 
-# Results
+\vspace{5mm}
 
-## Gender differences in short-term mating behaviors in the full population
+**Results**
+
+***Gender Differences in Short-term Mating Behaviors in the Full Population***
 
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=100mm]{figures/fig1_men_vs_women.pdf}
-  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women.
-Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
-Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The means were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
-  \label{fig:men_vs_women}
-\end{figure}
+[Figure 1 near here]
 
@@
 
-## Heterosexual individuals in the mating pool
+***Heterosexual Individuals in the Mating Pool***
 
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{figures/fig2_men_vs_women_inpool.pdf}
-  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
-Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool.
-Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The means were calculated using the population of heterosexual men and women who successfully participated in the mating pool (proportion: \textit{M\textsubscript{men}} = `r m_inpool.mean_011`, \textit{M\textsubscript{women}} = `r f_inpool.mean_011`).}
-  \label{fig:men_vs_women_inpool}
-\end{figure}
+[Figure 2 near here]
 
-## Comparing heterosexual and gay men
+***Comparing Heterosexual and Gay Men***
 
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{figures/fig3_hetero_vs_gay_men.pdf}
-  \caption{\textbf{Short-term mating behaviors of heterosexual men and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
-Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
-Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The means were calculated using the full population of heterosexual men and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
-  \label{fig:hetero_vs_gay}
-\end{figure}
+[Figure 3 near here]
 
-## Experimental conditions giving rise to gender differences in short-term mating behaviors
+***Experimental Conditions Giving Rise to Gender Differences in Short-term Mating Behaviors***
 
@@
 
-```{r table_1, include=TRUE, echo=FALSE}
-results %>%
-  filter(hls %in% c("0_0_0", "0_0_1", "0_1_0", "0_1_1")) %>%
-  select(m_exp_ip.mean, m_exp_ip.sd,
-         f_exp_ip.mean, f_exp_ip.sd, exp_ip.d,
-         m_partner_ip.mean, m_partner_ip.sd,
-         f_partner_ip.mean, f_partner_ip.sd, partner_ip.d) %>%
-  mutate(
-    exp_ip.d = abs(exp_ip.d),
-    partner_ip.d = abs(partner_ip.d)
-  ) %>%
-  mutate(across(where(is.numeric), inline_hook)) %>%
-  mutate(
-    condition =
-      c("Same likelihood*Same standard",
-        "Same likelihood*Different standard",
-        "Different likelihood*Same standard",
-        "Different likelihood*Different standard")
-  ) %>%
-  column_to_rownames("condition") %>%
-  kable(
-    digits = 2, format = "latex", booktabs = TRUE,
-    caption = "\\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model}",
-    row.names = TRUE, col.names = c(rep(c(rep(c("M", "SD"), 2), "d"), 2))
-    ) %>%
-  row_spec(0, italic = TRUE, align = "c") %>%
-  add_header_above(
-    c(" " = 1,
-      "Men" = 2, "Women" = 2, " " = 1,
-      "Men" = 2, "Women" = 2, " " = 1)
-    ) %>%
-  add_header_above(
-    c(" " = 1,
-      "Average short-term mating\nexperiences (in-pool)" = 5,
-      "Average short-term\nmates (in-pool)" = 5)
-    ) %>%
-  column_spec(1, width = "2in") %>%
-  footnote(
-    general = "\\\\textit{Note.} The means were calculated with subsamples of men and women who had ever engaged in short-term mating behaviors.
-See Supplemental Materials for the mean and standard deviation of sample sizes.",
-    general_title = "", escape = FALSE,
-    threeparttable = TRUE, fixed_small_size = TRUE) %>%
-  kable_styling(latex_options = "scale_down")
-```
+[Table 1 near here]
 
@@
 
-```{r table_2, include=TRUE, echo=FALSE}
-results %>%
-  filter(hls %in% c("1_0_0", "1_0_1", "1_1_0", "1_1_1")) %>%
-  select(m_exp_all.mean, m_exp_all.sd,
-         f_exp_all.mean, f_exp_all.sd, exp_all.d,
-         m_partner_all.mean, m_partner_all.sd,
-         f_partner_all.mean, f_partner_all.sd, partner_all.d) %>%
-  mutate(
-    exp_all.d = abs(exp_all.d),
-    partner_all.d = abs(partner_all.d)
-  ) %>%
-  mutate(across(where(is.numeric), inline_hook)) %>%
-  mutate(
-    condition =
-      c("Same likelihood*Same standard",
-        "Same likelihood*Different standard",
-        "Different likelihood*Same standard",
-        "Different likelihood*Different standard")
-  ) %>%
-  column_to_rownames("condition") %>%
-  kable(
-    digits = 2, format = "latex", booktabs = TRUE,
-    caption = "\\textbf{Short-term mating behaviors of gay men and lesbian women after 1,000 time steps in the model}",
-    row.names = TRUE, col.names = c(rep(c(rep(c("M", "SD"), 2), "d"), 2))
-    ) %>%
-  row_spec(0, italic = TRUE, align = "c") %>%
-  add_header_above(
-    c(" " = 1,
-      "Men" = 2, "Women" = 2, " " = 1,
-      "Men" = 2, "Women" = 2, " " = 1)
-    ) %>%
-  add_header_above(
-    c(" " = 1,
-      "Average short-term mating\nexperiences" = 5,
-      "Average short-term mates" = 5)
-    ) %>%
-  column_spec(1, width = "2in") %>%
-  footnote(
-    general = "\\\\textit{Note.} \\\\textit{N\\\\textsubscript{men}} = \\\\textit{N\\\\textsubscript{women}} = 150 in all conditions.",
-    general_title = "", escape = FALSE,
-    threeparttable = TRUE, fixed_small_size = TRUE) %>%
-  kable_styling(latex_options = "scale_down")
-```
+[Table 2 near here]
 
-# Discussion
+\vspace{5mm}
+
+**Discussion**
 
@@
 
-# Conclusion
+\vspace{5mm}
+
+**Conclusion**
 
@@
 
-# Acknowledgements
+\vspace{5mm}
+
+**Acknowledgements**
 
@@
 
-# Data availability
+\vspace{5mm}
+
+**Declaration of Competing Interest**
+
+We declare that there are no known competing interests that might have influenced the work reported in this paper.
+
+\vspace{5mm}
+
+**Data Availability**
 
@@
 
-# References {-}
+**References**
 
 <div id="refs"></div>
+
+\newpage
+
+```{r table_1, include=TRUE, echo=FALSE}
+results %>%
+  filter(hls %in% c("0_0_0", "0_0_1", "0_1_0", "0_1_1")) %>%
+  select(m_exp_ip.mean, m_exp_ip.sd,
+         f_exp_ip.mean, f_exp_ip.sd, exp_ip.d,
+         m_partner_ip.mean, m_partner_ip.sd,
+         f_partner_ip.mean, f_partner_ip.sd, partner_ip.d) %>%
+  mutate(
+    exp_ip.d = abs(exp_ip.d),
+    partner_ip.d = abs(partner_ip.d)
+  ) %>%
+  mutate(across(where(is.numeric), inline_hook)) %>%
+  mutate(
+    condition =
+      c("Same likelihood*Same standard",
+        "Same likelihood*Different standard",
+        "Different likelihood*Same standard",
+        "Different likelihood*Different standard")
+  ) %>%
+  column_to_rownames("condition") %>%
+  kable(
+    digits = 2, format = "latex", booktabs = TRUE,
+    caption = "\\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model}",
+    row.names = TRUE, col.names = c(rep(c(rep(c("M", "SD"), 2), "d"), 2))
+    ) %>%
+  row_spec(0, italic = TRUE, align = "c") %>%
+  add_header_above(
+    c(" " = 1,
+      "Men" = 2, "Women" = 2, " " = 1,
+      "Men" = 2, "Women" = 2, " " = 1)
+    ) %>%
+  add_header_above(
+    c(" " = 1,
+      "Average short-term mating\nexperiences (in-pool)" = 5,
+      "Average short-term\nmates (in-pool)" = 5)
+    ) %>%
+  column_spec(1, width = "2in") %>%
+  footnote(
+    general = "\\\\textit{Note.} The means were calculated with subsamples of men and women who had ever engaged in short-term mating behaviors.
+See Supplemental Materials for the mean and standard deviation of sample sizes.",
+    general_title = "", escape = FALSE,
+    threeparttable = TRUE, fixed_small_size = TRUE) %>%
+  kable_styling(latex_options = "scale_down")
+```
+
+```{r table_2, include=TRUE, echo=FALSE}
+results %>%
+  filter(hls %in% c("1_0_0", "1_0_1", "1_1_0", "1_1_1")) %>%
+  select(m_exp_all.mean, m_exp_all.sd,
+         f_exp_all.mean, f_exp_all.sd, exp_all.d,
+         m_partner_all.mean, m_partner_all.sd,
+         f_partner_all.mean, f_partner_all.sd, partner_all.d) %>%
+  mutate(
+    exp_all.d = abs(exp_all.d),
+    partner_all.d = abs(partner_all.d)
+  ) %>%
+  mutate(across(where(is.numeric), inline_hook)) %>%
+  mutate(
+    condition =
+      c("Same likelihood*Same standard",
+        "Same likelihood*Different standard",
+        "Different likelihood*Same standard",
+        "Different likelihood*Different standard")
+  ) %>%
+  column_to_rownames("condition") %>%
+  kable(
+    digits = 2, format = "latex", booktabs = TRUE,
+    caption = "\\textbf{Short-term mating behaviors of gay men and lesbian women after 1,000 time steps in the model}",
+    row.names = TRUE, col.names = c(rep(c(rep(c("M", "SD"), 2), "d"), 2))
+    ) %>%
+  row_spec(0, italic = TRUE, align = "c") %>%
+  add_header_above(
+    c(" " = 1,
+      "Men" = 2, "Women" = 2, " " = 1,
+      "Men" = 2, "Women" = 2, " " = 1)
+    ) %>%
+  add_header_above(
+    c(" " = 1,
+      "Average short-term mating\nexperiences" = 5,
+      "Average short-term mates" = 5)
+    ) %>%
+  column_spec(1, width = "2in") %>%
+  footnote(
+    general = "\\\\textit{Note.} \\\\textit{N\\\\textsubscript{men}} = \\\\textit{N\\\\textsubscript{women}} = 150 in all conditions.",
+    general_title = "", escape = FALSE,
+    threeparttable = TRUE, fixed_small_size = TRUE) %>%
+  kable_styling(latex_options = "scale_down")
+```
+
+\newpage
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=100mm]{figures/fig1_men_vs_women.pdf}
+  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women.
+Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
+Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
+The means were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
+  \label{fig:men_vs_women}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figures/fig2_men_vs_women_inpool.pdf}
+  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
+Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool.
+Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
+The means were calculated using the population of heterosexual men and women who successfully participated in the mating pool (proportion: \textit{M\textsubscript{men}} = `r m_inpool.mean_011`, \textit{M\textsubscript{women}} = `r f_inpool.mean_011`).}
+  \label{fig:men_vs_women_inpool}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figures/fig3_hetero_vs_gay_men.pdf}
+  \caption{\textbf{Short-term mating behaviors of heterosexual men and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
+Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
+Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
+The means were calculated using the full population of heterosexual men and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
+  \label{fig:hetero_vs_gay}
+\end{figure}

### 2022-07-21 submission/manuscript.tex
edit for resubmission to JSR, close #24

@@
 \documentclass[
-  11pt,
+  12pt,
 ]{article}
@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \setmainfont[]{Times New Roman}
 \fi
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \newlength{\cslhangindent}
@@
 \usepackage{setspace}\doublespacing
-\usepackage{helvet}
-\renewcommand*\familydefault{\sfdefault}
 \usepackage{booktabs}
@@
 
-\hypertarget{abstract}{%
-\section*{Abstract}\label{abstract}}
-\addcontentsline{toc}{section}{Abstract}
+\textbf{Abstract}
 
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\textbf{Introduction}
 
@@
 
-\hypertarget{gender-differences-in-short-term-mating-preferences}{%
-\subsection{Gender differences in short-term mating
-preferences}\label{gender-differences-in-short-term-mating-preferences}}
+\textbf{\emph{Gender Differences in Short-term Mating Preferences}}
 
@@
 
-\hypertarget{constraints-on-mens-preferences-for-short-term-mating}{%
-\subsection{Constraints on men's preferences for short-term
-mating}\label{constraints-on-mens-preferences-for-short-term-mating}}
+\textbf{\emph{Constraints on Men's Preferences for Short-term Mating}}
 
@@
 
-\hypertarget{a-simple-model-of-short-term-mating-behaviors}{%
-\subsection{A simple model of short-term mating
-behaviors}\label{a-simple-model-of-short-term-mating-behaviors}}
+\textbf{\emph{A Simple Model of Short-term Mating Behaviors}}
 
@@
 
-We formulated the following hypotheses: assuming gender differences in
-preferences for short-term mating, 1) there would be no gender
-differences in short-term mating behaviors between heterosexual men and
-women when considering the full population, 2) a smaller proportion of
-heterosexual men (vs.~heterosexual women) would have ever engaged in
-short-term mating, 3) in a population of heterosexual individuals who
-had any short-term mating, men would have a higher average number of
-short-term mating behaviors than women, 4) gay men would engage in more
-short-term mating behaviors compared to lesbian women, and 5) compared
-to heterosexual men.
-
-\hypertarget{material-and-methods}{%
-\section{Material and methods}\label{material-and-methods}}
-
-\hypertarget{model-design}{%
-\subsection{Model Design}\label{model-design}}
+The present study contributed to the existing literature by explicitly
+investigating the causal consequences of mating preferences on mating
+behaviors. It also compared heterosexual and gay men's mating behaviors
+under the same set of assumptions regarding preferences. We formulated
+the following hypotheses: assuming gender differences in preferences for
+short-term mating, 1) there would be no gender differences in short-term
+mating behaviors between heterosexual men and women when considering the
+full population, 2) a smaller proportion of heterosexual men
+(vs.~heterosexual women) would have ever engaged in short-term mating,
+3) in a population of heterosexual individuals who had any short-term
+mating, men would have a higher average number of short-term mating
+behaviors than women, 4) gay men would engage in more short-term mating
+behaviors compared to lesbian women, and 5) compared to heterosexual
+men.
+
+\vspace{5mm}
+
+\textbf{Materials and Methods}
+
+\textbf{\emph{Model Design}}
 
@@
 
-\hypertarget{experiment-design}{%
-\subsection{Experiment Design}\label{experiment-design}}
+\textbf{\emph{Experiment Design}}
 
@@
 
-\hypertarget{model-schedule}{%
-\subsection{Model Schedule}\label{model-schedule}}
-
-\hypertarget{initial-setup}{%
-\subsubsection{Initial setup}\label{initial-setup}}
+\textbf{\emph{Model Schedule}}
+
+\emph{Initial Setup}
 
@@
 
-\hypertarget{procedures}{%
-\subsubsection{Procedures}\label{procedures}}
-
-\hypertarget{procedures-for-heterosexual-agents.}{%
-\paragraph{Procedures for heterosexual
-agents.}\label{procedures-for-heterosexual-agents.}}
-
-At each time step, agents first checked whether they were in a long-term
-relationship. If they were in a long-term relationship, they did not
-move. If they were not in a long-term relationship, they set their
-heading randomly (if they were within the movement range from the
-birthplace) or faced the birthplace (if they were out of the movement
-range from the birthplace) and moved by a random distance. The random
-distance was less than half of the movement range. Then, the agents
-decided on whether to engage in short-term mating using the
-predetermined likelihood (either 25\% or 40\%).
+\emph{Procedures}
+
+\textbf{\emph{Procedures for heterosexual agents.}} At each time step,
+agents first checked whether they were in a long-term relationship. If
+they were in a long-term relationship, they did not move. If they were
+not in a long-term relationship, they set their heading randomly (if
+they were within the movement range from the birthplace) or faced the
+birthplace (if they were out of the movement range from the birthplace)
+and moved by a random distance. The random distance was less than half
+of the movement range. Then, the agents decided on whether to engage in
+short-term mating using the predetermined likelihood (either 25\% or
+40\%).
 
@@
 
-\hypertarget{procedures-for-gay-men-and-lesbian-women-agents.}{%
-\paragraph{Procedures for gay men and lesbian women
-agents.}\label{procedures-for-gay-men-and-lesbian-women-agents.}}
-
-At each time step, men and women moved and decided on short-term mating
-as the agents did in the heterosexual case. Half of the agents (75 men
-and 75 women) were also given an initiator status. The initiators
-checked to see whether there were other agents at the same location. The
-rest of the procedures were identical to the heterosexual procedures,
-except that the agents only chose those with the same gender as
-potential short-term mates or long-term partners.
-
-\hypertarget{simulations}{%
-\subsection{Simulations}\label{simulations}}
+\textbf{\emph{Procedures for gay men and lesbian women agents.}} At each
+time step, men and women moved and decided on short-term mating as the
+agents did in the heterosexual case. Half of the agents (75 men and 75
+women) were also given an initiator status. The initiators checked to
+see whether there were other agents at the same location. The rest of
+the procedures were identical to the heterosexual procedures, except
+that the agents only chose those with the same gender as potential
+short-term mates or long-term partners.
+
+\textbf{\emph{Simulations}}
 
@@
 
-\hypertarget{statistical-analyses}{%
-\subsection{Statistical analyses}\label{statistical-analyses}}
+\textbf{\emph{Statistical Analyses}}
 
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{gender-differences-in-short-term-mating-behaviors-in-the-full-population}{%
-\subsection{Gender differences in short-term mating behaviors in the
-full
-population}\label{gender-differences-in-short-term-mating-behaviors-in-the-full-population}}
+\vspace{5mm}
+
+\textbf{Results}
+
+\textbf{\emph{Gender Differences in Short-term Mating Behaviors in the
+Full Population}}
 
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=100mm]{figures/fig1_men_vs_women.pdf}
-  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women.
-Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
-Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The means were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
-  \label{fig:men_vs_women}
-\end{figure}
+{[}Figure 1 near here{]}
 
@@
 
-\hypertarget{heterosexual-individuals-in-the-mating-pool}{%
-\subsection{Heterosexual individuals in the mating
-pool}\label{heterosexual-individuals-in-the-mating-pool}}
+\textbf{\emph{Heterosexual Individuals in the Mating Pool}}
 
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{figures/fig2_men_vs_women_inpool.pdf}
-  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
-Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool.
-Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The means were calculated using the population of heterosexual men and women who successfully participated in the mating pool (proportion: \textit{M\textsubscript{men}} = 0.38, \textit{M\textsubscript{women}} = 0.51).}
-  \label{fig:men_vs_women_inpool}
-\end{figure}
-
-\hypertarget{comparing-heterosexual-and-gay-men}{%
-\subsection{Comparing heterosexual and gay
-men}\label{comparing-heterosexual-and-gay-men}}
+{[}Figure 2 near here{]}
+
+\textbf{\emph{Comparing Heterosexual and Gay Men}}
 
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{figures/fig3_hetero_vs_gay_men.pdf}
-  \caption{\textbf{Short-term mating behaviors of heterosexual men and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
-Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
-Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
-The means were calculated using the full population of heterosexual men and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
-  \label{fig:hetero_vs_gay}
-\end{figure}
-
-\hypertarget{experimental-conditions-giving-rise-to-gender-differences-in-short-term-mating-behaviors}{%
-\subsection{Experimental conditions giving rise to gender differences in
-short-term mating
-behaviors}\label{experimental-conditions-giving-rise-to-gender-differences-in-short-term-mating-behaviors}}
+{[}Figure 3 near here{]}
+
+\textbf{\emph{Experimental Conditions Giving Rise to Gender Differences
+in Short-term Mating Behaviors}}
 
@@
 (Table 1).
+
+{[}Table 1 near here{]}
+
+Among gay men and lesbian women, gender differences in short-term mating
+behaviors emerged both when they had different short-term mating
+likelihood and when they had different mating standards. Gay men
+(vs.~lesbian women) had a higher average number of short-term mating
+experiences and short-term mates when they had a higher short-term
+mating likelihood (experiences: \emph{M\textsubscript{men}} = 0.80,
+\emph{SD\textsubscript{men}} = 0.23, \emph{M\textsubscript{women}} =
+0.32, \emph{SD\textsubscript{women}} = 0.10, Cohen's \emph{d} = 2.67;
+partners: \emph{M\textsubscript{men}} = 0.52,
+\emph{SD\textsubscript{men}} = 0.13, \emph{M\textsubscript{women}} =
+0.25, \emph{SD\textsubscript{women}} = 0.07, Cohen's \emph{d} = 2.60),
+or when they had lower mating standards (experiences:
+\emph{M\textsubscript{men}} = 1.05, \emph{SD\textsubscript{men}} = 0.18,
+\emph{M\textsubscript{women}} = 0.32, \emph{SD\textsubscript{women}} =
+0.10, Cohen's \emph{d} = 5.10; partners: \emph{M\textsubscript{men}} =
+0.82, \emph{SD\textsubscript{men}} = 0.12, \emph{M\textsubscript{women}}
+= 0.25, \emph{SD\textsubscript{women}} = 0.07, Cohen's \emph{d} = 5.78).
+In comparison, virtually no gender differences in short-term mating
+behaviors existed when gay men and lesbian women had the same short-term
+mating likelihood and mating standards (Table 2).
+
+{[}Table 2 near here{]}
+
+\vspace{5mm}
+
+\textbf{Discussion}
+
+The present study used agent-based modeling to investigate whether men
+and women's differential preferences for short-term mating would result
+in gender differences in short-term mating behaviors, and if so, then
+under what conditions they would result in differences in the number of
+short-term mating experiences and short-term mates. We formulated five
+hypotheses: 1) there would be no gender differences in short-term mating
+behaviors between heterosexual men and women when considering the full
+population, 2) a smaller proportion of heterosexual men
+(vs.~heterosexual women) would have ever engaged in short-term mating,
+3) in a population of heterosexual individuals who had any short-term
+mating, men would have a higher average number of short-term mating
+behaviors than women, 4) gay men would engage in more short-term mating
+behaviors compared to lesbian women, and 5) compared to heterosexual
+men. The results from 1,000 time steps in a model simulating men and
+women's mating behaviors provided strong evidence in favor of our
+hypotheses. First of all, we found no gender differences in short-term
+mating behaviors between heterosexual men and women when the full
+population was considered. However, compared to heterosexual women,
+there was a smaller proportion of heterosexual men participating in the
+mating pool, but they had higher average numbers of short-term mating
+experiences and short-term mates. Secondly, gay men had higher average
+numbers of short-term mating experiences and short-term mate compared to
+both lesbian women and heterosexual men.
+
+As expected, when all individuals in the population were considered,
+heterosexual men and women did not differ in short-term mating behaviors
+despite their differential preferences for short-term mating. This is
+not surprising since the sex ratio was 1:1 in our model. Heterosexual
+men and women had an equal total number of both short-term mating
+experiences and short-term mates. It therefore follows that the average
+number of short-term mating experiences and short-term mates must be
+equal between men and women as well. However, we did find that when we
+only looked at individuals in the mating pool (from which more men than
+women were excluded), men engaged in more short-term mating behaviors
+compared to women. This was because there were more women than men in
+the mating pool, resulting in lower averages among heterosexual women
+despite the equal numbers of experiences and mates in total.
+
+Moreover, gender differences in short-term mating behaviors emerged
+among individuals in the mating pool when heterosexual men and women had
+different mating standards, but not when they had different short-term
+mating likelihood. When women had a higher standard than men, less men
+than women in the population were above a potential partner's standard
+and thus had a chance to have sex with them. This contributed to the
+unequal number of men and women in the mating pool, which led to gender
+differences in short-term mating behaviors among this population. In
+comparison, when men and women had different short-term mating
+likelihood, the probability of any pair of them ending up having sex is
+always the product of their individual likelihood (since men and women
+made decisions independently). As this probability is the same for both
+parties, the gender difference in short-term mating likelihood did not
+translate into different behaviors.
+
+In the light of these results, previous empirical observations of gender
+differences in short-term mating behaviors among heterosexual
+individuals (e.g., Petersen \& Hyde, 2010) appear perplexing (e.g.,
+Gurman, 1989). Possible explanations for these empirical results that
+seem illogical considering the simulation findings may have to do with
+features of the observation process. One possibility is sampling bias in
+the observations (e.g., Wiederman \& Dubois, 1998) since surveys
+regarding short-term mating behaviors may tend to attract individuals
+who already engage in such behaviors. Our results suggest that when this
+group of individuals is considered, there can be gender differences in
+short-term mating behaviors that do not exist in the full population. A
+second explanation is that heterosexual men and women's self-reported
+sexual behaviors are affected by social desirability bias due to gender
+norms. Men may overreport since having more sexual partners can show
+their masculinity and yield them reputation benefits, while women may
+underreport because this violates the chastity norm (Fisher, 2013). A
+third explanation is that men and women have different estimation
+strategies of their sexual experiences. Men may tend to approximate and
+round up, while women's tendency to count instances may lead to lower
+estimations (Brown \& Sinclair, 1999; Mitchell et al., 2019).
+
+Among gay men and lesbian women, large gender differences in short-term
+mating behaviors existed when men and women had differential preferences
+for short-term mating, which was in line with empirical observations
+(e.g., Peplau et al., 1997, 2004). This was likely because the number of
+short-term mating experiences and short-term mates no longer counted
+towards men and women simultaneously. Any gender differences in mating
+preferences would result in differences in behaviors. A closer look at
+the results did support this postulation. Both a difference in the
+likelihood of short-term mating and in mating standards alone resulted
+in gender differences in mating behaviors. This was likely because the
+former increased the probability of both parties of a given gay couple
+deciding to have short-term mating, and the latter increased the
+probability of both meeting each other's standards, compared to the case
+of a given lesbian couple.
+
+Also, as gay men's preferences for short-term mating were not
+constrained by those of women, we found that gay men engaged in more
+short-term mating behaviors compared to heterosexual men. This was
+consistent with the empirical literature (e.g., Peplau et al., 1997).
+Interestingly, gay men and heterosexual men had the same short-term
+mating likelihood and the same standards for short-term mates in our
+model. The only difference was a change in the preferences of potential
+partners. When men's partners had stronger preferences for short-term
+mating (i.e., having men vs.~having women as potential partners), men
+also appeared to engage in more short-term mating behaviors.
+
+\vspace{5mm}
+
+\textbf{Conclusion}
+
+Using agent-based modeling to simulate short-term mating behaviors, we
+found when men (vs.~women) had stronger preferences for short-term
+mating, heterosexual men and women engaged in short-term mating
+behaviors to the same extent when all individuals in the population were
+considered. However, among individuals who participated in the mating
+pool, men had more such behaviors than women. Gay men engaged in more
+short-term mating behaviors compared to both lesbian women and
+heterosexual men.
+
+These results highlight the distinction between preferences and
+behaviors in human mating. Individuals' mating behaviors do not only
+depend on one's own preferences, but are also constrained by partners'
+preferences. Future research should not only focus on the psychological
+aspect of human mating but also pay attention to the interaction between
+individuals' psychology and its behavioral context. These results also
+cast doubt to the prevalent belief in the gender differences in
+short-term mating behaviors, especially among heterosexual individuals.
+Our findings suggest that there may be factors in the observation
+process, such as sampling bias, that contribute to the observed
+differences. Future research in human sexuality should note such
+possibilities and interpret any observed gender differences in
+short-term mating behaviors with caution.
+
+\vspace{5mm}
+
+\textbf{Acknowledgements}
+
+We thank {[}name masked for peer review{]} and {[}name masked for peer
+review{]} for providing helpful feedback in the development of this
+study. This research did not receive any specific grant from funding
+agencies in the public, commercial, or not-for-profit sectors.
+
+\vspace{5mm}
+
+\textbf{Declaration of Competing Interest}
+
+We declare that there are no known competing interests that might have
+influenced the work reported in this paper.
+
+\vspace{5mm}
+
+\textbf{Data Availability}
+
+All model, data, and analysis code (including its history) are available
+at: {[}link masked for peer review{]}.
+
+\newpage
+
+\textbf{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-archer_reality_2019}{}}%
+Archer, J. (2019). The reality and evolutionary significance of human
+psychological sex differences. \emph{Biological Reviews}, \emph{94}(4),
+1381--1415. \url{https://doi.org/10.1111/brv.12507}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bailey_effects_1994}{}}%
+Bailey, J. M., Gaulin, S., Agyei, Y., \& Gladue, B. A. (1994). Effects
+of gender and sexual orientation on evolutionarily relevant aspects of
+human mating psychology. \emph{Journal of Personality and Social
+Psychology}, \emph{66}(6), 1081--1093.
+\url{https://doi.org/10.1037/0022-3514.66.6.1081}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brown_estimating_1999}{}}%
+Brown, N. R., \& Sinclair, R. C. (1999). Estimating number of lifetime
+sexual partners: Men and women do it differently. \emph{The Journal of
+Sex Research}, \emph{36}(3), 292--297.
+\url{https://doi.org/10.1080/00224499909551999}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bryant_relationship_1994}{}}%
+Bryant, A. S., \& Demian. (1994). Relationship characteristics of
+american gay and lesbian couples. \emph{Journal of Gay \& Lesbian Social
+Services}, \emph{1}(2), 101--117.
+\url{https://doi.org/10.1300/J041v01n02_06}
+
+\leavevmode\vadjust pre{\hypertarget{ref-buss_sexual_1993}{}}%
+Buss, D. M., \& Schmitt, D. P. (1993). Sexual strategies theory: An
+evolutionary perspective on human mating. \emph{Psychological Review},
+\emph{100}(2), 204--232.
+\url{https://doi.org/doi:10.1037/0033-295X.100.2.204d}
+
+\leavevmode\vadjust pre{\hypertarget{ref-buss2019mate}{}}%
+Buss, D. M., \& Schmitt, D. P. (2019). Mate preferences and their
+behavioral manifestations. \emph{Annual Review of Psychology},
+\emph{70}, 77--110.
+
+\leavevmode\vadjust pre{\hypertarget{ref-conley_women_2011}{}}%
+Conley, T. D., Moors, A. C., Matsick, J. L., Ziegler, A., \& Valentine,
+B. A. (2011). Women, men, and the bedroom: Methodological and conceptual
+insights that narrow, reframe, and eliminate gender differences in
+sexuality. \emph{Current Directions in Psychological Science},
+\emph{20}(5), 296--300. \url{https://doi.org/10.1177/0963721411418467}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fisher2013gender}{}}%
+Fisher, T. D. (2013). Gender roles and pressure to be truthful: The
+bogus pipeline modifies gender differences in sexual but not non-sexual
+behavior. \emph{Sex Roles}, \emph{68}(7), 401--414.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ghaznavi2019trends}{}}%
+Ghaznavi, C., Sakamoto, H., Yoneoka, D., Nomura, S., Shibuya, K., \&
+Ueda, P. (2019). Trends in heterosexual inexperience among young adults
+in japan: Analysis of national surveys, 1987--2015. \emph{BMC Public
+Health}, \emph{19}(1), 1--10.
+
+\leavevmode\vadjust pre{\hypertarget{ref-s_j_gurman_six_1989}{}}%
+Gurman, S. J. (1989). Six of one... \emph{Nature}, \emph{12}, 342.
+\url{https://www.nature.com/articles/342012d0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hald_receptivity_2010}{}}%
+Hald, G. M., \& Høgh-Olesen, H. (2010). Receptivity to sexual
+invitations from strangers of the opposite gender. \emph{Evolution and
+Human Behavior}, \emph{31}(6), 453--458.
+\url{https://doi.org/10.1016/j.evolhumbehav.2010.07.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-haydon2014prevalence}{}}%
+Haydon, A. A., Cheng, M. M., Herring, A. H., McRee, A.-L., \& Halpern,
+C. T. (2014). Prevalence and predictors of sexual inexperience in
+adulthood. \emph{Archives of Sexual Behavior}, \emph{43}(2), 221--230.
+
+\leavevmode\vadjust pre{\hypertarget{ref-herbenick_sexual_2017}{}}%
+Herbenick, D., Bowling, J., Fu, T.-C. (Jane)., Dodge, B., Guerra-Reyes,
+L., \& Sanders, S. (2017). Sexual diversity in the {United States}:
+Results from a nationally representative probability sample of adult
+women and men. \emph{{PLOS} {ONE}}, \emph{12}(7), e0181198.
+\url{https://doi.org/10.1371/journal.pone.0181198}
+
+\leavevmode\vadjust pre{\hypertarget{ref-kenrick_evolution_1990}{}}%
+Kenrick, D. T., Sadalla, E. K., Groth, G., \& Trost, M. R. (1990).
+Evolution, traits, and the stages of human courtship: Qualifying the
+parental investment model. \emph{Journal of Personality}, \emph{58}(1),
+97--116. \url{https://doi.org/10.1111/j.1467-6494.1990.tb00909.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-matsick_gender_2021}{}}%
+Matsick, J. L., Kruk, M., Conley, T. D., Moors, A. C., \& Ziegler, A.
+(2021). Gender similarities and differences in casual sex acceptance
+among lesbian women and gay men. \emph{Archives of Sexual Behavior},
+\emph{50}(3), 1151--1166.
+\url{https://doi.org/10.1007/s10508-020-01864-y}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mcburney_preferred_2005}{}}%
+McBurney, D. H., Zapp, D. J., \& Streeter, S. A. (2005). Preferred
+number of sexual partners: Tails of distributions and tales of mating
+systems. \emph{Evolution and Human Behavior}, \emph{26}(3), 271--278.
+\url{https://doi.org/10.1016/j.evolhumbehav.2004.09.005}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mitchell_why_2019}{}}%
+Mitchell, K. R., Mercer, C. H., Prah, P., Clifton, S., Tanton, C.,
+Wellings, K., \& Copas, A. (2019). Why do men report more opposite-sex
+sexual partners than women? Analysis of the gender discrepancy in a
+british national probability survey. \emph{The Journal of Sex Research},
+\emph{56}(1), 1--8. \url{https://doi.org/10.1080/00224499.2018.1481193}
+
+\leavevmode\vadjust pre{\hypertarget{ref-oliver_gender_1993}{}}%
+Oliver, M. B., \& Hyde, J. S. (1993). Gender differences in sexuality: A
+meta-analysis. \emph{Psychological Bulletin}, \emph{114}(1), 29--51.
+https://doi.org/\url{http://dx.doi.org/10.1037/0033-2909.114.1.29}
+
+\leavevmode\vadjust pre{\hypertarget{ref-peplau_national_1997}{}}%
+Peplau, L. A., Cochran, S. D., \& Mays, V. (1997). A national survey of
+the intimate relationships of african american lesbians and gay men: A
+look at commitment, satisfaction, sexual behavior, and {HIV} disease. In
+\emph{Ethnic and cultural diversity among lesbians and gay men} (pp.
+11--38). Sage Publications.
+
+\leavevmode\vadjust pre{\hypertarget{ref-peplau_sexuality_2004}{}}%
+Peplau, L. A., Fingerhut, A., \& Beals, K. P. (2004). Sexuality in the
+relationships of lesbians and gay men. In \emph{The handbook of
+sexuality in close relationships} (pp. 349--369). Lawrence Erlbaum
+Associates Publishers.
+
+\leavevmode\vadjust pre{\hypertarget{ref-petersen_meta-analytic_2010}{}}%
+Petersen, J. L., \& Hyde, J. S. (2010). A meta-analytic review of
+research on gender differences in sexuality, 1993--2007.
+\emph{Psychological Bulletin}, \emph{136}(1), 21--38.
+\url{https://doi.org/10.1037/a0017504}
+
+\leavevmode\vadjust pre{\hypertarget{ref-r}{}}%
+R Core Team. (2022). \emph{R: A language and environment for statistical
+computing}. R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-regan_minimum_1998}{}}%
+Regan, P. C. (1998). Minimum mate selection standards as a function of
+perceived mate value, relationship context, and gender. \emph{Journal of
+Psychology \& Human Sexuality}, \emph{10}(1), 53--73.
+\url{https://doi.org/10.1300/J056v10n01_04}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rissel_heterosexual_2014}{}}%
+Rissel, C., Badcock, P. B., Smith, A. M. A., Richters, J., Visser, R. O.
+de, Grulich, A. E., Simpson, J. M., Rissel, C., Badcock, P. B., Smith,
+A. M. A., Richters, J., Visser, R. O. de, Grulich, A. E., \& Simpson, J.
+M. (2014). Heterosexual experience and recent heterosexual encounters
+among {A}ustralian adults: The second {A}ustralian study of health and
+relationships. \emph{Sexual Health}, \emph{11}(5), 416--426.
+\url{https://doi.org/10.1071/SH14105}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schmitt_universal_2003}{}}%
+Schmitt, D. P. (2003). Universal sex differences in the desire for
+sexual variety: Tests from 52 nations, 6 continents, and 13 islands.
+\emph{Journal of Personality and Social Psychology}, \emph{85}(1), 85.
+\url{https://doi.org/10.1037/0022-3514.85.1.85}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schmitt_are_2001}{}}%
+Schmitt, D. P., Shackelford, T. K., \& Buss, D. M. (2001). Are men
+really more 'oriented' toward short-term mating than women? A critical
+review of theory and research. \emph{Psychology, Evolution \& Gender},
+\emph{3}(3), 211--239. \url{https://doi.org/10.1080/14616660110119331}
+
+\leavevmode\vadjust pre{\hypertarget{ref-symons_evolution_1979}{}}%
+Symons, D. (1979). \emph{The evolution of human sexuality}. Oxford
+University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-walter_sex_2020}{}}%
+Walter, K. V., Conroy-Beam, D., Buss, D. M., Asao, K., Sorokowska, A.,
+Sorokowski, P., Aavik, T., Akello, G., Alhabahba, M. M., Alm, C., Amjad,
+N., Anjum, A., Atama, C. S., Atamtürk Duyar, D., Ayebare, R., Batres,
+C., Bendixen, M., Bensafia, A., Bizumic, B., \ldots{} Zupančič, M.
+(2020). Sex differences in mate preferences across 45 countries: A
+large-scale replication. \emph{Psychological Science}, \emph{31}(4),
+408--423. \url{https://doi.org/10.1177/0956797620904154}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
+Wickham, H. (2016). \emph{{ggplot2: Elegant Graphics for Data
+Analysis}}. Springer-Verlag New York.
+\url{https://ggplot2.tidyverse.org}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wiederman_evolution_1998}{}}%
+Wiederman, M. W., \& Dubois, S. L. (1998). Evolution and sex differences
+in preferences for short-term mates: Results from a policy capturing
+study. \emph{Evolution and Human Behavior}, \emph{19}(3), 153--170.
+\url{https://doi.org/10.1016/S1090-5138(98)00006-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wilensky_1999}{}}%
+Wilensky, U. (1999). \emph{NetLogo}. Center for Connected Learning;
+Computer-Based Modeling. \url{http://ccl.northwestern.edu/netlogo/}
+
+\end{CSLReferences}
+
+\newpage
 
@@
 
-Among gay men and lesbian women, gender differences in short-term mating
-behaviors emerged both when they had different short-term mating
-likelihood and when they had different mating standards. Gay men
-(vs.~lesbian women) had a higher average number of short-term mating
-experiences and short-term mates when they had a higher short-term
-mating likelihood (experiences: \emph{M\textsubscript{men}} = 0.80,
-\emph{SD\textsubscript{men}} = 0.23, \emph{M\textsubscript{women}} =
-0.32, \emph{SD\textsubscript{women}} = 0.10, Cohen's \emph{d} = 2.67;
-partners: \emph{M\textsubscript{men}} = 0.52,
-\emph{SD\textsubscript{men}} = 0.13, \emph{M\textsubscript{women}} =
-0.25, \emph{SD\textsubscript{women}} = 0.07, Cohen's \emph{d} = 2.60),
-or when they had lower mating standards (experiences:
-\emph{M\textsubscript{men}} = 1.05, \emph{SD\textsubscript{men}} = 0.18,
-\emph{M\textsubscript{women}} = 0.32, \emph{SD\textsubscript{women}} =
-0.10, Cohen's \emph{d} = 5.10; partners: \emph{M\textsubscript{men}} =
-0.82, \emph{SD\textsubscript{men}} = 0.12, \emph{M\textsubscript{women}}
-= 0.25, \emph{SD\textsubscript{women}} = 0.07, Cohen's \emph{d} = 5.78).
-In comparison, virtually no gender differences in short-term mating
-behaviors existed when gay men and lesbian women had the same short-term
-mating likelihood and mating standards (Table 2).
-
 \begin{table}
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-The present study used agent-based modeling to investigate whether men
-and women's differential preferences for short-term mating would result
-in gender differences in short-term mating behaviors, and if so, then
-under what conditions they would result in differences in the number of
-short-term mating experiences and short-term mates. We formulated five
-hypotheses: 1) there would be no gender differences in short-term mating
-behaviors between heterosexual men and women when considering the full
-population, 2) a smaller proportion of heterosexual men
-(vs.~heterosexual women) would have ever engaged in short-term mating,
-3) in a population of heterosexual individuals who had any short-term
-mating, men would have a higher average number of short-term mating
-behaviors than women, 4) gay men would engage in more short-term mating
-behaviors compared to lesbian women, and 5) compared to heterosexual
-men. The results from 1,000 time steps in a model simulating men and
-women's mating behaviors provided strong evidence in favor of our
-hypotheses. First of all, we found no gender differences in short-term
-mating behaviors between heterosexual men and women when the full
-population was considered. However, compared to heterosexual women,
-there was a smaller proportion of heterosexual men participating in the
-mating pool, but they had higher average numbers of short-term mating
-experiences and short-term mates. Secondly, gay men had higher average
-numbers of short-term mating experiences and short-term mate compared to
-both lesbian women and heterosexual men.
-
-As expected, when all individuals in the population were considered,
-heterosexual men and women did not differ in short-term mating behaviors
-despite their differential preferences for short-term mating. This is
-not surprising since the sex ratio was 1:1 in our model. Heterosexual
-men and women had an equal total number of both short-term mating
-experiences and short-term mates. It therefore follows that the average
-number of short-term mating experiences and short-term mates must be
-equal between men and women as well. However, we did find that when we
-only looked at individuals in the mating pool (from which more men than
-women were excluded), men engaged in more short-term mating behaviors
-compared to women. This was because there were more women than men in
-the mating pool, resulting in lower averages among heterosexual women
-despite the equal numbers of experiences and mates in total.
-
-Moreover, gender differences in short-term mating behaviors emerged
-among individuals in the mating pool when heterosexual men and women had
-different mating standards, but not when they had different short-term
-mating likelihood. When women had a higher standard than men, less men
-than women in the population were above a potential partner's standard
-and thus had a chance to have sex with them. This contributed to the
-unequal number of men and women in the mating pool, which led to gender
-differences in short-term mating behaviors among this population. In
-comparison, when men and women had different short-term mating
-likelihood, the probability of any pair of them ending up having sex is
-always the product of their individual likelihood (since men and women
-made decisions independently). As this probability is the same for both
-parties, the gender difference in short-term mating likelihood did not
-translate into different behaviors.
-
-In the light of these results, previous empirical observations of gender
-differences in short-term mating behaviors among heterosexual
-individuals (e.g., Petersen \& Hyde, 2010) appear perplexing (e.g.,
-Gurman, 1989). Possible explanations for these empirical results that
-seem illogical considering the simulation findings may have to do with
-features of the observation process. One possibility is sampling bias in
-the observations (e.g., Wiederman \& Dubois, 1998) since surveys
-regarding short-term mating behaviors may tend to attract individuals
-who already engage in such behaviors. Our results suggest that when this
-group of individuals is considered, there can be gender differences in
-short-term mating behaviors that do not exist in the full population. A
-second explanation is that heterosexual men and women's self-reported
-sexual behaviors are affected by social desirability bias due to gender
-norms. Men may overreport since having more sexual partners can show
-their masculinity and yield them reputation benefits, while women may
-underreport because this violates the chastity norm (Fisher, 2013). A
-third explanation is that men and women have different estimation
-strategies of their sexual experiences. Men may tend to approximate and
-round up, while women's tendency to count instances may lead to lower
-estimations (Brown \& Sinclair, 1999; Mitchell et al., 2019).
-
-Among gay men and lesbian women, large gender differences in short-term
-mating behaviors existed when men and women had differential preferences
-for short-term mating, which was in line with empirical observations
-(e.g., Peplau et al., 1997, 2004). This was likely because the number of
-short-term mating experiences and short-term mates no longer counted
-towards men and women simultaneously. Any gender differences in mating
-preferences would result in differences in behaviors. A closer look at
-the results did support this postulation. Both a difference in the
-likelihood of short-term mating and in mating standards alone resulted
-in gender differences in mating behaviors. This was likely because the
-former increased the probability of both parties of a given gay couple
-deciding to have short-term mating, and the latter increased the
-probability of both meeting each other's standards, compared to the case
-of a given lesbian couple.
-
-Also, as gay men's preferences for short-term mating were not
-constrained by those of women, we found that gay men engaged in more
-short-term mating behaviors compared to heterosexual men. This was
-consistent with the empirical literature (e.g., Peplau et al., 1997).
-Interestingly, gay men and heterosexual men had the same short-term
-mating likelihood and the same standards for short-term mates in our
-model. The only difference was a change in the preferences of potential
-partners. When men's partners had stronger preferences for short-term
-mating (i.e., having men vs.~having women as potential partners), men
-also appeared to engage in more short-term mating behaviors.
-
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-Using agent-based modeling to simulate short-term mating behaviors, we
-found when men (vs.~women) had stronger preferences for short-term
-mating, heterosexual men and women engaged in short-term mating
-behaviors to the same extent when all individuals in the population were
-considered. However, among individuals who participated in the mating
-pool, men had more such behaviors than women. Gay men engaged in more
-short-term mating behaviors compared to both lesbian women and
-heterosexual men.
-
-These results highlight the distinction between preferences and
-behaviors in human mating. Individuals' mating behaviors do not only
-depend on one's own preferences, but are also constrained by partners'
-preferences. Future research should not only focus on the psychological
-aspect of human mating but also pay attention to the interaction between
-individuals' psychology and its behavioral context. These results also
-cast doubt to the prevalent belief in the gender differences in
-short-term mating behaviors, especially among heterosexual individuals.
-Our findings suggest that there may be factors in the observation
-process, such as sampling bias, that contribute to the observed
-differences. Future research in human sexuality should note such
-possibilities and interpret any observed gender differences in
-short-term mating behaviors with caution.
-
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-We thank {[}name masked for peer review{]} and {[}name masked for peer
-review{]} for providing helpful feedback in the development of this
-study. This research did not receive any specific grant from funding
-agencies in the public, commercial, or not-for-profit sectors.
-
-\hypertarget{data-availability}{%
-\section{Data availability}\label{data-availability}}
-
-All model, data, and analysis code (including its history) are available
-at: {[}link masked for peer review{]}.
-
 \newpage
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-archer_reality_2019}{}}%
-Archer, J. (2019). The reality and evolutionary significance of human
-psychological sex differences. \emph{Biological Reviews}, \emph{94}(4),
-1381--1415. \url{https://doi.org/10.1111/brv.12507}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bailey_effects_1994}{}}%
-Bailey, J. M., Gaulin, S., Agyei, Y., \& Gladue, B. A. (1994). Effects
-of gender and sexual orientation on evolutionarily relevant aspects of
-human mating psychology. \emph{Journal of Personality and Social
-Psychology}, \emph{66}(6), 1081--1093.
-\url{https://doi.org/10.1037/0022-3514.66.6.1081}
-
-\leavevmode\vadjust pre{\hypertarget{ref-brown_estimating_1999}{}}%
-Brown, N. R., \& Sinclair, R. C. (1999). Estimating number of lifetime
-sexual partners: Men and women do it differently. \emph{The Journal of
-Sex Research}, \emph{36}(3), 292--297.
-\url{https://doi.org/10.1080/00224499909551999}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bryant_relationship_1994}{}}%
-Bryant, A. S., \& Demian. (1994). Relationship characteristics of
-american gay and lesbian couples. \emph{Journal of Gay \& Lesbian Social
-Services}, \emph{1}(2), 101--117.
-\url{https://doi.org/10.1300/J041v01n02_06}
-
-\leavevmode\vadjust pre{\hypertarget{ref-buss_sexual_1993}{}}%
-Buss, D. M., \& Schmitt, D. P. (1993). Sexual strategies theory: An
-evolutionary perspective on human mating. \emph{Psychological Review},
-\emph{100}(2), 204--232.
-\url{https://doi.org/doi:10.1037/0033-295X.100.2.204d}
-
-\leavevmode\vadjust pre{\hypertarget{ref-buss2019mate}{}}%
-Buss, D. M., \& Schmitt, D. P. (2019). Mate preferences and their
-behavioral manifestations. \emph{Annual Review of Psychology},
-\emph{70}, 77--110.
-
-\leavevmode\vadjust pre{\hypertarget{ref-conley_women_2011}{}}%
-Conley, T. D., Moors, A. C., Matsick, J. L., Ziegler, A., \& Valentine,
-B. A. (2011). Women, men, and the bedroom: Methodological and conceptual
-insights that narrow, reframe, and eliminate gender differences in
-sexuality. \emph{Current Directions in Psychological Science},
-\emph{20}(5), 296--300. \url{https://doi.org/10.1177/0963721411418467}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fisher2013gender}{}}%
-Fisher, T. D. (2013). Gender roles and pressure to be truthful: The
-bogus pipeline modifies gender differences in sexual but not non-sexual
-behavior. \emph{Sex Roles}, \emph{68}(7), 401--414.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ghaznavi2019trends}{}}%
-Ghaznavi, C., Sakamoto, H., Yoneoka, D., Nomura, S., Shibuya, K., \&
-Ueda, P. (2019). Trends in heterosexual inexperience among young adults
-in japan: Analysis of national surveys, 1987--2015. \emph{BMC Public
-Health}, \emph{19}(1), 1--10.
-
-\leavevmode\vadjust pre{\hypertarget{ref-s_j_gurman_six_1989}{}}%
-Gurman, S. J. (1989). Six of one... \emph{Nature}, \emph{12}, 342.
-\url{https://www.nature.com/articles/342012d0}
-
-\leavevmode\vadjust pre{\hypertarget{ref-hald_receptivity_2010}{}}%
-Hald, G. M., \& Høgh-Olesen, H. (2010). Receptivity to sexual
-invitations from strangers of the opposite gender. \emph{Evolution and
-Human Behavior}, \emph{31}(6), 453--458.
-\url{https://doi.org/10.1016/j.evolhumbehav.2010.07.004}
-
-\leavevmode\vadjust pre{\hypertarget{ref-haydon2014prevalence}{}}%
-Haydon, A. A., Cheng, M. M., Herring, A. H., McRee, A.-L., \& Halpern,
-C. T. (2014). Prevalence and predictors of sexual inexperience in
-adulthood. \emph{Archives of Sexual Behavior}, \emph{43}(2), 221--230.
-
-\leavevmode\vadjust pre{\hypertarget{ref-herbenick_sexual_2017}{}}%
-Herbenick, D., Bowling, J., Fu, T.-C. (Jane)., Dodge, B., Guerra-Reyes,
-L., \& Sanders, S. (2017). Sexual diversity in the {United States}:
-Results from a nationally representative probability sample of adult
-women and men. \emph{{PLOS} {ONE}}, \emph{12}(7), e0181198.
-\url{https://doi.org/10.1371/journal.pone.0181198}
-
-\leavevmode\vadjust pre{\hypertarget{ref-kenrick_evolution_1990}{}}%
-Kenrick, D. T., Sadalla, E. K., Groth, G., \& Trost, M. R. (1990).
-Evolution, traits, and the stages of human courtship: Qualifying the
-parental investment model. \emph{Journal of Personality}, \emph{58}(1),
-97--116. \url{https://doi.org/10.1111/j.1467-6494.1990.tb00909.x}
-
-\leavevmode\vadjust pre{\hypertarget{ref-matsick_gender_2021}{}}%
-Matsick, J. L., Kruk, M., Conley, T. D., Moors, A. C., \& Ziegler, A.
-(2021). Gender similarities and differences in casual sex acceptance
-among lesbian women and gay men. \emph{Archives of Sexual Behavior},
-\emph{50}(3), 1151--1166.
-\url{https://doi.org/10.1007/s10508-020-01864-y}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcburney_preferred_2005}{}}%
-McBurney, D. H., Zapp, D. J., \& Streeter, S. A. (2005). Preferred
-number of sexual partners: Tails of distributions and tales of mating
-systems. \emph{Evolution and Human Behavior}, \emph{26}(3), 271--278.
-\url{https://doi.org/10.1016/j.evolhumbehav.2004.09.005}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mitchell_why_2019}{}}%
-Mitchell, K. R., Mercer, C. H., Prah, P., Clifton, S., Tanton, C.,
-Wellings, K., \& Copas, A. (2019). Why do men report more opposite-sex
-sexual partners than women? Analysis of the gender discrepancy in a
-british national probability survey. \emph{The Journal of Sex Research},
-\emph{56}(1), 1--8. \url{https://doi.org/10.1080/00224499.2018.1481193}
-
-\leavevmode\vadjust pre{\hypertarget{ref-oliver_gender_1993}{}}%
-Oliver, M. B., \& Hyde, J. S. (1993). Gender differences in sexuality: A
-meta-analysis. \emph{Psychological Bulletin}, \emph{114}(1), 29--51.
-https://doi.org/\url{http://dx.doi.org/10.1037/0033-2909.114.1.29}
-
-\leavevmode\vadjust pre{\hypertarget{ref-peplau_national_1997}{}}%
-Peplau, L. A., Cochran, S. D., \& Mays, V. (1997). A national survey of
-the intimate relationships of african american lesbians and gay men: A
-look at commitment, satisfaction, sexual behavior, and {HIV} disease. In
-\emph{Ethnic and cultural diversity among lesbians and gay men} (pp.
-11--38). Sage Publications.
-
-\leavevmode\vadjust pre{\hypertarget{ref-peplau_sexuality_2004}{}}%
-Peplau, L. A., Fingerhut, A., \& Beals, K. P. (2004). Sexuality in the
-relationships of lesbians and gay men. In \emph{The handbook of
-sexuality in close relationships} (pp. 349--369). Lawrence Erlbaum
-Associates Publishers.
-
-\leavevmode\vadjust pre{\hypertarget{ref-petersen_meta-analytic_2010}{}}%
-Petersen, J. L., \& Hyde, J. S. (2010). A meta-analytic review of
-research on gender differences in sexuality, 1993--2007.
-\emph{Psychological Bulletin}, \emph{136}(1), 21--38.
-\url{https://doi.org/10.1037/a0017504}
-
-\leavevmode\vadjust pre{\hypertarget{ref-r}{}}%
-R Core Team. (2022). \emph{R: A language and environment for statistical
-computing}. R Foundation for Statistical Computing.
-\url{https://www.R-project.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-regan_minimum_1998}{}}%
-Regan, P. C. (1998). Minimum mate selection standards as a function of
-perceived mate value, relationship context, and gender. \emph{Journal of
-Psychology \& Human Sexuality}, \emph{10}(1), 53--73.
-\url{https://doi.org/10.1300/J056v10n01_04}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rissel_heterosexual_2014}{}}%
-Rissel, C., Badcock, P. B., Smith, A. M. A., Richters, J., Visser, R. O.
-de, Grulich, A. E., Simpson, J. M., Rissel, C., Badcock, P. B., Smith,
-A. M. A., Richters, J., Visser, R. O. de, Grulich, A. E., \& Simpson, J.
-M. (2014). Heterosexual experience and recent heterosexual encounters
-among {A}ustralian adults: The second {A}ustralian study of health and
-relationships. \emph{Sexual Health}, \emph{11}(5), 416--426.
-\url{https://doi.org/10.1071/SH14105}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schmitt_universal_2003}{}}%
-Schmitt, D. P. (2003). Universal sex differences in the desire for
-sexual variety: Tests from 52 nations, 6 continents, and 13 islands.
-\emph{Journal of Personality and Social Psychology}, \emph{85}(1), 85.
-\url{https://doi.org/10.1037/0022-3514.85.1.85}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schmitt_are_2001}{}}%
-Schmitt, D. P., Shackelford, T. K., \& Buss, D. M. (2001). Are men
-really more 'oriented' toward short-term mating than women? A critical
-review of theory and research. \emph{Psychology, Evolution \& Gender},
-\emph{3}(3), 211--239. \url{https://doi.org/10.1080/14616660110119331}
-
-\leavevmode\vadjust pre{\hypertarget{ref-symons_evolution_1979}{}}%
-Symons, D. (1979). \emph{The evolution of human sexuality}. Oxford
-University Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-walter_sex_2020}{}}%
-Walter, K. V., Conroy-Beam, D., Buss, D. M., Asao, K., Sorokowska, A.,
-Sorokowski, P., Aavik, T., Akello, G., Alhabahba, M. M., Alm, C., Amjad,
-N., Anjum, A., Atama, C. S., Atamtürk Duyar, D., Ayebare, R., Batres,
-C., Bendixen, M., Bensafia, A., Bizumic, B., \ldots{} Zupančič, M.
-(2020). Sex differences in mate preferences across 45 countries: A
-large-scale replication. \emph{Psychological Science}, \emph{31}(4),
-408--423. \url{https://doi.org/10.1177/0956797620904154}
-
-\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
-Wickham, H. (2016). \emph{{ggplot2: Elegant Graphics for Data
-Analysis}}. Springer-Verlag New York.
-\url{https://ggplot2.tidyverse.org}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wiederman_evolution_1998}{}}%
-Wiederman, M. W., \& Dubois, S. L. (1998). Evolution and sex differences
-in preferences for short-term mates: Results from a policy capturing
-study. \emph{Evolution and Human Behavior}, \emph{19}(3), 153--170.
-\url{https://doi.org/10.1016/S1090-5138(98)00006-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wilensky_1999}{}}%
-Wilensky, U. (1999). \emph{NetLogo}. Center for Connected Learning;
-Computer-Based Modeling. \url{http://ccl.northwestern.edu/netlogo/}
-
-\end{CSLReferences}
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=100mm]{figures/fig1_men_vs_women.pdf}
+  \caption{\textbf{Short-term mating behaviors of men and women after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women.
+Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
+Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
+The means were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
+  \label{fig:men_vs_women}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figures/fig2_men_vs_women_inpool.pdf}
+  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
+Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool.
+Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
+The means were calculated using the population of heterosexual men and women who successfully participated in the mating pool (proportion: \textit{M\textsubscript{men}} = 0.38, \textit{M\textsubscript{women}} = 0.51).}
+  \label{fig:men_vs_women_inpool}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figures/fig3_hetero_vs_gay_men.pdf}
+  \caption{\textbf{Short-term mating behaviors of heterosexual men and gay men after 1,000 time steps in the model when gender differences existed in mating preferences.} Violin plots summarizing the outcome variables.
+Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
+Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar.
+The means were calculated using the full population of heterosexual men and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
+  \label{fig:hetero_vs_gay}
+\end{figure}
 

### 2022-07-21 submission/title_page.Rmd
edit for resubmission to JSR, close #24

@@
 output:
-  pdf_document
+  pdf_document:
+    latex_engine: xelatex
+mainfont: Times New Roman
 geometry: margin=1.0in
-fontsize: 11pt
+fontsize: 12pt
 header-includes:
@@
   - \usepackage{setspace}\doublespacing
-  - \usepackage{helvet}
-  - \renewcommand*\familydefault{\sfdefault}
 ---
@@
 
-**Declaration of Competing Interest:** We declare that there are no known competing interests that might have influenced the work reported in this paper.
-
-\vspace{5mm}
-
 Word count: 5103

### 2022-07-21 code/plot_hetero_vs_gay_men.R

@@ -2,7 +2,7 @@
 
 # name: plot_hetero_vs_gay_men.R
 # input: data/processed/casual_sex_sim.csv
-# output: submission/figures/fig3_hetero_vs_gay_men.pdf
+# output: submission/figures/fig3_hetero_vs_gay_men.pdf submission/figures/fig3_hetero_vs_gay_men.jpeg
 # notes: none
 
 # load libraries
@@ -12,7 +12,7 @@ args <- commandArgs(trailingOnly = TRUE)
 #args <- c("data/processed/casual_sex_sim.csv", "submission/figures/fig3_hetero_vs_gay_men.pdf")
 
 input_file <- args[1]
-output_file <- args[2]
+output_file <- args[-1]
 
 # read file
 casual_tib <- here(input_file) %>% 
@@ -75,4 +75,6 @@ casual_tib %>%
     legend.text = element_text(size = 12)
   )
 
-ggsave(output_file, width = 9, height = 5)
+ggsave(output_file[1], width = 9, height = 5)
+
+ggsave(output_file[2], width = 9, height = 5)

### 2022-07-21 code/plot_men_vs_women.R

@@ -2,7 +2,7 @@
 
 # name: plot_men_vs_women.R
 # input: data/processed/casual_sex_sim.csv
-# output: submission/figures/fig1_men_vs_women.pdf
+# output: submission/figures/fig1_men_vs_women.pdf submission/figures/fig1_men_vs_women.jpeg
 # notes: none
 
 # load libraries
@@ -12,7 +12,7 @@ args <- commandArgs(trailingOnly = TRUE)
 #args <- c("data/processed/casual_sex_sim.csv", "submission/figures/fig1_men_vs_women.pdf")
 
 input_file <- args[1]
-output_file <- args[2]
+output_file <- args[-1]
 
 # read file
 casual_tib <- here(input_file) %>% 
@@ -79,4 +79,6 @@ casual_tib %>%
     legend.box.spacing = unit(0, "npc")
   )
 
-ggsave(output_file, width = 5, height = 6)
+ggsave(output_file[1], width = 5, height = 6)
+
+ggsave(output_file[2], width = 5, height = 6)

### 2022-07-21 code/plot_men_vs_women_inpool.R

@@ -2,7 +2,7 @@
 
 # name: plot_men_vs_women_inpool.R
 # input: data/processed/casual_sex_sim.csv
-# output: submission/figures/fig1_men_vs_women_inpool.pdf
+# output: submission/figures/fig2_men_vs_women_inpool.pdf submission/figures/fig2_men_vs_women_inpool.jpeg
 # notes: none
 
 # load libraries
@@ -12,7 +12,7 @@ args <- commandArgs(trailingOnly = TRUE)
 #args <- c("data/processed/casual_sex_sim.csv", "submission/figures/fig2_men_vs_women_inpool.pdf")
 
 input_file <- args[1]
-output_file <- args[2]
+output_file <- args[-1]
 
 # read file
 casual_tib <- here(input_file) %>% 
@@ -77,4 +77,6 @@ casual_tib %>%
     legend.text = element_text(size = 12)
   )
 
-ggsave(output_file, width = 9, height = 5)
+ggsave(output_file[1], width = 9, height = 5)
+
+ggsave(output_file[2], width = 9, height = 5)

### 2022-11-17 submission/supplemental_materials.Rmd
added sensitivity analyses into supplemental materials, close #28

@@
 numbersections: false
-indent: true
 bibliography: reference.bib
@@
 header-includes:
+  - \usepackage{lscape}
+  - \newcommand{\blandscape}{\begin{landscape}}
+  - \newcommand{\elandscape}{\end{landscape}}
   - \newcommand{\bcenter}{\begin{center}}
@@
   - \usepackage[font=small,labelfont=bf]{caption}
-  - \usepackage{indentfirst}
   - \pagenumbering{gobble}
@@
 
+# main analyses results
 results_inpool <-
@@
   read_csv() %>%
-  rename(hls = homosexual_dlikelihood_dstandard) %>%
+  rename(hls = homosexual_dlikelihood_dstandard_lt) %>%
   mutate(across(.col = c(f_inpool.mean:m_outpool.sd,
@@
   filter(str_detect(hls, "^0"))
+
+# sensitivity analyses results
+sa_results <-
+  here("data/processed/sa_des_and_test_result.csv") %>%
+  read_csv() %>%
+  rename(hls = homosexual_dlikelihood_dstandard_lt) %>%
+  mutate(across(.col = c(f_inpool.mean:m_outpool.sd,
+                inpool.conf.low:inpool.conf.high,
+                outpool.conf.low:outpool.conf.high),
+                ~ .x/150)) %>%
+  mutate(across(contains("p.value"), ~format(.x, digits = 2, nsmall = 3))) %>%
+  mutate(across(contains("p.value"), ~ ifelse(.x >= .001,
+                                              str_remove(.x, "^0"),
+                                              "< .001")
+                                              ))
+
+sa_results_hg <-
+  here("data/processed/sa_compare_hetero_gay_men.csv") %>%
+  read_csv() %>%
+  rename(ls = dlikelihood_dstandard_lt) %>%
+  mutate(across(contains("p.value"), ~format(.x, digits = 2, nsmall = 3))) %>%
+  mutate(across(contains("p.value"), ~ ifelse(.x >= .001,
+                                              str_remove(.x, "^0"),
+                                              "< .001")
+                                              ))
 
@@
 
-## Overview, Design Concepts, and Details of the Model
+## A. Overview, Design Concepts, and Details of the Model
 
@@
     \item Set number-of-partner-short the length of short-term-history
-    \item If short-term-likelihood equals male-/female-short-term-likelihood, set short-term-likelihood to a third of its value
+    \item If coupled? is true and short-term-likelihood equals male-/female-short-term-likelihood, set short-term-likelihood to a third of its value
   \end{enumerate}
@@
 
-\noindent \textbf{Supplemental Table 3:} Mean proportion of heterosexual men and women in the mating pool and its standard deviation after 1,000 time steps in the model.
+\bcenter
+
+## B. Additional Analyses
+
+\ecenter
+
+\textbf{Supplemental Table B1: Mean proportion of heterosexual men and women in the mating pool and its standard deviation after 1,000 time steps in the model.}
 
@@
 
+\bcenter
+
+## C. Sensitivity Analyses
+
+\ecenter
+
+\renewcommand{\tablename}{Supplemental Table}
+\renewcommand{\figurename}{Supplemental Figure}
+
+This section presents the results from sensitivity analyses to complement the main results presented in the paper.
+We set the parameter long-term-likelihood to 0, 2, 4, 6, 8, and repeated the same set of statistical analyses as the main study for each value.
+This was to show that the results were robust across different assumptions on the rate of forming long-term relationship.
+The simulations for sensitivity analyses adopted the same experimental designs but was run only 100 times for each set of parameter setting.
+
+### Sensitivity Analysis on Gender Differences in Short-term Mating Behaviors in the Full Population
+
+\newpage
+
+\renewcommand{\thefigure}{C1}
+\begin{figure}[h]
+  \centering
+  \includegraphics{figures/sa_fig1_men_vs_women.pdf}
+  \caption{\textbf{Short-term mating behaviors of men and women for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences.} Line plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women.
+Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
+The points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar in some sets of parameter setting.
+The means were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
+  \label{fig:men_vs_women}
+\end{figure}
+
+```{r table_1, include=FALSE, echo=FALSE}
+# note the following code is tentative and the latex code of the table is mannually editted
+sa_results %>%
+  filter(str_detect(hls, pattern = "^(.)_1_1_(.)")) %>% 
+  mutate(
+    exp_all.d = abs(exp_all.d),
+    partner_all.d = abs(partner_all.d)
+  ) %>%
+  mutate(across(where(is.numeric), inline_hook)) %>%
+  unite(exp_all.conf.low, exp_all.conf.high, sep = ", ",
+        col = "exp_all.conf") %>% 
+  unite(partner_all.conf.low, partner_all.conf.high, sep = ", ",
+        col = "partner_all.conf") %>% 
+  mutate(
+    condition = seq(1, 10, by = 1),
+    exp_all.conf = paste0("[", exp_all.conf, "]"),
+    partner_all.conf = paste0("[", partner_all.conf, "]")
+    ) %>%
+  select(condition, m_exp_all.mean, m_exp_all.sd,
+         f_exp_all.mean, f_exp_all.sd, 
+         exp_all.conf, exp_all.d,
+         m_partner_all.mean, m_partner_all.sd,
+         f_partner_all.mean, f_partner_all.sd, 
+         partner_all.conf, partner_all.d)%>%
+  column_to_rownames("condition") %>%
+  kable(
+    digits = 2, format = "latex", booktabs = TRUE,
+    caption = "\\textbf{Short-term mating behaviors of men and women for 0-8 long-term relationship likelihood when gender differences existed in mating preferences}",
+    row.names = TRUE, 
+    col.names = c(rep(c(rep(c("M", "SD"), 2), "Difference CI [LL, UL]","d"), 2))
+    ) %>%
+  row_spec(0, italic = TRUE, align = "c") %>%
+  add_header_above(
+    c(" " = 1,
+      "Men" = 2, "Women" = 2, " " = 2,
+      "Men" = 2, "Women" = 2, " " = 2)
+    ) %>%
+  add_header_above(
+    c(" " = 1,
+      "Average short-term mating\nexperiences" = 6,
+      "Average short-term\nmates" = 6)
+    ) %>%
+  column_spec(1, width = "0.5in") %>%
+  footnote(
+    general = "\\\\textit{Note.} The means were calculated using the full population of men and women in the model (\\\\textit{N\\\\textsubscript{men}} = \\\\textit{N\\\\textsubscript{women}} = 150).",
+    general_title = "", escape = FALSE,
+    threeparttable = TRUE, fixed_small_size = TRUE) %>% 
+  kable_styling(latex_options = "scale_down")
+```
+
+\newpage
+
+\blandscape
+
+\begingroup
+\renewcommand{\arraystretch}{1.5}
+
+\renewcommand{\thetable}{C1}
+\begin{table}
+
+\caption{\textbf{Short-term mating behaviors of men and women for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences}}
+\centering
+\begin{threeparttable}
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{0.5in}cccccccccccc}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Average short-term mating experiences} & \multicolumn{6}{c}{Average short-term mates} \\
+\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{2}{c}{ } \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11}
+\multicolumn{1}{c}{\makecell[c]{Long-term\\Likelihood (\%)}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\makecell[c]{Mean difference\\95\%CI [LL, UL]}} & \multicolumn{1}{c}{\makecell[c]{Cohen's \\ \em{d}}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\makecell[c]{Mean difference\\95\%CI [LL, UL]}} & \multicolumn{1}{c}{\makecell[c]{Cohen's \\ \em{d}}}\\
+\midrule
+\multicolumn{13}{l}{\textit{Experiment 1: Heterosexual individuals}} \\
+\multicolumn{1}{c}{0} & 5.94 & 0.61 & 5.94 & 0.61 & {}[–0.17, 0.17] & 0.00 & 3.43 & 0.34 & 3.43 & 0.34 & {}[–0.10, 0.10] & 0.00\\
+\multicolumn{1}{c}{2} & 2.57 & 0.30 & 2.57 & 0.30 & {}[–0.08, 0.08] & 0.00 & 1.65 & 0.17 & 1.65 & 0.17 & {}[–0.05, 0.05] & 0.00\\
+\multicolumn{1}{c}{4} & 1.97 & 0.29 & 1.97 & 0.29 & {}[–0.08, 0.08] & 0.00 & 1.23 & 0.15 & 1.23 & 0.15 & {}[–0.04, 0.04] & 0.00\\
+\multicolumn{1}{c}{6} & 1.66 & 0.27 & 1.66 & 0.27 & {}[–0.07, 0.07] & 0.00 & 1.02 & 0.13 & 1.02 & 0.13 & {}[–0.04, 0.04] & 0.00\\
+\multicolumn{1}{c}{8} & 1.53 & 0.26 & 1.53 & 0.26 & {}[–0.07, 0.07] & 0.00 & 0.88 & 0.12 & 0.88 & 0.12 & {}[–0.03, 0.03] & 0.00\\
+\addlinespace
+\multicolumn{13}{l}{\textit{Experiment 2: Gay men and lesbian women}} \\
+\multicolumn{1}{c}{0} & 8.75 & 0.76 & 1.09 & 0.21 & {}[–7.81, –7.50] & 13.71 & 5.42 & 0.43 & 0.88 & 0.16 & {}[–4.64, –4.46] & 14.04\\
+\multicolumn{1}{c}{2} & 5.02 & 0.48 & 0.61 & 0.16 & {}[–4.51, –4.31] & 12.45 & 3.38 & 0.30 & 0.51 & 0.13 & {}[–2.93, –2.80] & 12.20\\
+\multicolumn{1}{c}{4} & 3.92 & 0.47 & 0.45 & 0.12 & {}[–3.56, –3.37] & 10.04 & 2.67 & 0.28 & 0.37 & 0.09 & {}[–2.35, –2.23] & 10.90\\
+\multicolumn{1}{c}{6} & 3.22 & 0.43 & 0.40 & 0.11 & {}[–2.91, –2.73] & 8.95 & 2.21 & 0.26 & 0.33 & 0.08 & {}[–1.94, –1.83] & 9.95\\
+\multicolumn{1}{c}{8} & 2.88 & 0.39 & 0.36 & 0.09 & {}[–2.60, –2.44] & 8.80 & 1.92 & 0.22 & 0.28 & 0.07 & {}[–1.68, –1.59] & 10.12\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\small
+\item \textit{Note.} \textit{M} = Mean.
+\textit{SD} = Standard deviation.
+CI = Confidence interval.
+LL = Lower limit.
+UL = Upper limit.
+The means were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\endgroup
+
+\elandscape
+
+\newpage
+
+### Sensitivity Analysis on Heterosexual Individuals in the Mating Pool
+
+\renewcommand{\thefigure}{C2}
+\begin{figure}[h]
+  \centering
+  \includegraphics{figures/sa_fig2_men_vs_women_inpool.pdf}
+  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences.} Line plots summarizing the outcome variables.
+Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool.
+Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar in some sets of parameter setting.
+The means were calculated using the population of heterosexual men and women who successfully participated in the mating pool (See Table C2 for the mean and standard deviation of the proportion of individuals in the mating pool).}
+  \label{fig:men_vs_women_inpool}
+\end{figure}
+
+\newpage
+
+\blandscape
+
+```{r table_2, include=FALSE, echo=FALSE}
+sa_results %>%
+  filter(str_detect(hls, pattern = "^0_1_1")) %>%
+  mutate(
+    inpool.d = abs(inpool.d),
+    exp_ip.d = abs(exp_ip.d),
+    partner_ip.d = abs(partner_ip.d)
+  ) %>%
+  mutate(across(where(is.numeric), inline_hook)) %>%
+  unite(inpool.conf.low, inpool.conf.high, sep = ", ",
+        col = "inpool.conf") %>% 
+  unite(exp_ip.conf.low, exp_ip.conf.high, sep = ", ",
+        col = "exp_ip.conf") %>% 
+  unite(partner_ip.conf.low, partner_ip.conf.high, sep = ", ",
+        col = "partner_ip.conf") %>% 
+  mutate(
+    condition = seq(0, 8, by = 2),
+    inpool.conf = paste0("[", inpool.conf, "]"),
+    exp_ip.conf = paste0("[", exp_ip.conf, "]"),
+    partner_ip.conf = paste0("[", partner_ip.conf, "]")
+    ) %>%
+  select(condition, 
+         m_inpool.mean, m_inpool.sd,
+         f_inpool.mean, f_inpool.sd,
+         inpool.conf, inpool.d,
+         m_exp_ip.mean, m_exp_ip.sd,
+         f_exp_ip.mean, f_exp_ip.sd, 
+         exp_ip.conf, exp_ip.d,
+         m_partner_ip.mean, m_partner_ip.sd,
+         f_partner_ip.mean, f_partner_ip.sd, 
+         partner_ip.conf, partner_ip.d) %>%
+  column_to_rownames("condition") %>%
+  kable(
+    digits = 2, format = "latex", booktabs = TRUE,
+    caption = "\\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool for 0-8 long-term relationship likelihood when gender differences existed in mating preferences}",
+    row.names = TRUE, 
+    col.names = c(rep(c(rep(c("M", "SD"), 2), "Mean difference 95 CI [LL, UL]","d"), 3))
+    ) %>%
+  row_spec(0, italic = TRUE, align = "c") %>%
+  add_header_above(
+    c(" " = 1,
+      "Men" = 2, "Women" = 2, " " = 2,
+      "Men" = 2, "Women" = 2, " " = 2,
+      "Men" = 2, "Women" = 2, " " = 2)
+    ) %>%
+  add_header_above(
+    c(" " = 1,
+      "Mean proportion of individuals in the mating pool" = 6,
+      "Average short-term mating experiences (in-pool)" = 6,
+      "Average short-term mates (in-pool)" = 6)
+    ) %>%
+  column_spec(1, width = "0.5in") %>%
+  footnote(
+    general = "\\\\textit{Note.} \\\\textit{M} = Mean.
+\\\\textit{SD} = Standard deviation.
+CI = Confidence interval.
+LL = Lower limit.
+UL = Upper limit.
+The means were calculated with subsamples of men and women who had ever engaged in short-term mating behaviors.",
+    general_title = "", escape = FALSE,
+    threeparttable = TRUE, fixed_small_size = TRUE) %>% 
+  kable_styling(latex_options = "scale_down")
+```
+
+\begingroup
+\renewcommand{\arraystretch}{1.5}
+
+\renewcommand{\thetable}{C2}
+\begin{table}
+
+\caption{\textbf{Proportion and short-term mating behaviors of heterosexual men and women in the mating pool for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences}}
+\centering
+\begin{threeparttable}
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{0.3in}cccccccccccccccccc}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Mean proportion of individuals in the mating pool} & \multicolumn{6}{c}{Average short-term mating experiences (in-pool)} & \multicolumn{6}{c}{Average short-term mates (in-pool)} \\
+\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13} \cmidrule(l{3pt}r{3pt}){14-19}
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{2}{c}{ } \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){14-15} \cmidrule(l{3pt}r{3pt}){16-17}
+\multicolumn{1}{c}{\makecell[c]{Long-term\\Likelihood\\(\%)}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\makecell[c]{Mean difference\\95\%CI [LL, UL]}} & \multicolumn{1}{c}{\makecell[c]{Cohen's \\ \em{d}}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\makecell[c]{Mean difference\\95\%CI [LL, UL]}} & \multicolumn{1}{c}{\makecell[c]{Cohen's \\ \em{d}}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\makecell[c]{Mean difference\\95\%CI [LL, UL]}} & \multicolumn{1}{c}{\makecell[c]{Cohen's \\ \em{d}}}\\
+\midrule
+\multicolumn{1}{c}{0} & 0.50 & 0.04 & 0.89 & 0.03 & {}[0.38, 0.40] & 10.79 & 11.87 & 0.67 & 6.67 & 0.59 & {}[–5.37, –5.02] & 8.25 & 6.85 & 0.34 & 3.85 & 0.33 & {}[–3.10, –2.91] & 8.98\\
+\multicolumn{1}{c}{2} & 0.47 & 0.04 & 0.75 & 0.04 & {}[0.26, 0.28] & 7.19 & 5.43 & 0.42 & 3.44 & 0.31 & {}[–2.09, –1.89] & 5.42 & 3.48 & 0.22 & 2.21 & 0.16 & {}[–1.33, –1.22] & 6.52\\
+\multicolumn{1}{c}{4} & 0.44 & 0.04 & 0.65 & 0.05 & {}[0.20, 0.23] & 4.53 & 4.50 & 0.51 & 3.01 & 0.32 & {}[–1.61, –1.37] & 3.51 & 2.81 & 0.22 & 1.88 & 0.14 & {}[–0.98, –0.88] & 4.97\\
+\multicolumn{1}{c}{6} & 0.42 & 0.04 & 0.59 & 0.05 & {}[0.16, 0.19] & 3.67 & 3.96 & 0.48 & 2.80 & 0.33 & {}[–1.28, –1.05] & 2.85 & 2.43 & 0.20 & 1.72 & 0.12 & {}[–0.76, –0.67] & 4.26\\
+\multicolumn{1}{c}{8} & 0.40 & 0.04 & 0.54 & 0.05 & {}[0.14, 0.16] & 3.36 & 3.87 & 0.51 & 2.81 & 0.36 & {}[–1.19, –0.94] & 2.43 & 2.24 & 0.19 & 1.62 & 0.12 & {}[–0.66, –0.57] & 3.92\\
+\bottomrule
+\end{tabular}}
+\begin{tablenotes}
+\small
+\item \textit{Note.} \textit{M} = Mean.
+\textit{SD} = Standard deviation.
+CI = Confidence interval.
+LL = Lower limit.
+UL = Upper limit.
+The means were calculated with \\ subsamples of men and women who had ever engaged in short-term mating behaviors.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\endgroup
+
+\elandscape
+
+\newpage
+
+### Sensitivity Analysis on the Comparison Between Heterosexual and Gay Men
+
+\renewcommand{\thefigure}{C3}
+\begin{figure}[h]
+  \centering
+  \includegraphics{figures/sa_fig3_hetero_vs_gay_men.pdf}
+  \caption{\textbf{Short-term mating behaviors of heterosexual men and gay men for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences.} Line plots summarizing the outcome variables.
+Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
+Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar in some sets of parameter setting.
+The means were calculated using the full population of heterosexual men and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
+  \label{fig:hetero_vs_gay}
+\end{figure}
+
+\newpage
+
+\blandscape
+
+```{r table_3, include=FALSE, echo=FALSE}
+sa_results_hg %>%
+  filter(str_detect(ls, pattern = "^1_1")) %>%
+  mutate(
+    exp_all.d = abs(m_exp_all.d),
+    partner_all.d = abs(m_partner_all.d)
+  ) %>%
+  mutate(across(where(is.numeric), inline_hook)) %>%
+  unite(m_exp_all.conf.low, m_exp_all.conf.high, sep = ", ",
+        col = "exp_all.conf") %>% 
+  unite(m_partner_all.conf.low, m_partner_all.conf.high, sep = ", ",
+        col = "partner_all.conf") %>% 
+  mutate(
+    condition = seq(0, 8, by = 2),
+    exp_all.conf = paste0("[", exp_all.conf, "]"),
+    partner_all.conf = paste0("[", partner_all.conf, "]")
+    ) %>%
+  select(condition, 
+         m_exp_all.mean_0, m_exp_all.sd_0,
+         m_exp_all.mean_1, m_exp_all.sd_1, 
+         exp_all.conf, exp_all.d,
+         m_partner_all.mean_0, m_partner_all.sd_0,
+         m_partner_all.mean_1, m_partner_all.sd_1, 
+         partner_all.conf, partner_all.d) %>%
+  column_to_rownames("condition") %>%
+  kable(
+    digits = 2, format = "latex", booktabs = TRUE,
+    caption = "\\textbf{Short-term mating behaviors of heterosexual men and gay men for 0-8 long-term relationship likelihood when gender differences existed in mating preferences}",
+    row.names = TRUE, 
+    col.names = c(rep(c(rep(c("M", "SD"), 2), "Mean difference 95 CI [LL, UL]","d"), 2))
+    ) %>%
+  row_spec(0, italic = TRUE, align = "c") %>%
+  add_header_above(
+    c(" " = 1,
+      "Heterosexual men" = 2, "Gay men" = 2, " " = 2,
+      "Heterosexual men" = 2, "Gay men" = 2, " " = 2)
+    ) %>%
+  add_header_above(
+    c(" " = 1,
+      "Average short-term mating experiences" = 6,
+      "Average short-term mates" = 6)
+    ) %>%
+  column_spec(1, width = "0.5in") %>%
+  footnote(
+    general = "\\\\textit{Note.} \\\\textit{M} = Mean.
+\\\\textit{SD} = Standard deviation.
+CI = Confidence interval.
+LL = Lower limit.
+UL = Upper limit.
+The means were calculated using the full population of heterosexual men and gay men in the model.",
+    general_title = "", escape = FALSE,
+    threeparttable = TRUE, fixed_small_size = TRUE) %>% 
+  kable_styling(latex_options = "scale_down")
+```
+
+\begingroup
+\renewcommand{\arraystretch}{1.5}
+
+\renewcommand{\thetable}{C3}
+
+\begin{table}
+
+\caption{\textbf{Short-term mating behaviors of heterosexual men and gay men for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences}}
+\centering
+\begin{threeparttable}
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{0.5in}cccccccccccc}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Average short-term mating experiences} & \multicolumn{6}{c}{Average short-term mates} \\
+\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{\makecell[c]{Heterosexual\\men}} & \multicolumn{2}{c}{Gay men} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{\makecell[c]{Heterosexual\\men}} & \multicolumn{2}{c}{Gay men} & \multicolumn{2}{c}{ } \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11}
+\multicolumn{1}{c}{\makecell[c]{Long-term\\Likelihood\\(\%)}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\makecell[c]{Mean difference\\95\%CI [LL, UL]}} & \multicolumn{1}{c}{\makecell[c]{Cohen's \\ \em{d}}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\em{M}} & \multicolumn{1}{c}{\em{SD}} & \multicolumn{1}{c}{\makecell[c]{Mean difference\\95\%CI [LL, UL]}} & \multicolumn{1}{c}{\makecell[c]{Cohen's \\ \em{d}}}\\
+\midrule
+\multicolumn{1}{c}{0} & 5.94 & 0.61 & 8.75 & 0.76 & {}[–3.00, –2.62] & 4.06 & 3.43 & 0.34 & 5.42 & 0.43 & {}[–2.10, –1.89] & 5.15\\
+\multicolumn{1}{c}{2} & 2.57 & 0.30 & 5.02 & 0.48 & {}[–2.57, –2.34] & 6.17 & 1.65 & 0.17 & 3.38 & 0.30 & {}[–1.80, –1.66] & 6.99\\
+\multicolumn{1}{c}{4} & 1.97 & 0.29 & 3.92 & 0.47 & {}[–2.06, –1.84] & 4.94 & 1.23 & 0.15 & 2.67 & 0.28 & {}[–1.50, –1.38] & 6.35\\
+\multicolumn{1}{c}{6} & 1.66 & 0.27 & 3.22 & 0.43 & {}[–1.67, –1.46] & 4.34 & 1.02 & 0.13 & 2.21 & 0.26 & {}[–1.25, –1.14] & 5.85\\
+\multicolumn{1}{c}{8} & 1.53 & 0.26 & 2.88 & 0.39 & {}[–1.44, –1.25] & 4.01 & 0.88 & 0.12 & 1.92 & 0.22 & {}[–1.08, –0.99] & 5.93\\
+\bottomrule
+\end{tabular}}
+\begin{tablenotes}
+\small
+\item \textit{Note.} \textit{M} = Mean.
+\textit{SD} = Standard deviation.
+CI = Confidence interval.
+LL = Lower limit.
+UL = Upper limit.
+The means were calculated using the full population of heterosexual men and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\endgroup
+
+\elandscape
+
 ## References

### 2022-11-17 code/sa_plot_hetero_vs_gay_men.R

@@ -44,19 +44,19 @@ casual_tib %>%
   pivot_longer(c(m_exp_all, m_partner_all), values_to = "value",
                names_to = "variable", names_pattern = "m_(.*)") %>% 
   ggplot(aes(x = lt_likelihood, y = value, color = homosexual)) +
-  stat_summary(fun = "mean", geom = "point",
-               position = position_dodge(width = 0.7)) +
+  stat_summary(fun = "mean", geom = "point", size = 2.5,
+               position = position_dodge(width = 0.9)) +
   stat_summary(fun.data = mean_cl_normal, geom = "errorbar", 
-               width = 0.4, size = 0.5, 
-               position = position_dodge(width = 0.7)) +
-  stat_summary(fun = "mean", geom = "line", 
-               position = position_dodge(width = 0.7)) +
+               width = 0.8, size = 0.7, 
+               position = position_dodge(width = 0.9)) +
+  stat_summary(fun = "mean", geom = "line", size = 0.1,
+               position = position_dodge(width = 0.9)) +
   geom_text(
     data = facet_label, aes(label = label, x = x, y = y), 
     hjust = 1, fontface = 2, inherit.aes = FALSE
   ) +
   scale_color_discrete(
-    type = wes_palette("Darjeeling2", 2, type = "discrete"),
+    type = wes_palette("Royal1", 2, type = "discrete"),
     name = "", labels = c("Heterosexual men", "Gay men")
   ) +
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 8, by = 1)) +

### 2022-11-17 code/sa_plot_men_vs_women.R

@@ -51,17 +51,17 @@ casual_tib %>%
                values_to = "value", names_to = c("gender", "variable"),
                names_pattern = "(.)_(.*)") %>% 
   ggplot(aes(x = lt_likelihood, y = value, color = gender)) +
-  stat_summary(fun = "mean", geom = "point",
-               position = position_dodge(width = 0.7)) +
+  stat_summary(fun = "mean", geom = "point", size = 2.5,
+               position = position_dodge(width = 0.9)) +
   stat_summary(fun.data = mean_cl_normal, geom = "errorbar", 
-               width = 0.4, size = 0.5, 
-               position = position_dodge(width = 0.7)) +
-  stat_summary(fun = "mean", geom = "line", 
-               position = position_dodge(width = 0.7)) +
+               width = 1, size = 0.7, 
+               position = position_dodge(width = 0.9)) +
+  stat_summary(fun = "mean", geom = "line", size = 0.1,
+               position = position_dodge(width = 0.9)) +
   geom_text(data = facet_label, aes(label = label, x = x, y = y), 
             hjust = 0, fontface = 2, inherit.aes = FALSE) +
   scale_color_discrete(
-    type = wes_palette("Darjeeling2", 2, type = "discrete"),
+    type = wes_palette("Royal1", 2, type = "discrete"),
     name = "", labels = c("Women", "Men")
   ) +
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 8, by = 1)) +

### 2022-11-17 code/sa_plot_men_vs_women_inpool.R

@@ -46,19 +46,19 @@ casual_tib %>%
                values_to = "value", names_to = c("gender", "variable"),
                names_pattern = "(.)_(.*)") %>% 
   ggplot(aes(x = lt_likelihood, y = value, color = gender)) +
-  stat_summary(fun = "mean", geom = "point",
-               position = position_dodge(width = 0.7)) +
+  stat_summary(fun = "mean", geom = "point", size = 2.5,
+               position = position_dodge(width = 0.9)) +
   stat_summary(fun.data = mean_cl_normal, geom = "errorbar", 
-               width = 0.4, size = 0.5, 
-               position = position_dodge(width = 0.7)) +
-  stat_summary(fun = "mean", geom = "line", 
-               position = position_dodge(width = 0.7)) +
+               width = 0.8, size = 0.7, 
+               position = position_dodge(width = 0.9)) +
+  stat_summary(fun = "mean", geom = "line", size = 0.1,
+               position = position_dodge(width = 0.9)) +
   geom_text(
     data = facet_label, aes(label = label, x = x, y = y), 
     hjust = 1, fontface = 2, inherit.aes = FALSE
   ) +
   scale_color_discrete(
-    type = wes_palette("Darjeeling2", 2, type = "discrete"),
+    type = wes_palette("Royal1", 2, type = "discrete"),
     name = "", labels = c("Women", "Men")
   ) +
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 12, by = 2)) +

### 2022-11-23 submission/supplemental_materials.Rmd
changed the gender terms to sex terms and finished response, close #29

@@
 
-# Supplemental Materials to "An Agent-Based Model of Gender and Sexual Orientation Differences in Short-Term Mating Behaviors as a Result of Mating Preferences"
+# Supplemental Materials to "An Agent-Based Model of Sex and Sexual Orientation Differences in Short-Term Mating Behaviors as a Result of Mating Preferences"
 
@@
 The model simulated sex differences in short-term mating behavior.
-Findings in evolutionary psychology suggest that men have a stronger desire for short-term mating than women [@regan_minimum_1998].
+Findings in evolutionary psychology suggest that males have a stronger desire for short-term mating than females [@regan_minimum_1998].
 They are also less choosy regarding short-term mating partners [@buss2019mate; @buss_sexual_1993].
-This model explores both heterosexual and gay men’s as well as heterosexual and lesbian women’s behavioral outcomes under these assumptions.
+This model explores both heterosexual and gay males’ as well as heterosexual and lesbian females' behavioral outcomes under these assumptions.
 
 The first version of the model simulated short-term mating behaviors among heterosexual individuals, short-term mating and/or long-term relationships were formed only between individuals of the opposite sex.
-The second version of the model simulated the behaviors among gay men and lesbian women, where individuals only had short-term matings and/or formed long-term relationships with those of the same sex.
+The second version of the model simulated the behaviors among gay males and lesbian females, where individuals only had short-term matings and/or formed long-term relationships with those of the same sex.
 The key parameters were individuals’ likelihood of engaging in short-term mating and their standards for a short-term partner.
@@
     \item 300 agents were created with all state variables set to the default
-    \item A number of agents were set to either men (number-of-male) or women (300 – number-of-men) with their respective short-term mating likelihood (short-term-likelihood), and standard for a short-term mate (mating-standard)
+    \item A number of agents were set to either males (number-of-male) or females (300 – number-of-men) with their respective short-term mating likelihood (short-term-likelihood), and standard for a short-term mate (mating-standard)
   \end{enumerate}
@@
 
-  \item Short-term and long-term mating (To avoid double count, only women execute this chunk. This does not affect the model outcomes.)
+  \item Short-term and long-term mating (To avoid double count, only females execute this chunk. This does not affect the model outcomes.)
   \begin{enumerate}
-    \item If any men here, women randomly select one as the target for short-term mating
+    \item If any males here, females randomly select one as the target for short-term mating
     \begin{enumerate}
@@
     \end{enumerate}
-    \item If any men here and women are not coupled, women randomly select one as the potential partner for long-term mating
+    \item If any males here and females are not coupled, females randomly select one as the potential partner for long-term mating
     \begin{enumerate}
@@
 
-*Interaction.* Women and men interacted to have short-term mating behaviors or form long-term relationships.
+*Interaction.* Females and males interacted to have short-term mating behaviors or form long-term relationships.
 
@@
 
-\textbf{Supplemental Table B1: Mean proportion of heterosexual men and women in the mating pool and its standard deviation after 1,000 time steps in the model.}
+\textbf{Supplemental Table B1: Mean proportion of heterosexual males and females in the mating pool and its standard deviation after 1,000 time steps in the model.}
 
@@
     c(" " = 1,
-      "Men" = 2, "Women" = 2)
+      "Males" = 2, "Females" = 2)
     ) %>%
@@
 
-### Sensitivity Analysis on Gender Differences in Short-term Mating Behaviors in the Full Population
+### Sensitivity Analysis on Sex Differences in Short-term Mating Behaviors in the Full Population
 
@@
   \includegraphics{figures/sa_fig1_men_vs_women.pdf}
-  \caption{\textbf{Short-term mating behaviors of men and women for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences.} Line plots summarizing the outcome variables separately for heterosexual individuals and gay men and lesbian women.
+  \caption{\textbf{Short-term mating behaviors of males and females for 0-8\% long-term relationship likelihood when sex differences existed in mating preferences.} Line plots summarizing the outcome variables separately for heterosexual individuals and gay males and lesbian females.
 Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
 The points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar in some sets of parameter setting.
-The means were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).}
+The means were calculated using the full population of males and females in the model (\textit{N\textsubscript{male}} = \textit{N\textsubscript{female}} = 150).}
   \label{fig:men_vs_women}
@@
 
-\caption{\textbf{Short-term mating behaviors of men and women for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences}}
+\caption{\textbf{Short-term mating behaviors of males and females for 0-8\% long-term relationship likelihood when sex differences existed in mating preferences}}
 \centering
@@
 \cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{2}{c}{ } \\
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Males} & \multicolumn{2}{c}{Females} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{Males} & \multicolumn{2}{c}{Females} & \multicolumn{2}{c}{ } \\
 \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11}
@@
 \addlinespace
-\multicolumn{13}{l}{\textit{Experiment 2: Gay men and lesbian women}} \\
+\multicolumn{13}{l}{\textit{Experiment 2: Gay males and lesbian females}} \\
 \multicolumn{1}{c}{0} & 8.75 & 0.76 & 1.09 & 0.21 & {}[–7.81, –7.50] & 13.71 & 5.42 & 0.43 & 0.88 & 0.16 & {}[–4.64, –4.46] & 14.04\\
@@
 UL = Upper limit.
-The means were calculated using the full population of men and women in the model (\textit{N\textsubscript{men}} = \textit{N\textsubscript{women}} = 150).
+The means were calculated using the full population of males and females in the model (\textit{N\textsubscript{male}} = \textit{N\textsubscript{female}} = 150).
 \end{tablenotes}
@@
   \includegraphics{figures/sa_fig2_men_vs_women_inpool.pdf}
-  \caption{\textbf{Short-term mating behaviors of heterosexual men and women in the mating pool for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences.} Line plots summarizing the outcome variables.
+  \caption{\textbf{Short-term mating behaviors of heterosexual males and females in the mating pool for 0-8\% long-term relationship likelihood when sex differences existed in mating preferences.} Line plots summarizing the outcome variables.
 Plot (A) shows the average number of short-term mating experiences in the mating pool, and plot (B) shows the average number of short-term mates in the mating pool.
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar in some sets of parameter setting.
-The means were calculated using the population of heterosexual men and women who successfully participated in the mating pool (See Table C2 for the mean and standard deviation of the proportion of individuals in the mating pool).}
+The means were calculated using the population of heterosexual males and females who successfully participated in the mating pool (See Table C2 for the mean and standard deviation of the proportion of individuals in the mating pool).}
   \label{fig:men_vs_women_inpool}
@@
 
-\caption{\textbf{Proportion and short-term mating behaviors of heterosexual men and women in the mating pool for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences}}
+\caption{\textbf{Proportion and short-term mating behaviors of heterosexual males and females in the mating pool for 0-8\% long-term relationship likelihood when sex differences existed in mating preferences}}
 \centering
@@
 \cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13} \cmidrule(l{3pt}r{3pt}){14-19}
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{Men} & \multicolumn{2}{c}{Women} & \multicolumn{2}{c}{ } \\
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Males} & \multicolumn{2}{c}{Females} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{Males} & \multicolumn{2}{c}{Females} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{Males} & \multicolumn{2}{c}{Females} & \multicolumn{2}{c}{ } \\
 \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){14-15} \cmidrule(l{3pt}r{3pt}){16-17}
@@
 UL = Upper limit.
-The means were calculated with \\ subsamples of men and women who had ever engaged in short-term mating behaviors.
+The means were calculated with \\ subsamples of males and females who had ever engaged in short-term mating behaviors.
 \end{tablenotes}
@@
 
-### Sensitivity Analysis on the Comparison Between Heterosexual and Gay Men
+### Sensitivity Analysis on the Comparison Between Heterosexual and Gay Males
 
@@
   \includegraphics{figures/sa_fig3_hetero_vs_gay_men.pdf}
-  \caption{\textbf{Short-term mating behaviors of heterosexual men and gay men for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences.} Line plots summarizing the outcome variables.
+  \caption{\textbf{Short-term mating behaviors of heterosexual males and gay males for 0-8\% long-term relationship likelihood when sex differences existed in mating preferences.} Line plots summarizing the outcome variables.
 Plot (A) shows the average number of short-term mating experiences, and plot (B) shows the average number of short-term mates.
 Central points show mean values and whiskers represent standard errors, but the standard errors are small and overlap to form a single bar in some sets of parameter setting.
-The means were calculated using the full population of heterosexual men and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
+The means were calculated using the full population of heterosexual males and gay mlaes in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).}
   \label{fig:hetero_vs_gay}
@@
 
-\caption{\textbf{Short-term mating behaviors of heterosexual men and gay men for 0-8\% long-term relationship likelihood when gender differences existed in mating preferences}}
+\caption{\textbf{Short-term mating behaviors of heterosexual males and gay males for 0-8\% long-term relationship likelihood when sex differences existed in mating preferences}}
 \centering
@@
 \cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{\makecell[c]{Heterosexual\\men}} & \multicolumn{2}{c}{Gay men} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{\makecell[c]{Heterosexual\\men}} & \multicolumn{2}{c}{Gay men} & \multicolumn{2}{c}{ } \\
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{\makecell[c]{Heterosexual\\males}} & \multicolumn{2}{c}{Gay males} & \multicolumn{2}{c}{ } & \multicolumn{2}{c}{\makecell[c]{Heterosexual\\males}} & \multicolumn{2}{c}{Gay males} & \multicolumn{2}{c}{ } \\
 \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11}
@@
 UL = Upper limit.
-The means were calculated using the full population of heterosexual men and gay men in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).
+The means were calculated using the full population of heterosexual males and gay males in the model (\textit{N\textsubscript{hetero}} = \textit{N\textsubscript{gay}} = 150).
 \end{tablenotes}

### 2022-11-23 code/plot_hetero_vs_gay_men.R

@@ -52,7 +52,7 @@ casual_tib %>%
     ) +
   scale_fill_discrete(
     type = wes_palette("Darjeeling2", 2, type = "discrete"),
-    name = "", labels = c("Heterosexual men", "Gay men")
+    name = "", labels = c("Heterosexual male", "Gay male")
   ) +
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 4, by = 1)) +
   labs(x = "", y = NULL) +

### 2022-11-23 code/plot_men_vs_women.R

@@ -37,7 +37,7 @@ facet_label <-
 y_lab <- labeller(
   homosexual = c(
     `0` = "Experiment 1\nHeterosexual individuals",
-    `1` = "Experiment 2\nGay men and lesbian women"),
+    `1` = "Experiment 2\nGay males and lesbian females"),
   variable = c(
     `exp_all` = "Average number of\nshort-term mating experiences",
     `partner_all` = "Average number of\nshort-term mates")
@@ -58,7 +58,7 @@ casual_tib %>%
   ) +
   scale_fill_discrete(
     type = wes_palette("Darjeeling2", 2, type = "discrete"),
-    name = "", labels = c("Women", "Men")
+    name = "", labels = c("Female", "Male")
   ) +
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 4, by = 1)) +
   labs(x = "", y = NULL) +

### 2022-11-23 code/plot_men_vs_women_inpool.R

@@ -54,7 +54,7 @@ casual_tib %>%
   ) +
   scale_fill_discrete(
     type = wes_palette("Darjeeling2", 2, type = "discrete"),
-    name = "", labels = c("Women", "Men")
+    name = "", labels = c("Female", "Male")
   ) +
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 6, by = 1)) +
   labs(x = "", y = NULL) +

### 2022-11-23 code/sa_plot_hetero_vs_gay_men.R

@@ -57,7 +57,7 @@ casual_tib %>%
   ) +
   scale_color_discrete(
     type = wes_palette("Royal1", 2, type = "discrete"),
-    name = "", labels = c("Heterosexual men", "Gay men")
+    name = "", labels = c("Heterosexual male", "Gay male")
   ) +
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 8, by = 1)) +
   labs(x = "Long-term Likelihood (%)", y = NULL) +

### 2022-11-23 code/sa_plot_men_vs_women.R

@@ -37,7 +37,7 @@ facet_label <-
 y_lab <- labeller(
   homosexual = c(
     `0` = "Experiment 1\nHeterosexual individuals",
-    `1` = "Experiment 2\nGay men and lesbian women"),
+    `1` = "Experiment 2\nGay males and lesbian females"),
   variable = c(
     `exp_all` = "Average number of\nshort-term mating experiences",
     `partner_all` = "Average number of\nshort-term mates")
@@ -62,7 +62,7 @@ casual_tib %>%
             hjust = 0, fontface = 2, inherit.aes = FALSE) +
   scale_color_discrete(
     type = wes_palette("Royal1", 2, type = "discrete"),
-    name = "", labels = c("Women", "Men")
+    name = "", labels = c("Female", "Male")
   ) +
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 8, by = 1)) +
   labs(x = "Long-term Likelihood (%)", y = NULL) +

### 2022-11-23 code/sa_plot_men_vs_women_inpool.R

@@ -59,7 +59,7 @@ casual_tib %>%
   ) +
   scale_color_discrete(
     type = wes_palette("Royal1", 2, type = "discrete"),
-    name = "", labels = c("Women", "Men")
+    name = "", labels = c("Female", "Male")
   ) +
   scale_y_continuous(limits = c(0, NA), breaks = seq(0, 12, by = 2)) +
   labs(x = "Long-term Likelihood (%)", y = NULL) +
